### 2013-09-24 tex/sigproc-sp.tex
Add the ACM latex template and page with redaction guidlines.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}
\usepackage{epsfig}

\begin{document}

\title{B Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\epsfig{file=fly.eps}
\caption{A sample black and white graphic (.eps format).}
\end{figure}

\begin{figure}
\centering
\epsfig{file=fly.eps, height=1in, width=1in}
\caption{A sample black and white graphic (.eps format)
that has been resized with the \texttt{epsfig} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

\begin{figure}
\centering
% \psfig{file=rosette.ps, height=1in, width=1in,}
\caption{A sample black and white graphic (.ps format) that has
been resized with the \texttt{psfig} command.}
\end{figure}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

\begin{figure*}
\centering
\epsfig{file=flies.eps}
\caption{A sample black and white graphic (.eps format)
that needs to span two columns of text.}
\end{figure*}
and don't forget to end the environment with
{figure*}, not {figure}!

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The acm\_proc\_article-sp document class file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}

### 2013-10-28 tex/0-abstract.tex
Create paper stucture.

--- 2013-09-24 tex/sigproc-sp.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-\usepackage{epsfig}
-
-\begin{document}
-
-\title{B Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
-Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
-% 2nd. author
-\alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
-}
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
-
-\maketitle
-\begin{abstract}
 This paper provides a sample of a \LaTeX\ document which conforms to
@@
 output produced by the dvi file.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-\terms{Theory}
-
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
-
-\section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
-
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
-
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
-
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
-
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
-
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
-
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
-
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-conference
-proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps}
-\caption{A sample black and white graphic (.eps format).}
-\end{figure}
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps, height=1in, width=1in}
-\caption{A sample black and white graphic (.eps format)
-that has been resized with the \texttt{epsfig} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-\begin{figure}
-\centering
-% \psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.}
-\end{figure}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-\begin{figure*}
-\centering
-\epsfig{file=flies.eps}
-\caption{A sample black and white graphic (.eps format)
-that needs to span two columns of text.}
-\end{figure*}
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The acm\_proc\_article-sp document class file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-\balancecolumns
-% That's all folks!
-\end{document}

### 2013-10-28 tex/6-conclusion-and-future-work.tex
Create paper stucture.

--- 2013-09-24 tex/sigproc-sp.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-\usepackage{epsfig}
-
-\begin{document}
-
-\title{B Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
-Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
-% 2nd. author
-\alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
-}
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
-
-\maketitle
-\begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms to
-the formatting guidelines for ACM SIG Proceedings.
-It complements the document \textit{Author's Guide to Preparing
-ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-\terms{Theory}
-
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
-
-\section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
-
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
-
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
-
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
-
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
-
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
-
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
-
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-conference
-proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps}
-\caption{A sample black and white graphic (.eps format).}
-\end{figure}
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps, height=1in, width=1in}
-\caption{A sample black and white graphic (.eps format)
-that has been resized with the \texttt{epsfig} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-\begin{figure}
-\centering
-% \psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.}
-\end{figure}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-\begin{figure*}
-\centering
-\epsfig{file=flies.eps}
-\caption{A sample black and white graphic (.eps format)
-that needs to span two columns of text.}
-\end{figure*}
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
+\section{Conclusion and Future Work}
 This paragraph will end the body of this sample document.
@@
 examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The acm\_proc\_article-sp document class file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-\balancecolumns
-% That's all folks!
-\end{document}

### 2013-10-28 tex/main.tex
Create paper stucture.

--- 2013-09-24 tex/sigproc-sp.tex
@@
 \usepackage{epsfig}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{url}
+\usepackage{hyperref}
+\newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
+\newcommand{\surl}[1]{\urlstyle{ff}\url{#1}}
 
@@
 
-\title{B Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
-Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
+\title{Web feed based content extraction with JavaScript rendering for the Invenio crawler}
 
-\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
+\numberofauthors{3}
+
 \author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
 % 1st. author
 \alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
+Blanvillain Olivier\\
+       \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
+       \affaddr{1014 Lausanne, Switzerland}\\
+       \email{olivier.blanvillain@epfl.ch}
 % 2nd. author
@@
        \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
 }
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
 
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms to
-the formatting guidelines for ACM SIG Proceedings.
-It complements the document \textit{Author's Guide to Preparing
-ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file.
+\input{0-abstract.tex}
 \end{abstract}
@@
 
-\section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
+\input{1-intro.tex}
+\input{2-related-work.tex}
+\input{3-architecture.tex}
+\input{4-algorithms.tex}
+\input{5-evaluation.tex}
+\input{6-conclusion-and-future-work.tex}
 
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
-
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
-
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
-
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
-
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
-
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
-
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-conference
-proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps}
-\caption{A sample black and white graphic (.eps format).}
-\end{figure}
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps, height=1in, width=1in}
-\caption{A sample black and white graphic (.eps format)
-that has been resized with the \texttt{epsfig} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-\begin{figure}
-\centering
-% \psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.}
-\end{figure}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-\begin{figure*}
-\centering
-\epsfig{file=flies.eps}
-\caption{A sample black and white graphic (.eps format)
-that needs to span two columns of text.}
-\end{figure*}
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
 \bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The acm\_proc\_article-sp document class file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-\balancecolumns
-% That's all folks!
+\bibliography{sigproc}
 \end{document}

### 2013-10-29 tex/2-related-work.tex
Snapshot of the project as sent in the first email.

\section{Related work}
2-related-work.tex

Web Object Identification for Web Automation and Meta-Search,
\surl{http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf}

Self-supervised Automated Wrapper Generation for Weblog Data Extraction,
\surl{https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod_published.pdf}

Web Data Extraction, Applications and Techniques: A Survey,
\surl{http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf}

Archiving Data Objects using Web Feeds,
\surl{http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf}

Intelligent and Adaptive Crawling of Web Applications for Web Archiving,
\surl{http://pierre.senellart.com/publications/faheem2013intelligent.pdf}

Zero-cost Labelling with Web Feeds for Weblog Data Extraction,
\surl{http://www2013.org/companion/p73.pdf}

OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications,
\surl{http://www.vldb.org/pvldb/vol4/p1016-furche.pdf}

### 2013-10-29 tex/3-architecture.tex
Snapshot of the project as sent in the first email.

\section{Architecture}

\subsection{Scrapy and Invenio}
Introduce both projects with their respective strengths, tool/technology justification.

\subsection{JavaScript Rendering}
\begin{enumerate}
  \item PhantomJS
  \item "Show more comments" click
  \item Done upfront, every thing else is independent
\end{enumerate}

\subsection{Extraction Process}
High level overview: XPath build from RSS feeds

### 2013-10-29 tex/4-algorithms.tex
Snapshot of the project as sent in the first email.

\section{Algorithms}

\subsection{Content extraction}
\begin{enumerate}
  \item The algorithm
  \item Choice of selectors (id, else class)
  \item Choice of string similarity
\end{enumerate}

\subsection{Variations for comments and date}
All the details about how to use the same algorithm to extract comments and dates.

### 2013-10-29 tex/5-evaluation.tex
Snapshot of the project as sent in the first email.

\section{Evaluation}

\subsection{Introcution}
What is evaluated (not comments, iframes, authors, dates...)

\subsection{Content extraction}
\begin{enumerate}
  \item running time
  \item quality of output compared
\end{enumerate}

\subsection{JavaScript rendering}
\begin{enumerate}
  \item running time
\end{enumerate}

### 2013-10-29 tex/1-intro.tex
Update with graphic descriptions and compared project links.

\section{Intro}
1-intro.tex
\begin{enumerate}
  \item Introduce the importance for blog preservation
  \item Explain the difficulties in harvesting blogs
  \item Explain why open source and Invenio
  \item Introduce the blog crawler
\end{enumerate}

### 2013-10-29 tex/5-evaluation.tex
Update with graphic descriptions and compared project links.

@@
 \subsection{Content extraction}
+Compare:
+\begin{itemize}
+  \item Our solution
+  \item Boilerpipe \surl{https://github.com/misja/python-boilerpipe}
+  \item Goose \surl{https://github.com/grangier/python-goose}
+  \item Readability \surl{https://github.com/buriy/python-readability}
+\end{itemize}
+On:
 \begin{enumerate}
-  \item running time
-  \item quality of output compared
+  \item Running time
+  \begin{itemize}
+    \item Plot duration as a function of the page length
+    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
+  \end{itemize}
+  \item Quality of output compared:
+  \begin{itemize}
+    \item Chart of success pourcentages
+  \end{itemize}
 \end{enumerate}
@@
 \subsection{JavaScript rendering}
-\begin{enumerate}
-  \item running time
-\end{enumerate}
+Compare:
+\begin{itemize}
+  \item "Wget crawl" \surl{http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/}
+  \item wkhtmltopdf \surl{http://code.google.com/p/wkhtmltopdf/}
+  \item Selenium + full browser
+  \item probably others
+\end{itemize}
+On:
+\begin{itemize}
+  \item Table comparing functionalities of each solution
+  \item Histogram of redering time per browser (phantomjs/chrome/firefox)
+\end{itemize}

### 2013-10-29 tex/6-conclusion-and-future-work.tex
Update with graphic descriptions and compared project links.

@@
 \section{Conclusion and Future Work}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
+\begin{itemize}
+  \item Recap the problem and the objective
+  \item Summarize how've solved it
+  \item Mention challenges and problems
+  \item Hint for future work
+\end{itemize}

### 2013-10-29 tex/5-evaluation.tex
Extract the dataset blog contents and urls, included last suggestion from vangelis.
Move dataset to /dataset.

@@
 What is evaluated (not comments, iframes, authors, dates...)
+\\ define the dataset and your competing algorithms the best way possible.
+
+The dataset is a small sample coming from the Spinn3r dataset. The Spinn3r dataset was released for ICWSM 2011 conference.
 
@@
   \item Our solution
-  \item Boilerpipe \surl{https://github.com/misja/python-boilerpipe}
+  \item Boilerpipe q\surl{https://github.com/misja/python-boilerpipe}
   \item Goose \surl{https://github.com/grangier/python-goose}

### 2013-11-01 tex/main.tex
Snapshot of the project as sent in the first email.
Add a few ideas from reading the WebDataExtraction,ApplicationsAndTechniques survey, add sripts to run and score theextraction methods.
New title idea.

@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
+\documentclass{acm_proc_article-sp}
 
-\documentclass{acm_proc_article-sp}
 \usepackage{epsfig}
@@
 \usepackage{hyperref}
+
 \newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
@@
 
-\title{Web feed based content extraction with JavaScript rendering for the Invenio crawler}
+% \title{Web feed based content extraction with JavaScript rendering for the Invenio crawler}
+\title{BlogForever Crawler: Techniques and Algorithms to Harvest the Modern Web}
+% to Extract Data From the Modern Web}
+% Modern Web Pages}
 
@@
 \alignauthor
-Blanvillain Olivier\\
+Olivier Blanvillain\\
        \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
@@
 \alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
+Nikos Kasioumis\\
+       \affaddr{European Organization for Nuclear Research (CERN)}\\
+       \affaddr{1211 Geneva 23, Switzerland}\\
+       \email{nikos.kasioumis@cern.ch}
 % 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
+\alignauthor
+Vangelis Banos\\
+       \affaddr{Department of Informatics}\\
+       \affaddr{Aristotle University of Thessaloniki, Greece}\\
+       \email{vbanos@gmail.com}
 }

### 2013-11-01 tex/3-architecture.tex
Add a few ideas from reading the WebDataExtraction,ApplicationsAndTechniques survey, add sripts to run and score theextraction methods.
Improve score from 68.2% to 73.7% by taking top queries for all pages for the feed and not only the first one.

@@
 Introduce both projects with their respective strengths, tool/technology justification.
+
+\begin{enumerate}
+  \item Stateless
+  \item Trade of efficiency for addaptability
+  \item Stuctural maintenence is given because by recompute them each time
+\end{enumerate}
 
@@
 
+While some (Archiving Data Objects using Web Feeds -> Perenniality of Web archives.) take the
+
+Google Blogspot Dynamic Views: \surl{http://buzz.blogger.com/2012/02/dynamic-views-update-3-gadgets.html}, \surl{https://support.google.com/blogger/answer/1229061?hl=en}
+
 \subsection{Extraction Process}

### 2013-11-01 tex/0-abstract.tex
First abstract draft.

@@
-This paper provides a sample of a \LaTeX\ document which conforms to
-the formatting guidelines for ACM SIG Proceedings.
-It complements the document \textit{Author's Guide to Preparing
-ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
+Blogs are by nature a very dynamic and volatile communication medium.
+The BlogForever project aims to provide a generic platform for blog preservation.
+This paper presents a key component of this archiving system: the Web Crawler.
+More precisely, our discussion will concentrate on techniques to automaticaly extract content, authors, date and comments of blog posts.
 
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
+Web technologies are evolving very rapidly.
+The recent trend toward using JavaScript to dynamically generate pages on the client side represent a new challenge for the web crawler.
+We will show how we integrated the headless web browser into the our spider to overcome these obstacles.
 
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file.
+We present a simple and robust algorithm based on string similarity to build wrappers from web feeds. Being applicable to all posts of a blog, the resulting extraction procedure scale for large blogs.

### 2013-11-01 tex/0-abstract.tex
Wrapped.
Update 0-abstract.tex

@@
-Blogs are by nature a very dynamic and volatile communication medium.
-The BlogForever project aims to provide a generic platform for blog preservation.
-This paper presents a key component of this archiving system: the Web Crawler.
-More precisely, our discussion will concentrate on techniques to automaticaly extract content, authors, date and comments of blog posts.
-
-Web technologies are evolving very rapidly.
-The recent trend toward using JavaScript to dynamically generate pages on the client side represent a new challenge for the web crawler.
-We will show how we integrated the headless web browser into the our spider to overcome these obstacles.
-
-We present a simple and robust algorithm based on string similarity to build wrappers from web feeds. Being applicable to all posts of a blog, the resulting extraction procedure scale for large blogs.
+Blogs are by nature a very dynamic and volatile communication medium. The
+BlogForever project aims to provide a generic platform for blog preservation,
+thus ensuring access to this information to future generations. This paper
+presents a key component of this archiving system: the web crawler. More
+precisely, our discussion will concentrate on techniques to automatically
+extract content, authors, date and comments of blog posts. One of the main
+challenges in the preservation of web objects is the rapid evolution of
+technologies. For instance, the recent trend towards using JavaScript to
+dynamically generate pages on the client side constitute a new obstacle for
+today's crawlers. We will show how we integrated a headless web browser into the
+harvesting process in order to address these matters. Furthermore, we present a
+simple and robust algorithm based on string matching between web feeds and page
+content to generate wrappers. Being applicable to all posts of a blog, the
+resulting extraction procedure scales for large blogs.

### 2013-11-02 tex/3-techniques.tex
Update and rename 3-architecture.tex to 3-techniques.tex

\section{Techniques}

This section gives a high level overview of the techniques used in our crawler. We will first give an overview of the overall software architecture, precisely locating the different modules that are addressed in this paper. Secondly the JavaScript rendering process will be

# Architecture
- top down
- stateless, global scalability
- scrapy, dl policies and post identification
- item pipeline, modularity
- js rendering done upfront, everything else general

# JavaScript rendering
- challenges
Ajax
Google Blogspot Dynamic Views: \surl{http://buzz.blogger.com/2012/02/dynamic-views-update-3-gadgets.html}, \surl{https://support.google.com/blogger/answer/1229061?hl=en}
- present phjs, also here screenshot
- ez of use vs power
- our click show more use case
- parallelization

# Content Extraction
- two phase process:
- wrapper generation, next section
- use per blog
- a word about maintainability, given because by recompute them each tim

### 2013-11-02 tex/0-abstract.tex
typo

@@
 technologies. For instance, the recent trend towards using JavaScript to
-dynamically generate pages on the client side constitute a new obstacle for
+dynamically generate pages on the client side constitutes a new obstacle for
 today's crawlers. We will show how we integrated a headless web browser into the

### 2013-11-04 tex/1-intro.tex
Extract the dataset blog contents and urls, included last suggestion from vangelis.
Move dataset to /dataset.

@@
 \section{Intro}
-1-intro.tex
+
+Aims and contributions of this work. Example from my last paper to see the format:
+\surl{http://purl.pt/24107/1/iPres2013_PDF/CLEAR\%20a\%20credible\%20method\%20to\%20evaluate\%20website\%20archivability.pdf}
+
 \begin{enumerate}
@@
 \end{enumerate}
+
+Challenges consist of:
+\begin{enumerate}
+  \item Providing a high degree of automation
+  \item Dealing with large volumes of data
+\end{enumerate}
+
+Semi-structured nature of Web pages
+
+Labeled ordered rooted trees
+XML Path Language(XPath)

### 2013-11-06 tex/4-architecture.tex
Algorithms assumptions.

\section{Architectute}

This section gives an overview of the overall software architecture of our crawler. After a breif introductions of the tool, we will explain how our approach allow to use the crawler on a large scale distributed architectute. We will then see how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to dynamically generate post content and comments.

\subsection{Architecture}
- scrapy, dl policies and post identification \\
- item pipeline, modularity \\
- js rendering done upfront, everything else general \\

\subsection{Scalability}
- stateless \\
- scrapyd \\

\subsection{JavaScript rendering}
- challenges \\
Ajax
Google Blogspot Dynamic Views: \surl{http://buzz.blogger.com/2012/02/dynamic-views-update-3-gadgets.html}, \surl{https://support.google.com/blogger/answer/1229061?hl=en}
- present phjs, also here screenshot \\
- ez of use vs power \\
- our click show more use case \\
- parallelization \\

### 2013-11-08 tex/4-algorithms.tex

@@
 \section{Algorithms}
+This section explains in details the content wrapper generation algorithm and it's variations for authors, date and comments.
+We will see how our seemingly brute force approach can be tweaked in order to achieve reasonable running times.
+
+\subsection{intro}
+Being a subset of XML, (HTML) (HTML) is often categorized as semi-structured document*. Root labeled ordered tree
+
+"div"
+
+When working with blogs, web feed are saving grace
+
+definitions, args and return value
 
 \subsection{Content extraction}
-\begin{enumerate}
-  \item The algorithm
-  \item Choice of selectors (id, else class)
-  \item Choice of string similarity
-\end{enumerate}
+related algos, generale brute force vue
+
+algorithm
+selectors (id, else class)
+string similarity
 
@@
 All the details about how to use the same algorithm to extract comments and dates.
+
+Concretely, a wrapper is an procedure to extract relevant data from a document. In our case, we aim to build queries in the XML path language (XPath) to extract relevant data from blog posts.
+
+Each time a new crawl is initiated our system builds a set of wrappers that are then used for the entirety of the blog.
+With this wrappers in hands, extraction data from the HTML page of a blog post is nothing more than parsing the HTML page running each XPath query, which can all by done with standard * libraries.

### 2013-11-10 tex/4-techniques.tex
Back to techniques instead of architecture.

\section{Techniques}

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display content. The overall software architecture with then be discussed, introducing the tools that come before and after the content extraction process: Scrapy and In2venio. *

\subsection{JavaScript rendering}
- challenges \\
Ajax
Google Blogspot Dynamic Views: \surl{http://buzz.blogger.com/2012/02/dynamic-views-update-3-gadgets.html}, \surl{https://support.google.com/blogger/answer/1229061?hl=en}
- present phjs, also here screenshot \\
- ez of use vs power \\
- our click show more use case \\
- parallelization \\
- js rendering done upfront, everything else general \\

\subsection{Architecture}
\subsubsection{Item pipeline}
- item pipeline, modularity \\

\subsubsection{Scalability}
- stateless \\
- scrapyd \\

\subsection{Enriching Scrapy}
Our project is build on top of Scrapy\TODO{link}, an open source python framework for web crawling. In addition to the extraction aspects of the project, we also enrich the framework with two components specific to blog post extraction: blog post identification and download policies.

Given an entry to a blog, Scrapy provides the infrastructure to look over all pages on the same domain. In order to identify the subset of pages that are actually blog posts, we build a "blog post identification" function that given an URL, returns whether or not it is a blog post. This function uses a regular expression that is constructed from the web feed entries: the only set of known blog post URLs.

Due to space constraints, more precise description and evaluation of these components where not included in this paper.

### 2013-11-11 tex/4-techniques.tex
Add download priority heuristic

@@
 Our project is build on top of Scrapy\TODO{link}, an open source python framework for web crawling.
-In addition to the extraction aspects of the project, we also enrich the framework with two components specific to blog post extraction: blog post identification and download policies.
+In addition to the extraction aspects of the project, we also enrich the framework with two components specific to blog-post extraction: blog-post identification and download priority heuristic.
 
 Given an entry to a blog, Scrapy provides the infrastructure to look over all pages on the same domain.
-In order to identify the subset of pages that are actually blog posts, we build a "blog post identification" function that given an URL, returns whether or not it is a blog post.
-This function uses a regular expression that is constructed from the web feed entries: the only set of known blog post URLs.
+In order to identify the subset of pages that are actually blog-posts, we build a \emph{blog-post identification} function that given an URL, returns whether or not it is a blog-post.
+This function uses a regular expression that is constructed from the web feed entries: the only set of known blog-post URLs.
 
-Due to space constraints, more precise description and evaluation of these components where not included in this paper.
+In order to efficiently deal with blogs with a large number non-blog-post pages, this mechanism is not sufficient.
+Indeed, after all pages identify as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts.
+To replace the naïve random walks, deaph first search and breath first search web site traversals, we use a priority queue with an heuristic function.
+Our \emph{download priority heuristic}works with a simple machine learning algorithm that given an URL predicts the number of links to blog-post the corresponding page will contain.
+Each time a page is dowloaded the number of blog-post links it contains is computer and given to the machine learning ...
+
+Due to space constraints, more precise description and evaluation of these two components where not included in this paper.

### 2013-11-11 tex/3-algorithms.tex

\section{Algorithms}

This section explains in details the content wrapper generation algorithm and it's variations for authors, date and comments. We will see how our seemingly brute force approach can be tweaked in order to achieve reasonable running times.

\subsection{Assumptions}
Being a subset of XML, (HTML)* (HTML) documents are often categorized as semi-structured*. Some sementic tags were recently introduced in HTML*footnote* language specification, bringing **. If properly used, tags such as `<article>`, `<title>` and `<date>` can greatly simlify the tasks of content identification and extraction. However, the practice shows that these recent convetions are use by very few websites. Most are still using the more traditional aproach where pages are arbitrery hierarchi of `<div>` tags with arbitrery `class` or `id` names.

Working with blogs allows to make assumptions that are central in our extraction procedure:
1. Web feeds provide structured and standardised view of the last posts
2. Posts of a same blog share the same HTMP structure.

In average, web feeds contain around 20 entries \cite{french paper} which is generally lower than the total number of posts in a blog. In order to effectively archive old content from blogs it is necessery to download and process pages beyong the one referenced by the feed. The algorithm we are going to present in this section as for function to build wrappers for the relevent data of blog posts, which are going to be use

Concretely, a wrapper is an procedure to extract relevant data from a document. In our case, we aim to build queries in the XML path language (XPath) to extract relevant data from blog posts.

Each time a new crawl is initiated our system builds a set of wrappers that are then used for the entirety of the blog. With this wrappers in hands, extraction data from the HTML page of a blog post is nothing more than parsing the HTML page running each XPath query, which can all by done with the standard python librarie \footnote{lxml, beautifullsoop}.

- use per blog
- a word about maintainability, given because by recompute them each tim

\subsection{Content extraction}
- definitions, args and return value \\
- related algos, generale brute force vue \\
- algorithm \\
- selectors (id, else class) \\
- string similarity \\

\subsection{Variations for comments and date}
All the details about how to use the same algorithm to extract comments and dates.

### 2013-11-12 tex/4-techniques.tex
Progress...

@@
 This section gives an overview of different techniques used in our crawler.
-We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display content.
-The overall software architecture with then be discussed, introducing the tools that come before and after the content extraction process: Scrapy and In2venio.
-*
+We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
+The overall software architecture with then be discussed, introducing the tools that come before and after the content extraction process: Scrapy and Invenio.
 
 \subsection{JavaScript rendering}
-- challenges \\
-Ajax
-Google Blogspot Dynamic Views: \surl{http://buzz.blogger.com/2012/02/dynamic-views-update-3-gadgets.html}, \surl{https://support.google.com/blogger/answer/1229061?hl=en}
-- present phjs, also here screenshot \\
-- ez of use vs power \\
-- our click show more use case \\
-- parallelization \\
-- js rendering done upfront, everything else general \\
+% Introduction
+JavaScript is a widely used use language for client-side web scripting.
+While some applications simply use it for aesthetics aspects such as menus and animations, an increasing number of websites use JavaScript to download and display content.
+In such circumstances, traditional HTML based crawled would not see the web site as it would be presented to a human visitor and might therefore be obsolete for extracting data from the page.
+
+% Motivation
+In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation.
+The most frequent cases where blogs using the Disqus\TODO{link} and LiveFyre\TODO{link} comment hosting services.
+These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essiential comes down to including a JavaScript snippet in the target web page.
+Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users.
+Less commonly, some blogs are fully rendered using JavaScript.
+Concretely, when loading such website the web browser will not recieve the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content.
+On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \TODO{link to \surl{http://buzz.blogger.com/2011/09/dynamic-views-seven-new-ways-to-share.html}} that use this mechanism.
+
+% The solution
+the solution: phjs \cite{readability}
+js rendering done upfront, everything else general
+screenshot ?
+
+- ez of use vs power, fine because it's automated
 
@@
 \subsubsection{Scalability}
+- http://www.reactivemanifesto.org/
 - stateless \\
@@
 Indeed, after all pages identify as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts.
-To replace the naïve random walks, deaph first search and breath first search web site traversals, we use a priority queue with an heuristic function.
-Our \emph{download priority heuristic}works with a simple machine learning algorithm that given an URL predicts the number of links to blog-post the corresponding page will contain.
-Each time a page is dowloaded the number of blog-post links it contains is computer and given to the machine learning ...
+To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where URL priorities are determined by a simple machine learning system.
+Given an URL, the machine learning system predicts the number of links to blog-post the corresponding page will contain.
+Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and given to the machine learning system that will store this value and take it into account for its future prediction.
+This mechanism has shown to be indispensable for web sites that host on the single domain a blog along with a large number of non-blog web pages, such as a forum or a wiki.
 

### 2013-11-12 tex/4-techniques.tex
Update readme with gen main.bib instructions.

@@
 % The solution
-the solution: phjs \cite{readability}
-js rendering done upfront, everything else general
-screenshot ?
-
+- the solution: phjs
+- js rendering done upfront, everything else general
+- python scripting click click use case
 - ez of use vs power, fine because it's automated

### 2013-11-12 tex/4-techniques.tex
Progress

--- 2013-11-12 tex/4-techniques.tex
@@
 In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation.
-The most frequent cases where blogs using the Disqus\TODO{link} and LiveFyre\TODO{link} comment hosting services.
-These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essiential comes down to including a JavaScript snippet in the target web page.
+The most frequent cases where blogs using the Disqus\cite{disqus2013} and LiveFyre\cite{livefyre2013} comment hosting services.
+These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page.
 Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users.
 Less commonly, some blogs are fully rendered using JavaScript.
-Concretely, when loading such website the web browser will not recieve the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content.
-On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \TODO{link to \surl{http://buzz.blogger.com/2011/09/dynamic-views-seven-new-ways-to-share.html}} that use this mechanism.
+Concretely, when loading such website the web browser will not receive the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content.
+On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \cite{antinharasymiv2011} that use this mechanism.
 
 % The solution
-the solution: phjs \cite{readability}
-js rendering done upfront, everything else general
-screenshot ?
+To support blogs with JavaScript generated content we embed a full web browser into the crawler.
+After considering mutliple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performences and scipting capabilities.
+In order to take full advantage of all extraction capabilities, the JavaScript rendering is done as the very first step of blog post processing.
+This way, every other part of the project is independent of whether or not the page its currently processing was actually rendered by PhantomJS or comes directly from the web server.
+Extracting blog post content, comments and images therefore works equally well on both blogs with JavaScript generated content and traditional HTML blogs.
 
-- ez of use vs power, fine because it's automated
+- python scripting click click use case
 
@@
 \subsection{Enriching Scrapy}
-Our project is build on top of Scrapy\TODO{link}, an open source python framework for web crawling.
+Our project is build on top of Scrapy\cite{scrapy2013}, an open source python framework for web crawling.
 In addition to the extraction aspects of the project, we also enrich the framework with two components specific to blog-post extraction: blog-post identification and download priority heuristic.

### 2013-11-13 tex/4-techniques.tex
Add Click click scripting paragraph under techniques.

@@
 After considering mutliple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performences and scipting capabilities.
-In order to take full advantage of all extraction capabilities, the JavaScript rendering is done as the very first step of blog post processing.
+In order to take full advantage of all the extraction functionalities, the JavaScript rendering is done as the very first step of blog post processing.
 This way, every other part of the project is independent of whether or not the page its currently processing was actually rendered by PhantomJS or comes directly from the web server.
@@
 
-- python scripting click click use case
+% Click click scripting
+In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities.
+When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a "Show More Comments" buttons.
+As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded.
+As you will see in the evaluation section, \TODO{we will see..}
 
-\subsection{Architecture}
-\subsubsection{Item pipeline}
-- item pipeline, modularity \\
-
-\subsubsection{Scalability}
-- http://www.reactivemanifesto.org/
-- stateless \\
-- scrapyd \\
+% \subsection{Architecture}
+% \subsubsection{Item pipeline}
+% - item pipeline, modularity \\
 
@@
 Due to space constraints, more precise description and evaluation of these two components where not included in this paper.
+
+\subsubsection{Scalability}
+At the time of writing...
+- http://www.reactivemanifesto.org/
+- stateless \\
+- scrapyd \\

### 2013-11-13 tex/4-techniques.tex
Fix some text on techniques, add image with scrapy architecture.

@@
 We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
-The overall software architecture with then be discussed, introducing the tools that come before and after the content extraction process: Scrapy and Invenio.
+The overall software architecture with then be discussed, introducing the Scrapy framework and the different addition we implemented for our use case.
 
@@
 To support blogs with JavaScript generated content we embed a full web browser into the crawler.
-After considering mutliple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performences and scipting capabilities.
+After considering multiple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities.
 In order to take full advantage of all the extraction functionalities, the JavaScript rendering is done as the very first step of blog post processing.
@@
 In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities.
-When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a "Show More Comments" buttons.
+When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons.
 As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded.
@@
 
+\subsection{Architecture}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
+  \caption{Overview of the crawler architecture.}
+  \label{architecture}
+\end{figure}
+
+Our project is build on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling.
+Scrapy provide an elegant and modulable high-level architecture which we followed in our implementation of the BlogForever Crawler.
+As illustrated in Figure~\ref{architecture}, Scrapy is divided in several components: \emph{Spiders}, \emph{Item Pipeline}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}, where each of can be used to implement a different functionality.
+
+Our use case has two types of spiders: NewCrawl and UpdateCrawl, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog.
+After downloading the HTML page, blog posts are packed into Items and sent through the folloing pipeline of operation:
+\begin{enumerate}[noitemsep]
+  \item Render JavaScript
+  \item Extract content
+  \item Extract comments
+  \item Download images
+  \item Propagate resulting records to the Invenio backend
+\end{enumerate}
+This pipeline design, often called the \emph{pipes and filters pattern}\cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity.
+Indeed, disabeling JavaScript rendering or plugging in an alternative backend can be done by editing a single configuration line.
+
+The default Scrapy behavior
+** In addition to the extraction aspects of the project, we also
+
 \subsection{Enriching Scrapy}
-Our project is build on top of Scrapy\cite{scrapy2013}, an open source python framework for web crawling.
-In addition to the extraction aspects of the project, we also enrich the framework with two components specific to blog-post extraction: blog-post identification and download priority heuristic.
-
-Given an entry to a blog, Scrapy provides the infrastructure to look over all pages on the same domain.
-In order to identify the subset of pages that are actually blog-posts, we build a \emph{blog-post identification} function that given an URL, returns whether or not it is a blog-post.
-This function uses a regular expression that is constructed from the web feed entries: the only set of known blog-post URLs.
+In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: blog-post identification and download priority heuristic.
+Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner.
+The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post.
+Internally, this function uses a regular expression constructed for each blog from it's web feed entries.
+These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs.
+This simple approach requieres that blog uses the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur) has showed to be .....................................
 
@@
 
-\subsubsection{Scalability}
+\subsection{Scalability}
+Scrapy is written with Twisted, a popular event-driven networking framework for Python. Thus, it’s implemented using a non-blocking (aka asynchronous) code for concurrency.
+
+Scrapy uses the Twisted\cite{twisted2013} asynchronous networking engine
+
 At the time of writing...

### 2013-11-14 tex/4-techniques.tex
scaling

@@
 
-The default Scrapy behavior
-** In addition to the extraction aspects of the project, we also
-
 \subsection{Enriching Scrapy}
@@
 These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs.
-This simple approach requieres that blog uses the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur) has showed to be .....................................
+This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur).
+In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.
 
-In order to efficiently deal with blogs with a large number non-blog-post pages, this mechanism is not sufficient.
-Indeed, after all pages identify as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts.
-To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where URL priorities are determined by a simple machine learning system.
-Given an URL, the machine learning system predicts the number of links to blog-post the corresponding page will contain.
-Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and given to the machine learning system that will store this value and take it into account for its future prediction.
-This mechanism has shown to be indispensable for web sites that host on the single domain a blog along with a large number of non-blog web pages, such as a forum or a wiki.
+In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient.
+Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts.
+To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm.
+Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain.
+Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data.
+that will then be taken it into account during future predictions.
+This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.
 
@@
 \subsection{Scalability}
+When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable.
+
+{{If one of these layers does not participate—making blocking calls to the database, relying on shared mutable state, calling out to expensive synchronous operations—then the whole pipeline stalls and users will suffer through increased latency and reduced scalability.}}\cite{reactivemanifesto2013}
+
+At the time of writting we did not had the chance to work on a distributed depoyement of the BlogForever project. However, the crawler was built tu be
+
 Scrapy is written with Twisted, a popular event-driven networking framework for Python. Thus, it’s implemented using a non-blocking (aka asynchronous) code for concurrency.

### 2013-11-14 tex/4-techniques.tex
Techniques done.

@@
 
-Our use case has two types of spiders: NewCrawl and UpdateCrawl, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog.
+Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog.
 After downloading the HTML page, blog posts are packed into Items and sent through the folloing pipeline of operation:
@@
 \subsection{Scalability}
-When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable.
+When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto\cite{thereactivemanifesto2013}:
 
-{{If one of these layers does not participate—making blocking calls to the database, relying on shared mutable state, calling out to expensive synchronous operations—then the whole pipeline stalls and users will suffer through increased latency and reduced scalability.}}\cite{reactivemanifesto2013}
+\begin{quoting}
+  If one of these layers does not participate—making blocking calls to the database, relying on shared mutable state, calling out to expensive synchronous operations—then the whole pipeline stalls and users will suffer through increased latency and reduced scalability.
+\end{quoting}
 
-At the time of writting we did not had the chance to work on a distributed depoyement of the BlogForever project. However, the crawler was built tu be
+At the time of writing we did not had the chance to work on a distributed deployment of the BlogForever project.
+However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, where designed to be usable as part of a event-driven, scalable and fault resilient distributed system.
 
-Scrapy is written with Twisted, a popular event-driven networking framework for Python. Thus, it’s implemented using a non-blocking (aka asynchronous) code for concurrency.
+\Anotecontent{commentfeed}{Blogs that do not provide a global comment feed need a special handling.
+If comment feeds are attached to each blog post, periodically checking for comment updates might be done with a reasonable cost.
+However, in the worst case where no comment feeds are provided, the only solution is to periodically do a full crawl of the blog to capture new comments.}
 
-Scrapy uses the Twisted\cite{twisted2013} asynchronous networking engine
-
-At the time of writing...
-- http://www.reactivemanifesto.org/
-- stateless \\
-- scrapyd \\
+Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities.
+\emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias.
+Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{commentfeed} and a time, and returns records of objects that where emitted after the given time.
+The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably.
+Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python.
+Scrapy also provides a built-in service to start spiders with an HTTP JSON API.
+With these tools in hand, the only component to implement in order to achieve a scalable and fault resilient distributed crawling system is an entity to keep track of available crawlers and does appropriate load balancing between them.

### 2013-11-14 tex/3-algorithms.tex
Add footnote.
Complete techiques head paragraph with a sentence on scalability.

@@
 
-This section explains in details the content wrapper generation algorithm and it's variations for authors, date and comments.
+This section explains in details the algorithm we developed to extract blog posts content and it's variations for authors, date and comments.
+webfeeeeeeeeds
 We will see how our seemingly brute force approach can be tweaked in order to achieve reasonable running times.
@@
 \subsection{Assumptions}
-Being a subset of XML, (HTML)* (HTML) documents are often categorized as semi-structured*.
-Some sementic tags were recently introduced in HTML*footnote* language specification, bringing **.
-If properly used, tags such as `<article>`, `<title>` and `<date>` can greatly simlify the tasks of content identification and extraction.
-However, the practice shows that these recent convetions are use by very few websites.
-Most are still using the more traditional aproach where pages are arbitrery hierarchi of `<div>` tags with arbitrery `class` or `id` names.
+
+\cite{worldwidewebconsortiumw3c2002}
+If properly used, tags such as `<article>`, `<title>` and `<date>` can greatly simplify the tasks of content identification and extraction.
+However, practice shows that these recent conventions are use by very few websites.
+
+Most are still using the more traditional approach where pages are arbitrary hierarchy of `<div>` tags with arbitrary `class` or `id` names.
 
@@
 2. Posts of a same blog share the same HTMP structure.
+\footnote{We constated in the evaluation that all blogs where our system failed to extract content violated one of these assumptions.}
 
@@
 - definitions, args and return value \\
-- related algos, generale brute force vue \\
-- algorithm \\
-- selectors (id, else class) \\
-- string similarity \\
 
 \subsection{Variations for comments and date}
-All the details about how to use the same algorithm to extract comments and dates.
+
+\section{Algorithms}
+
+\subsection{Motivation}
+- getting content from html is not easy. \cite{w3c2002}
+- assumptions when working with blogs
+- web feeds limitations
+- input output
+
+\subsection{Content extraction}
+- related algos, generale brute force vue
+- algorithm
+- xpath selectors (id, else class, else path)
+- string similarity
+- caching
+
+\subsection{Variations for comments, date and authors extraction}
+- comments
+- date authors

### 2013-11-14 tex/4-techniques.tex
Complete techiques head paragraph with a sentence on scalability.

@@
 We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
-The overall software architecture with then be discussed, introducing the Scrapy framework and the different addition we implemented for our use case.
+The overall software architecture with then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case.
+The section will conclude with a discussion about how the crawler design leads nicely into a scalable and fault resilient distributed architecture.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{JavaScript rendering}
@@
 
-% \subsection{Architecture}
-% \subsubsection{Item pipeline}
-% - item pipeline, modularity \\
-
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Architecture}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Enriching Scrapy}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Scalability}

### 2013-11-14 tex/3-algorithms.tex
Restructure algos.

@@
 This section explains in details the algorithm we developed to extract blog posts content and it's variations for authors, date and comments.
-webfeeeeeeeeds
-We will see how our seemingly brute force approach can be tweaked in order to achieve reasonable running times.
+We will see how blog specific characteristics can be exploited to obtain an extraction procedure applicable to all posts of a blog.
+A careful attention will be paid to minimizing algorithmic complexity while keeping the simple and general approach of the algorithm.
 
-\subsection{Assumptions}
+%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Motivation}
+- getting content from HTML is not easy.
+\cite{worldwidewebconsortiumw3c2002}
 
-\cite{worldwidewebconsortiumw3c2002}
-If properly used, tags such as `<article>`, `<title>` and `<date>` can greatly simplify the tasks of content identification and extraction.
-However, practice shows that these recent conventions are use by very few websites.
+% Assumptions when working with blogs
+\Anotecontent{assumptions}{We observed during evaluation that all failing test blogs where violating one of these assumptions.}
+Working with blogs allows to make assumptions\Anote{assumptions} that are central in our extraction procedure:
+\begin{enumerate}
+  \item Web feeds provide a structured and standardized view of the most recent posts
+  \item Posts of a same blog share the similar HTMP structure.
+\end{enumerate}
 
-Most are still using the more traditional approach where pages are arbitrary hierarchy of `<div>` tags with arbitrary `class` or `id` names.
+% Web feeds limitations
+In average, web feeds only contain about 20 entries \cite{french paper} which is generally lower than the total number of posts in a blog.
+In order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.
+The algorithm we are going to present in this section as for function to build wrappers for the relevant data of blog posts, which are going to be use
 
-Working with blogs allows to make assumptions that are central in our extraction procedure:
-1. Web feeds provide structured and standardised view of the last posts
-2. Posts of a same blog share the same HTMP structure.
-\footnote{We constated in the evaluation that all blogs where our system failed to extract content violated one of these assumptions.}
+% Per blog procedure, inputs/output
+Each time a new crawl is initiated our system builds a set of wrappers that are then used for the entirety of the blog.
+With this wrappers in hands, extraction data from the HTML page of a blog post is nothing more than parsing the HTML page running each XPath query, which can all by done with the standard python library \footnote{lxml, beautifullsoop}.
 
-In average, web feeds contain around 20 entries \cite{french paper} which is generally lower than the total number of posts in a blog.
-In order to effectively archive old content from blogs it is necessery to download and process pages beyong the one referenced by the feed.
-The algorithm we are going to present in this section as for function to build wrappers for the relevent data of blog posts, which are going to be use
-
-Concretely, a wrapper is an procedure to extract relevant data from a document. In our case, we aim to build queries in the XML path language (XPath) to extract relevant data from blog posts.
-
-Each time a new crawl is initiated our system builds a set of wrappers that are then used for the entirety of the blog.
-With this wrappers in hands, extraction data from the HTML page of a blog post is nothing more than parsing the HTML page running each XPath query, which can all by done with the standard python librarie \footnote{lxml, beautifullsoop}.
-
-- use per blog
-- a word about maintainability, given because by recompute them each tim
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Content extraction}
-- definitions, args and return value \\
-
-\subsection{Variations for comments and date}
-
-\section{Algorithms}
-
-\subsection{Motivation}
-- getting content from html is not easy. \cite{w3c2002}
-- assumptions when working with blogs
-- web feeds limitations
-- input output
-
-\subsection{Content extraction}
-- related algos, generale brute force vue
+- related algorithms, general brute force viewpoint
 - algorithm
-- xpath selectors (id, else class, else path)
+- XPath selectors (id, else class, else path)
 - string similarity
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Variations for comments, date and authors extraction}

### 2013-11-15 tex/3-algorithms.tex
algo++

@@
 This section explains in details the algorithm we developed to extract blog posts content and it's variations for authors, date and comments.
-We will see how blog specific characteristics can be exploited to obtain an extraction procedure applicable to all posts of a blog.
-A careful attention will be paid to minimizing algorithmic complexity while keeping the simple and general approach of the algorithm.
+We will see how we can take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
+A careful attention will be paid to minimizing algorithmic complexity while keeping the approach simple and general.
 
@@
 \subsection{Motivation}
-- getting content from HTML is not easy.
-\cite{worldwidewebconsortiumw3c2002}
+% HTML extraction is non trival
+Extracting metadata and content from HTML is not easy.
+Standards and recommendations have been present for quite some time, and tend to be quite strict on how the HTML documents should be organized.
+For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not be used more than once per page\cite{w3c2002}.
+More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}.
+In fact, a majority of web designer rely on the generic \code{<span></span>} and \code{<div></div>} containers with a custom \code{class} or \code{id} attributes to organize HTML pages.
+Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.
 
 % Assumptions when working with blogs
-\Anotecontent{assumptions}{We observed during evaluation that all failing test blogs where violating one of these assumptions.}
-Working with blogs allows to make assumptions\Anote{assumptions} that are central in our extraction procedure:
-\begin{enumerate}
-  \item Web feeds provide a structured and standardized view of the most recent posts
-  \item Posts of a same blog share the similar HTMP structure.
+\Anotecontent{noteA}{We observed during evaluation that all failing test blogs where violating one of these assumptions.}
+
+Working with blogs allows to make assumptions\Anote{noteA} that will be central in our extraction procedure:
+\begin{enumerate}[label={(\arabic*)}]
+  \item \label{havefeed} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
+  \item \label{similarhtml} Posts of a same blog share a similar HTML structure.
 \end{enumerate}
-
-% Web feeds limitations
-In average, web feeds only contain about 20 entries \cite{french paper} which is generally lower than the total number of posts in a blog.
+On average, web feeds only contain about 20 entries\cite{oita2010}, less than the total number of posts in an average blog.
 In order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.
-The algorithm we are going to present in this section as for function to build wrappers for the relevant data of blog posts, which are going to be use
-
-% Per blog procedure, inputs/output
-Each time a new crawl is initiated our system builds a set of wrappers that are then used for the entirety of the blog.
-With this wrappers in hands, extraction data from the HTML page of a blog post is nothing more than parsing the HTML page running each XPath query, which can all by done with the standard python library \footnote{lxml, beautifullsoop}.
 
@@
 \subsection{Content extraction}
+% \Anotecontent{vague}{The definition of the objective extraction rule is voluntarily vague, }
+
+% Per blog procedure, inputs/output
+The algorithm we are going to present in this section as for function to build an extraction rule for a relevant data of blog posts.
+It takes an input a set of pairs of HTML pages and target contents, and returns a extraction rule.
+The extraction rule should be such that when applied to one of the page, it will return data close to the target content of the corresponding page.
+
+input : A set $pageZipTarget$ of Html page and Text target pairs
+output: Best extraction rule
+Q <- empty list
+foreach (page, target) \in pageZipTarget do
+  Q <- Q + BestExtractionRule(page, target)
+return the extraction rule with highest occurrence in Q
+
+ALGO1.
+
+Given a blog, the crawler can use assumption \ref{havefeed} to obtain inputs for ALGO1.
+Indeed a web feeds provide either a textual content or a textual description for each of it's entries, as well as a link to the corresponding page.
+Assumptions \ref{similarhtml} suggests the existence of solution: an extraction rule appropriate for each input pages/target content pairs.
+\ref{similarhtml} is also key to ensure applicability of the rule to all posts of the blog.
+
+2
+
 - related algorithms, general brute force viewpoint

### 2013-11-15 tex/4-techniques.tex
algo++

@@
 \subsection{Enriching Scrapy}
-In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: blog-post identification and download priority heuristic.
+% Into, blog-post identification
+In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}.
 Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner.
@@
 
+% download priority heuristic
 In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient.
@@
 Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain.
-Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data.
-that will then be taken it into account during future predictions.
+This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next.
+Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken it into account during future predictions.
 This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.
@@
 
-\Anotecontent{commentfeed}{Blogs that do not provide a global comment feed need a special handling.
+\Anotecontent{noteC}{Blogs that do not provide a global comment feed need a special handling.
 If comment feeds are attached to each blog post, periodically checking for comment updates might be done with a reasonable cost.
@@
 \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias.
-Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{commentfeed} and a time, and returns records of objects that where emitted after the given time.
+Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time.
 The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably.

### 2013-11-15 tex/main.tex
Back to archi after discussion with Nicos.
Algorithms assumptions.
Back to techniques instead of architecture.
Progress...
Fix some text on techniques, add image with scrapy architecture.
Techniques done.
algo++

@@
 
+\usepackage[autostyle=false, style=english]{csquotes}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{color}
+\usepackage{enumitem}
 \usepackage{epsfig}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
+\usepackage{graphicx}
+\usepackage{hyperref}
+\usepackage{quoting}
 \usepackage{url}
-\usepackage{hyperref}
+\usepackage{sepfootnotes}
+
+\newfootnotes{A}
+\MakeOuterQuote{"}
+\quotingsetup{vskip=0pt,font={itshape}}
+\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
+\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
 
 \newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
+\newcommand{\code}[1]{\texttt{#1}}
 \newcommand{\surl}[1]{\urlstyle{ff}\url{#1}}
@@
 
-% \title{Web feed based content extraction with JavaScript rendering for the Invenio crawler}
-\title{BlogForever Crawler: Techniques and Algorithms to Harvest the Modern Web}
-% to Extract Data From the Modern Web}
-% Modern Web Pages}
+  \title{BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs}
 
@@
          \affaddr{1014 Lausanne, Switzerland}\\
-       \email{olivier.blanvillain@epfl.ch}
+         \email{\surl{olivier.blanvillain@epfl.ch}}
   % 2nd. author
@@
          \affaddr{1211 Geneva 23, Switzerland}\\
-       \email{nikos.kasioumis@cern.ch}
+         \email{\surl{nikos.kasioumis@cern.ch}}
   % 3rd. author
@@
          \affaddr{Aristotle University of Thessaloniki, Greece}\\
-       \email{vbanos@gmail.com}
+         \email{\surl{vbanos@gmail.com}}
   }
@@
   \maketitle
+
   \begin{abstract}
@@
 
-% A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+  % % A category with the (minimum) three required fields
+  % \category{H.4}{Information Systems Applications}{Miscellaneous}
+  % %A category including the fourth, optional field follows...
+  % \category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
-\terms{Theory}
+  \terms{Algorithms, Software Engineering}
 
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+  \keywords{Web archiving, Web crawling, ...}
 
@@
   \input{2-related-work.tex}
-\input{3-architecture.tex}
-\input{4-algorithms.tex}
+  \clearpage
+  \input{3-algorithms.tex}
+  \clearpage
+  \input{4-techniques.tex}
+  \clearpage
   \input{5-evaluation.tex}
+  \clearpage
   \input{6-conclusion-and-future-work.tex}
@@
   \bibliographystyle{abbrv}
-\bibliography{sigproc}
+  \bibliography{main}
+
 \end{document}

### 2013-11-18 tex/3-algorithms.tex
Add algo1.

@@
 % Per blog procedure, inputs/output
-The algorithm we are going to present in this section as for function to build an extraction rule for a relevant data of blog posts.
+Algorithm \ref{extraction} we are going to present in this section as for function to build an extraction rule for a relevant data of blog posts.
 It takes an input a set of pairs of HTML pages and target contents, and returns a extraction rule.
-The extraction rule should be such that when applied to one of the page, it will return data close to the target content of the corresponding page.
+The returned extraction rule should be such that when applied to one of the input page, the extracted text is close to the target content of the corresponding page.
 
-input : A set $pageZipTarget$ of Html page and Text target pairs
-output: Best extraction rule
-Q <- empty list
-foreach (page, target) \in pageZipTarget do
-  Q <- Q + BestExtractionRule(page, target)
-return the extraction rule with highest occurrence in Q
+\begin{algorithm}
+  \caption{Best Extraction Rule}\label{extraction}
+  \setstretch{1.1}
+  \thinspace
+  \SetKw{Of}{of}
+  \SetKw{In}{in}
+  \SetKwFunction{Pair}{}
+  \SetKwFunction{Apply}{Apply}
+  \SetKwFunction{AllRules}{AllRules}
+  \SetKwFunction{Similarity}{Similarity}
+  \SetKwInOut{Input}{input}
+  \SetKwInOut{Output}{output}
+  \DontPrintSemicolon
 
-ALGO1.
+  \Input{Set $pageZipTarget$ of Html and Text pairs}
+  \Output{Best extraction rule}
+  \BlankLine
+  $topRules \longleftarrow new~list$\;
+  \ForEach{\Pair{page, target} \In $pageZipTarget$}{
+    $score \longleftarrow new~map$\;
+    \ForEach{$rule$ \In \AllRules{page}}{
+      $extracted \longleftarrow$ \Apply{rule, page}\;
+      $score$ \Of $rule \longleftarrow$ \Similarity{extracted, target}\;
+    }
+    $topRules \longleftarrow topRules$ + rule with highest $score$\;
+  }
+  \Return{\emph{rule with highest occurrence in} $topRules$}\;
+\end{algorithm}
 
@@
 \ref{similarhtml} is also key to ensure applicability of the rule to all posts of the blog.
-
-2
 

### 2013-11-18 tex/3-algorithms.tex
General comment, embarrassingly parallel

@@
 \subsection{Content extraction}
-% \Anotecontent{vague}{The definition of the objective extraction rule is voluntarily vague, }
-
-% Per blog procedure, inputs/output
-Algorithm \ref{extraction} we are going to present in this section as for function to build an extraction rule for a relevant data of blog posts.
-It takes an input a set of pairs of HTML pages and target contents, and returns a extraction rule.
-The returned extraction rule should be such that when applied to one of the input page, the extracted text is close to the target content of the corresponding page.
+% Per blog procedure, related work
+In order to extract content, authors, date and comments of posts of a blog, we will proceed by first building extraction rules from the information given on the web feed.
+These rules will take advantage of the HTML structure similarities between pages of a same blog in order to be applicable to all posts of a blog.
+The approach is not new and has already showed to give great results (\cite{gkotsis2013}, \cite{oita2010}), outperforming a more generic state-of-the-art extraction algorithms which works directly from the HTML page, without the need for a web feed.
 
@@
 
-Given a blog, the crawler can use assumption \ref{havefeed} to obtain inputs for ALGO1.
+% Algo, inputs/output
+Algorithm \ref{extraction} shows the procedure we use to build the extraction rule for content of blog posts.
+It takes as input a set of pairs of HTML pages and target contents, and returns a extraction rule.
+The returned extraction rule should be such that when applied to one of the input page, the extracted text is close to the target content of the corresponding page.
+
+% General comment, embarrassingly parallel
+The idea is quite simple: compute the best extraction rule for each page/target tuple and return the most frequent rule.
+Making each of these computation independent might seems like a lose of information compared to another solution such as setting score of each rule to the average of it's score over all pages of the feed.
+However observed several cases were the independent solution performs better.
+When the web feed has a large portion of media only posts or with very short text, mean based solution tend to be more influenced by these outliers and are more likely to return wrong rules with constant low scores.
+In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop are independent and can be executed on multiple threads.
+
+% Input from assumptions.
+Given a blog, the crawler can use assumption \ref{havefeed} to obtain inputs for Algorithm \ref{extraction}.
 Indeed a web feeds provide either a textual content or a textual description for each of it's entries, as well as a link to the corresponding page.
@@
 
-- related algorithms, general brute force viewpoint
-- algorithm
 - XPath selectors (id, else class, else path)
-- string similarity
-- caching
+- string similarity, caching
 

### 2013-11-20 tex/3-algorithms.tex
Pull out algos and tables, 3-algorithms close to done.

--- 2013-11-15 tex/3-algorithms.tex
@@
 Extracting metadata and content from HTML is not easy.
-Standards and recommendations have been present for quite some time, and tend to be quite strict on how the HTML documents should be organized.
-For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not be used more than once per page\cite{w3c2002}.
+Standards and recommendations have been present for quite some time, and strict specify how HTML documents should be organized.
+For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
 More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}.
-In fact, a majority of web designer rely on the generic \code{<span></span>} and \code{<div></div>} containers with a custom \code{class} or \code{id} attributes to organize HTML pages.
+In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{class} or \code{id} attributes to organize HTML pages.
 Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.
@@
 % Assumptions when working with blogs
-\Anotecontent{noteA}{We observed during evaluation that all failing test blogs where violating one of these assumptions.}
+\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed than most of the failing blogs are violating one of these assumptions.}
 
-Working with blogs allows to make assumptions\Anote{noteA} that will be central in our extraction procedure:
+With web blogs as our target websites we made the following assumptions\Anote{assumptions} that will be central in our extraction procedure:
+n procedure:
 \begin{enumerate}[label={(\arabic*)}]
-  \item \label{havefeed} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
-  \item \label{similarhtml} Posts of a same blog share a similar HTML structure.
+  \item \label{havefeedAssum} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
+  \item \label{similarhtmlAssum} Posts of a same blog share a similar HTML structure.
 \end{enumerate}
 On average, web feeds only contain about 20 entries\cite{oita2010}, less than the total number of posts in an average blog.
-In order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.
+Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.
 
@@
 \subsection{Content extraction}
-% \Anotecontent{vague}{The definition of the objective extraction rule is voluntarily vague, }
+% Per blog procedure, related work
+In order to extract content, authors, date and comments of posts of a blog, we will proceed by first building extraction rules from the information given on it's web feed.
+These rules will take advantage of the similarities between HTML structure of pages on a same blog in order to be applicable to all posts of a blog.
+The approach is not new and has already showed to give great results (\cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that works directly on HTML pages, without the need for a web feed.
 
-% Per blog procedure, inputs/output
-The algorithm we are going to present in this section as for function to build an extraction rule for a relevant data of blog posts.
-It takes an input a set of pairs of HTML pages and target contents, and returns a extraction rule.
-The extraction rule should be such that when applied to one of the page, it will return data close to the target content of the corresponding page.
+\extractionAlgo
 
-input : A set $pageZipTarget$ of Html page and Text target pairs
-output: Best extraction rule
-Q <- empty list
-foreach (page, target) \in pageZipTarget do
-  Q <- Q + BestExtractionRule(page, target)
-return the extraction rule with highest occurrence in Q
+% Algorithm, inputs/output
+Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for content of blog posts.
+It takes as input a set of pairs of HTML pages and target contents, and returns an extraction rule.
+This rule should be such that when applied to one of the input pages, the extracted text is close to the corresponding target content.
 
-ALGO1.
+% General comment, embarrassingly parallel
+The idea is quite simple: compute the best extraction rule for each page/target pair and return the most frequent best rule.
+Making each of these computation independent might seems like a lose of information compared to alternative solutions such as having a global score for each rule computed as the average of it's score over all pages of the feed.
+We observed in our tests several cases were the independent solution performs better.
+When the web feed has a large portion of posts with very few text, mean based solutions tend to be more influenced by these outliers and are inclined to return wrong results with constant low scores.
+In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivialy be executed by multiple threads.
 
-Given a blog, the crawler can use assumption \ref{havefeed} to obtain inputs for ALGO1.
+% Input from assumptions.
+Given a blog, the crawler can use assumption \ref{havefeedAssum} to obtain inputs for Algorithm \ref{extractionAlgo}.
 Indeed a web feeds provide either a textual content or a textual description for each of it's entries, as well as a link to the corresponding page.
-Assumptions \ref{similarhtml} suggests the existence of solution: an extraction rule appropriate for each input pages/target content pairs.
-\ref{similarhtml} is also key to ensure applicability of the rule to all posts of the blog.
+Assumptions \ref{similarhtmlAssum} suggests the existence of solution: an extraction rule appropriate for each input pages/target content pairs.
+\ref{similarhtmlAssum} is also key to ensure applicability of the rule to all posts of the blog.
 
-2
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Extraction rules and string similarity}
+% XPath selectors (id, else class, else path)
+In our implementation, rules are queries in the XML Path Language (XPath).
+Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{apply} function use Algorithm \ref{extractionAlgo}.
+We experimented with 3 types of XPath queries: selection over \code{id} attribute, selection over \code{class} attribute and selection with absolute path.
+We have found that ignoring nodes without \code{id} or \code{class} absolutes prunes out a lot of uninteresting HTML nodes without decreasing  the quality of the result.
+Also when both \code{id} and \code{class} attributes are present the \code{id} attribute shows to be a stronger selector, here matching the HTML specification regarding the uniqueness of \code{id}.
+This observations led to the following \code{\ref{allrulesAlgo}} function:
 
-- related algorithms, general brute force viewpoint
-- algorithm
-- XPath selectors (id, else class, else path)
-- string similarity
-- caching
+\allrulesAlgo
+
+% String similarity
+Unsurprisingly, the choice of string similarity has a strong influence on the running time and precision of the extraction procedure.
+We use Sørensen–Dice coefficient similarity\cite{dice1945}, which is to the best of our knowledge the only string similarity fulfilling the following criteria:
+
+\begin{enumerate}
+  \item \label{wordorderProp} Have low sensibility to word ordering
+  \item \label{substringProp} Favor substrings over strings of similar length
+  \item \label{lineraProp} Run in linear time
+\end{enumerate}
+
+Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where web feeds contain only an abstract or the first paragraph of the post content.
+The following table illustrates these two properties with examples, also giving the Levenshtein\cite{levenshtein1966} similarity to illustrate the poor performance of string matching based similarities.
+
+\similarityTable
+
+The Sørensen–Dice coefficient methods operates by first building sets of pairs of adjacent characters, also knows as \emph{Bigrams}, and then applying the \emph{quotient of similarity} formula:
+
+\similarityAlgo
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Linear time reformulation}
 

### 2013-11-20 tex/3-algorithms.tex
up

@@
 
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Linear time reformulation}
+\subsection{Time complexity, linear reformulation}
+
+We will now show that Algorithm \ref{extractionAlgo} has a quadratic running time. Let's first assume that we have at our disposal a linera time HTML parser that build an index on
+
+As stated before, the outer simply splits the input into independent computations. \ref{allrulesAlgo} return a lkajsd flkasjd félkasjd félaksdjfélaskdjf
+% Algo 1 is quadratic
+
+% Linera reformulation
+
+% Algo 2
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Variations for comments, date and authors extraction}
+\subsection{Variations for comments and authors}
 - comments

### 2013-11-20 tex/3-algorithms.tex
Time complexity.

--- 2013-11-20 tex/3-algorithms.tex
@@
 More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}.
-In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{class} or \code{id} attributes to organize HTML pages.
+In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{id} or \code{class} attributes to organize HTML pages.
 Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.
@@
 \begin{enumerate}[label={(\arabic*)}]
-  \item \label{havefeedAssum} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
-  \item \label{similarhtmlAssum} Posts of a same blog share a similar HTML structure.
+  \item\label{havefeedAssum} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
+  \item\label{similarhtmlAssum} Posts of a same blog share a similar HTML structure.
 \end{enumerate}
@@
 These rules will take advantage of the similarities between HTML structure of pages on a same blog in order to be applicable to all posts of a blog.
-The approach is not new and has already showed to give great results (\cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that works directly on HTML pages, without the need for a web feed.
+The approach is not new and has already showed to give great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that works directly on HTML pages, without the need for a web feed.
 
@@
 In our implementation, rules are queries in the XML Path Language (XPath).
-Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{apply} function use Algorithm \ref{extractionAlgo}.
+Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{Apply} function use Algorithm \ref{extractionAlgo}.
 We experimented with 3 types of XPath queries: selection over \code{id} attribute, selection over \code{class} attribute and selection with absolute path.
@@
 Also when both \code{id} and \code{class} attributes are present the \code{id} attribute shows to be a stronger selector, here matching the HTML specification regarding the uniqueness of \code{id}.
-This observations led to the following \code{\ref{allrulesAlgo}} function:
+This observations led to the following \coderef{allrulesAlgo} function:
 
@@
 \begin{enumerate}
-  \item \label{wordorderProp} Have low sensibility to word ordering
-  \item \label{substringProp} Favor substrings over strings of similar length
-  \item \label{lineraProp} Run in linear time
+  \item\label{wordorderProp} Have low sensibility to word ordering
+  \item\label{substringProp} Favor substrings over strings of similar length
+  \item\label{linearProp} Run in linear time
 \end{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Linear time reformulation}
+\subsection{Time complexity, linear reformulation}
+
+With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time.
+Let's first assume that we have at our disposal a linear time HTML parser which builds an appropriate data-structure indexed on \code{id} and \code{class} attributes, effectively making \code{Apply} $\in$ \Oof{1}.
+As stated before, the outer loop splits the input into independent computations, and each call to \coderef{allrulesAlgo} returns less rules than the number of nodes in HTML tree, in linear time.
+Therefor, the body of the inner loop will be executed a linear number of time.
+Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} will run in \Oof{n}, leading a overall quadratic running time.
+
+While caching the bigram computation of target gives a speed up
+
+% Algo 1 is quadratic
+
+% Linera reformulation
+
+% Algo 2
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Variations for comments, date and authors extraction}
+\subsection{Variations for comments and authors}
 - comments

### 2013-11-21 tex/3-algorithms.tex
Linear algo started.

@@
 
+% Algo 1 is quadratic
 With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time.
@@
 Therefor, the body of the inner loop will be executed a linear number of time.
-Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} will run in \Oof{n}, leading a overall quadratic running time.
+Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} will run in \Oof{n}, leading to an overall quadratic running time.
+
+% Linera reformulation
+There is a reformulation of Algorithm \ref{extractionAlgo} with linar running time.
+As you will see, it requiers to break the separation in annex functions by bringing string similariy and HTML tree traversal logic into the core of the algorithm.
+It works like this
+
+\linearAlgo
+
+-> (algo)
+-> complecity analisis
+
+The reason we presented Algorithm \ref{extractionAlgo} and
 
 While caching the bigram computation of target gives a speed up
-
-% Algo 1 is quadratic
-
-% Linera reformulation
-
-% Algo 2
 

### 2013-11-21 tex/3-algorithms.tex
Algorithm 2 done.

@@
 \subsection{Motivation}
-% HTML extraction is non trival
+\comment{HTML extraction is non trival}%
 Extracting metadata and content from HTML is not easy.
-Standards and recommendations have been present for quite some time, and strict specify how HTML documents should be organized.
+Standards and recommendations have been present for quite some time, strictly specifying how HTML documents should be organized.
 For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
 More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}.
-In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{id} or \code{class} attributes to organize HTML pages.
+In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{id} or \code{class} attributes to organize pages, and it is not uncommon to enconter incorrect HTML.
 Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.
 
-% Assumptions when working with blogs
 \Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed than most of the failing blogs are violating one of these assumptions.}
 
-With web blogs as our target websites we made the following assumptions\Anote{assumptions} that will be central in our extraction procedure:
-n procedure:
+\comment{Assumptions when working with blogs}%
+With web blogs as our target websites we made the following assumptionsthat will play a central role in our extraction procedure\Anote{assumptions}:
 \begin{enumerate}[label={(\arabic*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
+  \item\label{havefeedAssum} Blogs provide web feeds: a structured and standardized view of blogs most recent posts,
   \item\label{similarhtmlAssum} Posts of a same blog share a similar HTML structure.
 \end{enumerate}
-On average, web feeds only contain about 20 entries\cite{oita2010}, less than the total number of posts in an average blog.
+Usually, web feeds only contain about 20 entries\cite{oita2010}, less than the total number of posts in an average blog.
 Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.
@@
 \subsection{Content extraction}
-% Per blog procedure, related work
+\comment{Per blog procedure, related work}%
 In order to extract content, authors, date and comments of posts of a blog, we will proceed by first building extraction rules from the information given on it's web feed.
@@
 
-% Algorithm, inputs/output
+\comment{Algorithm, inputs/output}%
 Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for content of blog posts.
@@
 
-% General comment, embarrassingly parallel
+\comment{General comment, embarrassingly parallel}%
 The idea is quite simple: compute the best extraction rule for each page/target pair and return the most frequent best rule.
@@
 
-% Input from assumptions.
+\comment{Input from assumptions.}%
 Given a blog, the crawler can use assumption \ref{havefeedAssum} to obtain inputs for Algorithm \ref{extractionAlgo}.
@@
 \subsection{Extraction rules and string similarity}
-% XPath selectors (id, else class, else path)
+\comment{XPath selectors (id, else class, else path)}%
 In our implementation, rules are queries in the XML Path Language (XPath).
@@
 
-% String similarity
+\comment{String similarity}%
 Unsurprisingly, the choice of string similarity has a strong influence on the running time and precision of the extraction procedure.
@@
 
-The Sørensen–Dice coefficient methods operates by first building sets of pairs of adjacent characters, also knows as \emph{Bigrams}, and then applying the \emph{quotient of similarity} formula:
+The Sørensen–Dice coefficient methods operates by first building sets of pairs of adjacent characters, also knows as \emph{bigram}, and then applying the \emph{quotient of similarity} formula:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Time complexity, linear reformulation}
+\subsection{Time complexity and linear reformulation}
 
-% Algo 1 is quadratic
+\comment{Algo 1 is quadratic}%
 With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time.
@@
 
-% Linera reformulation
-There is a reformulation of Algorithm \ref{extractionAlgo} with linar running time.
-As you will see, it requiers to break the separation in annex functions by bringing string similariy and HTML tree traversal logic into the core of the algorithm.
-It works like this
+\comment{Linear reformulation}%
+We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time.
+While very intuitive, the original idea of first generating extraction rules and then picking these best rule prevents an effective reuse of previously computed bigrams.
+For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \ref{similarityAlgo} function.
+At this point, the information of where the string could be spitted into substring with already computed bigrams is not accessible, and the bigram of the page has to be computed by linearly traversing the full string.
+To overcome this limitation and implement an effective memoization \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigram from it's children bigrams, effectively avoiding a complete string serialization.
 
@@
 
--> (algo)
--> complecity analisis
-
-The reason we presented Algorithm \ref{extractionAlgo} and
-
-While caching the bigram computation of target gives a speed up
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Variations for comments and authors}
+\subsection{Variations for comments, dates and authors}
 - comments

### 2013-11-21 tex/4-techniques.tex
Linear algo started.
Algorithm 2 done.

@@
 \subsection{JavaScript rendering}
-% Introduction
+\comment{Introduction}%
 JavaScript is a widely used use language for client-side web scripting.
@@
 
-% Motivation
+\comment{Motivation}%
 In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation.
@@
 
-% The solution
+\comment{The solution}%
 To support blogs with JavaScript generated content we embed a full web browser into the crawler.
@@
 
-% Click click scripting
+\comment{Click click scripting}%
 In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities.
@@
   \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
-  \caption{Overview of the crawler architecture.}
+  \caption{Overview of the crawler architecture.\TODO{Source}}
   \label{architecture}
@@
 
-Our project is build on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling.
+Our project is build on top of Scrapy\cite{scra py2013}, an open source Python framework for web crawling.
 Scrapy provide an elegant and modulable high-level architecture which we followed in our implementation of the BlogForever Crawler.
@@
 \subsection{Enriching Scrapy}
-% Into, blog-post identification
+\comment{Into, blog-post identification}%
 In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}.
@@
 
-% download priority heuristic
+\comment{download priority heuristic}%
 In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient.

### 2013-11-22 tex/3-algorithms.tex
Reread it all.

--- 2013-11-20 tex/3-algorithms.tex
@@
 \subsection{Motivation}
-% HTML extraction is non trival
+% html extraction is non trival
 Extracting metadata and content from HTML is not easy.
-Standards and recommendations have been present for quite some time, and strict specify how HTML documents should be organized.
+Standards and recommendations have been present for quite some time, strictly specifying how HTML documents should be organized.
 For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
 More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}.
-In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{id} or \code{class} attributes to organize HTML pages.
+In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{id} or \code{class} attributes to organize pages, and it is not uncommon to enconter incorrect HTML.
 Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.
 
-% Assumptions when working with blogs
-\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed than most of the failing blogs are violating one of these assumptions.}
+\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed than failing tests where either due to a violation of one of these assumptions, or to an insufficient amount of text in posts, such as \emph{photoblogs} with short captions.}
 
-With web blogs as our target websites we made the following assumptions\Anote{assumptions} that will be central in our extraction procedure:
-n procedure:
+% assumptions when working with blogs
+With web blogs as our target websites we made the following assumptions that will play a central role in the extraction procedure\Anote{assumptions}:
 \begin{enumerate}[label={(\arabic*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
+  \item\label{havefeedAssum} Blogs provide web feeds: a structured and standardized view of blogs most recent posts,
   \item\label{similarhtmlAssum} Posts of a same blog share a similar HTML structure.
 \end{enumerate}
-On average, web feeds only contain about 20 entries\cite{oita2010}, less than the total number of posts in an average blog.
+Web feeds contain about 20 entries\cite{oita2010}, often less than the total number of posts in blogs.
 Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.
@@
 \subsection{Content extraction}
-% Per blog procedure, related work
-In order to extract content, authors, date and comments of posts of a blog, we will proceed by first building extraction rules from the information given on it's web feed.
+% per blog procedure, related work
+To extract content, authors, date and comments of blog posts, we will proceed by first building extraction rules from the information given on it's web feed.
 These rules will take advantage of the similarities between HTML structure of pages on a same blog in order to be applicable to all posts of a blog.
-The approach is not new and has already showed to give great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that works directly on HTML pages, without the need for a web feed.
+The approach is not new and has already showed to give great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that works directly on HTML pages.
 
@@
 
-% Algorithm, inputs/output
-Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for content of blog posts.
+% algorithm, inputs/output
+Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for blog post contents.
 It takes as input a set of pairs of HTML pages and target contents, and returns an extraction rule.
-This rule should be such that when applied to one of the input pages, the extracted text is close to the corresponding target content.
+This rule will be such that when applied input pages, the extracted texts are close to the corresponding target contents.
+\comment{this last sentence might not be very clear (?), but this is very important.}%
 
-% General comment, embarrassingly parallel
+% general idea, embarrassingly parallel
 The idea is quite simple: compute the best extraction rule for each page/target pair and return the most frequent best rule.
-Making each of these computation independent might seems like a lose of information compared to alternative solutions such as having a global score for each rule computed as the average of it's score over all pages of the feed.
-We observed in our tests several cases were the independent solution performs better.
-When the web feed has a large portion of posts with very few text, mean based solutions tend to be more influenced by these outliers and are inclined to return wrong results with constant low scores.
+Making each of these computation independent might seems like a lose of information compared to alternative solutions such as having a global score for each rule, computed as the average of it's score over all pages of the feed.
+We observed in our experimentation several cases were the independent solution performs better.
+When web feeds have many posts with very few text, mean based solutions tend to be more influenced by these outliers and are inclined to return wrong rules which never return target contents but constantly have an average score.
+
 In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivialy be executed by multiple threads.
 
-% Input from assumptions.
-Given a blog, the crawler can use assumption \ref{havefeedAssum} to obtain inputs for Algorithm \ref{extractionAlgo}.
-Indeed a web feeds provide either a textual content or a textual description for each of it's entries, as well as a link to the corresponding page.
-Assumptions \ref{similarhtmlAssum} suggests the existence of solution: an extraction rule appropriate for each input pages/target content pairs.
-\ref{similarhtmlAssum} is also key to ensure applicability of the rule to all posts of the blog.
+% input from assumptions.
+Before going in details about annex functions and time complexity, we explain how the previously stated assumptions relate to Algorithm \ref{extractionAlgo}.
+Given a blog, assumption \ref{havefeedAssum} allows the crawler to obtain inputs for the algorithm.
+Indeed, web feeds provide either textual content or description of its entries, as well as a link to the corresponding page.
+Assumption \ref{similarhtmlAssum} garenties the existence of an appropriate an extraction rule, as well it's applicability to all posts of the blog.
 
-\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Extraction rules and string similarity}
-% XPath selectors (id, else class, else path)
+% xpath selectors (id, else class, else path)
 In our implementation, rules are queries in the XML Path Language (XPath).
-Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{Apply} function use Algorithm \ref{extractionAlgo}.
-We experimented with 3 types of XPath queries: selection over \code{id} attribute, selection over \code{class} attribute and selection with absolute path.
-We have found that ignoring nodes without \code{id} or \code{class} absolutes prunes out a lot of uninteresting HTML nodes without decreasing  the quality of the result.
-Also when both \code{id} and \code{class} attributes are present the \code{id} attribute shows to be a stronger selector, here matching the HTML specification regarding the uniqueness of \code{id}.
+Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{Apply} function used Algorithm \ref{extractionAlgo}.
+We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with path in the HTML tree.
+We have found that ignoring nodes without \code{id} or \code{class} attributes prunes out many uninteresting HTML nodes without decreasing  the quality of the result.
+Also when both \code{id} and \code{class} attributes are present, we can ignore the \code{class} has \code{id}s should be unique.
 This observations led to the following \coderef{allrulesAlgo} function:
@@
 
-% String similarity
+% string similarity
 Unsurprisingly, the choice of string similarity has a strong influence on the running time and precision of the extraction procedure.
-We use Sørensen–Dice coefficient similarity\cite{dice1945}, which is to the best of our knowledge the only string similarity fulfilling the following criteria:
+We use Sørensen–Dice coefficient similarity\cite{dice1945}, which is to the best of our knowledge the only string similarity fulfilling the following criterias:
 
@@
 
-Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where web feeds contain only an abstract or the first paragraph of the post content.
-The following table illustrates these two properties with examples, also giving the Levenshtein\cite{levenshtein1966} similarity to illustrate the poor performance of string matching based similarities.
+Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where web feeds contain only an abstract or a subset of the post content.
+The following table \comment{or with a caption?}illustrates these two properties with examples, also giving the Levenshtein\cite{levenshtein1966} similarity to illustrate poor performances of string matching based similarities.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Time complexity, linear reformulation}
+\subsection{Time complexity and linear reformulation}
 
+% algo 1 is quadratic
 With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time.
-Let's first assume that we have at our disposal a linear time HTML parser which builds an appropriate data-structure indexed on \code{id} and \code{class} attributes, effectively making \code{Apply} $\in$ \Oof{1}.
-As stated before, the outer loop splits the input into independent computations, and each call to \coderef{allrulesAlgo} returns less rules than the number of nodes in HTML tree, in linear time.
-Therefor, the body of the inner loop will be executed a linear number of time.
-Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} will run in \Oof{n}, leading a overall quadratic running time.
+Let's first assume that we have at our disposal a linear time HTML parser and a data-structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
+As stated before, the outer loop splits the input into independent computations, and each call to \coderef{allrulesAlgo} returns (in linear time) less rules than the number of nodes of the HTML tree argument.
+Therefore, the body of the inner loop will be executed a linear number of time.
+Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.
 
-While caching the bigram computation of target gives a speed up
+\linearAlgo
 
-% Algo 1 is quadratic
-
-% Linera reformulation
-
-% Algo 2
+% linear reformulation
+We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time.
+While very intuitive, the original idea of first generating extraction rules and then picking these best rule prevents an effective reuse of previously computed bigrams.
+For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function.
+At this point, the information of where the string could be spitted into substring with already computed bigrams is not accessible, and the bigrams of the page has to be computed by linearly traversing the full string.
+To overcome this limitation and implement an effective $memoization$ \comment{without R!}over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from it's children bigrams, effectively avoiding serialization of HTML subtrees.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Variations for comments and authors}
+\subsection{Variations for comments, dates and authors}
 - comments

### 2013-11-25 tex/3-algorithms.tex
alicia

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Extraction rules and string similarity}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Time complexity and linear reformulation}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Variations for comments, dates and authors}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Variations for authors, dates and comments}
+As is, algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performed poorly for authors and dates extraction and are not suitable for comment extraction.
+The case of author is problematic because is not uncommon to encounter the name a post author in several places in the pages.
+Because of this, to return a rule to extract the owner of the blog instead of the post author.
+In cases the blog owner and the post author is the same person in the feed entries but not across all the blog, we might extract the wrong information when the two differ.
+The heuristic we used to fix this issue is to add a new component in the scores of author extraction rules: the \emph{tree distance} between the current node and the node holding the post content.
+
+Dates are affected by the same issue often having duplicated in a page, but
+
+- date authors
+
 - comments
-- date authors

### 2013-11-25 tex/1-intro.tex
Minor fixes in captions + some of variations subsection.

@@
 
-Aims and contributions of this work. Example from my last paper to see the format:
-\surl{http://purl.pt/24107/1/iPres2013_PDF/CLEAR\%20a\%20credible\%20method\%20to\%20evaluate\%20website\%20archivability.pdf}
+Aims and contributions of this work. Example from my last paper to see the format:\\
+http://purl.pt/24107/1/iPres2013\_PDF/\\
+CLEAR\%20a\%20credible\%20method\%20to\%20\\
+evaluate\%20website\%20archivability.pdf
 

### 2013-11-25 tex/2-related-work.tex
Minor fixes in captions + some of variations subsection.

@@
 Web Object Identification for Web Automation and Meta-Search,
-\surl{http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf}
+\\
+http://www.dbai.tuwien.ac.at/proj/ta\\
+mcrow/download/Kordomatis2013WIMS.pdf
 
 Self-supervised Automated Wrapper Generation for Weblog Data Extraction,
-\surl{https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod_published.pdf}
+\\
+https://github.com/OlivierBlanvillai\\
+n/blogforever-crawler-publication/raw\\
+/master/papers/bncod\_published.pdf
 
 Web Data Extraction, Applications and Techniques: A Survey,
-\surl{http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf}
+\\
+http://www.emilio.ferrara.name/wp-co\\
+ntent/uploads/2011/07/survey-csur.pdf
 
 Archiving Data Objects using Web Feeds,
-\surl{http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf}
+\\
+http://hal.archives-ouvertes.fr/docs\\
+/00/53/79/62/PDF/iwawienna.pdf
 
 Intelligent and Adaptive Crawling of Web Applications for Web Archiving,
-\surl{http://pierre.senellart.com/publications/faheem2013intelligent.pdf}
+\\
+http://pierre.senellart.com/publicat\\
+ions/faheem2013intelligent.pdf
 
 Zero-cost Labelling with Web Feeds for Weblog Data Extraction,
-\surl{http://www2013.org/companion/p73.pdf}
+\\
+http://www2013.org/companion/p73.pdf\\
 
 OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications,
-\surl{http://www.vldb.org/pvldb/vol4/p1016-furche.pdf}
+\\
+http://www.vldb.org/pvldb/vol4/p1016\\
+-furche.pdf

### 2013-11-25 tex/3-algorithms.tex
Minor
Minor fixes in captions + some of variations subsection.

--- 2013-11-22 tex/3-algorithms.tex
@@
 Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where web feeds contain only an abstract or a subset of the post content.
-The following table \comment{or with a caption?}illustrates these two properties with examples, also giving the Levenshtein\cite{levenshtein1966} similarity to illustrate poor performances of string matching based similarities.
+Table \ref{similarityTable} illustrates these two properties with examples, also giving the Levenshtein\cite{levenshtein1966} similarity to illustrate poor performances of string matching based similarities.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Time complexity and linear reformulation}
-
 % algo 1 is quadratic
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Variations for comments, dates and authors}
-- comments
-- date authors
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Variations for authors, dates and comments}
+% Intro, authors
+As is, algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performed poorly for authors and dates extraction and are not suitable for comment extraction.
+The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score.
+The heuristic we use to get around this issue consists in adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
+This new score component takes advantage of the positioning of post's authors which is often a direct child or shares parent with the post content node.
+
+% Dates, authors
+Dates are affected by the same issue of often being duplicated in a page, which is complexified by the inconsistances of format between the dates provided in web feeds and their representation on web pages.
+Our solution uses the same tree distance score component presented
+
+% Comments

### 2013-11-25 tex/5-evaluation.tex
Progress...
Progress
Minor fixes in captions + some of variations subsection.

@@
   \item Our solution
-  \item Boilerpipe q\surl{https://github.com/misja/python-boilerpipe}
-  \item Goose \surl{https://github.com/grangier/python-goose}
-  \item Readability \surl{https://github.com/buriy/python-readability}
+  \item Boilerpipe https://github.com/misja/python-boilerpipe
+  \item Goose https://github.com/grangier/python-goose
+  \item Readability https://github.com/buriy/python-readability
 \end{itemize}
@@
 \begin{itemize}
-  \item "Wget crawl" \surl{http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/}
-  \item wkhtmltopdf \surl{http://code.google.com/p/wkhtmltopdf/}
+  \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/\\creating-a-snapshot-of-a-blog-post-using-wget/
+  \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
   \item Selenium + full browser
@@
   \item Table comparing functionalities of each solution
-  \item Histogram of redering time per browser (phantomjs/chrome/firefox)
+  \item Histogram of redering time per browser\\(phantomjs/chrome/firefox)
 \end{itemize}
+
+- ez of use vs power, fine because it's automated
+- c++ vs java vs scala vs go \cite{hundt2011}

### 2013-11-26 tex/3-algorithms.tex
Variations++

@@
 \subsection{Variations for authors, dates and comments}
-% Intro, authors
+% Intro
 As is, algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performed poorly for authors and dates extraction and are not suitable for comment extraction.
+This subsection presents variations of the general extraction techniques presented before.
+Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.
+
+% Authors
 The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score.
@@
 % Dates, authors
-Dates are affected by the same issue of often being duplicated in a page, which is complexified by the inconsistances of format between the dates provided in web feeds and their representation on web pages.
-Our solution uses the same tree distance score component presented
+Dates are affected by the same duplication issue, as well as inconsistence of format between web feeds and web pages.
+Our solution to build date extraction rules extends what we presented before for authors by using multiple \emph{target} strings.
+For instance, if the feed indicates that a post was published on \stringliteral{2013-12-09}, our algorithm will search for a rule to extract one of \stringliteral{}, \stringliteral{}, \stringliteral{} and so on.
+We use a list of \TODO{0} target date formats that was empirically built during our experiments.
+While this list is certainly not exhaustive, our approach using string similarity on multiple target is robust to format changes.
+We did not took the time to support dates in multiple languages but it would be a straightforward modification.
 
 % Comments
+Comments are usually available is separated web feeds, organized by blog post.
+Similarity to blog feeds, comment feeds have a limited number en entries, and in case of overflow content has to be extracted from the post web page.

### 2013-11-26 tex/4-techniques.tex
Reread it all.
Minor fixes in captions + some of variations subsection.
Variations++

--- 2013-11-15 tex/4-techniques.tex
@@
 The most frequent cases where blogs using the Disqus\cite{disqus2013} and LiveFyre\cite{livefyre2013} comment hosting services.
-These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page.
+These tools are very handy to setup for web-masters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page.
 Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users.
@@
 When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons.
-As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded.
-As you will see in the evaluation section, \TODO{we will see..}
+As part of the page load process we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded.
+Path to Disqus and LiveFyre buttons were manually obtained and are store in a configuration file.
+This is the only non-generic of the extraction stack which would require human intervention to maintain and extend for other commenting platforms.
 
@@
 \begin{figure}
+  \capstart
   \centering
   \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
-  \caption{Overview of the crawler architecture.}
+  \caption{Overview of the crawler architecture.\\\small{(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2013})}}
   \label{architecture}
@@
   \item Download images
-  \item Propagate resulting records to the Invenio backend
+  \item Propagate resulting records to the Invenio back-end
 \end{enumerate}
 This pipeline design, often called the \emph{pipes and filters pattern}\cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity.
-Indeed, disabeling JavaScript rendering or plugging in an alternative backend can be done by editing a single configuration line.
+Indeed, disabeling JavaScript rendering or plugging in an alternative back-end can be done by editing a single configuration line.
 
@@
 \subsection{Scalability}
-When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto\cite{thereactivemanifesto2013}:
+When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto \cite{thereactivemanifesto2013}:
 

### 2013-11-27 tex/3-algorithms.tex
Variations done.

@@
 This rule will be such that when applied input pages, the extracted texts are close to the corresponding target contents.
-\comment{this last sentence might not be very clear (?), but this is very important.}%
+\comment{this last sentence might not be clear (?), this is quite important.}%
 
@@
 
-% linear reformulation
+% Linear reformulation
 We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time.
@@
 At this point, the information of where the string could be spitted into substring with already computed bigrams is not accessible, and the bigrams of the page has to be computed by linearly traversing the full string.
-To overcome this limitation and implement an effective $memoization$ \comment{without R!}over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from it's children bigrams, effectively avoiding serialization of HTML subtrees.
+To overcome this limitation and implement $memoization$ \comment{without R!}over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from children bigrams.
+This way we avoid serializing HTML subtrees at each bigrams computation and have a guaranty that each character of the HTML page will be read at most once during bigrams computations.
+Thus, the cumlated time needed to compute bigrams of \emph{node.text} is linear.
+
+% End of proof
+To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all its inner loop computations other than bigrams of \emph{node.text} can be done in constant \emph{amortized} time.
+As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iterations is one.
+Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams lenght computation.
+Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operation can be done in constant time.
 
@@
 Our solution to build date extraction rules extends what we presented before for authors by using multiple \emph{target} strings.
-For instance, if the feed indicates that a post was published on \stringliteral{2013-12-09}, our algorithm will search for a rule to extract one of \stringliteral{}, \stringliteral{}, \stringliteral{} and so on.
-We use a list of \TODO{0} target date formats that was empirically built during our experiments.
+For instance, if the feed indicates that a post was published on
+\stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule to extract one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
+We use a list of \TODO{none so far :(} target date formats that was empirically built during our experiments.
 While this list is certainly not exhaustive, our approach using string similarity on multiple target is robust to format changes.
@@
 % Comments
-Comments are usually available is separated web feeds, organized by blog post.
-Similarity to blog feeds, comment feeds have a limited number en entries, and in case of overflow content has to be extracted from the post web page.
+Comments are usually available in a separated web feeds, organized by blog post.
+Similarity to blog feeds, comment feeds have a limited number en entries, and in case of overflow data has to be extracted from the post web page.
+To do so we use algorithm \ref{extractionAlgo} with the following modifications:
+\begin{enumerate}
+  \item\label{lessthanfeedMod} Rules that return less HTML nodes than the number of comments on the feed are filtered out.
+  \item\label{assignmentMod} The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
+\end{enumerate}
+Our crawler executes this algorithm on each page with comment overflow, and thus supports blogs with multiple commenting engines.
+Comment contents are extracted first, which allows to narrow down modification \ref{lessthanfeedMod} by fixing the target number of comments.

### 2013-11-27 tex/5-evaluation.tex
Variations done.

@@
 \begin{enumerate}
-  \item Running time
-  \begin{itemize}
-    \item Plot duration as a function of the page length
-    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
-  \end{itemize}
-  \item Quality of output compared:
-  \begin{itemize}
-    \item Chart of success pourcentages
-  \end{itemize}
+  \item Quality of output compared, Chart of success pourcentages
+  \item Running time, Plot duration as a function of the number or pages (our should only take time to build the rules)
 \end{enumerate}
@@
   \item Table comparing functionalities of each solution
-  \item Histogram of redering time per browser\\(phantomjs/chrome/firefox)
+  \item Histogram of redering time per browser\\(phantomjs/chrome/firefox?)
 \end{itemize}
@@
 - c++ vs java vs scala vs go \cite{hundt2011}
+
+\begin{figure}[htbp]
+  \centering
+  \begin{gnuplot}[terminal=epslatex,terminaloptions=color]
+    plot [0:2*pi] sin(x) title 'Sine', cos(x) title 'Cosine'
+  \end{gnuplot}
+\end{figure}

### 2013-11-27 tex/testfigure.tex
Add first gnuplot figure.

\begin{figure}[ht]
  \centering
  \begin{gnuplot}[scale=.75,terminal=epslatex,terminaloptions=color]
    set size ratio 0.618
    set yrange [0:50]
    set xrange [0:70]
    plot "data/runningtime.txt"\
       using 0:1 smooth cumulative with lines linewidth 5 title 'ContentExtractor',\
    "" using 0:2 smooth cumulative with lines linewidth 5 title 'Boilerpipe',\
    "" using 0:3 smooth cumulative with lines linewidth 5 title 'Goose',\
    "" using 0:4 smooth cumulative with lines linewidth 5 title 'Readability'
  \end{gnuplot}
\end{figure}
%lskdfjlsjflskjfls

### 2013-11-27 tex/3-algorithms.tex
Grammar, syntax and vocabulary corrections
Also, some inline comments.

--- 2013-11-25 tex/3-algorithms.tex
@@
 
-This section explains in details the algorithm we developed to extract blog posts content and it's variations for authors, date and comments.
+This section explains in detail the algorithms we developed to extract blog posts' content and its variations for authors, dates and comments.
 We will see how we can take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
-A careful attention will be paid to minimizing algorithmic complexity while keeping the approach simple and general.
+We focused on minimizing the algorithmic complexity while keeping our approach simple and generic enough.
 
@@
 \subsection{Motivation}
-% html extraction is non trival
-Extracting metadata and content from HTML is not easy.
-Standards and recommendations have been present for quite some time, strictly specifying how HTML documents should be organized.
+% html extraction is not trival
+Extracting metadata and content from HTML documents is a challenging task.
+Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organized.
 For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
-More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}.
-In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{id} or \code{class} attributes to organize pages, and it is not uncommon to enconter incorrect HTML.
-Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.
+More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but still suffer from very low usage: under 0.5\%\cite{andrewrogers2013}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages, and it is common to encounter incorrect HTML.
+Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques have to be employed.
 
@@
 % assumptions when working with blogs
-With web blogs as our target websites we made the following assumptions that will play a central role in the extraction procedure\Anote{assumptions}:
+Having blogs as our target websites we made the following assumptions that play a central role in the extraction process\Anote{assumptions}:
 \begin{enumerate}[label={(\arabic*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds: a structured and standardized view of blogs most recent posts,
-  \item\label{similarhtmlAssum} Posts of a same blog share a similar HTML structure.
+  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,
+  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
 \end{enumerate}
-Web feeds contain about 20 entries\cite{oita2010}, often less than the total number of posts in blogs.
-Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.
+Web feeds usually contain about 20 entries\cite{oita2010}\comment{maybe say that 1 entry is 1 post?}, often less than the total number of posts in blogs.
+Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the ones referenced in the feed.
 
@@
 % per blog procedure, related work
-To extract content, authors, date and comments of blog posts, we will proceed by first building extraction rules from the information given on it's web feed.
-These rules will take advantage of the similarities between HTML structure of pages on a same blog in order to be applicable to all posts of a blog.
-The approach is not new and has already showed to give great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that works directly on HTML pages.
+To extract content, authors, dates and comments from blog posts, we proceed by first building extraction rules from the data given in the blog's web feed.
+These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog.
+This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.
 
@@
 % algorithm, inputs/output
-Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for blog post contents.
-It takes as input a set of pairs of HTML pages and target contents, and returns an extraction rule.
-This rule will be such that when applied input pages, the extracted texts are close to the corresponding target contents.
-\comment{this last sentence might not be very clear (?), but this is very important.}%
+Algorithm \ref{extractionAlgo} shows the steps we follow to build extraction rules for the content pof blog posts.
+As input, it takes a set of pairs of HTML pages and target contents, and finally returns an extraction rule.
+This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.
+\comment{Does it make more sense now?
+Is it correct?
+To be honest, I'm not 100\% what you were trying to say.}%
 
 % general idea, embarrassingly parallel
-The idea is quite simple: compute the best extraction rule for each page/target pair and return the most frequent best rule.
-Making each of these computation independent might seems like a lose of information compared to alternative solutions such as having a global score for each rule, computed as the average of it's score over all pages of the feed.
-We observed in our experimentation several cases were the independent solution performs better.
-When web feeds have many posts with very few text, mean based solutions tend to be more influenced by these outliers and are inclined to return wrong rules which never return target contents but constantly have an average score.
+The idea is quite simple: to compute the best extraction rule for each pair of HTML page and target conent and to finally return the most frequent best rule.
+Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed.
+In our experimentation we observed several cases where the independent solution performs better\comment{reference or proof?}.
+When web feeds have many posts with very short content each, mean based solutions tend to be more influenced by these outliers\comment{other word for outliers?} and are inclined to return erronous rules which fail to return target contents but constantly have an average score.
 
-In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivialy be executed by multiple threads.
+In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here?}: iterations of the outer loop can trivialy be executed by multiple threads.
 
 % input from assumptions.
-Before going in details about annex functions and time complexity, we explain how the previously stated assumptions relate to Algorithm \ref{extractionAlgo}.
-Given a blog, assumption \ref{havefeedAssum} allows the crawler to obtain inputs for the algorithm.
-Indeed, web feeds provide either textual content or description of its entries, as well as a link to the corresponding page.
-Assumption \ref{similarhtmlAssum} garenties the existence of an appropriate an extraction rule, as well it's applicability to all posts of the blog.
+Before going into further details about annex functions and time complexity, we should explain how the previously stated assumptions relate to Algorithm \ref{extractionAlgo}.
+Given a blog, assumption \ref{havefeedAssum} allows the crawler to obtain input for the algorithm.
+Indeed, web feeds provide either textual content or descriptions for their entries, as well as links to the corresponding pages.
+Assumption \ref{similarhtmlAssum} guaranties the existence of an appropriate an extraction rule, as well as its applicability to all the posts of a blog.
 
@@
 In our implementation, rules are queries in the XML Path Language (XPath).
-Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{Apply} function used Algorithm \ref{extractionAlgo}.
-We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with path in the HTML tree.
+Consequently, standard libraries can be used parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}.
+We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absokute path in the HTML tree.
 We have found that ignoring nodes without \code{id} or \code{class} attributes prunes out many uninteresting HTML nodes without decreasing the quality of the result.
-Also when both \code{id} and \code{class} attributes are present, we can ignore the \code{class} has \code{id}s should be unique.
-This observations led to the following \coderef{allrulesAlgo} function:
+Also when both \code{id} and \code{class} attributes are present, we can ignore the \code{class} as we expect the \code{id} to be unique.
+These observations led to the following \coderef{allrulesAlgo} function:
 
@@
 % string similarity
-Unsurprisingly, the choice of string similarity has a strong influence on the running time and precision of the extraction procedure.
-We use Sørensen–Dice coefficient similarity\cite{dice1945}, which is to the best of our knowledge the only string similarity fulfilling the following criterias:
+Unsurprisingly, the choice of the string similarity algorithm greatly influences the running time and precision of the extraction process.
+We chose the Sørensen–Dice similarity coefficient\cite{dice1945}, which, to the best of our knowledge\comment{maybe remove this?
+it weakens our choice a bit.}, is the only string similarity algorithm fulfilling the following criteria:
 
 \begin{enumerate}
-  \item\label{wordorderProp} Have low sensibility to word ordering
-  \item\label{substringProp} Favor substrings over strings of similar length
-  \item\label{linearProp} Run in linear time
+  \item\label{wordorderProp} Has low sensitivity to word ordering
+  \item\label{substringProp} Favors substrings over strings of similar length
+  \item\label{linearProp} Runs in linear time
 \end{enumerate}
 
-Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where web feeds contain only an abstract or a subset of the post content.
-Table \ref{similarityTable} illustrates these two properties with examples, also giving the Levenshtein\cite{levenshtein1966} similarity to illustrate poor performances of string matching based similarities.
+Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post content.
+Table \ref{similarityTable} illustrates these two properties with examples, while comparing the chosen algorithm to the Levenshtein string similarity algorithm\cite{levenshtein1966} to illustrate poor performances of string matching based similarities.\comment{rephrase "poor performances of string matching based similarities"}
 
@@
 
-The Sørensen–Dice coefficient methods operates by first building sets of pairs of adjacent characters, also knows as \emph{bigram}, and then applying the \emph{quotient of similarity} formula:
+The Sørensen–Dice coefficient methods operate by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:
 
@@
 % algo 1 is quadratic
-With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time.
-Let's first assume that we have at our disposal a linear time HTML parser and a data-structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
-As stated before, the outer loop splits the input into independent computations, and each call to \coderef{allrulesAlgo} returns (in linear time) less rules than the number of nodes of the HTML tree argument.
-Therefore, the body of the inner loop will be executed a linear number of time.
-Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.
+With both the \coderef{allrulesAlgo} and \coderef{similarityAlgo} functions defined, we will show that Algorithm \ref{extractionAlgo} has a quadratic running time.
+First, let's assume that we have at our disposal a linear time HTML parser and a data structure with HTML nodes indexed on their \code{id} and \code{class} attributes\comment{does this need rephrasing to be clearer?}, effectively making \code{Apply}~$\in$~\Oof{1}.
+As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) less rules than the number of nodes of the HTML tree argument.
+Therefore, the body of the inner loop will be executed in a linear amount of time.
+Because the extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.
 
@@
 
-% linear reformulation
+% Linear reformulation
 We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time.
-While very intuitive, the original idea of first generating extraction rules and then picking these best rule prevents an effective reuse of previously computed bigrams.
+While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams.
 For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function.
-At this point, the information of where the string could be spitted into substring with already computed bigrams is not accessible, and the bigrams of the page has to be computed by linearly traversing the full string.
-To overcome this limitation and implement an effective $memoization$ \comment{without R!}over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from it's children bigrams, effectively avoiding serialization of HTML subtrees.
+At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string.
+To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from children bigrams\comment{instead: from their children?}.
+This way we avoid serializing HTML subtrees for each bigram computation and we can guaranty that each character of the HTML page will be read at most once during the bigrams computation.
+Thus, the cumlated time needed to compute the bigrams of \emph{node.text} is linear.
+
+% End of proof
+To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all its inner loop computations other than bigrams of \emph{node.text} can be done in constant \emph{amortized} time.
+As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigram unions per inner loop iteration is one.
+Each \emph{quotient of similarity} computation requires one bigram intersection and three bigram length computations.
+Over a finite alphabet (we used printable ASCII), bigram sizes have bounded size and each of these operations can be done in constant time.
 
@@
 \subsection{Variations for authors, dates and comments}
-% Intro, authors
-As is, algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performed poorly for authors and dates extraction and are not suitable for comment extraction.
+% Intro
+In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performe poorly for author and date extraction and are not suitable for comment extraction.
+This subsection presents variations on the general extraction techniques presented before.
+Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.
+
+% Authors
 The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score.
-The heuristic we use to get around this issue consists in adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
+The heuristic we use to get around this issue consists of adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
 This new score component takes advantage of the positioning of post's authors which is often a direct child or shares parent with the post content node.
@@
 % Dates, authors
-Dates are affected by the same issue of often being duplicated in a page, which is complexified by the inconsistances of format between the dates provided in web feeds and their representation on web pages.
-Our solution uses the same tree distance score component presented
+Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages.
+Our solution is to use multiple \emph{target} strings, while extending the rule that we previously described for author extraction.
+For instance, if the feed indicates that a post was published on
+\stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will create a rule that extracts one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
+We use a list of \TODO{none so far :(} target date formats that was empirically built during our experiments.
+While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is robust and tolerant to format variations.
+We do not, so far, support dates in multiple languages but English was sufficient for our experiments.
 
 % Comments
+Comments are usually available in separate web feeds, one per blog post.
+Similarly to blog feeds, comment feeds have a limited number of entries, and in case a blog post has more comments than the ones appearing in the feed, comments have to be extracted from the post web page.
+To do so we use algorithm \ref{extractionAlgo} with the following modifications:
+\begin{enumerate}
+  \item\label{lessthanfeedMod} Rules that return less HTML nodes than the number of comments on the feed are filtered out.
+  \item\label{assignmentMod} The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
+\end{enumerate}
+Our crawler executes this algorithm on each post that present a comment feed overflow, thus supporting blogs with multiple commenting engines.
+Comment contents are extracted first, which allows to narrow down modifications \ref{lessthanfeedMod} by fixing the target number of comments.

### 2013-11-28 tex/5-evaluation.tex
Add first gnuplot figure.
Eval plan

--- 2013-11-25 tex/5-evaluation.tex
@@
 
-\subsection{Introcution}
-What is evaluated (not comments, iframes, authors, dates...)
-\\ define the dataset and your competing algorithms the best way possible.
+Our evaluation will be articulated in two parts.
+Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extract content from web articles.
+The comparison will show that our blog targeted solution has better performances both in term of precision and running time.
+Secondly, a discussion will be held regarding the different alternative to archive data beyong HTML
 
-The dataset is a small sample coming from the Spinn3r dataset. The Spinn3r dataset was released for ICWSM 2011 conference.
+% intro, plan
+% hard to evaluate anything else, ttbook we r z only 1
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Content extraction}
-Compare:
-\begin{itemize}
-  \item Our solution
+
+% intro, plan
+
+% other projects
 \item Boilerpipe https://github.com/misja/python-boilerpipe
@@
 \item Readability https://github.com/buriy/python-readability
-\end{itemize}
-On:
-\begin{enumerate}
-  \item Running time
-  \begin{itemize}
-    \item Plot duration as a function of the page length
-    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
-  \end{itemize}
-  \item Quality of output compared:
-  \begin{itemize}
-    \item Chart of success pourcentages
-  \end{itemize}
-\end{enumerate}
+% limitation because different approach
 
+% dataset
+% result (table)
+% discussion
+
+% running time setup (single core, gc disabled, measure time spent in respective extraction functions)
+% result (plot)
+% discussion (c++ vs java vs scala vs go \cite{hundt2011})
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{JavaScript rendering}
-Compare:
-\begin{itemize}
-  \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/\\creating-a-snapshot-of-a-blog-post-using-wget/
+
+% intro, plan (why we pick these projects, what we want to show with this evaluation)
+
+\item "Wget crawl" http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/
 \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
+\item OXPath
 \item Selenium + full browser
-  \item probably others
-\end{itemize}
-On:
-\begin{itemize}
-  \item Table comparing functionalities of each solution
-  \item Histogram of redering time per browser\\(phantomjs/chrome/firefox)
-\end{itemize}
 
-- ez of use vs power, fine because it's automated
-- c++ vs java vs scala vs go \cite{hundt2011}
+% table to recap
+
+% discussion (ez of use vs power, fine because it's automated)
+
+\input{testfigure.tex}

### 2013-11-28 tex/0-abstract.tex
Add sublime project.
Progress...

@@
-Blogs are by nature a very dynamic and volatile communication medium. The
-BlogForever project aims to provide a generic platform for blog preservation,
-thus ensuring access to this information to future generations. This paper
-presents a key component of this archiving system: the web crawler. More
-precisely, our discussion will concentrate on techniques to automatically
-extract content, authors, date and comments of blog posts. One of the main
-challenges in the preservation of web objects is the rapid evolution of
-technologies. For instance, the recent trend towards using JavaScript to
-dynamically generate pages on the client side constitutes a new obstacle for
-today's crawlers. We will show how we integrated a headless web browser into the
-harvesting process in order to address these matters. Furthermore, we present a
-simple and robust algorithm based on string matching between web feeds and page
-content to generate wrappers. Being applicable to all posts of a blog, the
-resulting extraction procedure scales for large blogs.
+Blogs are by nature a very dynamic and volatile communication medium.
+The BlogForever project aims on providing a generic platform for blog preservation, thus ensuring access to this information for future generations.
+This paper presents a key component of this archiving system: the web crawler.
+More precisely, our discussion will concentrate on techniques to automatically extract content, authors, dates and comments from blog posts.
+One of the main challenges in the preservation of web objects is the rapid evolution of technologies.
+For instance, the recent trend towards using JavaScript to dynamically generate pages on the client side constitutes a new obstacle for today's crawlers.
+We will show how we integrated a web browser into the harvesting process in order to address this issue.
+Furthermore, we will present a simple and robust algorithm based on string matching between web feeds and page content to generate wrappers.
+Being applicable to all posts of a blog, the resulting extraction process scales to blogs with large amounts of posts.
+\comment{"being applicable to all posts of a blog" --> sounds a bit weird.}

### 2013-11-28 tex/3-algorithms.tex

@@
 
-The Sørensen–Dice coefficient methods operate by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:
+The Sørensen–Dice coefficient method operates by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:
 

### 2013-11-28 tex/3-algorithms.tex
Updates after discussion + ongoing evaluation.

@@
 Consequently, standard libraries can be used parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}.
-We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absokute path in the HTML tree.
+We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree.
 We have found that ignoring nodes without \code{id} or \code{class} attributes prunes out many uninteresting HTML nodes without decreasing the quality of the result.
@@
 With both the \coderef{allrulesAlgo} and \coderef{similarityAlgo} functions defined, we will show that Algorithm \ref{extractionAlgo} has a quadratic running time.
-First, let's assume that we have at our disposal a linear time HTML parser and a data structure with HTML nodes indexed on their \code{id} and \code{class} attributes\comment{does this need rephrasing to be clearer?}, effectively making \code{Apply}~$\in$~\Oof{1}.
-As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) less rules than the number of nodes of the HTML tree argument.
-Therefore, the body of the inner loop will be executed in a linear amount of time.
-Because the extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.
-
-\linearAlgo
+First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
+As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument.
+Therefore, the body of the inner loop will be executed \Oof{n} times.
+Because the extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.
 
@@
 At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string.
-To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from children bigrams\comment{instead: from their children?}.
-This way we avoid serializing HTML subtrees for each bigram computation and we can guaranty that each character of the HTML page will be read at most once during the bigrams computation.
-Thus, the cumlated time needed to compute the bigrams of \emph{node.text} is linear.
+To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams.
+This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation.
+Thus, the cumlated time needed to compute bigrams of \emph{node.text} is linear.
+
+\linearAlgo
 

### 2013-11-28 tex/5-evaluation.tex
Updates after discussion + ongoing evaluation.

@@
 % other projects
-\item Boilerpipe https://github.com/misja/python-boilerpipe
-\item Goose https://github.com/grangier/python-goose
-\item Readability https://github.com/buriy/python-readability
+% \item Boilerpipe https://github.com/misja/python-boilerpipe
+% \item Goose https://github.com/grangier/python-goose
+% \item Readability https://github.com/buriy/python-readability
 % limitation because different approach
@@
 % result (table)
-% discussion
+\precisionTable
+% discussion (15 feed entry)
 
@@
 % result (plot)
+\input{testfigure.tex}
+
 % discussion (c++ vs java vs scala vs go \cite{hundt2011})
@@
 
-\item "Wget crawl" http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/
-\item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
-\item OXPath
-\item Selenium + full browser
+% \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/
+% \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/ http://blogforever.eu/blog/2011/05/17/rendering-and-storing-web-pages-using-wkhtmltopdf/
+% \item OXPath
+% \item Selenium + full browser
 
@@
 % discussion (ez of use vs power, fine because it's automated)
-
-\input{testfigure.tex}

### 2013-11-28 tex/testfigure.tex
Updates after discussion + ongoing evaluation.

@@
   \centering
-  \begin{gnuplot}[scale=.75,terminal=epslatex,terminaloptions=color]
+  \begin{gnuplot}
+    set terminal epslatex color
+    set size 0.71
     set size ratio 0.618
-    set yrange [0:50]
+
+    # set title 'title'
+    set ylabel 'Cumulated running time (sec.)' offset 1.3
+    set xlabel 'Processed pages'
+
+    set yrange [0:55]
     set xrange [0:70]
-    plot "data/runningtime.txt"\
-       using 0:1 smooth cumulative with lines linewidth 5 title 'ContentExtractor',\
-    "" using 0:2 smooth cumulative with lines linewidth 5 title 'Boilerpipe',\
-    "" using 0:3 smooth cumulative with lines linewidth 5 title 'Goose',\
-    "" using 0:4 smooth cumulative with lines linewidth 5 title 'Readability'
+
+    set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey'
+
+    plot 'data/runningtime.txt'\
+       u 0:1 smooth cumulative w lines linewidth 5 title 'Our Approach',\
+    '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
+    '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
+    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose',\
   \end{gnuplot}

### 2013-11-28 tex/0-abstract.tex
Add missing files, update abstract.

@@
 We will show how we integrated a web browser into the harvesting process in order to address this issue.
-Furthermore, we will present a simple and robust algorithm based on string matching between web feeds and page content to generate wrappers.
-Being applicable to all posts of a blog, the resulting extraction process scales to blogs with large amounts of posts.
-\comment{"being applicable to all posts of a blog" --> sounds a bit weird.}
+Furthermore, we will present a simple and robust algorithm to generate extraction rules based on string matching between a web feed and blog page contents.
+Our crawler will then use these rules throughout the blog, leading to a scalable extraction process.

### 2013-11-28 tex/3-algorithms.tex
Fixes

@@
 More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but still suffer from very low usage: under 0.5\%\cite{andrewrogers2013}.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages, and it is common to encounter incorrect HTML.
+In fact, the majority of websites rely on the generic\TODO{reference this as well as incorrect HTML} \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages, and it is common to encounter incorrect HTML.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques have to be employed.
@@
 \begin{enumerate}[label={(\arabic*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,
+  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,\TODO{mention RSS and Atom, just to confirm to the reader what a web feed is.}
   \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
@@
 These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog.
-This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.
+This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.\comment{This might be a bit too raw, give more context at this point?}
 
@@
 Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed.
-In our experimentation we observed several cases where the independent solution performs better\comment{reference or proof?}.
-When web feeds have many posts with very short content each, mean based solutions tend to be more influenced by these outliers\comment{other word for outliers?} and are inclined to return erronous rules which fail to return target contents but constantly have an average score.
+In our experimentation we observed several cases where the independent solution performs better\comment{example, reference or proof?}.
+When web feeds have many posts with very short content each, mean based solutions tend to be more influenced by these outliers and are inclined to return erronous rules which fail to return target contents but constantly have an average score.
 
@@
 We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree.
-We have found that ignoring nodes without \code{id} or \code{class} attributes prunes out many uninteresting HTML nodes without decreasing the quality of the result.
+We have found that ignoring nodes without \code{id} or \code{class} attributes prunes out \TODO{link to previous ref on <div> and incorrect html}many uninteresting HTML nodes without decreasing the quality of the result.
 Also when both \code{id} and \code{class} attributes are present, we can ignore the \code{class} as we expect the \code{id} to be unique.
@@
   \item\label{wordorderProp} Has low sensitivity to word ordering
-  \item\label{substringProp} Favors substrings over strings of similar length
+  \item\label{lengthProp} Has low sensitivity to length variations
   \item\label{linearProp} Runs in linear time
@@
 
-Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post content.
+Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post content.
 Table \ref{similarityTable} illustrates these two properties with examples, while comparing the chosen algorithm to the Levenshtein string similarity algorithm\cite{levenshtein1966} to illustrate poor performances of string matching based similarities.\comment{rephrase "poor performances of string matching based similarities"}

### 2013-11-29 tex/5-evaluation.tex
Working on titles.

@@
 Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extract content from web articles.
-The comparison will show that our blog targeted solution has better performances both in term of precision and running time.
-Secondly, a discussion will be held regarding the different alternative to archive data beyong HTML
-
-% intro, plan
-% hard to evaluate anything else, ttbook we r z only 1
+The comparison will show that our blog targeted solution has better performances both in term of running time and success rates.
+Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code.
+Extraction of authors, dates and comments is not part of the evaluation because of the lack of publicly available competing projects and reference data sets.
 
@@
 \subsection{Content extraction}
+The evaluation of post content extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{} and Goose\cite{}.
+Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content.
+These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit the fact that pages of a same blog share a similar HTML structure (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
+Readability works by ....
+Boilerpipe uses a very ....
+Goose implements a more sofisticated algorithm which ....
 
+Table \ref{precisionTable} shows the
+
+Success rates of post content extraction
+
+To evaluate post content extraction 
 % intro, plan
@@
 % limitation because different approach
+Success rates of Content extraction is evaluation
 

### 2013-11-29 tex/testfigure.tex
Fix compilation errors with gnuplot and commath.

@@
     '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
-    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose',\
+    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
   \end{gnuplot}

### 2013-11-29 tex/3-algorithms.tex
Fix compilation errors with gnuplot and commath.
Fix/respond to some comments.

@@
-\section{Algorithms}
+\section{Algorithms}\label{algorithms}
 
@@
 More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but still suffer from very low usage: under 0.5\%\cite{andrewrogers2013}.
-In fact, the majority of websites rely on the generic\TODO{reference this as well as incorrect HTML} \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages, and it is common to encounter incorrect HTML.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques have to be employed.
@@
 \begin{enumerate}[label={(\arabic*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,\TODO{mention RSS and Atom, just to confirm to the reader what a web feed is.}
+  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,\TODO{mention RSS and Atom, just to confirm to the reader what a web feed is?}
   \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
 \end{enumerate}
-Web feeds usually contain about 20 entries\cite{oita2010}\comment{maybe say that 1 entry is 1 post?}, often less than the total number of posts in blogs.
+Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs.
 Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the ones referenced in the feed.
@@
 This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.
-\comment{Does it make more sense now?
-Is it correct?
-To be honest, I'm not 100\% what you were trying to say.}%
 
@@
 Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed.
-In our experimentation we observed several cases where the independent solution performs better\comment{example, reference or proof?}.
+In our experimentation we observed several cases where the independent solution performs better\TODO{example, reference or proof?}.
 When web feeds have many posts with very short content each, mean based solutions tend to be more influenced by these outliers and are inclined to return erronous rules which fail to return target contents but constantly have an average score.
 
-In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here?}: iterations of the outer loop can trivialy be executed by multiple threads.
+In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here?
+-> Can't find a good one..}: iterations of the outer loop can trivialy be executed by multiple threads.
 
@@
 We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree.
-We have found that ignoring nodes without \code{id} or \code{class} attributes prunes out \TODO{link to previous ref on <div> and incorrect html}many uninteresting HTML nodes without decreasing the quality of the result.
+
+Ignoring nodes without \code{id} or \code{class} attributes turns out to prune out many uninteresting HTML nodes without decreasing the quality of the result.
+
 Also when both \code{id} and \code{class} attributes are present, we can ignore the \code{class} as we expect the \code{id} to be unique.
@@
 Unsurprisingly, the choice of the string similarity algorithm greatly influences the running time and precision of the extraction process.
-We chose the Sørensen–Dice similarity coefficient\cite{dice1945}, which, to the best of our knowledge\comment{maybe remove this?
-it weakens our choice a bit.}, is the only string similarity algorithm fulfilling the following criteria:
+We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge\comment{maybe remove this?
+it weakens our choice a bit.
+-> at the same time it might not be the only one...}, is the only string similarity algorithm fulfilling the following criteria:
 
@@
 Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post content.
-Table \ref{similarityTable} illustrates these two properties with examples, while comparing the chosen algorithm to the Levenshtein string similarity algorithm\cite{levenshtein1966} to illustrate poor performances of string matching based similarities.\comment{rephrase "poor performances of string matching based similarities"}
+Table \ref{similarityTable} gives examples to illustrate how these two properties are fulfilled by the Sørensen–Dice coefficient similarity but do not hold for \emph{edit distance} based similarities such as the Levenshtein\cite{levenshtein1966} similarity.
 

### 2013-11-29 dataset/scoreTitles.sh

@@ -1,0 +1,5 @@
+#!/bin/sh
+
+python score.py titles/ ../../blogforever-crawler/titles
+python score.py titles/ TT/goose/
+python score.py titles/ TT/readability/

### 2013-11-29 tex/runningtimesfigure.tex
Improve figure marings and add title the the Extraction success rates table.

\begin{figure}[ht]
  \hspace{-30pt}
  \begin{gnuplot}
    set terminal epslatex color
    set size 0.733
    set size ratio 0.618

    # set title 'title'
    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed pages'

    set yrange [0:55]
    set xrange [0:65]

    set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey'

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 5 title 'Algorithm \ref{extractionAlgo}',\
    '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
  \end{gnuplot}
\end{figure}

### 2013-11-29 tex/3-algorithms.tex
Minor

@@
 We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree.
-
-Ignoring nodes without \code{id} or \code{class} attributes turns out to prune out many uninteresting HTML nodes without decreasing the quality of the result.
-
-Also when both \code{id} and \code{class} attributes are present, we can ignore the \code{class} as we expect the \code{id} to be unique.
-These observations led to the following \coderef{allrulesAlgo} function:
+\code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better blog consistency than absolute paths.
+For these reasons, the \coderef{allrulesAlgo} function only returns the best rule for each node:
 

### 2013-11-29 tex/5-evaluation.tex
Fix/respond to some comments.
Improve figure marings and add title the the Extraction success rates table.
Minor

@@
 \subsection{Content extraction}
-The evaluation of post content extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{} and Goose\cite{}.
+The evaluation of post content extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}.
 Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content.
@@
 To evaluate post content extraction
+\cite{burton2011} % <- dataset
 % intro, plan
@@
 % result (plot)
-\input{testfigure.tex}
+\input{runningtimesfigure.tex}
 

### 2013-11-29 tex/3-algorithms.tex
Re-read all the paper, lots of rephrasing.

@@
 More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but still suffer from very low usage: under 0.5\%\cite{andrewrogers2013}.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages\cite{brianwilson2008}\TODO{FIX REF!}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques have to be employed.
@@
 Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs.
-Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the ones referenced in the feed.
+Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.
 
@@
 % algorithm, inputs/output
-Algorithm \ref{extractionAlgo} shows the steps we follow to build extraction rules for the content pof blog posts.
+Algorithm \ref{extractionAlgo} shows the steps we follow to build extraction rules for the content of blog posts.
 As input, it takes a set of pairs of HTML pages and target contents, and finally returns an extraction rule.
@@
 % general idea, embarrassingly parallel
-The idea is quite simple: to compute the best extraction rule for each pair of HTML page and target conent and to finally return the most frequent best rule.
+The idea is quite simple: to compute the best extraction rule for each pair of HTML page and target content and to finally return the most frequent best rule.
 Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed.
 In our experimentation we observed several cases where the independent solution performs better\TODO{example, reference or proof?}.
-When web feeds have many posts with very short content each, mean based solutions tend to be more influenced by these outliers and are inclined to return erronous rules which fail to return target contents but constantly have an average score.
+When web feeds have posts with very short content, mean based solutions tend to be more influenced by these outliers and are inclined to return erronous rules which fail to return target contents but constantly have an average score.\TODO{rephrase!}
 
-In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here?
+In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here?
 -> Can't find a good one..}: iterations of the outer loop can trivialy be executed by multiple threads.
@@
 Indeed, web feeds provide either textual content or descriptions for their entries, as well as links to the corresponding pages.
-Assumption \ref{similarhtmlAssum} guaranties the existence of an appropriate an extraction rule, as well as its applicability to all the posts of a blog.
+Assumption \ref{similarhtmlAssum} guaranties the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.
 
@@
 In our implementation, rules are queries in the XML Path Language (XPath).
-Consequently, standard libraries can be used parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}.
+Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}.
 We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree.
@@
 This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation.
-Thus, the cumlated time needed to compute bigrams of \emph{node.text} is linear.
+Thus, the cumulated time needed to compute bigrams of \emph{node.text} is linear.
 
@@
 % Intro
-In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performe poorly for author and date extraction and are not suitable for comment extraction.
+In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will perform poorly for author and date extraction and are not suitable for comment extraction.
 This subsection presents variations on the general extraction techniques presented before.
@@
 The heuristic we use to get around this issue consists of adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
-This new score component takes advantage of the positioning of post's authors which is often a direct child or shares parent with the post content node.
+This new score component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.
 
@@
 \begin{enumerate}
-  \item\label{lessthanfeedMod} Rules that return less HTML nodes than the number of comments on the feed are filtered out.
-  \item\label{assignmentMod} The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
+  \item Rules that return less HTML nodes than the number of comments on the feed are filtered out.
+  \item The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
 \end{enumerate}
 Our crawler executes this algorithm on each post that present a comment feed overflow, thus supporting blogs with multiple commenting engines.
-Comment contents are extracted first, which allows to narrow down modifications \ref{lessthanfeedMod} by fixing the target number of comments.
+Comment contents are extracted first, which allows to narrow down the first modification by fixing a target number of comments.

### 2013-11-29 tex/4-techniques.tex
Re-read all the paper, lots of rephrasing.

--- 2013-11-15 tex/4-techniques.tex
@@
 The overall software architecture with then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case.
-The section will conclude with a discussion about how the crawler design leads nicely into a scalable and fault resilient distributed architecture.
+Finally we will talk about deployement to scalable, fault resilient distributed architecture.
 
@@
 JavaScript is a widely used use language for client-side web scripting.
-While some applications simply use it for aesthetics aspects such as menus and animations, an increasing number of websites use JavaScript to download and display content.
-In such circumstances, traditional HTML based crawled would not see the web site as it would be presented to a human visitor and might therefore be obsolete for extracting data from the page.
+While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content.
+In such cases, traditional HTML based crawled do not see web pages as they would be presented to a human visitor and might therefore be obsolete for data extraction.
 
 % Motivation
-In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation.
-The most frequent cases where blogs using the Disqus\cite{disqus2013} and LiveFyre\cite{livefyre2013} comment hosting services.
-These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page.
-Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users.
+In our experiments crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation.
+The most frequent cases where blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services.
+These tools are very handy to setup for web-masters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in each target page.
+Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments.
 Less commonly, some blogs are fully rendered using JavaScript.
-Concretely, when loading such website the web browser will not receive the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content.
-On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \cite{antinharasymiv2011} that use this mechanism.
+When loading such website, the web browser will not receive the page content as an HTML file, but will instead have execute JavaScript code to download and display the page content.
+One example can be found on the Blogger platforms which provides as one of its default templates the \emph{Dynamic Views} which use this mechanism \cite{antinharasymiv2011}.
 
@@
 To support blogs with JavaScript generated content we embed a full web browser into the crawler.
-After considering multiple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities.
-In order to take full advantage of all the extraction functionalities, the JavaScript rendering is done as the very first step of blog post processing.
-This way, every other part of the project is independent of whether or not the page its currently processing was actually rendered by PhantomJS or comes directly from the web server.
-Extracting blog post content, comments and images therefore works equally well on both blogs with JavaScript generated content and traditional HTML blogs.
+After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities.
+The JavaScript rendering is done as the very first step of web page processing.
+Extracting blog post content, comments or images therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.
 
 % Click click scripting
-In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities.
 When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons.
-As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded.
-As you will see in the evaluation section, \TODO{we will see..}
+As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded.
+Paths to Disqus and LiveFyre \emph{show more} buttons were manually obtained and are the only non-generic element of the extraction stack which will require human intervention to maintain and extend to other commenting platforms.
 
@@
 \begin{figure}
+  \capstart
   \centering
   \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
-  \caption{Overview of the crawler architecture.}
+  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2013})}
   \label{architecture}
@@
 
-Our project is build on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling.
-Scrapy provide an elegant and modulable high-level architecture which we followed in our implementation of the BlogForever Crawler.
-As illustrated in Figure~\ref{architecture}, Scrapy is divided in several components: \emph{Spiders}, \emph{Item Pipeline}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}, where each of can be used to implement a different functionality.
+Our crawler is built on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling.
+Scrapy provide an elegant and modulable architecture illustrated in Figure~\ref{architecture}.
+Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.
 
 Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog.
-After downloading the HTML page, blog posts are packed into Items and sent through the folloing pipeline of operation:
+After downloading its HTML\TODO{rephrase!}, a web page is packed into an \emph{Item} and sent through the following pipeline of operation:
 \begin{enumerate}[noitemsep]
@@
   \item Download images
-  \item Propagate resulting records to the Invenio backend
+  \item Propagate resulting records to the Invenio back-end
 \end{enumerate}
-This pipeline design, often called the \emph{pipes and filters pattern}\cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity.
-Indeed, disabeling JavaScript rendering or plugging in an alternative backend can be done by editing a single configuration line.
+This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity.
+Indeed, disabeling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.
 
@@
 % Into, blog-post identification
-In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}.
+In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}.
 Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner.

### 2013-11-29 tex/5-evaluation.tex
Re-read all the paper, lots of rephrasing.

@@
 Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code.
-Extraction of authors, dates and comments is not part of the evaluation because of the lack of publicly available competing projects and reference data sets.
+Extraction of authors, dates and comments is not part of evaluation because of the lack of publicly available competing projects and reference data sets.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Content extraction}
-The evaluation of post content extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Content extraction Precision}
+To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}.
 Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content.
-These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit the fact that pages of a same blog share a similar HTML structure (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
+These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit structural similarities of pages of a blog (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
 Readability works by ....
@@
 
+% dataset
+\cite{burton2011}
+
+% table
 Table \ref{precisionTable} shows the
+\precisionTable
 
-Success rates of post content extraction
+% short discussion, stress the fact that we use different tools
 
-To evaluate post content extraction
-\cite{burton2011} % <- dataset
-% intro, plan
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Content running time}
 
-% other projects
-% \item Boilerpipe https://github.com/misja/python-boilerpipe
-% \item Goose https://github.com/grangier/python-goose
-% \item Readability https://github.com/buriy/python-readability
-% limitation because different approach
-Success rates of Content extraction is evaluation
-
-% dataset
-% result (table)
-\precisionTable
-% discussion (15 feed entry)
-
-% running time setup (single core, gc disabled, measure time spent in respective extraction functions)
+% rsetup (single core, gc disabled, measure time spent in respective extraction functions)
 % result (plot)
@@
 
-% discussion (c++ vs java vs scala vs go \cite{hundt2011})
+% discussion: we are "cheating" on scalability
+% discussion: raw perf (15 feed entry)
+% discussion: (c++ vs java vs scala vs go \cite{hundt2011})
 

### 2013-11-30 tex/4-techniques.tex
Grammar and typos.

@@
 We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
-The overall software architecture with then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case.
+The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case.
 Finally we will talk about deployement to scalable, fault resilient distributed architecture.
@@
 % Introduction
-JavaScript is a widely used use language for client-side web scripting.
+JavaScript is a widely used language for client-side web scripting.
 While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content.
@@
 % The solution
-To support blogs with JavaScript generated content we embed a full web browser into the crawler.
+To support blogs with JavaScript generated content, we embed a full web browser into the crawler.
 After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities.
@@
 Scrapy provide an elegant and modulable architecture illustrated in Figure~\ref{architecture}.
-Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.
+Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.
 
@@
   \item Extract comments
-  \item Download images
+  \item Download medias
   \item Propagate resulting records to the Invenio back-end
@@
 In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}.
-Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner.
-The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post.
+Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner.
+The \emph{blog-post identification} function is able to identify from an URL whether or not the corresponding page is a blog-post.
 Internally, this function uses a regular expression constructed for each blog from it's web feed entries.
-These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs.
-This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur).
+These constitute the only set of known blog post URLs, and can therefore be used to identify the structure of blog post URLs.
+This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur).
 In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.
@@
 % download priority heuristic
-In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient.
+In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog-post identification mechanism is not sufficient.
 Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts.
@@
 This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next.
-Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken it into account during future predictions.
+Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions.
 This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.
@@
 
-At the time of writing we did not had the chance to work on a distributed deployment of the BlogForever project.
-However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, where designed to be usable as part of a event-driven, scalable and fault resilient distributed system.
+At the time of writing we did not had the chance to work on the deployment of the BlogForever project on a distributed environment.
+However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, where designed to be usable as part of an event-driven, scalable and fault resilient distributed system.
 
@@
 The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably.
+
 Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python.

### 2013-11-30 tex/5-evaluation.tex
Grammar and typos.

@@
 Our evaluation will be articulated in two parts.
-Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extract content from web articles.
+Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extracting content from web articles.
 The comparison will show that our blog targeted solution has better performances both in term of running time and success rates.
@@
 To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}.
-Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content.
-These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit structural similarities of pages of a blog (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
-Readability works by ....
+These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
+
+Readability relies mainly on common naming practices among web-developers  .
+
 Boilerpipe uses a very ....
+% Boilerpipe is probably one of the best open source packages when it comes to full article text extraction that leverages on machine learning.
+The overall algorithm works by computing both text and structural features on parts of the document and based on these features, decide if the observed part of the document belongs to the article text or not.
+The decision rules are inferred by a classifier trained on a set of labeled documents.
+% To obtain a set of learning examples that are fed into a classifier, boilerplate observes a list of features on different levels of the HTML document:
+
+% text frequency in the whole corpus: to obtain phrases commonly used in useless parts of the document
+% presence of particular tags that enclose a block of text: <h#> headline, <p> paragraph, <a> anchor and <div> division
+% shallow text features: average word length, average sentence length, absolute number of words in the segment
+% local context of text: absolute and relative position of the text block
+% heuristic features: number of words that start with an uppercase letter, number of words written in all-caps, number of date and time tokens, link density and certain ratios of those previously listed
+% density of text blocks: number of words in a wrapped fixed column width text block divided by number of lines of the same block
+% Each HTML document is segmented into atomic text blocks that are annotated with features listed above and labeled (by a human annotator) with content or boilerpate class.
+
+% In the original paper authors used decision trees and SVMs, trained on previously mentioned set of learning examples, to classify parts of the newly observed document as content or boilerplate text.
+
 Goose implements a more sofisticated algorithm which ....
+% clusters of paragraphs, word dencity and link dencity
 
@@
 
+Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, identify and extract content, tit.
 % rsetup (single core, gc disabled, measure time spent in respective extraction functions)

### 2013-11-30 tex/5-evaluation.tex
Add a paragraph to introduce the precisionTable.

--- 2013-11-29 tex/5-evaluation.tex
@@
 To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}.
-Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content.
-These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit structural similarities of pages of a blog (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
-Readability works by ....
-Boilerpipe uses a very ....
-Goose implements a more sofisticated algorithm which ....
+These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
 
-% dataset
-\cite{burton2011}
+\comment{Is it useful to present algorithms of the three other projects?
+\\ Readability relies mainly on common naming practices among web-developers
+\\ Boilerpipe: http://tomazkovacic.com/blog/14/extracting-article-text-from-html-documents/
+\\ Goose clusters of paragraphs, word dencity and link dencity}
 
-% table
-Table \ref{precisionTable} shows the
+Table \ref{precisionTable} shows extraction success rates of content and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.
+An extraction was considered successful when the returned string is a least 0.5 similar to the reference string, with respect to the Sørensen–Dice coefficient similarity.
+
 \precisionTable

### 2013-11-30 tex/runningtimesfigure.tex
Minor
Add a paragraph to introduce the precisionTable.

@@
 \begin{figure}[ht]
-  \hspace{-30pt}
+  \hspace{-29pt}
   \begin{gnuplot}
     set terminal epslatex color
-    set size 0.733
+    set size 0.725
     set size ratio 0.618
@@
 
-    set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey'
+    set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey' linetype 2
 

### 2013-12-01 tex/3-algorithms.tex
Eval++

@@
 We will see how we can take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
-We focused on minimizing the algorithmic complexity while keeping our approach simple and generic enough.
+We focused on minimizing the algorithmic complexity while keeping our approach simple and generic.
 
@@
 For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
-More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but still suffer from very low usage: under 0.5\%\cite{andrewrogers2013}.
+More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites.
 In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages\cite{brianwilson2008}\TODO{FIX REF!}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
-Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques have to be employed.
+Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
 
-\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed than failing tests where either due to a violation of one of these assumptions, or to an insufficient amount of text in posts, such as \emph{photoblogs} with short captions.}
+\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these assumptions, or to an insufficient amount of text in posts, such as \emph{photoblogs} with short captions.}
 
 % assumptions when working with blogs
-Having blogs as our target websites we made the following assumptions that play a central role in the extraction process\Anote{assumptions}:
+Having blogs as our target websites, the assumptions we made and which play a central role in the extraction process are the following\Anote{assumptions}:
 \begin{enumerate}[label={(\arabic*)}]
@@
 % per blog procedure, related work
-To extract content, authors, dates and comments from blog posts, we proceed by first building extraction rules from the data given in the blog's web feed.
+To extract content, authors, dates and comments from blog posts, we started by building extraction rules from the data given in the blog's web feed.
 These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog.
@@
 % general idea, embarrassingly parallel
-The idea is quite simple: to compute the best extraction rule for each pair of HTML page and target content and to finally return the most frequent best rule.
+The idea is quite simple: to compute the best extraction rule for each pair of HTML pages and target content and to finally return the most frequent best rule.
 Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed.
 In our experimentation we observed several cases where the independent solution performs better\TODO{example, reference or proof?}.
-When web feeds have posts with very short content, mean based solutions tend to be more influenced by these outliers and are inclined to return erronous rules which fail to return target contents but constantly have an average score.\TODO{rephrase!}
+When web feeds have posts with very short content, mean based solutions tend to be more influenced by these outliers and are inclined to return erroneous rules which fail to return target contents but constantly have an average score.\TODO{rephrase!}
 
 In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here?
--> Can't find a good one..}: iterations of the outer loop can trivialy be executed by multiple threads.
+-> Can't find a good one..}: iterations of the outer loop can trivially be executed by multiple threads.
 
@@
 Indeed, web feeds provide either textual content or descriptions for their entries, as well as links to the corresponding pages.
-Assumption \ref{similarhtmlAssum} guaranties the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.
+Assumption \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.
 

### 2013-12-01 tex/5-evaluation.tex
Eval++

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Content extraction Precision}
+\subsection{Extraction success rates}
 To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}.
 These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
-
-\comment{Is it useful to present algorithms of the three other projects?
-\\ Readability relies mainly on common naming practices among web-developers
-\\ Boilerpipe: http://tomazkovacic.com/blog/14/extracting-article-text-from-html-documents/
-\\ Goose clusters of paragraphs, word dencity and link dencity}
 
@@
 
-% short discussion, stress the fact that we use different tools
+On our test-set algorithm~\ref{extractionAlgo} outperformed the concurrence by 4.9\% margin on content extraction and a 10.1\% margin on title extraction.
+It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages.
+Contrariwise,\TODO{is this transition ok?} our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages.
+Therefore, results showed in table \ref{precisionTable} should not be interpreted as general evaluation of quality of the different projects, but simply mean that our approach is more suitable when working with blogs.
 
@@
 
-Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, identify and extract content, tit.
+In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure.
+The two point of interest are the time required to process a single page and the cumulated running time required to process multiple pages of a blog.
+The first result is significant for the \emph{UpdateCrawl} procedure, which is responsible for obtaining updates of already monitored blogs, and the second result regards the \emph{NewCrawl} procedure triggered when a new blog is added to the system and all previously published content has to be processed.
+
+Our measurements were made with garbage collector disabled on a otherwise idle core of a \TODO{Intel X} processor.  asdjf élaksd jfélkas jfélkas jfélaskjd félakjd fékas jfdéasdj féaksd jf
+
+% rtime eval, scalability with size of blogs
+
 % rsetup (single core, gc disabled, measure time spent in respective extraction functions)
+
 % result (plot)
-\input{runningtimesfigure.tex}
 
-% discussion: we are "cheating" on scalability
-% discussion: raw perf (15 feed entry)
-% discussion: (c++ vs java vs scala vs go \cite{hundt2011})
+\input{runningtimeFigure.tex}
+
+% discussion: again, we are "cheating" on scalability
+% discussion: raw perf (15 feed entry),
+% discussion: (c++ vs java vs scala vs go \cite{hundt2011})Implemented in Javascript, Java and Scala respectively
 

### 2013-12-01 tex/runningtimeFigure.tex
Eval++

\begin{figure}[ht]
  \hspace{-33pt}
  \begin{gnuplot}
    set terminal epslatex color
    set size 0.765
    set size ratio 0.618

    set title 'Figure 2: title'
    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed pages'

    set yrange [0:55]
    set xrange [0:65]

    set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey' linetype 2

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 5 title 'Algorithm \ref{extractionAlgo}',\
    '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
  \end{gnuplot}
\end{figure}

% \begin{figure}[ht]
%   \vspace{-59pt}
%   \hspace{-29pt}
%   \begin{gnuplot}
%     set terminal epslatex color
%     set size 0.725
%     set size ratio 0.618

%     set ylabel 'Cumulated running time (sec.)' offset 1.3
%     set xlabel 'Processed pages'

%     set yrange [0:55]
%     set xrange [0:65]

%     set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey' linetype 2

%     plot 'data/runningtime.txt'\
%        u 0:1 smooth cumulative w lines linewidth 5 title 'Algorithm \ref{extractionAlgo}',\
%     '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
%     '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
%     '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
%   \end{gnuplot}
% \end{figure}

### 2013-12-02 tex/1-intro.tex
First attempt on an introduction to the paper

--- 2013-10-29 tex/1-intro.tex
@@
 \section{Intro}
-1-intro.tex
+
 \begin{enumerate}
@@
 \end{enumerate}
+
+Challenges consist of:
+\begin{enumerate}
+  \item Providing a high degree of automation
+  \item Dealing with large volumes of data
+\end{enumerate}
+
+\comment{general introduction to web archiving and web crawlers}
+Web archiving is the process of harvesting and gathering web content in order to safely preserve it for posterity.
+As the volume and importance of the information on the World Wide Web increases, web archiving becomes more and more relevant and its importance becomes clearer.\\
+Web crawlers are an essential part of web archiving, allowing for automated capturing of these resources.\\
+An efficient and accurate web crawler is the first crucial step to successful digital preservation.\\
+\\
+\comment{introduction to blogs, their nature and their significance}
+An estimate xx\% of current web content is blogs (reference). OR There is an estimate of xxxxx blogs online currently.\\
+A blog is a \emph{frequently updated web site consisting of personal observations, excerpts from other sources, etc., typically run by a single person, and usually with hyperlinks to other sites; an online journal or diary.}\\
+\comment{http://www.oed.com/view/Entry/256743\#eid11173991}
+Given the nature of blogs, they are expectedly dynamic and highly volatile web resources.\\
+\\
+Blogs are nowadays a popular means of communication and expression of ideas and have been adopted by universities, institutions and scolars (reference?).\\
+Blogs have recenlty been used to disseminate ideas in times of political turmoil or even war. (examples, Egypt, Syria etc)\\
+Their political, scientific and cultural significance is undisputed. (rephrase to avoid need for reference?)\\
+\\
+However, to this day there is no standard method or authority that ensures blog archiving and xx\% dissapear every day (reference).\\
+\comment{A Tale of a Disappearing Website : http://blogs.loc.gov/digitalpreservation/2012/01/a-tale-of-a-disappearing-website/}
+\comment{Considerations for the Preservation of Blogs : http://www.digitalpreservationeurope.eu/publications/briefs/preservartion\_blogs.pdf}
+Therefore, it is crucial that the necessary foundations for blog archiving are put in place.\\
+\\
+\comment{present background in blog archiving and constraints}
+The blogosphere is a massive web resource of unstructured data.\\
+Identifying, harvesting and parsing that data can be a very challenging task.\\
+Challenges and constraints: size of blogosphere, heterogeneous nature of different publishing platforms, ever-changing structure, dynamically created content using modern web technologies.\\
+complexity in parsing blogs from unstructured data to structured information.\\
+programmatic access to blog content unavailable\\
+unpredictable publishing rate --> scalability\\
+\\
+\comment{present issues in current solutions}
+Is this needed? Can write in "Related Work" instead.
+\\
+\comment{present our main ideas and principles}
+Web feeds\\
+HTML + XPATH\\
+efficient string similarity\\
+JavaScript\\
+\\
+\comment{present our statement and target}
+improve efficiency, accuracy and general quality to help with archiving and understanding, using (information retrieval).
+\\
+\comment{present the contents of the paper}
+In chapter 1, chapter 2....
+\\
+Notes:\\
+\\
+(from wikipedia) The largest web archiving organization based on a bulk crawling approach is the Internet Archive which strives to maintain an archive of the entire Web.
+National libraries, national archives and various consortia of organizations are also involved in archiving culturally important Web content.
+Commercial web archiving software and services are also available to organizations who need to archive their own web content for corporate heritage, regulatory, or legal purposes.
+\\
+\\
+\comment{Aims and contributions of this work. Example from my last paper to see the format:\\
+http://purl.pt/24107/1/iPres2013\_PDF/\\
+CLEAR\%20a\%20credible\%20method\%20to\%20\\
+evaluate\%20website\%20archivability.pdf}
+\comment{Semi-structured nature of Web pages\\
+Labeled ordered rooted trees\\
+XML Path Language(XPath)}

### 2013-12-02 tex/5-evaluation.tex
Eval++

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% All experiments are reproducable by following instructions on the \emph{evaluation} branch of the BlogForever-Crawler version control **.
+% https://github.com/OlivierBlanvillain/blogforever-crawler-publication
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Extraction success rates}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Content running time}
+\subsection{Content extraction running times}
 
+% running time eval, scalability with size of blogs
 In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure.
-The two point of interest are the time required to process a single page and the cumulated running time required to process multiple pages of a blog.
-The first result is significant for the \emph{UpdateCrawl} procedure, which is responsible for obtaining updates of already monitored blogs, and the second result regards the \emph{NewCrawl} procedure triggered when a new blog is added to the system and all previously published content has to be processed.
+The main point of interest will be the scalability of extraction procedures as the number of processes pages increases.
+This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published data on a blog.
 
-Our measurements were made with garbage collector disabled on a otherwise idle core of a \TODO{Intel X} processor.  asdjf élaksd jfélkas jfélkas jfélaskjd félakjd fékas jfdéasdj féaksd jf
+% setup
+Our measurements were made with garbage collector disabled on a otherwise idle core of an \TODO{Intel X} processor.
+Experimental data where obtained by taking the median of 11 mesurements.
+confidence intervals ..
+in ..
+as (max 0.002 sec)
 
-% rtime eval, scalability with size of blogs
-
-% rsetup (single core, gc disabled, measure time spent in respective extraction functions)
+Figure 2 shows the cumulated time spent on each content extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of process blog posts on the \surl{http://quantumdiaries.org/} website.
 
 % result (plot)
-
 \input{runningtimeFigure.tex}
@@
 % discussion: again, we are "cheating" on scalability
+
 % discussion: raw perf (15 feed entry),
 % discussion: (c++ vs java vs scala vs go \cite{hundt2011})Implemented in Javascript, Java and Scala respectively
+% YUNO algo 2
 

### 2013-12-02 tex/2-related-work.tex
First partial attempt to related work

@@
 \section{Related work}
-2-related-work.tex
 
-Web Object Identification for Web Automation and Meta-Search,
-\\
-http://www.dbai.tuwien.ac.at/proj/ta\\
-mcrow/download/Kordomatis2013WIMS.pdf
+Web archiving is a challenging and very interesting problem and has been the subject of many studies as well as the goal of several projects.
+A fraction of these focuses on the specific problem of blog harvesting and archiving.
+These studies and projects focus on the unique nature of blogs as dynamic web resources with a usually common set of attributes.
+Each entry in a blog, commonly called a post, has a title, an author, a publication date, some content and possibly some descriptive tags.
+Blogs are also strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference).
+Web feeds are structured documents (often XML-based) that advertize and provide access to a website's content.
+Given their format, web feeds constitute an excellent source for blog archiving.
+They do, however, present some problems: (a) web feeds contain only the latest posts of a blog (usually 20) and (b) web feeds may only provide a summary or a fraction of the entire content of each blog post.
+More advanced methods and techniques have to be employed in order to achieve quality blog archiving.
+In this section we review some studies and projects that introduce and describe such techniques.
+\comment{Maybe this is repetitive, some of these things should already have been mentioned in the introduction}
 
-Self-supervised Automated Wrapper Generation for Weblog Data Extraction,
-\\
-https://github.com/OlivierBlanvillai\\
-n/blogforever-crawler-publication/raw\\
-/master/papers/bncod\_published.pdf
+\comment{list the projects and compare them to what we do}
 
-Web Data Extraction, Applications and Techniques: A Survey,
-\\
-http://www.emilio.ferrara.name/wp-co\\
-ntent/uploads/2011/07/survey-csur.pdf
+Web Object Identification for Web Automation and Meta-Search\\
+http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf\\
+In this paper we deal with the problem of finding specific web objects on previously unseen web pages.
+The problem consists of the sub problems of how to describe the desired objects (e.g., a specific submit button)and how to identify them on new web pages.
+This general problem is fundamental to many fields of research like Web Data Extraction, Web Form Understanding, Web Automation, etc.
+Our approach uses features based on the visual perceivable  characteristics of web objects for object description and machine learning techniques for object identification.
+Applied to a meta-search setting, this allows for a very universal solution.
+Here, the common elements of the considered search forms can be identified on previously unseen search pages, as long as they follow the same design principles.
 
-Archiving Data Objects using Web Feeds,
-\\
-http://hal.archives-ouvertes.fr/docs\\
-/00/53/79/62/PDF/iwawienna.pdf
+Self-supervised Automated Wrapper Generation for Weblog Data Extraction\\
+https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod\_published.pdf\\
 
-Intelligent and Adaptive Crawling of Web Applications for Web Archiving,
-\\
-http://pierre.senellart.com/publicat\\
-ions/faheem2013intelligent.pdf
+Web Data Extraction, Applications and Techniques: A Survey\\
+http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf\\
 
-Zero-cost Labelling with Web Feeds for Weblog Data Extraction,
-\\
+Archiving Data Objects using Web Feeds\\
+http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf\\
+
+Intelligent and Adaptive Crawling of Web Applications for Web Archiving\\
+http://pierre.senellart.com/publications/faheem2013intelligent.pdf\\
+
+Zero-cost Labelling with Web Feeds for Weblog Data Extraction\\
 http://www2013.org/companion/p73.pdf\\
 
-OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications,
-\\
-http://www.vldb.org/pvldb/vol4/p1016\\
--furche.pdf
+OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications\\
+http://www.vldb.org/pvldb/vol4/p1016-furche.pdf\\

### 2013-12-02 tex/5-evaluation.tex
Eval++ before mergin vengelis comments

@@
 % setup
-Our measurements were made with garbage collector disabled on a otherwise idle core of an \TODO{Intel X} processor.
-Experimental data where obtained by taking the median of 11 mesurements.
-confidence intervals ..
-in ..
-as (max 0.002 sec)
+Our measurements were made with garbage collector disabled on a otherwise idle core of an \emph{Intel Core i7-3770 3.4 GHz} processor.
+Experimental data was obtained by taking the median of 11 mesurements.
+On this setup we obtained very low standard deviations on the order of 2 milliseconds which are therefor
+
+confidence intervals .. in .. as (max 2ms)
 

### 2013-12-02 tex/3-algorithms.tex
Update 3-algorithms.tex

@@
 This section explains in detail the algorithms we developed to extract blog posts' content and its variations for authors, dates and comments.
-We will see how we can take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
-We focused on minimizing the algorithmic complexity while keeping our approach simple and generic.
+We explain how we take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
+Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.
 
@@
 Extracting metadata and content from HTML documents is a challenging task.
-Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organized.
+Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \TODO{ref to W3C standards}.
 For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
-More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organize structure pages\cite{brianwilson2008}\TODO{FIX REF!}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
+More recently, specifications such as Microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}\TODO{FIX REF!}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
+
+\TODO{Assumption is not a good word, we are based on facts from previous work.
+I suggest that you restructure this part as follows:
+
+Having blogs as our target websites, we are taking into account  the following facts that play a central role in the extraction process.
+
+1. "Blog is a kind of web page [with] frequent, usually brief posts, with the immediacy of reverse chronological order" (+ ref to BlogForever D2.2: BlogForever Data Model 
+https://zenodo.org/record/7488/files/BlogForever\_D2\_2WeblogDataModel.pdf
+
+2. blogs provide web feeds: structured and standardised views of the most recent blog posts.
+
+3. Web feeds contain information regarding the latest blog posts (usually 10 or 20 entries) + ref
+
+4. posts of the same blog share a similar HTML structure.
+
+Consequently, in order to effectively archive old blog content, it is necessary to download and process pages beyond the ones referenced in web feeds.
+}
 
@@
 \end{enumerate}
-Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs.
+Web feeds usually contain about 20 posts\cite{oita2010},\TODO{Add more info on web feeds, merge with the text on intro.} often less than the total number of posts in blogs.
 Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.
@@
 \subsection{Content extraction}
+\TODO{When I read this section for the first time, I was confused.
+After I also read 3.3 and 3.4 I understood better.
+You should have a nicely structured overview of the algorithm in 3.2 and have references for 3.3 and 3.4
+When you describe the algorithm overview, you should say explicitly that function X and operation Y is explained in section Z, etc}
 % per blog procedure, related work
 To extract content, authors, dates and comments from blog posts, we started by building extraction rules from the data given in the blog's web feed.
-These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog.
+\TODO{These rules take advantaged of the facts presented in 3.1 to create a more efficient data extraction process, outperforming more generic extraction algorithms that work directly with HTML pages.}These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog.
 This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.\comment{This might be a bit too raw, give more context at this point?}
@@
 
+\TODO{similatiry -> score function}
 \similarityAlgo
@@
 This subsection presents variations on the general extraction techniques presented before.
-Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.
+\TODO{Rephrase this to say that we don't show the full algos because it's just as in the 2 previous with customised score function!}Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.
 

### 2013-12-02 tex/4-techniques.tex
Add a paragraph to introduce the precisionTable.
Update 4-techniques.tex

@@
 Our crawler is built on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling.
-Scrapy provide an elegant and modulable architecture illustrated in Figure~\ref{architecture}.
+Scrapy provide an elegant and modular architecture illustrated in Figure~\ref{architecture}.
 Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.
@@
 \subsection{Enriching Scrapy}
-% Into, blog-post identification
-In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}.
+% Into, blog post identification
+In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog post identification} and \emph{download priority heuristic}.
 Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner.
-The \emph{blog-post identification} function is able to identify from an URL whether or not the corresponding page is a blog-post.
+The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post.
 Internally, this function uses a regular expression constructed for each blog from it's web feed entries.
@@
 % download priority heuristic
-In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog-post identification mechanism is not sufficient.
-Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts.
+In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog post identification mechanism is not sufficient.
+Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog post pages to search for additional blog posts.
 To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm.
-Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain.
+Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain.
 This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next.
-Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions.
+Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions.
 This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.
@@
 Due to space constraints, more precise description and evaluation of these two components where not included in this paper.
+\TODO{Again these things are great and you should write a lot more, instead of explaining Javascript rendering so much in 4.1  (it is trivial compared to these nice algorithms).}
 
@@
 \subsection{Scalability}
-When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto \cite{thereactivemanifesto2013}:
+\TODO{merge with 4.3, remove all the usless things. I believe that scalability should be removed from here and included in future work in the end.
+
+Also, everyone knows what scalability is and we don't have a lot of space as we said earlier :)
+The Reactive manifesto is not necessary...}
+When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind. Citing the Reactive Manifesto \cite{thereactivemanifesto2013}:
 
@@
 Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities.
-\emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias.
+\emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog posts, comments and medias.
 Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time.

### 2013-12-02 tex/3-algorithms.tex
Update 3-algorithms.tex

@@
 As input, it takes a set of pairs of HTML pages and target contents, and finally returns an extraction rule.
-This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.
+This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.\TODO{You definitely need a better explanation}
 
 % general idea, embarrassingly parallel
+\TODO{This paragraph is not clear.}
 The idea is quite simple: to compute the best extraction rule for each pair of HTML pages and target content and to finally return the most frequent best rule.

### 2013-12-02 tex/0-abstract.tex

--- 2013-11-02 tex/0-abstract.tex
@@
-Blogs are by nature a very dynamic and volatile communication medium. The
-BlogForever project aims to provide a generic platform for blog preservation,
-thus ensuring access to this information to future generations. This paper
-presents a key component of this archiving system: the web crawler. More
-precisely, our discussion will concentrate on techniques to automatically
-extract content, authors, date and comments of blog posts. One of the main
-challenges in the preservation of web objects is the rapid evolution of
-technologies. For instance, the recent trend towards using JavaScript to
-dynamically generate pages on the client side constitutes a new obstacle for
-today's crawlers. We will show how we integrated a headless web browser into the
-harvesting process in order to address these matters. Furthermore, we present a
-simple and robust algorithm based on string matching between web feeds and page
-content to generate wrappers. Being applicable to all posts of a blog, the
-resulting extraction procedure scales for large blogs.
+Blogs are a dynamic communication medium which has been widely established on the web. The BlogForever project has developed an innovative system to harvest, preserve, manage and reuse blog content.
+This paper presents a key component of the BlogForever platform, the web crawler.
+More precisely, our work concentrates on techniques to automatically extract content such as articles, authors, dates and comments from blog posts.
+To achieve this goal, we introduce a simple and robust algorithm to generate extraction rules based on string matching using the blog's web feed in conjunction to blog hypertext.
+This approach is leading to a scalable blog data extraction process.
+Furthermore, we show how we integrate a web browser into the web harvesting process in order to address the data extraction from blogs which use rapidly evolving technologies such as JavaScript generated web content.

### 2013-12-02 tex/3-algorithms.tex
Fix some todos

@@
 Extracting metadata and content from HTML documents is a challenging task.
-Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \TODO{ref to W3C standards}.
+Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}.
 For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
 More recently, specifications such as Microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}\TODO{FIX REF!}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
 
-\TODO{Assumption is not a good word, we are based on facts from previous work.
-I suggest that you restructure this part as follows:
+\TODO{Assumption is not a good word, we are based on facts from previous work.}
+% I suggest that you restructure this part as follows:
 
-Having blogs as our target websites, we are taking into account  the following facts that play a central role in the extraction process.
+% Having blogs as our target websites, we are taking into account  the following facts that play a central role in the extraction process.
 
-1. "Blog is a kind of web page [with] frequent, usually brief posts, with the immediacy of reverse chronological order" (+ ref to BlogForever D2.2: BlogForever Data Model 
-https://zenodo.org/record/7488/files/BlogForever\_D2\_2WeblogDataModel.pdf
+% 1. "Blog is a kind of web page [with] frequent, usually brief posts, with the immediacy of reverse chronological order" (+ ref to BlogForever D2.2: BlogForever Data Model
+% https://zenodo.org/record/7488/files/BlogForever\_D2\_2WeblogDataModel.pdf
 
-2. blogs provide web feeds: structured and standardised views of the most recent blog posts.
+% 2. blogs provide web feeds: structured and standardised views of the most recent blog posts.
 
-3. Web feeds contain information regarding the latest blog posts (usually 10 or 20 entries) + ref
+% 3. Web feeds contain information regarding the latest blog posts (usually 10 or 20 entries) + ref
 
-4. posts of the same blog share a similar HTML structure.
+% 4. posts of the same blog share a similar HTML structure.
 
-Consequently, in order to effectively archive old blog content, it is necessary to download and process pages beyond the ones referenced in web feeds.
-}
+% Consequently, in order to effectively archive old blog content, it is necessary to download and process pages beyond the ones referenced in web feeds.}
 
@@
 
-In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here?
--> Can't find a good one..}: iterations of the outer loop can trivially be executed by multiple threads.
+In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.
 
@@
 Unsurprisingly, the choice of the string similarity algorithm greatly influences the running time and precision of the extraction process.
-We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge\comment{maybe remove this?
-it weakens our choice a bit.
--> at the same time it might not be the only one...}, is the only string similarity algorithm fulfilling the following criteria:
+We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge, is the only string similarity algorithm fulfilling the following criteria:
 
@@
 At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string.
-To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams.
+To overcome this limitation and implement \emph{memoization} over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams.
 This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation.
@@
 \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will create a rule that extracts one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
-We use a list of \TODO{none so far :(} target date formats that was empirically built during our experiments.
-While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is robust and tolerant to format variations.
-We do not, so far, support dates in multiple languages but English was sufficient for our experiments.
+We use a total of 8 target date formats that was empirically built during our experiments.
+While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is tolerant to small variations.
+So far we do not support dates in multiple languages, but adding new target formats base and languages detection would certainly by a possible extension of our date extraction algorithm.
 

### 2013-12-02 tex/4-techniques.tex
Fix some todos

@@
 The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case.
-Finally we will talk about deployement to scalable, fault resilient distributed architecture.
+Finally we will talk about deployment to scalable, fault resilient distributed architecture.
 
@@
 The JavaScript rendering is done as the very first step of web page processing.
-Extracting blog post content, comments or images therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.
+Extracting blog post content, comments or medias therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.
 
@@
 Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog.
-After downloading its HTML\TODO{rephrase!}, a web page is packed into an \emph{Item} and sent through the following pipeline of operation:
+After beeing downloaded and identified as blog posts (details in subsection \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
 \begin{enumerate}[noitemsep]
@@
 This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity.
-Indeed, disabeling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.
+Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Enriching Scrapy}
+\subsection{Enriching Scrapy}\label{enrichingscrapy}
 % Into, blog post identification
@@
 Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain.
-This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next.
+This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visit next.
 Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions.
@@
 
-Due to space constraints, more precise description and evaluation of these two components where not included in this paper.
-\TODO{Again these things are great and you should write a lot more, instead of explaining Javascript rendering so much in 4.1  (it is trivial compared to these nice algorithms).}
-
 %%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Scalability}
-\TODO{merge with 4.3, remove all the usless things. I believe that scalability should be removed from here and included in future work in the end.
+When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind\cite{thereactivemanifesto2013}.
+At the time of writing we did not had the chance to work on the deployment of the BlogForever project on a distributed environment.
+However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.
 
-Also, everyone knows what scalability is and we don't have a lot of space as we said earlier :)
-The Reactive manifesto is not necessary...}
-When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind. Citing the Reactive Manifesto \cite{thereactivemanifesto2013}:
-
-\begin{quoting}
-  If one of these layers does not participate—making blocking calls to the database, relying on shared mutable state, calling out to expensive synchronous operations—then the whole pipeline stalls and users will suffer through increased latency and reduced scalability.
-\end{quoting}
-
-At the time of writing we did not had the chance to work on the deployment of the BlogForever project on a distributed environment.
-However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, where designed to be usable as part of an event-driven, scalable and fault resilient distributed system.
-
-\Anotecontent{noteC}{Blogs that do not provide a global comment feed need a special handling.
-If comment feeds are attached to each blog post, periodically checking for comment updates might be done with a reasonable cost.
-However, in the worst case where no comment feeds are provided, the only solution is to periodically do a full crawl of the blog to capture new comments.}
-
-Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities.
-\emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog posts, comments and medias.
-Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time.
-The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably.
-
-Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python.
-Scrapy also provides a built-in service to start spiders with an HTTP JSON API.
-With these tools in hand, the only component to implement in order to achieve a scalable and fault resilient distributed crawling system is an entity to keep track of available crawlers and does appropriate load balancing between them.
+To achieve this property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
+Indeed, from a high level viewpoint, these two components are \emph{purely functional}:
+%
+\newcommand\URL{\mathbb{U}\text{RL}}
+\newcommand\DATE{\mathbb{D}\text{ATE}}
+\newcommand\RECORD{\mathbb{R}\text{ECORD}}
+\begin{equation*}
+  \begin{split}
+    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
+    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
+  \end{split}
+\end{equation*}
+Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset.
+By delegating all shared mutable state to the backend system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.

### 2013-12-02 tex/5-evaluation.tex
Fix some todos

@@
 \subsection{Extraction success rates}
-To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}.
+To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{python-readability2011}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{goose2012}.
 These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
@@
 It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages.
-Contrariwise,\TODO{is this transition ok?} our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages.
+Contrariwise, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages.
 Therefore, results showed in table \ref{precisionTable} should not be interpreted as general evaluation of quality of the different projects, but simply mean that our approach is more suitable when working with blogs.

### 2013-12-02 tex/runningtimeFigure.tex
Fix some todos

@@
 \begin{figure}[ht]
-  \hspace{-33pt}
+  \hspace{-34pt}
   \begin{gnuplot}
     set terminal epslatex color
-    set size 0.765
+    set size 0.76
     set size ratio 0.618
@@
     plot 'data/runningtime.txt'\
-       u 0:1 smooth cumulative w lines linewidth 5 title 'Algorithm \ref{extractionAlgo}',\
+       u 0:1 smooth cumulative w lines linewidth 5 title 'Our approach',\
     '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
@@
 \end{figure}
-
-% \begin{figure}[ht]
-%   \vspace{-59pt}
-%   \hspace{-29pt}
-%   \begin{gnuplot}
-%     set terminal epslatex color
-%     set size 0.725
-%     set size ratio 0.618
-
-%     set ylabel 'Cumulated running time (sec.)' offset 1.3
-%     set xlabel 'Processed pages'
-
-%     set yrange [0:55]
-%     set xrange [0:65]
-
-%     set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey' linetype 2
-
-%     plot 'data/runningtime.txt'\
-%        u 0:1 smooth cumulative w lines linewidth 5 title 'Algorithm \ref{extractionAlgo}',\
-%     '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
-%     '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
-%     '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
-%   \end{gnuplot}
-% \end{figure}

### 2013-12-02 tex/3-algorithms.tex
Up

@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Motivation}
+\subsection{Motivation}\label{motivation}
 % html extraction is not trival
@@
 % assumptions when working with blogs
-Having blogs as our target websites, the assumptions we made and which play a central role in the extraction process are the following\Anote{assumptions}:
+Having blogs as our target websites, we use the following observations \TODO{If ok, change everywhere else.} which play a central role in the extraction process\Anote{assumptions}:  
 \begin{enumerate}[label={(\arabic*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,\TODO{mention RSS and Atom, just to confirm to the reader what a web feed is?}
+  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog
   \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
 \end{enumerate}
-Web feeds usually contain about 20 posts\cite{oita2010},\TODO{Add more info on web feeds, merge with the text on intro.} often less than the total number of posts in blogs.
-Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.
+Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs.
+\TODO{Add more info on web feeds, merge with the text on intro?} Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.
 
@@
 When you describe the algorithm overview, you should say explicitly that function X and operation Y is explained in section Z, etc}
+
 % per blog procedure, related work
-To extract content, authors, dates and comments from blog posts, we started by building extraction rules from the data given in the blog's web feed.
-\TODO{These rules take advantaged of the facts presented in 3.1 to create a more efficient data extraction process, outperforming more generic extraction algorithms that work directly with HTML pages.}These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog.
-This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.\comment{This might be a bit too raw, give more context at this point?}
+To extract articles, authors, dates and comments from blog posts, we procede by building extraction rules from the data given in the blog's web feed.
+Concretely, this procedure takes as input a set of pairs of HTML pages and target contents.
+It will then search for an extraction rule that jkjhkjhkjhkjhkjhkjhkjh
+
+This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.\TODO{You definitely need a better explanation}
+
+These rules take advantaged of the assumption presented in \ref{motivation} to create a more efficient data extraction process, outperforming more generic extraction algorithms that work directly with HTML pages \cite{gkotsis2013}, \cite{oita2010}.
+
+These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog.
+This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.
 

### 2013-12-03 tex/3-algorithms.tex
Fix half of 3.2

@@
-\section{Algorithms}\label{algorithms}
+\section{Algorithms}
+\label{algorithms}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Motivation}\label{motivation}
+\subsection{Motivation}
+\label{motivation}
+
 % html extraction is not trival
@@
 \subsection{Content extraction}
+\label{contentextraction}
+
 \TODO{When I read this section for the first time, I was confused.
@@
 To extract articles, authors, dates and comments from blog posts, we procede by building extraction rules from the data given in the blog's web feed.
-Concretely, this procedure takes as input a set of pairs of HTML pages and target contents.
-It will then search for an extraction rule that jkjhkjhkjhkjhkjhkjhkjh
+The idea is to provide a set of \emph{training data} to the algorithm, pairs of HTML page and target content, which are then used to build an extraction rule capable of locating the target content on each HTML page.
 
-This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.\TODO{You definitely need a better explanation}
+% input from assumptions.
+Assumption \ref{havefeedAssum} allows the crawler to obtain input for the algorithm: each entry of the web feed provides a link to the corresponding we page as well as potential target content such as the article, it's title, authors and publication date.
+Assumption \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.
 
-These rules take advantaged of the assumption presented in \ref{motivation} to create a more efficient data extraction process, outperforming more generic extraction algorithms that work directly with HTML pages \cite{gkotsis2013}, \cite{oita2010}.
-
-These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog.
-This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.
+% In the case the reader does not know how to read pseudocode
+Algorithm \ref{extractionAlgo} show the generic procedure we use to build extraction rules.
+The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all extraction rules the best one with respect to a certain \code{ScoreFunction}.
+The rule which was the most frequently a \emph{best rule} is then returned.
 
@@
 
-% algorithm, inputs/output
-Algorithm \ref{extractionAlgo} shows the steps we follow to build extraction rules for the content of blog posts.
-As input, it takes a set of pairs of HTML pages and target contents, and finally returns an extraction rule.
-This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.\TODO{You definitely need a better explanation}
+% abs, plan
+Most functions in algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section.
+\ref{extractionrulesandstringsimilarity}, \ref{timecomplexityandlinearreformulation}, \ref{variationsforauthorsdatesandcomments}
 
@@
 
-% input from assumptions.
-Before going into further details about annex functions and time complexity, we should explain how the previously stated assumptions relate to Algorithm \ref{extractionAlgo}.
-Given a blog, assumption \ref{havefeedAssum} allows the crawler to obtain input for the algorithm.
-Indeed, web feeds provide either textual content or descriptions for their entries, as well as links to the corresponding pages.
-Assumption \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Extraction rules and string similarity}
+\label{extractionrulesandstringsimilarity}
+
 % xpath selectors (id, else class, else path)
@@
 \subsection{Time complexity and linear reformulation}
+\label{timecomplexityandlinearreformulation}
+
 % algo 1 is quadratic
@@
 \subsection{Variations for authors, dates and comments}
+\label{variationsforauthorsdatesandcomments}
+
 % Intro
 In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will perform poorly for author and date extraction and are not suitable for comment extraction.
-This subsection presents variations on the general extraction techniques presented before.
+This subsection presents variations on the general extraction
+\label{presentsvariationsonthegeneralextraction}techniques presented before.
 \TODO{Rephrase this to say that we don't show the full algos because it's just as in the 2 previous with customised score function!}Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.

### 2013-12-03 tex/3-algorithms.tex
3.2 fixed.

@@
 
-\TODO{When I read this section for the first time, I was confused.
-After I also read 3.3 and 3.4 I understood better.
-You should have a nicely structured overview of the algorithm in 3.2 and have references for 3.3 and 3.4
-When you describe the algorithm overview, you should say explicitly that function X and operation Y is explained in section Z, etc}
-
 % per blog procedure, related work
@@
 
-% In the case the reader does not know how to read pseudocode
+% textual pseudocode
 Algorithm \ref{extractionAlgo} show the generic procedure we use to build extraction rules.
@@
 
+% Embarrassingly parallel
+One might notice that each \emph{best rule} computation is independent and operates on a different input pairs.
+Therefore algorithm \ref{extractionAlgo} \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.
+
 % abs, plan
-Most functions in algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section.
-\ref{extractionrulesandstringsimilarity}, \ref{timecomplexityandlinearreformulation}, \ref{variationsforauthorsdatesandcomments}
-
-% general idea, embarrassingly parallel
-\TODO{This paragraph is not clear.}
-The idea is quite simple: to compute the best extraction rule for each pair of HTML pages and target content and to finally return the most frequent best rule.
-Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed.
-In our experimentation we observed several cases where the independent solution performs better\TODO{example, reference or proof?}.
-When web feeds have posts with very short content, mean based solutions tend to be more influenced by these outliers and are inclined to return erroneous rules which fail to return target contents but constantly have an average score.\TODO{rephrase!}
-
-In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.
+Functions in algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section.
+\ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article and title extraction.
+In \ref{timecomplexityandlinearreformulation} we analyses time complexity of Algorithm \ref{extractionAlgo} and give a linear time reformulation using dynamic programing.
+Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
 

### 2013-12-03 tex/3-algorithms.tex
3.3 fixed.

@@
 
-This section explains in detail the algorithms we developed to extract blog posts' content and its variations for authors, dates and comments.
+This section explains in detail the algorithms we developed to extract blog posts' article and its variations for authors, dates and comments.
 We explain how we take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
@@
 \TODO{Assumption is not a good word, we are based on facts from previous work.}
-% I suggest that you restructure this part as follows:
-
-% Having blogs as our target websites, we are taking into account the following facts that play a central role in the extraction process.
-
-% 1. "Blog is a kind of web page [with] frequent, usually brief posts, with the immediacy of reverse chronological order" (+ ref to BlogForever D2.2: BlogForever Data Model
-% https://zenodo.org/record/7488/files/BlogForever\_D2\_2WeblogDataModel.pdf
-
-% 2. blogs provide web feeds: structured and standardised views of the most recent blog posts.
-
-% 3. Web feeds contain information regarding the latest blog posts (usually 10 or 20 entries) + ref
-
-% 4. posts of the same blog share a similar HTML structure.
-
-% Consequently, in order to effectively archive old blog content, it is necessary to download and process pages beyond the ones referenced in web feeds.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
 \subsection{Extraction rules and string similarity}
@@
 
-% string similarity
-Unsurprisingly, the choice of the string similarity algorithm greatly influences the running time and precision of the extraction process.
+% score function := string similarity
+Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process.
+When targeting articles, extraction rules are scored with a string similarity function comparing extracted and target strings.
 We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge, is the only string similarity algorithm fulfilling the following criteria:
@@
 
-Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post content.
+Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post article.
 Table \ref{similarityTable} gives examples to illustrate how these two properties are fulfilled by the Sørensen–Dice coefficient similarity but do not hold for \emph{edit distance} based similarities such as the Levenshtein\cite{levenshtein1966} similarity.
@@
 
-\TODO{similatiry -> score function}
 \similarityAlgo

### 2013-12-03 tex/4-techniques.tex
3.3 fixed.

@@
 \subsection{Enriching Scrapy}\label{enrichingscrapy}
-% Into, blog post identification
+% into
 In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog post identification} and \emph{download priority heuristic}.
+
+% blog post identification
 Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner.
 The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post.
-Internally, this function uses a regular expression constructed for each blog from it's web feed entries.
-These constitute the only set of known blog post URLs, and can therefore be used to identify the structure of blog post URLs.
+Internally, this function uses a per blog regular expression constructed from web feed entry URLs.
 This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur).
@@
 This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.
+
+\TODO{Give more details: this function implements a string score predictor using a the Distance-Weighted k-Nearest-Neighbor classifier, as described in \cite{dudani1976} http://ieeexplore.ieee.org/xpls/abs\_all.jsp?arnumber=5408784 This predictor can be used as an active machine learning algorithm by feeding it little by little with new url/score as they are discovered.}
 

### 2013-12-03 tex/3-algorithms.tex
3.5 close to done.

@@
 % html extraction is not trival
-Extracting metadata and content from HTML documents is a challenging task.
-Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}.
-For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
-More recently, specifications such as Microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}.
-Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
-
-\TODO{Assumption is not a good word, we are based on facts from previous work.}
+extracting metadata and content from html documents is a challenging task.
+standards and format recommendations have been around for quite some time, strictly specifying how html documents should be organised \cite{w3c2013}.
+for instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
+more recently, specifications such as microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites.
+in fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass html validation\cite{brianwilson2008-a}.
+under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.
 
@@
 
-% Embarrassingly parallel
+% embarrassingly parallel
 One might notice that each \emph{best rule} computation is independent and operates on a different input pairs.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
 \subsection{Extraction rules and string similarity}
@@
 
+% into: algo 1 defined
+With \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) functions defined, the definition of algorithm \ref{extractionAlgo} for article extraction is completed.
+We now proceed with a time complexity analysis which will show that this aproach has a quadratic running time.
+
 % algo 1 is quadratic
-With both the \coderef{allrulesAlgo} and \coderef{similarityAlgo} functions defined, we will show that Algorithm \ref{extractionAlgo} has a quadratic running time.
 First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
@@
 
-% Linear reformulation
-We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time.
+% linear reformulation
+We now present Algorithm \ref{linearAlgo}, linear time reformulation of Algorithm \ref{extractionAlgo} for article extraction using dynamic programming.
 While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams.
@@
 To overcome this limitation and implement \emph{memoization} over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams.
-This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation.
-Thus, the cumulated time needed to compute bigrams of \emph{node.text} is linear.
+This way we avoid serializing HTML subtrees for each bigram computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.
 
@@
 
-% End of proof
-To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all its inner loop computations other than bigrams of \emph{node.text} can be done in constant \emph{amortized} time.
-As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigram unions per inner loop iteration is one.
+% proof
+With bigrams computed in a dynamic programming manner, the cumulated time needed to compute \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear.
+To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.
+As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigram unions per inner loop iteration tends to one.
 Each \emph{quotient of similarity} computation requires one bigram intersection and three bigram length computations.
-Over a finite alphabet (we used printable ASCII), bigram sizes have bounded size and each of these operations can be done in constant time.
+Over a finite alphabet (we used printable ASCII), bigram sizes have bounded size and each of these operations takes constant time.
 
@@
 
-% Intro
+% intro
 In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will perform poorly for author and date extraction and are not suitable for comment extraction.
@@
 
-% Authors
-The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score.
-The heuristic we use to get around this issue consists of adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
-This new score component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.
+% authors
+The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, which results in several rules with maximum \coderef{similarityAlgo} score.
+The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
+This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.
 
-% Dates, authors
+% dates
 Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages.
-Our solution is to use multiple \emph{target} strings, while extending the rule that we previously described for author extraction.
-For instance, if the feed indicates that a post was published on
-\stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will create a rule that extracts one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
+Our solution for dates extraction extends authors \code{ScoreFunction} by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original \emph{target} date obtained from the web feed.
+For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
 We use a total of 8 target date formats that was empirically built during our experiments.
 While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is tolerant to small variations.
-So far we do not support dates in multiple languages, but adding new target formats base and languages detection would certainly by a possible extension of our date extraction algorithm.
+So far we do not support dates in multiple languages, but adding new target formats base and languages detection would be a simple extension of our date extraction algorithm.
 
-% Comments
+% comments
 Comments are usually available in separate web feeds, one per blog post.
 Similarly to blog feeds, comment feeds have a limited number of entries, and in case a blog post has more comments than the ones appearing in the feed, comments have to be extracted from the post web page.
-To do so we use algorithm \ref{extractionAlgo} with the following modifications:
-\begin{enumerate}
-  \item Rules that return less HTML nodes than the number of comments on the feed are filtered out.
-  \item The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
-\end{enumerate}
-Our crawler executes this algorithm on each post that present a comment feed overflow, thus supporting blogs with multiple commenting engines.
-Comment contents are extracted first, which allows to narrow down the first modification by fixing a target number of comments.
+To do so we use the following \code{ScoreFunction}:
+\begin{itemize}
+  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score.
+  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
+\end{itemize}
+Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines.
+Comment contents are extracted first, which allows to narrow down the initial filtering by fixing a target number of comments.
+
+\TODO{rush some time complexity analysis and conclude that we can do optimization analogs to algo 2 to obtain linear time on each extraction algo. }

### 2013-12-03 tex/3-algorithms.tex
Small changes after skype call + end of algorithms section.

@@
 more recently, specifications such as microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites.
-in fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass html validation\cite{brianwilson2008-a}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass html validation\cite{brianwilson2008-a}.
 under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.
 
-\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these assumptions, or to an insufficient amount of text in posts, such as \emph{photoblogs} with short captions.}
+\Anotecontent{observations}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these observations, or to an insufficient amount of text in posts, such as \emph{photoblogs} with short captions.}
 
-% assumptions when working with blogs
-Having blogs as our target websites, we use the following observations \TODO{If ok, change everywhere else.} which play a central role in the extraction process\Anote{assumptions}:
+% observations when working with blogs
+Having blogs as our target websites, we use the following observations which play a central role in the extraction process\Anote{observations}:
 \begin{enumerate}[label={(\arabic*)}]
@@
 Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs.
-\TODO{Add more info on web feeds, merge with the text on intro?} Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.
+Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.
 
@@
 
-% input from assumptions.
-Assumption \ref{havefeedAssum} allows the crawler to obtain input for the algorithm: each entry of the web feed provides a link to the corresponding we page as well as potential target content such as the article, it's title, authors and publication date.
-Assumption \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.
+% input from observations.
+Observation \ref{havefeedAssum} allows the crawler to obtain input for the algorithm: each entry of the web feed provides a link to the corresponding we page as well as potential target content such as the article, it's title, authors and publication date.
+Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.
 
@@
 % into: algo 1 defined
-With \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) functions defined, the definition of algorithm \ref{extractionAlgo} for article extraction is completed.
+With \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) functions defined, the definition of algorithm \ref{extractionAlgo} for article extraction is completed.
 We now proceed with a time complexity analysis which will show that this aproach has a quadratic running time.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Variations for authors, dates and comments}
+\subsection{Variations for authors, dates, comments}
 \label{variationsforauthorsdatesandcomments}
@@
 % intro
-In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will perform poorly for author and date extraction and are not suitable for comment extraction.
-This subsection presents variations on the general extraction
-\label{presentsvariationsonthegeneralextraction}techniques presented before.
-\TODO{Rephrase this to say that we don't show the full algos because it's just as in the 2 previous with customised score function!}Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.
+Using string similarity as only score measurement leads to poor performances on authors and dates extraction and is not suitable for comment extraction.
+This subsection presents variations of the previously presented \code{ScoreFunction} which address issues of these other contents.
 
@@
 
-\TODO{rush some time complexity analysis and conclude that we can do optimization analogs to algo 2 to obtain linear time on each extraction algo. }
+% rush some time complexity analysis
+Regarding time complexity, computing the \emph{tree distance} of all nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity.
+While evaluating rules for comments extraction requires more a expensive algorithm, the proportion of candidates left after filter out comment rules with an insufficient number of results was very low in practice.
+Analog  reformulations to the one explained in \ref{timecomplexityandlinearreformulation} can be applied for each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-03 tex/5-evaluation.tex
3.2 fixed.
Small changes after skype call + end of algorithms section.

@@
 To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{python-readability2011}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{goose2012}.
-These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).
+These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Content extraction running times}
@@
 In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure.
-The main point of interest will be the scalability of extraction procedures as the number of processes pages increases.
+The main point of interest will be the scalability of extraction procedures as the number of processed pages increases.
 This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published data on a blog.
@@
 On this setup we obtained very low standard deviations on the order of 2 milliseconds which are therefor
+
+\TODO{make a paragraph with linux, python and processor}
 

### 2013-12-04 tex/3-algorithms.tex
up

@@
 
-This section explains in detail the algorithms we developed to extract blog posts' article and its variations for authors, dates and comments.
-We explain how we take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
-Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.
+This section explains in detail the algorithm we developed to extract blog posts' article and its variations for authors, dates and comments.
+Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog.
+Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
 
@@
 % html extraction is not trival
-extracting metadata and content from html documents is a challenging task.
-standards and format recommendations have been around for quite some time, strictly specifying how html documents should be organised \cite{w3c2013}.
-for instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
-more recently, specifications such as microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass html validation\cite{brianwilson2008-a}.
-under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.
+Extracting metadata and content from html documents is a challenging task.
+Standards and format recommendations have been around for quite some time, strictly specifying how html documents should be organised \cite{w3c2013}.
+For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page \cite{w3c2002}.
+More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages \cite{brianwilson2008}, and more than 95\% of pages do not pass html validation \cite{brianwilson2008-a}.
+Under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.
 
-\Anotecontent{observations}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these observations, or to an insufficient amount of text in posts, such as \emph{photoblogs} with short captions.}
+\Anotecontent{observations}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these observations, or to an insufficient amount of text in posts.}
 
@@
 \begin{enumerate}[label={(\arabic*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog
+  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
   \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
 \end{enumerate}
-Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs.
-Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.
+Web feeds usually contain about 20 posts, often less than the total number of posts in blogs \cite{oita2010}.
+Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in web feeds.
 
@@
 % per blog procedure, related work
-To extract articles, authors, dates and comments from blog posts, we procede by building extraction rules from the data given in the blog's web feed.
-The idea is to provide a set of \emph{training data} to the algorithm, pairs of HTML page and target content, which are then used to build an extraction rule capable of locating the target content on each HTML page.
+To extract content from blog posts, we procede by building extraction rules from the data given in the blog's web feed.
+The idea is to use a set of \emph{training data}, pairs of HTML page and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.
 
 % input from observations.
-Observation \ref{havefeedAssum} allows the crawler to obtain input for the algorithm: each entry of the web feed provides a link to the corresponding we page as well as potential target content such as the article, it's title, authors and publication date.
-Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.
+Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding we page as well as target content such as the article, it's title, authors and publication date.
+Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.
 
@@
 Algorithm \ref{extractionAlgo} show the generic procedure we use to build extraction rules.
-The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all extraction rules the best one with respect to a certain \code{ScoreFunction}.
-The rule which was the most frequently a \emph{best rule} is then returned.
+The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}.
+The rule which is most frequently a \emph{best rule} is then returned.
 
@@
 One might notice that each \emph{best rule} computation is independent and operates on a different input pairs.
-Therefore algorithm \ref{extractionAlgo} \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.
+This implies that Algorithm \ref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.
 
 % abs, plan
-Functions in algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section.
-\ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article and title extraction.
+Functions in Algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section.
+\ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
 In \ref{timecomplexityandlinearreformulation} we analyses time complexity of Algorithm \ref{extractionAlgo} and give a linear time reformulation using dynamic programing.
@@
 We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree.
-\code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better blog consistency than absolute paths.
-For these reasons, the \coderef{allrulesAlgo} function only returns the best rule for each node:
+\code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better consistency than absolute paths over pages of a blog.
+For these reasons, the \coderef{allrulesAlgo} function returns a single rule per node:
 
@@
 Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process.
-When targeting articles, extraction rules are scored with a string similarity function comparing extracted and target strings.
-We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge, is the only string similarity algorithm fulfilling the following criteria:
+When targeting articles, extraction rules are scored with a string similarity function comparing the extracted and the target strings.
+We chose the Sørensen–Dice coefficient similarity \cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:
 
 \begin{enumerate}
-  \item\label{wordorderProp} Has low sensitivity to word ordering
-  \item\label{lengthProp} Has low sensitivity to length variations
-  \item\label{linearProp} Runs in linear time
+  \item\label{wordorderProp} Has low sensitivity to word ordering,
+  \item\label{lengthProp} Has low sensitivity to length variations,
+  \item\label{linearProp} Runs in linear time.
 \end{enumerate}
 
-Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post article.
-Table \ref{similarityTable} gives examples to illustrate how these two properties are fulfilled by the Sørensen–Dice coefficient similarity but do not hold for \emph{edit distance} based similarities such as the Levenshtein\cite{levenshtein1966} similarity.
+Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
+Table \ref{similarityTable} gives examples to illustrate how these two properties are fulfilled by the Sørensen–Dice coefficient similarity but do not hold for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.
 
@@
 At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string.
-To overcome this limitation and implement \emph{memoization} over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams.
-This way we avoid serializing HTML subtrees for each bigram computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.
+To overcome this limitation and implement \emph{memoization} over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams.
+This way we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.
 
@@
 To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.
-As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigram unions per inner loop iteration tends to one.
-Each \emph{quotient of similarity} computation requires one bigram intersection and three bigram length computations.
-Over a finite alphabet (we used printable ASCII), bigram sizes have bounded size and each of these operations takes constant time.
+As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one.
+Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations.
+Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.
 

### 2013-12-04 tex/3-algorithms.tex
up

@@
 Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
-Table \ref{similarityTable} gives examples to illustrate how these two properties are fulfilled by the Sørensen–Dice coefficient similarity but do not hold for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.
+Table \ref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.
 
@@
 % into: algo 1 defined
-With \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) functions defined, the definition of algorithm \ref{extractionAlgo} for article extraction is completed.
-We now proceed with a time complexity analysis which will show that this aproach has a quadratic running time.
+With functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) defined, the definition of Algorithm \ref{extractionAlgo} for article extraction is completed.
+We now proceed with a time complexity analysis.
 
@@
 Therefore, the body of the inner loop will be executed \Oof{n} times.
-Because the extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.
+Because each extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.
 
 % linear reformulation
-We now present Algorithm \ref{linearAlgo}, linear time reformulation of Algorithm \ref{extractionAlgo} for article extraction using dynamic programming.
-While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams.
+We now present Algorithm \ref{linearAlgo}, a linear time reformulation of Algorithm \ref{extractionAlgo} for article extraction using dynamic programming.
+While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams.
 For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function.
 At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string.
-To overcome this limitation and implement \emph{memoization} over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams.
-This way we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.
+To overcome this limitation and implement \emph{memoization} over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree and computes node bigrams from their children bigrams.
+This way, we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.
 
@@
 % proof
-With bigrams computed in a dynamic programming manner, the cumulated time needed to compute \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear.
-To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.
+With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear.
+To conclude the proof that Algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.
 As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Variations for authors, dates, comments}
@@
 % intro
-Using string similarity as only score measurement leads to poor performances on authors and dates extraction and is not suitable for comment extraction.
+Using string similarity as only score measurement leads to poor performances on authors and dates extraction, and is not suitable for comment extraction.
 This subsection presents variations of the previously presented \code{ScoreFunction} which address issues of these other contents.
@@
 % authors
-The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, which results in several rules with maximum \coderef{similarityAlgo} score.
+The case of authors is problematic because authors' names often appears in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score.
 The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
@@
 Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages.
-Our solution for dates extraction extends authors \code{ScoreFunction} by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original \emph{target} date obtained from the web feed.
+Our solution for dates extraction extends the \code{ScoreFunction} for authors by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original date obtained from the web feed.
 For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
-We use a total of 8 target date formats that was empirically built during our experiments.
-While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is tolerant to small variations.
 So far we do not support dates in multiple languages, but adding new target formats base and languages detection would be a simple extension of our date extraction algorithm.
@@
 Comments are usually available in separate web feeds, one per blog post.
-Similarly to blog feeds, comment feeds have a limited number of entries, and in case a blog post has more comments than the ones appearing in the feed, comments have to be extracted from the post web page.
+Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page.
 To do so we use the following \code{ScoreFunction}:
 \begin{itemize}
-  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score.
+  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
   \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
@@
 % rush some time complexity analysis
-Regarding time complexity, computing the \emph{tree distance} of all nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity.
-While evaluating rules for comments extraction requires more a expensive algorithm, the proportion of candidates left after filter out comment rules with an insufficient number of results was very low in practice.
-Analog  reformulations to the one explained in \ref{timecomplexityandlinearreformulation} can be applied for each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.
+Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity.
+While scoring rules for comments extraction requires a more expensive algorithm, the proportion of candidates left after filter out rules with an insufficient number of results is very low in practice.
+Analog reformulations to the one done with Algorithm \ref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-04 tex/4-techniques.tex
Small changes after skype call + end of algorithms section.
up

@@
 While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content.
-In such cases, traditional HTML based crawled do not see web pages as they would be presented to a human visitor and might therefore be obsolete for data extraction.
+In such cases, traditional HTML based crawled do not see web pages as they are presented to a human visitor and might therefore be obsolete for data extraction.
 
@@
 Less commonly, some blogs are fully rendered using JavaScript.
-When loading such website, the web browser will not receive the page content as an HTML file, but will instead have execute JavaScript code to download and display the page content.
-One example can be found on the Blogger platforms which provides as one of its default templates the \emph{Dynamic Views} which use this mechanism \cite{antinharasymiv2011}.
+When loading such website, the web browser will not receive the page content as an HTML file, but will instead have to execute JavaScript code to download and display the page content.
+The Blogger platforms provides as a default templates the \emph{Dynamic Views}, which use this mechanism \cite{antinharasymiv2011}.
 
@@
 The JavaScript rendering is done as the very first step of web page processing.
-Extracting blog post content, comments or medias therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.
+Extracting blog post articles, comments or medias therefore works equally well on blogs with JavaScript generated content and traditional HTML-only blogs.
 
 % Click click scripting
-When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons.
+When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} buttons.
 As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded.
-Paths to Disqus and LiveFyre \emph{show more} buttons were manually obtained and are the only non-generic element of the extraction stack which will require human intervention to maintain and extend to other commenting platforms.
+Paths to Disqus and LiveFyre \emph{show more} buttons were manually obtained and are the only non-generic element of our extraction stack which will require human intervention to maintain and extend to other commenting platforms.
 
@@
 Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog.
-After beeing downloaded and identified as blog posts (details in subsection \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
+After beeing downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
 \begin{enumerate}[noitemsep]
@@
   \item Download medias
-  \item Propagate resulting records to the Invenio back-end
+  \item Propagate resulting records to the back end
 \end{enumerate}
-This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity.
-Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.
+This pipeline design provides great modularity. Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.
 
@@
 % blog post identification
-Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner.
+Given an entry point to a website, the default Scrapy behavior looks over all pages of the same domain in a \emph{last-in-first-out} manner.
 The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post.
@@
 This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur).
-In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.
+In practice this assumption held for all blog platforms we encountered and seems to be a common practice among web developer.
 
 % download priority heuristic
-In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog post identification mechanism is not sufficient.
-Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog post pages to search for additional blog posts.
-To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm.
+In order to efficiently deal with blogs with a large number of non-blog-post pages, this \emph{blog post identification} mechanism is not sufficient.
+Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog-post pages to search for additional blog posts.
+To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined by a simple machine learning algorithm.
 Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain.
-This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visit next.
-Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions.
+This estimated number of links are then used as \emph{download priorities} to decide the best URL to visit next.
+Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data will then be taken into account during future predictions.
 This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.
@@
 When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind\cite{thereactivemanifesto2013}.
-At the time of writing we did not had the chance to work on the deployment of the BlogForever project on a distributed environment.
-However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.
+The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.
 
 To achieve this property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
-Indeed, from a high level viewpoint, these two components are \emph{purely functional}:
+From a high level viewpoint, these two components are \emph{purely functional}:
 %
@@
 Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset.
-By delegating all shared mutable state to the backend system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.
+By delegating all shared mutable state to the back end system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.

### 2013-12-05 tex/0-abstract.tex
Fix some todos
Minor fixes, add main.pdf under version control.

@@
-Blogs are a dynamic communication medium which has been widely established on the web. The BlogForever project has developed an innovative system to harvest, preserve, manage and reuse blog content.
+Blogs are a dynamic communication medium which has been widely established on the web.
+The BlogForever project has developed an innovative system to harvest, preserve, manage and reuse blog content.
 This paper presents a key component of the BlogForever platform, the web crawler.
@@
 This approach is leading to a scalable blog data extraction process.
-Furthermore, we show how we integrate a web browser into the web harvesting process in order to address the data extraction from blogs which use rapidly evolving technologies such as JavaScript generated web content.
+Furthermore, we show how we integrate a web browser into the web harvesting process in order to support the data extraction from blogs with JavaScript generated content.

### 2013-12-05 tex/4-techniques.tex
Minor fixes, add main.pdf under version control.

@@
 
-Our crawler is built on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling.
+Our crawler is built on top of Scrapy \cite{scrapy2013}, an open source Python framework for web crawling.
 Scrapy provide an elegant and modular architecture illustrated in Figure~\ref{architecture}.
@@
 \subsection{Scalability}
-When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind\cite{thereactivemanifesto2013}.
+When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind \cite{thereactivemanifesto2013}.
 The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.

### 2013-12-05 tex/5-evaluation.tex
Minor fixes, add main.pdf under version control.

@@
 Our evaluation will be articulated in two parts.
-Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extracting content from web articles.
-The comparison will show that our blog targeted solution has better performances both in term of running time and success rates.
+Firstly, we will compare the article extraction procedure presented in section \ref{algorithms} with three open source projects capable of extracting content and title of web articles.
+The comparison will show that our blog targeted solution has better performances both in term of success rate and running time.
 Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code.
@@
 \subsection{Extraction success rates}
-To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{python-readability2011}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{goose2012}.
+To evaluate post article and title extraction we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}.
 These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
 
-Table \ref{precisionTable} shows extraction success rates of content and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.
+Table \ref{precisionTable} shows extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.
 An extraction was considered successful when the returned string is a least 0.5 similar to the reference string, with respect to the Sørensen–Dice coefficient similarity.
+\TODO{fix 0.5...}
 
@@
 
-On our test-set algorithm~\ref{extractionAlgo} outperformed the concurrence by 4.9\% margin on content extraction and a 10.1\% margin on title extraction.
+On our test-set Algorithm~\ref{extractionAlgo} outperformed the concurrence by 4.9\% on article extraction and 10.1\% on title extraction.
 It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages.
 Contrariwise, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages.
-Therefore, results showed in table \ref{precisionTable} should not be interpreted as general evaluation of quality of the different projects, but simply mean that our approach is more suitable when working with blogs.
+Therefore, results showed in table \ref{precisionTable} should not be interpreted as general quality evaluation of the different projects, but simply show that our approach is more suitable when working with blogs.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Content extraction running times}
+\subsection{Article extraction running times}
 
 % running time eval, scalability with size of blogs
-In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure.
-The main point of interest will be the scalability of extraction procedures as the number of processed pages increases.
-This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published data on a blog.
+In addition to the quality of the extracted data we also evaluated the running time of the extraction procedures.
+The main point of interest will be the scalability of extraction procedures as the number of posts in the processed blog increases.
+This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published content on a blog.
 
 % setup
-Our measurements were made with garbage collector disabled on a otherwise idle core of an \emph{Intel Core i7-3770 3.4 GHz} processor.
+Our measurements were made with garbage collector disabled on an otherwise idle core of an \emph{Intel Core i7-3770 3.4 GHz} processor.
 Experimental data was obtained by taking the median of 11 mesurements.
@@
 
-Figure 2 shows the cumulated time spent on each content extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of process blog posts on the \surl{http://quantumdiaries.org/} website.
+Figure 2 shows the cumulated time spent on each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of process blog posts on the \surl{http://quantumdiaries.org/} website.
 

### 2013-12-06 tex/3-algorithms.tex
Update 3-algorithms.tex

@@
 % input from observations.
-Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding we page as well as target content such as the article, it's title, authors and publication date.
+Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, it's title, authors and publication date.
 Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

### 2013-12-06 tex/3-algorithms.tex
Update 3-algorithms.tex

--- 2013-12-04 tex/3-algorithms.tex
@@
 % input from observations.
-Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding we page as well as target content such as the article, it's title, authors and publication date.
+Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, its title, authors and publication date.
 Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.
@@
 % textual pseudocode
-Algorithm \ref{extractionAlgo} show the generic procedure we use to build extraction rules.
+Algorithm \ref{extractionAlgo} shows the generic procedure we use to build extraction rules.
 The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}.
@@
 \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
-In \ref{timecomplexityandlinearreformulation} we analyses time complexity of Algorithm \ref{extractionAlgo} and give a linear time reformulation using dynamic programing.
+In \ref{timecomplexityandlinearreformulation} we analyse time complexity of Algorithm \ref{extractionAlgo} and give a linear time reformulation using dynamic programing.
 Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

### 2013-12-06 tex/4-techniques.tex
Update 4-techniques.tex

@@
 To support blogs with JavaScript generated content, we embed a full web browser into the crawler.
-After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities.
+After considering multiple options, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities.
 The JavaScript rendering is done as the very first step of web page processing.
@@
 The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post.
-Internally, this function uses a per blog regular expression constructed from web feed entry URLs.
+Internally, for each blog, this function uses a regular expression constructed from web feed entry URLs.
 This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur).

### 2013-12-06 tex/3-algorithms.tex
up

--- 2013-12-04 tex/3-algorithms.tex
@@
 % textual pseudocode
-Algorithm \ref{extractionAlgo} show the generic procedure we use to build extraction rules.
+\autoref{extractionAlgo} show the generic procedure we use to build extraction rules.
 The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}.
@@
 One might notice that each \emph{best rule} computation is independent and operates on a different input pairs.
-This implies that Algorithm \ref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.
+This implies that \autoref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.
 
 % abs, plan
-Functions in Algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section.
+Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section.
 \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
-In \ref{timecomplexityandlinearreformulation} we analyses time complexity of Algorithm \ref{extractionAlgo} and give a linear time reformulation using dynamic programing.
+In \ref{timecomplexityandlinearreformulation} we analyses time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing.
 Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
@@
 In our implementation, rules are queries in the XML Path Language (XPath).
-Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}.
+Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in \autoref{extractionAlgo}.
 We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree.
@@
 Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
-Table \ref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.
+\autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.
 
@@
 % into: algo 1 defined
-With functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) defined, the definition of Algorithm \ref{extractionAlgo} for article extraction is completed.
+With functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) defined, the definition of \autoref{extractionAlgo} for article extraction is completed.
 We now proceed with a time complexity analysis.
@@
 % linear reformulation
-We now present Algorithm \ref{linearAlgo}, a linear time reformulation of Algorithm \ref{extractionAlgo} for article extraction using dynamic programming.
+We now present \autoref{linearAlgo}, a linear time reformulation of \autoref{extractionAlgo} for article extraction using dynamic programming.
 While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams.
-For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function.
+For instance, when evaluating the extraction rule for the HTML root node, \autoref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function.
 At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string.
-To overcome this limitation and implement \emph{memoization} over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree and computes node bigrams from their children bigrams.
+To overcome this limitation and implement \emph{memoization} over the bigrams computations, \autoref{linearAlgo} uses a post-order traversal of the HTML tree and computes node bigrams from their children bigrams.
 This way, we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.
@@
 With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear.
-To conclude the proof that Algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.
+To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.
 As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one.
@@
   \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
-  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
+  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
 \end{itemize}
@@
 While scoring rules for comments extraction requires a more expensive algorithm, the proportion of candidates left after filter out rules with an insufficient number of results is very low in practice.
-Analog reformulations to the one done with Algorithm \ref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.
+Analog reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-06 tex/5-evaluation.tex
up

@@
 Our evaluation will be articulated in two parts.
-Firstly, we will compare the article extraction procedure presented in section \ref{algorithms} with three open source projects capable of extracting content and title of web articles.
+Firstly, we will compare the article extraction procedure presented in \autoref{algorithms} with three open source projects capable of extracting content and title of web articles.
 The comparison will show that our blog targeted solution has better performances both in term of success rate and running time.
@@
 
-% All experiments are reproducable by following instructions on the \emph{evaluation} branch of the BlogForever-Crawler version control **.
-% https://github.com/OlivierBlanvillain/blogforever-crawler-publication
+Experiments were made on \emph{Debian GNU/Linux 7.2} with \emph{Python 2.7} on an \emph{Intel Core i7-3770 3.4 GHz} processor.
+Timing measurements used a single otherwise idle core with garbage collector disabled.
+The Git repository of this paper \cite{blogforever-crawler-publication} \TODO{cite blogforever-crawler-publication} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.
 
@@
 \subsection{Extraction success rates}
-To evaluate post article and title extraction we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}.
+To evaluate post article and title extraction we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively.
 These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
+\autoref{precisionTable} shows extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.
 
-Table \ref{precisionTable} shows extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.
-An extraction was considered successful when the returned string is a least 0.5 similar to the reference string, with respect to the Sørensen–Dice coefficient similarity.
-\TODO{fix 0.5...}
+% An extraction was considered successful when the returned string is a least 0.5 similar to the reference string, with respect to the Sørensen–Dice coefficient similarity.
 
@@
 
-On our test-set Algorithm~\ref{extractionAlgo} outperformed the concurrence by 4.9\% on article extraction and 10.1\% on title extraction.
+On our test-set \autoref{extractionAlgo} outperformed the concurrence by 4.9\% on article extraction and 10.1\% on title extraction.
 It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages.
 Contrariwise, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages.
-Therefore, results showed in table \ref{precisionTable} should not be interpreted as general quality evaluation of the different projects, but simply show that our approach is more suitable when working with blogs.
+Therefore, results showed in \autoref{precisionTable} should not be interpreted as general quality evaluation of the different projects, but simply show that our approach is more suitable when working with blogs.
 
@@
 % setup
-Our measurements were made with garbage collector disabled on an otherwise idle core of an \emph{Intel Core i7-3770 3.4 GHz} processor.
-Experimental data was obtained by taking the median of 11 mesurements.
-On this setup we obtained very low standard deviations on the order of 2 milliseconds which are therefor
+Experimental data was obtained by taking the arithmetic mean over 10 measurements, which we believe to be significant given that each result has a standard deviations on the order of 2 milliseconds.
+\comment{Do I have to justify the arithmetic mean?
+If yes, this could do: \surl{http://dl.acm.org/citation.cfm?id=5673}}
 
-\TODO{make a paragraph with linux, python and processor}
+\autoref{runningtime} shows the cumulated time spent on each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed of \surl{http://quantumdiaries.org/}.
 
-confidence intervals .. in .. as (max 2ms)
-
-Figure 2 shows the cumulated time spent on each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of process blog posts on the \surl{http://quantumdiaries.org/} website.
-
-% result (plot)
 \input{runningtimeFigure.tex}
 
-% discussion: again, we are "cheating" on scalability
+Past the initial computations, the cost to extract an article with our approach are almost null.
+This is a consequence of having a blog aware, rule based algorithm.
+If you recall the procedure presented in \autoref{algorithms}, the central idea was to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
+On this example, time cost of parsing a new blog post and using extraction rules is in the order of 3 milliseconds, which is not visible on the scale of \autoref{runningtime}.
+The three other evaluated solutions do not function this way: each blog post is processed as a new and independent input, leading to a close to linear running times.
 
-% discussion: raw perf (15 feed entry),
-% discussion: (c++ vs java vs scala vs go \cite{hundt2011})Implemented in Javascript, Java and Scala respectively
-% YUNO algo 2
+In \autoref{runningtime}, the vertical dashed line at 15 processed blog posts represents a suitable point of comparisons for processing time per blog posts.
+Indeed, as the test blog's web feed contains 15 entries, the time spent on processing the first blog post also includes the processing time of the web feed and it's 15 entries.
+\comment{Is this clear?}That being said, comparing raw performances of different algorithm implemented with different programming languages is not very informative given the high variations of running times observes across languages for identical algorithms \cite{hundt2011}.
+
+% python x23 just-in-time compilation speed up http://dl.acm.org/citation.cfm?id=2069181
 

### 2013-12-06 tex/6-conclusion-and-future-work.tex
Add a few ideas from reading the WebDataExtraction,ApplicationsAndTechniques survey, add sripts to run and score theextraction methods.
up

@@
 \section{Conclusion and Future Work}
-\begin{itemize}
+% What we presented, what we solved
+In this paper, we presented the internals of the BlogForever web crawler.
+Its central article extraction procedure based on extraction rules generation was introduced along with theoretical and empirical evidences validating the approach.
+Simple adaptation of this procedure allowed to extract different types of contents, including authors, dates and comments.
+In order to support
+
+blogs with JavaScript generated content
+
+We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.
+
+% Future work
+
+Plan:
+\begin{enumerate}
   \item Recap the problem and the objective
@@
   \item Hint for future work
-\end{itemize}
+\end{enumerate}
+
+Content:
+\begin{enumerate}
+  \item Web pages dynamically generated after filling a web form/doing some user action. This is not automated atm.
+  \item Spacial reasoning (we already have the page rendered w PhantomJS)
+  \item Low level PhantomJS hooks
+  \item Tree edit distance matching
+\end{enumerate}

### 2013-12-06 tex/3-algorithms.tex

@@
 % textual pseudocode
-\autoref{extractionAlgo} show the generic procedure we use to build extraction rules.
+\autoref{extractionAlgo} shows the generic procedure we use to build extraction rules.
 The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}.
@@
 \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
-In \ref{timecomplexityandlinearreformulation} we analyses time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing.
+In \ref{timecomplexityandlinearreformulation} we analyse time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing.
 Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

### 2013-12-06 tex/3-algorithms.tex
End of eval + conclusion future works.

@@
 % html extraction is not trival
-Extracting metadata and content from html documents is a challenging task.
-Standards and format recommendations have been around for quite some time, strictly specifying how html documents should be organised \cite{w3c2013}.
+Extracting metadata and content from HTML documents is a challenging task.
+Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}.
 For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page \cite{w3c2002}.
-More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages \cite{brianwilson2008}, and more than 95\% of pages do not pass html validation \cite{brianwilson2008-a}.
-Under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.
+More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}.
+Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
 
@@
 % per blog procedure, related work
-To extract content from blog posts, we procede by building extraction rules from the data given in the blog's web feed.
+To extract content from blog posts, we proceed by building extraction rules from the data given in the blog's web feed.
 The idea is to use a set of \emph{training data}, pairs of HTML page and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.
@@
 \autoref{extractionAlgo} shows the generic procedure we use to build extraction rules.
-The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}.
+The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute, out of all possible extraction rules, the best one with respect to a certain \code{ScoreFunction}.
 The rule which is most frequently a \emph{best rule} is then returned.
@@
 % embarrassingly parallel
-One might notice that each \emph{best rule} computation is independent and operates on a different input pairs.
+One might notice that each \emph{best rule} computation is independent and operates on a different input pair.
 This implies that \autoref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.
@@
 % into: algo 1 defined
-With functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) defined, the definition of \autoref{extractionAlgo} for article extraction is completed.
+The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is completed.
 We now proceed with a time complexity analysis.
@@
 To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.
-As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one.
+As the number of edges in a tree is one less than the number of nodes, the \emph{amortized} number of bigrams unions per inner loop iteration tends to one.
 Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations.
@@
 % authors
-The case of authors is problematic because authors' names often appears in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score.
-The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
+The case of authors is problematic because authors' names often appear in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score.
+The heuristic we use to get around this issue consists in adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
 This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.
@@
 Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity.
-While scoring rules for comments extraction requires a more expensive algorithm, the proportion of candidates left after filter out rules with an insufficient number of results is very low in practice.
+Scoring rules for comments extraction requires a more expensive algorithm.
+However, this is compensated by the fact that the proportion of candidates left, after filter out rules not returning enough results, is very low in practice.
 Analog reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-06 tex/4-techniques.tex
up
End of eval + conclusion future works.

@@
 We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
-The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case.
-Finally we will talk about deployment to scalable, fault resilient distributed architecture.
+The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
+Finally we will talk about the design choices we made in view of large scale deployment.
 
@@
 Our crawler is built on top of Scrapy \cite{scrapy2013}, an open source Python framework for web crawling.
-Scrapy provide an elegant and modular architecture illustrated in Figure~\ref{architecture}.
+Scrapy provide an elegant and modular architecture illustrated in \autoref{architecture}.
 Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.

### 2013-12-06 tex/6-conclusion-and-future-work.tex
End of eval + conclusion future works.

@@
 Simple adaptation of this procedure allowed to extract different types of contents, including authors, dates and comments.
-In order to support
-
-blogs with JavaScript generated content
-
+In order to support rapidly evolving web technologies such as JavaScript generated content, the crawler uses a web browser to render pages before processing.
 We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.
 
-% Future work
+% Future work, hybrid algos
+Future work could investigate \emph{hybrid} extraction algorithms to try to achieve near 100\% success rates.
+Even if overall our approach obtains better performs, there are few cases where other techniques managed to extract data where we did not.
+This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performances.
 
-Plan:
-\begin{enumerate}
-  \item Recap the problem and the objective
-  \item Summarize how've solved it
-  \item Mention challenges and problems
-  \item Hint for future work
-\end{enumerate}
+% Deployment on a distributed architecture  
+Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system.
+This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck which benefits from the use of multiple Internet access points.
+We intend to explore this opportunities in our future work.
 
-Content:
-\begin{enumerate}
-  \item Web pages dynamically generated after filling a web form/doing some user action. This is not automated atm.
-  \item Spacial reasoning (we already have the page rendered w PhantomJS)
-  \item Low level PhantomJS hooks
-  \item Tree edit distance matching
-\end{enumerate}
+% Low level PhantomJS hooks
+% I guess two future works is enough...
+
+% Conclude the conclude
+To open up further possibilities, the crawler presented in this paper is available under the MIT license from the project's website.
+\TODO{cite \\https://github.com/OlivierBlanvillain/blogforever-crawler or http://blogforever.eu/ ?}.

### 2013-12-07 tex/4-techniques.tex
Minor

@@
 % Motivation
-In our experiments crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation.
+In our experiments whilst crawling the blog sphere, we encountered several blogs were data was missed because of the lack of JavaScript interpretation.
 The most frequent cases where blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services.
-These tools are very handy to setup for web-masters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in each target page.
+For web-masters, these tools are very handy to setup because the entire comments infrastructure is externalized and the setup essentially comes down to including a JavaScript snippet in each target page.
 Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments.
 Less commonly, some blogs are fully rendered using JavaScript.
-When loading such website, the web browser will not receive the page content as an HTML file, but will instead have to execute JavaScript code to download and display the page content.
-The Blogger platforms provides as a default templates the \emph{Dynamic Views}, which use this mechanism \cite{antinharasymiv2011}.
+When loading such websites, the web browser will not receive page contents as HTML files, but will instead have to execute JavaScript code to download and display page contents.
+The Blogger platform provides as a default template the \emph{Dynamic Views}, which uses this mechanism \cite{antinharasymiv2011}.
 
@@
 After considering multiple options, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities.
-The JavaScript rendering is done as the very first step of web page processing.
-Extracting blog post articles, comments or medias therefore works equally well on blogs with JavaScript generated content and traditional HTML-only blogs.
+The JavaScript rendering is the very first step of web page processing.
+Therefore, Extracting blog post articles, comments or medias works equally well on blogs with JavaScript generated content and traditional HTML-only blogs.
 
@@
 As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded.
-Paths to Disqus and LiveFyre \emph{show more} buttons were manually obtained and are the only non-generic element of our extraction stack which will require human intervention to maintain and extend to other commenting platforms.
+Paths to Disqus and LiveFyre \emph{Show More} buttons were manually obtained.
+They constitute the only non-generic element of our extraction stack which will require human intervention to maintain and extend to other commenting platforms.
 
@@
 Our crawler is built on top of Scrapy \cite{scrapy2013}, an open source Python framework for web crawling.
-Scrapy provide an elegant and modular architecture illustrated in \autoref{architecture}.
+Scrapy provides an elegant and modular architecture illustrated in \autoref{architecture}.
 Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.
 
-Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog.
+Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog.
 After beeing downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
@@
 \end{enumerate}
-This pipeline design provides great modularity. Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.
+This pipeline design provides great modularity. Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.
 
@@
 This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur).
-In practice this assumption held for all blog platforms we encountered and seems to be a common practice among web developer.
+In practice this assumption held for all blog platforms we encountered and seems to be a common practice amongst web developers.
 
@@
 Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog-post pages to search for additional blog posts.
-To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined by a simple machine learning algorithm.
+To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities of new URLs are determined by a simple machine learning algorithm.
+%
 Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain.
@@
 Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data will then be taken into account during future predictions.
-This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.
+%
+This mechanism has shown to be mandatory for blogs hosting on a single domain a large number of non-blog web pages, such as a forum or a wiki.
 

### 2013-12-07 tex/5-evaluation.tex
End of eval + conclusion future works.
Minor

@@
 Experiments were made on \emph{Debian GNU/Linux 7.2} with \emph{Python 2.7} on an \emph{Intel Core i7-3770 3.4 GHz} processor.
-Timing measurements used a single otherwise idle core with garbage collector disabled.
+Timing measurements used a single dedicated core with garbage collector disabled.
 The Git repository of this paper \cite{blogforever-crawler-publication} \TODO{cite blogforever-crawler-publication} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.
@@
 In \autoref{runningtime}, the vertical dashed line at 15 processed blog posts represents a suitable point of comparisons for processing time per blog posts.
-Indeed, as the test blog's web feed contains 15 entries, the time spent on processing the first blog post also includes the processing time of the web feed and it's 15 entries.
+Indeed, as the test blog's web feed contains 15 blog posts, the time spent on processing the first blog post also includes the processing time of the web feed and it's 15 entries.
 \comment{Is this clear?}That being said, comparing raw performances of different algorithm implemented with different programming languages is not very informative given the high variations of running times observes across languages for identical algorithms \cite{hundt2011}.

### 2013-12-09 tex/4-techniques.tex
Remove TODO on ML details.

@@
 Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog-post pages to search for additional blog posts.
-To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities of new URLs are determined by a simple machine learning algorithm.
-%
-Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain.
-This estimated number of links are then used as \emph{download priorities} to decide the best URL to visit next.
-Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data will then be taken into account during future predictions.
-%
-This mechanism has shown to be mandatory for blogs hosting on a single domain a large number of non-blog web pages, such as a forum or a wiki.
+To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities of new URLs are determined by a machine learning system.
 
-\TODO{Give more details: this function implements a string score predictor using a the Distance-Weighted k-Nearest-Neighbor classifier, as described in \cite{dudani1976} http://ieeexplore.ieee.org/xpls/abs\_all.jsp?arnumber=5408784 This predictor can be used as an active machine learning algorithm by feeding it little by little with new url/score as they are discovered.}
+% Distance-Weighted k-Nearest-Neighbor
+The idea is to give a high priority to URLs which are believed to point to pages with links to blog post.
+These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}.
+To *lighten* our explanations we first introduce the following notation: let $L(u)$ be the number of links to blog posts contained in a page with URL $u$.
+Each time a page is downloaded, it's URL $u$ and $L(u)$ are given to the machine learning system as training data.
+When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$.
+The value of $L(v)$ is estimated by doing a weighted average on the values of the $k$ URLs most similar to $v$.
 
@@
 \subsection{Scalability}
-When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind \cite{thereactivemanifesto2013}.
+When aiming to work with a large number of inputs, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}.
 The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.
 
-To achieve this property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
+\TODO{To achieve this} property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
 From a high level viewpoint, these two components are \emph{purely functional}:

### 2013-12-09 tex/3-algorithms.tex
Minor
Solve some \cite TODOs.

@@
 \end{enumerate}
-Web feeds usually contain about 20 posts, often less than the total number of posts in blogs \cite{oita2010}.
+Web feeds usually contain about 20 blog posts, often less than the total number of posts in blogs \cite{oita2010}.
 Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in web feeds.
@@
 
-The Sørensen–Dice coefficient method operates by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:
+The Sørensen–Dice coefficient similarity algorithm operates by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:
 
@@
 % into: algo 1 defined
-The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is completed.
+The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is completed.
 We now proceed with a time complexity analysis.
@@
 % proof
-With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear.
+With bigrams computed in this dynamic programming manner, the overall time to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear.
 To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.

### 2013-12-09 tex/4-techniques.tex
Solve some \cite TODOs.

@@
   \centering
-  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
+  \includegraphics[width=0.47\textwidth]{scrapy_architecture}
   \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2013})}
@@
 These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}.
-To *lighten* our explanations we first introduce the following notation: let $L(u)$ be the number of links to blog posts contained in a page with URL $u$.
-Each time a page is downloaded, it's URL $u$ and $L(u)$ are given to the machine learning system as training data.
+Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$.
+Whenever a page is downloaded, it's URL $u$ and $L(u)$ are given to the machine learning system as training data.
 When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$.
-The value of $L(v)$ is estimated by doing a weighted average on the values of the $k$ URLs most similar to $v$.
+$L(v)$ is estimated by doing a weighted average on the values of the $k$ URLs most similar to $v$.
 
@@
 
-\TODO{To achieve this} property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
+To go in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
 From a high level viewpoint, these two components are \emph{purely functional}:
@@
 \end{equation*}
-Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset.
+%
+Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator.
 By delegating all shared mutable state to the back end system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.

### 2013-12-09 tex/5-evaluation.tex
Solve some \cite TODOs.

@@
 Timing measurements used a single dedicated core with garbage collector disabled.
-The Git repository of this paper \cite{blogforever-crawler-publication} \TODO{cite blogforever-crawler-publication} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.
+The Git repository of this paper \cite{repositoryofthispaper} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.
 

### 2013-12-09 tex/6-conclusion-and-future-work.tex
Solve some \cite TODOs.

@@
 % Conclude the conclude
-To open up further possibilities, the crawler presented in this paper is available under the MIT license from the project's website.
-\TODO{cite \\https://github.com/OlivierBlanvillain/blogforever-crawler or http://blogforever.eu/ ?}.
+To open up further possibilities, the crawler presented in this paper is available under the MIT license from the project's website \cite{blogforevercrawler}.

### 2013-12-09 tex/3-algorithms.tex
Merge Jake's comments.

@@
 
-This section explains in detail the algorithm we developed to extract blog posts' article and its variations for authors, dates and comments.
-Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog.
+This section explains in detail the algorithm we developed to extract blog posts article and its variations for authors, dates and comments.
+Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog\comment{"all posts of a blog" needs a better formulation.}.
 Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
@@
 More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure of pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
@@
 The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute, out of all possible extraction rules, the best one with respect to a certain \code{ScoreFunction}.
-The rule which is most frequently a \emph{best rule} is then returned.
+The rule which is most frequently the \emph{best rule} is then returned.
 
@@
 % abs, plan
-Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section.
+Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section.
 \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
@@
 First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
-As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument.
+As stated before, the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument.
 Therefore, the body of the inner loop will be executed \Oof{n} times.
@@
 % intro
-Using string similarity as only score measurement leads to poor performances on authors and dates extraction, and is not suitable for comment extraction.
-This subsection presents variations of the previously presented \code{ScoreFunction} which address issues of these other contents.
+Using string similarity as the only score measurement leads to poor performances on author and date extractions, and is not suitable for comment extraction.
+This subsection presents variations of the previously presented \code{ScoreFunction} which addresses issues of these other contents.
 
@@
 The case of authors is problematic because authors' names often appear in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score.
-The heuristic we use to get around this issue consists in adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
+The heuristic we use to get around this issue consists in adding a new component in the \code{ScoreFunction} for author extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
 This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.
@@
 % dates
-Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages.
-Our solution for dates extraction extends the \code{ScoreFunction} for authors by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original date obtained from the web feed.
+Dates are affected by the same duplication issue, as well as the inconsistency of format between web feeds and web pages.
+Our solution for date extraction extends the \code{ScoreFunction} for authors by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original date obtained from the web feed.
 For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
@@
 Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines.
-Comment contents are extracted first, which allows to narrow down the initial filtering by fixing a target number of comments.
+Comment contents are extracted first, which allows us to narrow down the initial filtering by fixing a target number of comments.
 
 % rush some time complexity analysis
-Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity.
-Scoring rules for comments extraction requires a more expensive algorithm.
+Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity.
+Scoring rules for comment extraction requires a more expensive algorithm.
 However, this is compensated by the fact that the proportion of candidates left, after filter out rules not returning enough results, is very low in practice.

### 2013-12-09 tex/4-techniques.tex
Merge Jake's comments.

@@
 % Introduction
-JavaScript is a widely used language for client-side web scripting.
+JavaScript is a widely used language for client-side scripting.
 While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content.
-In such cases, traditional HTML based crawled do not see web pages as they are presented to a human visitor and might therefore be obsolete for data extraction.
+In such cases, traditional HTML based crawlers do not see web pages as they are presented to a human visitor and might therefore be obsolete for data extraction.
 
@@
 Scrapy provides an elegant and modular architecture illustrated in \autoref{architecture}.
-Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.
+Several components can be plugged into Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing us to implement a different type of functionalities.
 
 Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog.
-After beeing downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
+After being downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
 \begin{enumerate}[noitemsep]
@@
   \item Extract comments
-  \item Download medias
+  \item Download media
   \item Propagate resulting records to the back end
@@
 This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur).
-In practice this assumption held for all blog platforms we encountered and seems to be a common practice amongst web developers.
+In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.
 
@@
 In order to efficiently deal with blogs with a large number of non-blog-post pages, this \emph{blog post identification} mechanism is not sufficient.
-Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog-post pages to search for additional blog posts.
+Indeed, after all pages identified as blog posts are processed, the crawler needs to download non-blog-post pages to search for additional blog posts.
 To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities of new URLs are determined by a machine learning system.
+This mechanism has shown to be mandatory for blogs hosting on a single domain a large number of non-blog web pages, such as a forum or a wiki.
 

### 2013-12-09 tex/5-evaluation.tex
Merge Jake's comments.

@@
 
-Experiments were made on \emph{Debian GNU/Linux 7.2} with \emph{Python 2.7} on an \emph{Intel Core i7-3770 3.4 GHz} processor.
-Timing measurements used a single dedicated core with garbage collector disabled.
+Experiments used \emph{Debian GNU/Linux 7.2}, \emph{Python 2.7} and an \emph{Intel Core i7-3770 3.4 GHz} processor.
+Timing measurements were made on a single dedicated core with garbage collector disabled.
 The Git repository of this paper \cite{repositoryofthispaper} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.

### 2013-12-10 tex/3-algorithms.tex
Minor corrections and comments in chapter 3

@@
 
-This section explains in detail the algorithm we developed to extract blog posts article and its variations for authors, dates and comments.
+This section explains in detail the algorithm we developed to extract blog posts articles \comment{should we explain here that article is the actual content (text) of a blog post?
+Or is it already clear enough?} as well as its variations for authors, dates and comments.
 Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog\comment{"all posts of a blog" needs a better formulation.}.
@@
 More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure of pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
@@
 % observations when working with blogs
-Having blogs as our target websites, we use the following observations which play a central role in the extraction process\Anote{observations}:
+Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
 \begin{enumerate}[label={(\arabic*)}]
@@
 \end{enumerate}
-Web feeds usually contain about 20 blog posts, often less than the total number of posts in blogs \cite{oita2010}.
-Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in web feeds.
+Web feeds usually contain about 20 blog posts, often less than the total number of posts in blogs \cite{oita2010}\comment{is this reference for the fact that feeds usually contain about 20 blog posts or for the fact that this number is often smaller than the total number of posts in a blog?}.
+Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in web feed.
 
@@
 To extract content from blog posts, we proceed by building extraction rules from the data given in the blog's web feed.
-The idea is to use a set of \emph{training data}, pairs of HTML page and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.
+The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.
 
 % input from observations.
-Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, its title, authors and publication date.
+Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, its title, authors and publication date.
 Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.
@@
 Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section.
-\ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
-In \ref{timecomplexityandlinearreformulation} we analyse time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing.
-Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
+Section \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
+In section \ref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give it a linear time reformulation using dynamic programing.
+Finally, section \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
 
@@
 In our implementation, rules are queries in the XML Path Language (XPath).
-Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in \autoref{extractionAlgo}.
-We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree.
-\code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better consistency than absolute paths over pages of a blog.
-For these reasons, the \coderef{allrulesAlgo} function returns a single rule per node:
+Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, providing the \code{Apply} function used in \autoref{extractionAlgo}.
+We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection using the absolute path in the HTML tree.
+\code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better consistency than absolute paths over pages of a blog\comment{this is an observation right?
+Maybe add something like have showd in our experiments...}.
+For these reasons\comment{there is a misscontinuation here.
+It's not for these reasons that we return a single rule per node.
+It's because we only need one rule per node.
+The rule is expressed in one of the three types mentioned above.}, the \coderef{allrulesAlgo} function returns a single rule per node:
 
@@
 Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process.
-When targeting articles, extraction rules are scored with a string similarity function comparing the extracted and the target strings.
+When targeting articles, extraction rules are scored\comment{scored has a different meaning here.
+Graded or sorted or something similar is more correct} with a string similarity function comparing the extracted strings with the target strings.
 We chose the Sørensen–Dice coefficient similarity \cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:
@@
 
-Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
+Properties \ref{wordorderProp} and \ref{lengthProp} are essential when we deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
 \autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.
@@
 % into: algo 1 defined
-The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is completed.
+The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is complet.
 We now proceed with a time complexity analysis.
@@
 % algo 1 is quadratic
-First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
+First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure, indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
 As stated before, the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument.
@@
 % intro
-Using string similarity as the only score measurement leads to poor performances on author and date extractions, and is not suitable for comment extraction.
-This subsection presents variations of the previously presented \code{ScoreFunction} which addresses issues of these other contents.
+Using string similarity as the only score measurement leads to poor performance on author and date extraction, and is not suitable for comment extraction.
+This subsection presents variations of the previously presented \code{ScoreFunction} which addresses issues of these other types of content.
 
@@
 The case of authors is problematic because authors' names often appear in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score.
-The heuristic we use to get around this issue consists in adding a new component in the \code{ScoreFunction} for author extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
-This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.
+The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for author extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
+This new component takes advantage of the positioning of a post's authors node which often is a direct child or shares its parent with the post content node.
 
@@
 For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
-So far we do not support dates in multiple languages, but adding new target formats base and languages detection would be a simple extension of our date extraction algorithm.
+So far we do not support dates in multiple languages, but adding new target formats base\comment{is the word base needed here?} and languages detection would be a simple extension of our date extraction algorithm.
 
@@
   \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
-  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
+  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as\comment{did you mean 'is a' instead of 'as'?} weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
 \end{itemize}
-Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines.
-Comment contents are extracted first, which allows us to narrow down the initial filtering by fixing a target number of comments.
+Our crawler executes this algorithm on each post with an overflow on its comment feed, thus supporting blogs with multiple commenting engines.
+The comment content is extracted first, allowing us to narrow down the initial filtering by fixing a target number of comments.
 
 % rush some time complexity analysis
-Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity.
-Scoring rules for comment extraction requires a more expensive algorithm.
-However, this is compensated by the fact that the proportion of candidates left, after filter out rules not returning enough results, is very low in practice.
-Analog reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.
+Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity.
+Scoring\comment{like before, Scoring should be Grading or Sorting or something like that} rules for comment extraction requires a more expensive algorithm.
+However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice.
+Similar reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.
+\comment{This last sentence might make the reader think: if they can be applied, they why didn't you apply them?}

### 2013-12-10 tex/4-techniques.tex
Minor corrections and comments in chapter 3

@@
 
-This section gives an overview of different techniques used in our crawler.
+This section gives an overview of the different techniques used in our crawler.
 We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
-The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
-Finally we will talk about the design choices we made in view of large scale deployment.
+The overall software architecture is then discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
+Finally we talk about the design choices we made in view of a large scale deployment.
 

### 2013-12-10 tex/3-algorithms.tex
Fix trival comments and respond to others.

@@
 This section explains in detail the algorithm we developed to extract blog posts articles \comment{should we explain here that article is the actual content (text) of a blog post?
-Or is it already clear enough?} as well as its variations for authors, dates and comments.
-Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog\comment{"all posts of a blog" needs a better formulation.}.
-Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
+Or is it already clear enough?}\TODO{I don't know.
+I used "blog post content" as "article + title + author + date + comments" in other sentences but it might be good to say somewhere that "blog post article" refers to the "core textual content of a blog post".} as well as its variations for authors, dates and comments.
+Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog \comment{"all posts of a blog" needs a better formulation.}Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
 
@@
 \end{enumerate}
-Web feeds usually contain about 20 blog posts, often less than the total number of posts in blogs \cite{oita2010}\comment{is this reference for the fact that feeds usually contain about 20 blog posts or for the fact that this number is often smaller than the total number of posts in a blog?}.
+Web feeds usually contain about 20 blog posts \cite{oita2010}, often less than the total number of posts in blogs.
 Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in web feed.
@@
 We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection using the absolute path in the HTML tree.
-\code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better consistency than absolute paths over pages of a blog\comment{this is an observation right?
-Maybe add something like have showd in our experiments...}.
+\code{id} attributes are expected to be unique, and \code{class} attributes have showed in our experiments to have better consistency than absolute paths over pages of a blog.
 For these reasons\comment{there is a misscontinuation here.
@@
 It's because we only need one rule per node.
-The rule is expressed in one of the three types mentioned above.}, the \coderef{allrulesAlgo} function returns a single rule per node:
+The rule is expressed in one of the three types mentioned above.}\TODO{The idea is that because there is such a strong hierarchy between the three rules (id > class > path), we only use "the best one".
+If it was not the case, we could also return 3 rules per node, which would triple the computation time.
+But I agree that it might not be very clear with "for these reasons"...}, the \coderef{allrulesAlgo} function returns a single rule per node:
 
@@
 Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process.
-When targeting articles, extraction rules are scored\comment{scored has a different meaning here.
-Graded or sorted or something similar is more correct} with a string similarity function comparing the extracted strings with the target strings.
+When targeting articles, extraction rules are scored \comment{scored has a different meaning here.
+Graded or sorted or something similar is more correct}\TODO{ranked?
+evaluated?
+We should rename ScoreFunction accordingly and propagate the change everywhere.} with a string similarity function comparing the extracted strings with the target strings.
 We chose the Sørensen–Dice coefficient similarity \cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:
@@
 For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
-So far we do not support dates in multiple languages, but adding new target formats base\comment{is the word base needed here?} and languages detection would be a simple extension of our date extraction algorithm.
+So far we do not support dates in multiple languages, but adding new target formats based on languages detection would be a simple extension of our date extraction algorithm.
 
@@
   \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
-  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as\comment{did you mean 'is a' instead of 'as'?} weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
+  \item Remaining rules are \TODO{scored} with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
 \end{itemize}
@@
 Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity.
-Scoring\comment{like before, Scoring should be Grading or Sorting or something like that} rules for comment extraction requires a more expensive algorithm.
+\TODO{Scoring} rules for comment extraction requires a more expensive algorithm.
 However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice.
-Similar reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.
-\comment{This last sentence might make the reader think: if they can be applied, they why didn't you apply them?}
+Analogous reformulations to the one done with \autoref{linearAlgo} can be straightforwardly applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-10 tex/4-techniques.tex
Minor corrections and comments on chapter 4

@@
 JavaScript is a widely used language for client-side scripting.
-While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content.
-In such cases, traditional HTML based crawlers do not see web pages as they are presented to a human visitor and might therefore be obsolete for data extraction.
+While some applications simply use it for aesthetics (menus, animations, \ldots), an increasing number of websites use JavaScript to download and display content.
+In such cases, traditional HTML based crawlers do not see\comment{instead of see, maybe interpret, understand, render?} web pages as they are presented to a human visitor\comment{coninuing the previous comment: ...as they are presented to a human visitor by a web browser} and might therefore be obsolete for data extraction.
 
 % Motivation
-In our experiments whilst crawling the blog sphere, we encountered several blogs were data was missed because of the lack of JavaScript interpretation.
-The most frequent cases where blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services.
-For web-masters, these tools are very handy to setup because the entire comments infrastructure is externalized and the setup essentially comes down to including a JavaScript snippet in each target page.
+In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation.
+The most frequent cases were blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services.
+For webmasters\comment{I think web-master is officially one word without the hyphen}, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
 Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments.
 Less commonly, some blogs are fully rendered using JavaScript.
-When loading such websites, the web browser will not receive page contents as HTML files, but will instead have to execute JavaScript code to download and display page contents.
-The Blogger platform provides as a default template the \emph{Dynamic Views}, which uses this mechanism \cite{antinharasymiv2011}.
+When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content.
+The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.
 
 % The solution
-To support blogs with JavaScript generated content, we embed a full web browser into the crawler.
-After considering multiple options, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities.
+To support blogs with JavaScript-generated content, we embed a full web browser into the crawler.
+After considering multiple options, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performance and scripting capabilities.
 The JavaScript rendering is the very first step of web page processing.
-Therefore, Extracting blog post articles, comments or medias works equally well on blogs with JavaScript generated content and traditional HTML-only blogs.
+Therefore, extracting blog post articles, comments or medias\comment{do you mean multimedia files?
+media is rather a concept in English and does not exist in plural} works equally well on blogs with JavaScript-generated content as well as on traditional HTML-only blogs.
 
 % Click click scripting
-When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} buttons.
+When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} button.
 As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded.
-Paths to Disqus and LiveFyre \emph{Show More} buttons were manually obtained.
-They constitute the only non-generic element of our extraction stack which will require human intervention to maintain and extend to other commenting platforms.
+Paths to Disqus and LiveFyre \emph{Show More} buttons are manually obtained.
+They constitute the only non-generic element of our extraction stack which requires human intervention to maintain and extend to other commenting platforms.
 
@@
 
-Our crawler is built on top of Scrapy \cite{scrapy2013}, an open source Python framework for web crawling.
+Our crawler is built on top of Scrapy \cite{scrapy2013}, an open-source Python framework for web crawling.
 Scrapy provides an elegant and modular architecture illustrated in \autoref{architecture}.
-Several components can be plugged into Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing us to implement a different type of functionalities.
+Several components can be plugged into the Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing us to implement a different type of functionality.
 
 Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog.
-After being downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
+After being downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
 \begin{enumerate}[noitemsep]
@@
   \item Extract comments
-  \item Download media
+  \item Download media\comment{as before, media is rather a concept. Should we replace with multimedia files?}
   \item Propagate resulting records to the back end
 \end{enumerate}
-This pipeline design provides great modularity. Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.
+This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.
 
@@
 % into
-In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog post identification} and \emph{download priority heuristic}.
+In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process down to the subsets of blog pages holding\comment{maybe replace "holding" with: "which are"} blog posts: \emph{blog post identification} and \emph{download priority heuristic}.
 
 % blog post identification
-Given an entry point to a website, the default Scrapy behavior looks over all pages of the same domain in a \emph{last-in-first-out} manner.
-The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post.
-Internally, for each blog, this function uses a regular expression constructed from web feed entry URLs.
-This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur).
-In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.
+Given an entry point to a website\comment{entry point == URL, right?
+Maybe clarify that here?}, the default Scrapy behavior looks over\comment{instead of "looks over" maybe "goes through" or "traverses" or "parses" or "looks at".
+Not sure, need some english-speaking person's opinion} all the pages of the same domain in a \emph{last-in-first-out} manner.
+The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not.
+Internally, for each blog, this function uses a regular expression constructed from the URLs found in the web feed for each entry\comment{this last sentence has been slightly rephrased.
+Please check that it still makes sense they way you want it.}.
+This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur).
+In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers\comment{is a reference needed here?}.
 
 % download priority heuristic
-In order to efficiently deal with blogs with a large number of non-blog-post pages, this \emph{blog post identification} mechanism is not sufficient.
-Indeed, after all pages identified as blog posts are processed, the crawler needs to download non-blog-post pages to search for additional blog posts.
-To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities of new URLs are determined by a machine learning system.
-This mechanism has shown to be mandatory for blogs hosting on a single domain a large number of non-blog web pages, such as a forum or a wiki.
+In order to efficiently deal with blogs that have a large number of pages which are not posts, the \emph{blog post identification} mechanism is not sufficient.
+Indeed, after all pages identified as blog posts are processed, the crawler needs to download all other pages to search for additional blog posts\comment{replace "non-blog-post" with "all other".
+Is that OK?}.
+To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities for new URLs are determined by a machine learning system.
+This mechanism has shown to be mandatory for blogs hosted on a single domain alongside large number of other types of web pages, such as those in forums or wikis.
 
 % Distance-Weighted k-Nearest-Neighbor
-The idea is to give a high priority to URLs which are believed to point to pages with links to blog post.
+The idea is to give high priority to URLs which are believed to point to pages with links to blog posts.
 These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}.
 Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$.
-Whenever a page is downloaded, it's URL $u$ and $L(u)$ are given to the machine learning system as training data.
+Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data.
 When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$.
-$L(v)$ is estimated by doing a weighted average on the values of the $k$ URLs most similar to $v$.
+$L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$\comment{rephrased this last sentence slightly.
+Please make sure that it still makes sense.}.
 
@@
 \subsection{Scalability}
-When aiming to work with a large number of inputs, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}.
-The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.
+When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}.
+The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.
 
-To go in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
-From a high level viewpoint, these two components are \emph{purely functional}:
+Heading in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
+From a high-level point of view, these two components are \emph{purely functional}:
 %
@@
 %
-Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator.
-By delegating all shared mutable state to the back end system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.
+where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator.
+By delegating all shared mutable state to the back end system (Invenio's database)\comment{this is the 1st mention of Invenio.
+Make sure to mention in the Introduction, or remove from here as well.}, web crawler instances can be added, removed and used interchangeably.

### 2013-12-10 tex/4-techniques.tex
Fix/respond to all comments.

@@
 While some applications simply use it for aesthetics (menus, animations, \ldots), an increasing number of websites use JavaScript to download and display content.
-In such cases, traditional HTML based crawlers do not see\comment{instead of see, maybe interpret, understand, render?} web pages as they are presented to a human visitor\comment{coninuing the previous comment: ...as they are presented to a human visitor by a web browser} and might therefore be obsolete for data extraction.
+In such cases, traditional HTML based crawlers do not see\comment{instead of see, maybe interpret, understand, render?}\TODO{I think I like the "see" better, even if it's informal it really transmits primary motivation for this JS rendering.} web pages as they are presented to a human visitor by a web browser, and might therefore be obsolete for data extraction.
 
@@
 The most frequent cases were blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services.
-For webmasters\comment{I think web-master is officially one word without the hyphen}, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
+For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
 Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments.
@@
 The JavaScript rendering is the very first step of web page processing.
-Therefore, extracting blog post articles, comments or medias\comment{do you mean multimedia files?
-media is rather a concept in English and does not exist in plural} works equally well on blogs with JavaScript-generated content as well as on traditional HTML-only blogs.
+Therefore, extracting blog post articles, comments or multimedia files works equally well on blogs with JavaScript-generated content and on traditional HTML-only blogs.
 
@@
 Paths to Disqus and LiveFyre \emph{Show More} buttons are manually obtained.
-They constitute the only non-generic element of our extraction stack which requires human intervention to maintain and extend to other commenting platforms.
+They constitute the only non-generic elements of our extraction stack which require human intervention to maintain and extend to other commenting platforms.
 
@@
   \item Extract comments
-  \item Download media\comment{as before, media is rather a concept. Should we replace with multimedia files?}
+  \item Download multimedia files
   \item Propagate resulting records to the back end
@@
 % into
-In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process down to the subsets of blog pages holding\comment{maybe replace "holding" with: "which are"} blog posts: \emph{blog post identification} and \emph{download priority heuristic}.
+In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process down to the subsets of pages which are blog posts: \emph{blog post identification} and \emph{download priority heuristic}.
 
 % blog post identification
-Given an entry point to a website\comment{entry point == URL, right?
-Maybe clarify that here?}, the default Scrapy behavior looks over\comment{instead of "looks over" maybe "goes through" or "traverses" or "parses" or "looks at".
-Not sure, need some english-speaking person's opinion} all the pages of the same domain in a \emph{last-in-first-out} manner.
+Given an URL entry point to a website, the default Scrapy behavior traverses all the pages of the same domain in a \emph{last-in-first-out} manner.
 The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not.
-Internally, for each blog, this function uses a regular expression constructed from the URLs found in the web feed for each entry\comment{this last sentence has been slightly rephrased.
-Please check that it still makes sense they way you want it.}.
+Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed.
 This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur).
-In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers\comment{is a reference needed here?}.
+In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers\comment{is a reference needed here?}\TODO{Isn't the "seems" enought?
+(I never encontered a blog where this is not the case...)}.
 
@@
 In order to efficiently deal with blogs that have a large number of pages which are not posts, the \emph{blog post identification} mechanism is not sufficient.
-Indeed, after all pages identified as blog posts are processed, the crawler needs to download all other pages to search for additional blog posts\comment{replace "non-blog-post" with "all other".
-Is that OK?}.
+Indeed, after all pages identified as blog posts are processed, the crawler needs to download all other pages to search for additional blog posts.
 To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities for new URLs are determined by a machine learning system.
@@
 When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$.
-$L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$\comment{rephrased this last sentence slightly.
-Please make sure that it still makes sense.}.
+$L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.
 
@@
 where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator.
-By delegating all shared mutable state to the back end system (Invenio's database)\comment{this is the 1st mention of Invenio.
-Make sure to mention in the Introduction, or remove from here as well.}, web crawler instances can be added, removed and used interchangeably.
+By delegating all shared mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.

### 2013-12-10 tex/3-algorithms.tex
Add comment on 34cd000 changes.

@@
 Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section.
-Section \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
-In section \ref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give it a linear time reformulation using dynamic programing.
-Finally, section \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
+\hyperref[extractionrulesandstringsimilarity]{Subsection~\ref*{extractionrulesandstringsimilarity}} % Waiting for \Autoref{}...
+defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
+In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give it\TODO{not sure about this it.} a linear time reformulation using dynamic programing.
+Finally, \autoref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
 
@@
 
-Properties \ref{wordorderProp} and \ref{lengthProp} are essential when we deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
+Properties \ref{wordorderProp} and \ref{lengthProp} are essential when dealing with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
 \autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.

### 2013-12-11 tex/5-evaluation.tex
Minor corrections and comments on chapter 5

@@
 
-Our evaluation will be articulated in two parts.
-Firstly, we will compare the article extraction procedure presented in \autoref{algorithms} with three open source projects capable of extracting content and title of web articles.
-The comparison will show that our blog targeted solution has better performances both in term of success rate and running time.
-Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code.
-Extraction of authors, dates and comments is not part of evaluation because of the lack of publicly available competing projects and reference data sets.
+Our evaluation is articulated in two parts.
+First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting content and title from web articles\comment{article has a different meaning here than what we've been using in the rest of the paper.
+Maybe switch to "capable of extracting content from web pages"?}.
+The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time.
+Second, a discussion is held regarding the different solutions available to archive data beyond what is available in the HTML source code.
+Extraction of authors, dates and comments is not part of this evaluation because of the lack of publicly available competing projects and reference data sets.
 
-Experiments used \emph{Debian GNU/Linux 7.2}, \emph{Python 2.7} and an \emph{Intel Core i7-3770 3.4 GHz} processor.
-Timing measurements were made on a single dedicated core with garbage collector disabled.
-The Git repository of this paper \cite{repositoryofthispaper} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.
+In our experiments we used \emph{Debian GNU/Linux 7.2}, \emph{Python 2.7} and an \emph{Intel Core i7-3770 3.4 GHz} processor.
+Timing measurements were made on a single dedicated core with garbage collection disabled.
+The Git repository for this paper \cite{repositoryofthispaper} contains the necessary scripts and instructions to reproduce all the evaluation experiments presented in this section.
 
@@
 \subsection{Extraction success rates}
-To evaluate post article and title extraction we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively.
-These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
-\autoref{precisionTable} shows extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.
+To evaluate the article and title extraction from a blog post we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively.
+These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
+\autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.
 
@@
 
-On our test-set \autoref{extractionAlgo} outperformed the concurrence by 4.9\% on article extraction and 10.1\% on title extraction.
-It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages.
-Contrariwise, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages.
-Therefore, results showed in \autoref{precisionTable} should not be interpreted as general quality evaluation of the different projects, but simply show that our approach is more suitable when working with blogs.
+On our test dataset \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction.
+It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page.
+Contrariwise\comment{:="in the opposite way or order." Maybe switch to something like "On the contrary"?}, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages\comment{this last sentence is a bit hard to understand.}.
+Therefore, results showen in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an demonstration\comment{or evidence or proof ?} that our approach is more suitable when working with blogs.
 
@@
 % running time eval, scalability with size of blogs
-In addition to the quality of the extracted data we also evaluated the running time of the extraction procedures.
-The main point of interest will be the scalability of extraction procedures as the number of posts in the processed blog increases.
-This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published content on a blog.
+In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure.
+The main point of interest is the ability of the extraction procedure to scale as the number of posts in the processed blog increases.
+This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published content on a blog\comment{"previously published" sounds a bit weird.
+Maybe something like "already published" or just "published"?}.
 
@@
 \comment{Do I have to justify the arithmetic mean?
-If yes, this could do: \surl{http://dl.acm.org/citation.cfm?id=5673}}
+If yes, this could do: \surl{http://dl.acm.org/citation.cfm?id=5673}}\comment{need to rephrase - let's discuss.}
 
-\autoref{runningtime} shows the cumulated time spent on each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed of \surl{http://quantumdiaries.org/}.
+\autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed.
+The reference blog we used was \surl{http://quantumdiaries.org/}.
 
@@
 
-Past the initial computations, the cost to extract an article with our approach are almost null.
-This is a consequence of having a blog aware, rule based algorithm.
-If you recall the procedure presented in \autoref{algorithms}, the central idea was to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
-On this example, time cost of parsing a new blog post and using extraction rules is in the order of 3 milliseconds, which is not visible on the scale of \autoref{runningtime}.
-The three other evaluated solutions do not function this way: each blog post is processed as a new and independent input, leading to a close to linear running times.
+Past the initial computations, the cost to extract an article with our approach is almost null\comment{zero, instead of null?}.
+This is a consequence of having a blog-aware, rule-based algorithm.
+If you recall\comment{a bit informal, switch to something like: "As already mentioned"?} the procedure presented in \autoref{algorithms}, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
+In this example, the cost, in time, for parsing a new blog post and applying the extraction rules is in the order of 3 milliseconds, which is not\comment{not --> almost not / barely} visible on the scale of \autoref{runningtime}.
+The three other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to close to linear running times.
 
-In \autoref{runningtime}, the vertical dashed line at 15 processed blog posts represents a suitable point of comparisons for processing time per blog posts.
-Indeed, as the test blog's web feed contains 15 blog posts, the time spent on processing the first blog post also includes the processing time of the web feed and it's 15 entries.
-\comment{Is this clear?}That being said, comparing raw performances of different algorithm implemented with different programming languages is not very informative given the high variations of running times observes across languages for identical algorithms \cite{hundt2011}.
+In \autoref{runningtime}, the vertical dashed line at 15 processed blog posts represents a suitable point a comparison of processing time per blog post.
+Indeed, as the test blog's web feed contains 15 blog posts, the time spent on processing the first blog post also includes the processing time of the web feed and its 15 entries.
+\comment{Is this clear?
+--> almost, let's discuss}That being said, comparing raw performance of different algorithms implemented in different programming languages is not very informative given the high variations of running times observed across languages for identical algorithms \cite{hundt2011}.
 

### 2013-12-11 tex/6-conclusion-and-future-work.tex
Minor corrections and comments in chapter 6

--- 2013-12-06 tex/6-conclusion-and-future-work.tex
@@
 % What we presented, what we solved
-In this paper, we presented the internals of the BlogForever web crawler.
-Its central article extraction procedure based on extraction rules generation was introduced along with theoretical and empirical evidences validating the approach.
-Simple adaptation of this procedure allowed to extract different types of contents, including authors, dates and comments.
-In order to support
+In this paper, we presented the internals of the BlogForever web crawler\comment{maybe rephrase, since this is not the current one, but a suggestion for an open source one?
+See how we introduced it, ask Vangelis.}.
+Its central article extraction procedure based on extraction rules generation was introduced along with theoretical\comment{evidence can't be theoritical.
+Maybe theoritical basis or explanation?} and empirical evidence validating the approach.
+A simple adaptation of this procedure that allows to extract different types of content, including authors, dates and comments was then presented.
+In order to support rapidly evolving web technologies such as JavaScript-generated content, the crawler uses a web browser to render pages before processing them.
+We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.\comment{Finally,...
+(mention evaluation here?)}
 
-blogs with JavaScript generated content
+% Future work, hybrid algos
+Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates.
+Even if the overall performance of our approach is better than those of comparable projects as shown in chapter 5\comment{please add correct latex reference}, there are still a few cases where other techniques managed to extract data and we did not.
+This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performance.
 
-We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.
+% Deployment on a distributed architecture
+Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system.
+This is particularly relevant in the domain of web crawling given that intensive network operations can become a serious bottleneck which benefits from the use of multiple Internet access points\comment{it sounds like the bottleneck benefits from the use of...
+--> rephrase, let's discuss}.
+We intend to explore this opportunities in our future work.
 
-% Future work
+% Low level PhantomJS hooks
+% I guess two future works is enough...
 
-Plan:
-\begin{enumerate}
-  \item Recap the problem and the objective
-  \item Summarize how've solved it
-  \item Mention challenges and problems
-  \item Hint for future work
-\end{enumerate}
-
-Content:
-\begin{enumerate}
-  \item Web pages dynamically generated after filling a web form/doing some user action. This is not automated atm.
-  \item Spacial reasoning (we already have the page rendered w PhantomJS)
-  \item Low level PhantomJS hooks
-  \item Tree edit distance matching
-\end{enumerate}
+% Conclude the conclude
+To open up further possibilities\comment{let's rephrase, can't think of something now.}, the crawler presented in this paper is available under the MIT license from the project's website \cite{blogforevercrawler}.
+\comment{why not put the website directly here?}

### 2013-12-11 tex/5-evaluation.tex
Partial fixes.

@@
 Our evaluation is articulated in two parts.
-First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting content and title from web articles\comment{article has a different meaning here than what we've been using in the rest of the paper.
-Maybe switch to "capable of extracting content from web pages"?}.
+First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting article and title from web pages.
 The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time.
@@
 \subsection{Extraction success rates}
-To evaluate the article and title extraction from a blog post we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively.
+To evaluate article and title extraction from blog posts we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively.
 These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
@@
 The main point of interest is the ability of the extraction procedure to scale as the number of posts in the processed blog increases.
-This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published content on a blog\comment{"previously published" sounds a bit weird.
-Maybe something like "already published" or just "published"?}.
+This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all published content on a blog.
 
@@
 
-Past the initial computations, the cost to extract an article with our approach is almost null\comment{zero, instead of null?}.
+Past the initial computations, the cost to extract an article with our approach is almost zero.
 This is a consequence of having a blog-aware, rule-based algorithm.
-If you recall\comment{a bit informal, switch to something like: "As already mentioned"?} the procedure presented in \autoref{algorithms}, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
-In this example, the cost, in time, for parsing a new blog post and applying the extraction rules is in the order of 3 milliseconds, which is not\comment{not --> almost not / barely} visible on the scale of \autoref{runningtime}.
+As already mentioned in \autoref{algorithms}, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
+In this example, the cost, in time, for parsing a new blog post and applying the extraction rules is in the order of 3 milliseconds, which is barely not visible on the scale of \autoref{runningtime}.
 The three other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to close to linear running times.

### 2013-12-11 tex/5-evaluation.tex
Partial fixes.

@@
-\section{Evaluation}
+\section{Evaluation}\label{evaluation}
 
@@
 It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page.
-Contrariwise\comment{:="in the opposite way or order." Maybe switch to something like "On the contrary"?}, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages\comment{this last sentence is a bit hard to understand.}.
-Therefore, results showen in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an demonstration\comment{or evidence or proof ?} that our approach is more suitable when working with blogs.
+On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages\TODO{this last sentence is a bit hard to understand}.
+Therefore, results showen in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an evidence that our approach is more suitable when working with blogs.
 
@@
 As already mentioned in \autoref{algorithms}, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
-In this example, the cost, in time, for parsing a new blog post and applying the extraction rules is in the order of 3 milliseconds, which is barely not visible on the scale of \autoref{runningtime}.
+In this example, the execution time needed for parsing a new blog post and applying the extraction rules is in the order of 3 milliseconds, which is barely not visible on the scale of \autoref{runningtime}.
 The three other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to close to linear running times.
 
-In \autoref{runningtime}, the vertical dashed line at 15 processed blog posts represents a suitable point a comparison of processing time per blog post.
-Indeed, as the test blog's web feed contains 15 blog posts, the time spent on processing the first blog post also includes the processing time of the web feed and its 15 entries.
-\comment{Is this clear?
---> almost, let's discuss}That being said, comparing raw performance of different algorithms implemented in different programming languages is not very informative given the high variations of running times observed across languages for identical algorithms \cite{hundt2011}.
+In \autoref{runningtime}, the vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post.
+Indeed, as the test blog's web feed contains 15 blog posts, the time spent on processing the first blog post also includes the processing time of the web feed and its 15 entries\TODO{Is this clear?
+--> almost, let's discuss}.
+That being said, comparing raw performance of different algorithms implemented in different programming languages is not very informative given the high variations of running times observed across languages for identical algorithms \cite{hundt2011}.
 

### 2013-12-11 tex/6-conclusion-and-future-work.tex
Partial fixes.

@@
 Its central article extraction procedure based on extraction rules generation was introduced along with theoretical\comment{evidence can't be theoritical.
-Maybe theoritical basis or explanation?} and empirical evidence validating the approach.
+Maybe theoritical basis or explanation?}\TODO{I thought it was a synonym for proof, \surl{http://goo.gl/DgUIX8} and \surl{http://goo.gl/Icqd2x}} and empirical evidence validating the approach.
 A simple adaptation of this procedure that allows to extract different types of content, including authors, dates and comments was then presented.
 In order to support rapidly evolving web technologies such as JavaScript-generated content, the crawler uses a web browser to render pages before processing them.
-We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.\comment{Finally,...
-(mention evaluation here?)}
+We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.\TODO{Finally, ...
+evaluation}
 
@@
 Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates.
-Even if the overall performance of our approach is better than those of comparable projects as shown in chapter 5\comment{please add correct latex reference}, there are still a few cases where other techniques managed to extract data and we did not.
+Even if the overall performance of our approach is better than those of comparable projects as shown in \autoref{evaluation}\TODO{It think it might be better to avoid references in abstract and conclusion as a lot of readers will skip everything else.
+Maybe "as shown in the Evaluation"?}, there are still a few cases where other techniques managed to extract data and we did not.
 This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performance.
@@
 Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system.
-This is particularly relevant in the domain of web crawling given that intensive network operations can become a serious bottleneck which benefits from the use of multiple Internet access points\comment{it sounds like the bottleneck benefits from the use of...
+This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck.
+The which benefits from the use of multiple Internet access points\comment{it sounds like the bottleneck benefits from the use of...
 --> rephrase, let's discuss}.

### 2013-12-11 tex/1-intro.tex
Fixed most comments/TODOs.

@@
 XML Path Language(XPath)}
+
+\TODO{should we explain here that article is the actual content (text) of a blog post?
+Or is it already clear enough?
+-> I don't know.
+I used "blog post content" as "article + title + author + date + comments" in other sentences but it might be good to say somewhere that "blog post article" refers to the "core textual content of a blog post".}
+
+\TODO{Is it ok to call this "the BlogForever cralwer", given that it will be the 3rd implementation?}

### 2013-12-11 tex/3-algorithms.tex
Fixed most comments/TODOs.

@@
 
-This section explains in detail the algorithm we developed to extract blog posts articles \comment{should we explain here that article is the actual content (text) of a blog post?
-Or is it already clear enough?}\TODO{I don't know.
-I used "blog post content" as "article + title + author + date + comments" in other sentences but it might be good to say somewhere that "blog post article" refers to the "core textual content of a blog post".} as well as its variations for authors, dates and comments.
-Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog \comment{"all posts of a blog" needs a better formulation.}Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
+This section explains in detail the algorithm we developed to extract blog posts articles as well as its variations for authors, dates and comments.
+Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of a blog \comment{Does "all posts of a blog" need a better formulation?
+Maybe "across/throughout a blog"?}.Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
 
@@
 defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
-In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give it\TODO{not sure about this it.} a linear time reformulation using dynamic programing.
+In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing.
 Finally, \autoref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
@@
 \code{id} attributes are expected to be unique, and \code{class} attributes have showed in our experiments to have better consistency than absolute paths over pages of a blog.
-For these reasons\comment{there is a misscontinuation here.
-It's not for these reasons that we return a single rule per node.
-It's because we only need one rule per node.
-The rule is expressed in one of the three types mentioned above.}\TODO{The idea is that because there is such a strong hierarchy between the three rules (id > class > path), we only use "the best one".
-If it was not the case, we could also return 3 rules per node, which would triple the computation time.
-But I agree that it might not be very clear with "for these reasons"...}, the \coderef{allrulesAlgo} function returns a single rule per node:
+For these reasons we opt to always favor \code{class} over path, and \code{id} over \code{class}, such that the \coderef{allrulesAlgo} function returns a single rule per node.
 
@@
 Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process.
-When targeting articles, extraction rules are scored \comment{scored has a different meaning here.
-Graded or sorted or something similar is more correct}\TODO{ranked?
-evaluated?
-We should rename ScoreFunction accordingly and propagate the change everywhere.} with a string similarity function comparing the extracted strings with the target strings.
+When targeting articles, extraction rule scores are computed with a string similarity function comparing the extracted strings with the target strings.
 We chose the Sørensen–Dice coefficient similarity \cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:
@@
   \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
-  \item Remaining rules are \TODO{scored} with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
+  \item Remaining rule scores are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
 \end{itemize}
@@
 Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity.
-\TODO{Scoring} rules for comment extraction requires a more expensive algorithm.
+Computing scores or comment extraction rules requires a more expensive algorithm.
 However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice.

### 2013-12-11 tex/4-techniques.tex
Fixed most comments/TODOs.

@@
 While some applications simply use it for aesthetics (menus, animations, \ldots), an increasing number of websites use JavaScript to download and display content.
-In such cases, traditional HTML based crawlers do not see\comment{instead of see, maybe interpret, understand, render?}\TODO{I think I like the "see" better, even if it's informal it really transmits primary motivation for this JS rendering.} web pages as they are presented to a human visitor by a web browser, and might therefore be obsolete for data extraction.
+In such cases, traditional HTML based crawlers do not see web pages as they are presented to a human visitor by a web browser, and might therefore be obsolete for data extraction.
 
@@
 Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog.
-After being downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
+After being downloaded and identified as blog posts (details in \autoref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
 \begin{enumerate}[noitemsep]
@@
 This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur).
-In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers\comment{is a reference needed here?}\TODO{Isn't the "seems" enought?
-(I never encontered a blog where this is not the case...)}.
+In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.
 
@@
 where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator.
-By delegating all shared mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.
+By delegating all mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.

### 2013-12-11 tex/5-evaluation.tex
Fixed most comments/TODOs.

@@
 It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page.
-On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages\TODO{this last sentence is a bit hard to understand}.
+On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules.
 Therefore, results showen in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an evidence that our approach is more suitable when working with blogs.
@@
 % setup
-Experimental data was obtained by taking the arithmetic mean over 10 measurements, which we believe to be significant given that each result has a standard deviations on the order of 2 milliseconds.
-\comment{Do I have to justify the arithmetic mean?
-If yes, this could do: \surl{http://dl.acm.org/citation.cfm?id=5673}}\comment{need to rephrase - let's discuss.}
+Experimental data was obtained by taking the arithmetic mean over 10 measurements, which we believe to be significant given that standard deviations are of the order of 2 milliseconds.
 
 \autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed.
-The reference blog we used was \surl{http://quantumdiaries.org/}.
+We used the Quantum Diaries \cite{quantumdiaries} blog for this experiment.
 
@@
 
-Past the initial computations, the cost to extract an article with our approach is almost zero.
+Past the initial computations, the cost of processing a blog posts with our approach is almost zero.
 This is a consequence of having a blog-aware, rule-based algorithm.
-As already mentioned in \autoref{algorithms}, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
-In this example, the execution time needed for parsing a new blog post and applying the extraction rules is in the order of 3 milliseconds, which is barely not visible on the scale of \autoref{runningtime}.
-The three other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to close to linear running times.
+As already mentioned, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
+The initial increase in the curve of our approach corresponds to the extraction rules computations, which consist of processing the web feed and all blog posts it references.
+Subsequent computations only involve parsing blog posts and applying extraction rules, which takes about 3 milliseconds and is barely not visible on the scale of \autoref{runningtime}.
+The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximatly linear running times.
 
-In \autoref{runningtime}, the vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post.
-Indeed, as the test blog's web feed contains 15 blog posts, the time spent on processing the first blog post also includes the processing time of the web feed and its 15 entries\TODO{Is this clear?
---> almost, let's discuss}.
+The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post as the test blog's web feed contains 15 blog posts.
 That being said, comparing raw performance of different algorithms implemented in different programming languages is not very informative given the high variations of running times observed across languages for identical algorithms \cite{hundt2011}.
@@
 
+\TODO{}
 % intro, plan (why we pick these projects, what we want to show with this evaluation)

### 2013-12-11 tex/6-conclusion-and-future-work.tex
Fixed most comments/TODOs.

@@
 % What we presented, what we solved
-In this paper, we presented the internals of the BlogForever web crawler\comment{maybe rephrase, since this is not the current one, but a suggestion for an open source one?
-See how we introduced it, ask Vangelis.}.
-Its central article extraction procedure based on extraction rules generation was introduced along with theoretical\comment{evidence can't be theoritical.
-Maybe theoritical basis or explanation?}\TODO{I thought it was a synonym for proof, \surl{http://goo.gl/DgUIX8} and \surl{http://goo.gl/Icqd2x}} and empirical evidence validating the approach.
+In this paper, we presented the internals of the BlogForever web crawler.
+Its central article extraction procedure based on extraction rules generation was introduced along with theoretical and empirical evidence validating the approach.
 A simple adaptation of this procedure that allows to extract different types of content, including authors, dates and comments was then presented.
@@
 Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates.
-Even if the overall performance of our approach is better than those of comparable projects as shown in \autoref{evaluation}\TODO{It think it might be better to avoid references in abstract and conclusion as a lot of readers will skip everything else.
-Maybe "as shown in the Evaluation"?}, there are still a few cases where other techniques managed to extract data and we did not.
+Even if the overall performance of our approach is better than those of comparable projects (as shown in the evaluation), there are still a few cases where other techniques managed to extract data and we did not.
 This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performance.
@@
 This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck.
-The which benefits from the use of multiple Internet access points\comment{it sounds like the bottleneck benefits from the use of...
---> rephrase, let's discuss}.
+Crawler greatly benefits from the use of multiple Internet access points which makes them natural candidates for distributed computing.
 We intend to explore this opportunities in our future work.
 
-% Low level PhantomJS hooks
-% I guess two future works is enough...
-
 % Conclude the conclude
-To open up further possibilities\comment{let's rephrase, can't think of something now.}, the crawler presented in this paper is available under the MIT license from the project's website \cite{blogforevercrawler}.
-\comment{why not put the website directly here?}
+To open up further possibilities\comment{rephrase?}, the crawler presented in this paper is available under the MIT license from the project's website \cite{blogforevercrawler}.

### 2013-12-11 tex/3-algorithms.tex
Update 3-algorithms.tex

@@
   \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
-  \item Remaining rule scores are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
+  \item The scores of the remaining rules are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
 \end{itemize}
@@
 Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity.
-Computing scores or comment extraction rules requires a more expensive algorithm.
+Computing scores of comment extraction rules requires a more expensive algorithm.
 However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice.

### 2013-12-11 tex/5-evaluation.tex
Update 5-evaluation.tex

@@
 
-Past the initial computations, the cost of processing a blog posts with our approach is almost zero.
+Past the initial computations, the cost of processing a blog post with our approach is almost zero.
 This is a consequence of having a blog-aware, rule-based algorithm.
 As already mentioned, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
-The initial increase in the curve of our approach corresponds to the extraction rules computations, which consist of processing the web feed and all blog posts it references.
-Subsequent computations only involve parsing blog posts and applying extraction rules, which takes about 3 milliseconds and is barely not visible on the scale of \autoref{runningtime}.
+The initial increase in the curve of our approach corresponds to the computation of the extraction rules, which consists of processing the web feed and all the blog posts it references.
+Subsequent computations only involve parsing blog posts and applying extraction rules, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}.
 The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximatly linear running times.

### 2013-12-12 tex/5-evaluation.tex
Up

@@
 
-% setup
-Experimental data was obtained by taking the arithmetic mean over 10 measurements, which we believe to be significant given that standard deviations are of the order of 2 milliseconds.
-
+% the graph
 \autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed.
 We used the Quantum Diaries \cite{quantumdiaries} blog for this experiment.
+
+% standard deviations
+Data presented in this graph was obtained by taking the arithmetic mean over 10 measurements.
+These results are believed to be significant given that standard deviations are of the order of 2 milliseconds.
 
@@
 Subsequent computations only involve parsing blog posts and applying extraction rules, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}.
-The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximatly linear running times.
+The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.
 

### 2013-12-12 running-times/crawler/bibcrawl/pipelines/timeextrator.py
Add readme on each eval.

@@ -1,0 +1,92 @@
+# """TimeExtrator"""
+
+# from bibcrawl.utils.ohpython import *
+# from bibcrawl.utils.parsing import parseHTML
+# from bibcrawl.utils.stringsimilarity import cleanTags
+# from boilerpipe.extract import Extractor
+# from goose import Goose
+# from readability.readability import Document
+# from scrapy import log
+# from time import time
+# import gc
+# import sys
+
+# class TimeExtrator(object):
+#   def process_item(self, item, spider):
+#     gcenabled = gc.isenabled()
+#     gc.disable()
+#     try:
+#       contentExtractor = lambda _: spider.contentExtractor(parseHTML(_))
+#       boilerpipeExtractor = lambda _: Extractor(html=_).getText()
+#       gooseExtractor = lambda _: Goose().extract(raw_html=_).cleaned_text
+#       readabilityExtractor = lambda _: cleanTags(Document(_).summary())
+
+#       # CE, BP, GO, RE
+#       log.msg("{} {} {} {}".format(
+#         timeMeThis(partial(contentExtractor,     item.rawHtml)),
+#         timeMeThis(partial(boilerpipeExtractor,  item.rawHtml)),
+#         timeMeThis(partial(gooseExtractor,       item.rawHtml)),
+#         timeMeThis(partial(readabilityExtractor, item.rawHtml)),
+#       ))
+#     finally:
+#       if gcenabled:
+#         gc.enable()
+
+# def timeMeThis(e):
+#   t0 = time()
+#   e()
+#   return time() - t0
+
+"""TimeExtrator"""
+
+from bibcrawl.utils.ohpython import *
+from bibcrawl.utils.parsing import parseHTML
+from bibcrawl.utils.stringsimilarity import cleanTags
+from boilerpipe.extract import Extractor
+from goose import Goose
+from readability.readability import Document
+from scrapy import log
+from time import time
+import gc
+import sys
+from numpy import median, mean, std
+
+class TimeExtrator(object):
+  def process_item(self, item, spider):
+    gcenabled = gc.isenabled()
+    gc.disable()
+    try:
+      contentExtractor = lambda _: spider.contentExtractor(parseHTML(_))
+      boilerpipeExtractor = lambda _: Extractor(html=_).getText()
+      gooseExtractor = lambda _: Goose().extract(raw_html=_).cleaned_text
[…]

### 2013-12-12 running-times/crawler/bibcrawl/run.py

@@ -1,0 +1,71 @@
+"""main"""
+
+from bibcrawl.spiders.newcrawl import NewCrawl
+from bibcrawl.spiders.updatecrawl import UpdateCrawl
+from bibcrawl.spiders.evalcrawl import EvalCrawl
+from scrapy import signals
+from scrapy.crawler import Crawler
+from scrapy.settings import Settings
+from twisted.internet import reactor
+from datetime import date, timedelta, datetime
+from scrapy import log
+import sys
+
+def stop_reactor():
+  """Stops the twistedreactor."""
+  reactor.stop()
+
+def startSpider(spider):
+  pass
+
+def main():
+  """Crawler entry point."""
+  settings = Settings({
+      "ITEM_PIPELINES": [
+          # 'bibcrawl.pipelines.renderjavascript.RenderJavascript',
+          'bibcrawl.pipelines.processhtml.ProcessHtml',
+          'bibcrawl.pipelines.timeextrator.TimeExtrator',
+          # 'bibcrawl.pipelines.downloadimages.DownloadImages',
+          # 'bibcrawl.pipelines.downloadfeeds.DownloadFeeds',
+          # 'bibcrawl.pipelines.extractcomments.ExtractComments',
+          # 'bibcrawl.pipelines.backendpropagate.BackendPropagate',
+          # 'bibcrawl.pipelines.outpropagate.OutPropagate',
+      ],
+      "HTTPCACHE_POLICY": "scrapy.contrib.httpcache.DummyPolicy",
+      "HTTPCACHE_STORAGE": "scrapy.contrib.httpcache.FilesystemCacheStorage",
+      "HTTPCACHE_ENABLED": True,
+      "FILES_STORE": "img",
+
+      # "CONCURRENT_ITEMS": 1,
+      "STATS_DUMP": False,
+      "LOG_LEVEL": "DEBUG",
+      # "CONCURRENT_REQUESTS": 1,
+      # "CONCURRENT_REQUESTS_PER_DOMAIN": 1,
+      # "CONCURRENT_REQUESTS_PER_IP": 1
+  })
+
+  # Need test cases for this one: letitcrash.com
+  # techcrunch.com
+  # keikolynn.com
+
+  # spider = NewCrawl(domain="korben.info", maxDownloads=500)
+  # spider = UpdateCrawl(
+  #   startAt="http://korben.info/feed",
+  #   domain="korben.info",
+  #   since=datetime.now() - timedelta(days=1))
+
[…]

### 2013-12-12 success-rates/article/boilerpipe/gen.py

@@ -1,0 +1,20 @@
+import sys
+from boilerpipe.extract import Extractor
+from os import listdir
+from urllib2 import urlopen, HTTPError
+import codecs
+
+def main():
+  contents = sys.argv[1]
+  for url in listdir(contents):
+    print url
+    with codecs.open(url, "w", encoding="utf-8") as out:
+      try:
+        html = urlopen(url.replace("{", "/")).read()
+        extracted = Extractor(html=html)
+        out.write(extracted.getText())
+      except HTTPError:
+        out.write("")
+
+if __name__ == "__main__":
+  main()

### 2013-12-12 success-rates/article/goose/gen.py

@@ -1,0 +1,19 @@
+import sys
+from goose import Goose
+from os import listdir
+import codecs
+
+def main():
+  contents = sys.argv[1]
+  goose = Goose()
+  for url in listdir(contents):
+    print url
+    with codecs.open(url, "w", encoding="utf-8") as out:
+      try:
+        extracted = goose.extract(url=url.replace("{", "/"))
+        out.write(extracted.cleaned_text)
+      except IOError:
+        out.write("")
+
+if __name__ == "__main__":
+  main()

### 2013-12-12 success-rates/article/readability/gen.py

@@ -1,0 +1,21 @@
+import sys
+from lxml.html.clean import Cleaner
+from os import listdir
+from re import sub as resub
+from readability.readability import Document
+from urllib2 import urlopen, HTTPError
+import codecs
+
+def main():
+  contents = sys.argv[1]
+  for url in listdir(contents):
+    print url
+    with codecs.open(url, "w", encoding="utf-8") as out:
+      try:
+        html = urlopen(url.replace("{", "/")).read()
+        out.write((Document(html).summary()))
+      except HTTPError:
+        out.write("")
+
+if __name__ == "__main__":
+  main()

### 2013-12-12 success-rates/crawler/bibcrawl/pipelines/outpropagate.py

@@ -1,0 +1,29 @@
+"""OutPropagate"""
+from bibcrawl.utils.fixbadunicode import fix_bad_unicode
+from bibcrawl.utils.stringsimilarity import cleanTags
+
+class OutPropagate(object):
+  """
+  @type  item: bibcrawl.model.postitem.PostItem
+  @param item: the item to process
+  @type  spider: scrapy.spider.BaseSpider
+  @param spider: the spider that emitted this item
+  @rtype: bibcrawl.model.postitem.PostItem
+  @return: the processed item
+  """
+  def process_item(self, item, spider):
+    import codecs
+
+    path = "titles/" + item.url.replace("/", "{")
+    spider.logInfo(path)
+    nicecontent = fix_bad_unicode(cleanTags(item.title))
+    with codecs.open(path , "w", encoding="utf-8") as out:
+      out.write(nicecontent)
+
+    path = "content/" + item.url.replace("/", "{")
+    spider.logInfo(path)
+    nicecontent = fix_bad_unicode(cleanTags(item.content))
+    with codecs.open(path , "w", encoding="utf-8") as out:
+      out.write(nicecontent)
+
+    spider.logInfo("DONE:" + item.url)

### 2013-12-12 success-rates/crawler/bibcrawl/run.py

@@ -1,0 +1,71 @@
+"""main"""
+
+from bibcrawl.spiders.newcrawl import NewCrawl
+from bibcrawl.spiders.updatecrawl import UpdateCrawl
+from bibcrawl.spiders.evalcrawl import EvalCrawl
+from scrapy import signals
+from scrapy.crawler import Crawler
+from scrapy.settings import Settings
+from twisted.internet import reactor
+from datetime import date, timedelta, datetime
+from scrapy import log
+import sys
+
+def stop_reactor():
+  """Stops the twistedreactor."""
+  reactor.stop()
+
+def startSpider(spider):
+  pass
+
+def main():
+  """Crawler entry point."""
+  settings = Settings({
+      "ITEM_PIPELINES": [
+          # 'bibcrawl.pipelines.renderjavascript.RenderJavascript',
+          'bibcrawl.pipelines.processhtml.ProcessHtml',
+          # 'bibcrawl.pipelines.timeextrator.TimeExtrator',
+          # 'bibcrawl.pipelines.downloadimages.DownloadImages',
+          # 'bibcrawl.pipelines.downloadfeeds.DownloadFeeds',
+          # 'bibcrawl.pipelines.extractcomments.ExtractComments',
+          # 'bibcrawl.pipelines.backendpropagate.BackendPropagate',
+          'bibcrawl.pipelines.outpropagate.OutPropagate',
+      ],
+      "HTTPCACHE_POLICY": "scrapy.contrib.httpcache.DummyPolicy",
+      "HTTPCACHE_STORAGE": "scrapy.contrib.httpcache.FilesystemCacheStorage",
+      "HTTPCACHE_ENABLED": True,
+      "FILES_STORE": "img",
+
+      # "CONCURRENT_ITEMS": 1,
+      "STATS_DUMP": False,
+      "LOG_LEVEL": "DEBUG",
+      # "CONCURRENT_REQUESTS": 1,
+      # "CONCURRENT_REQUESTS_PER_DOMAIN": 1,
+      # "CONCURRENT_REQUESTS_PER_IP": 1
+  })
+
+  # Need test cases for this one: letitcrash.com
+  # techcrunch.com
+  # keikolynn.com
+
+  # spider = NewCrawl(domain="korben.info", maxDownloads=500)
+  # spider = UpdateCrawl(
+  #   startAt="http://korben.info/feed",
+  #   domain="korben.info",
+  #   since=datetime.now() - timedelta(days=1))
+
[…]

### 2013-12-12 success-rates/crawler/bibcrawl/spiders/evalcrawl.py

@@ -1,0 +1,41 @@
+"""EvalCrawl"""
+
+from bibcrawl.model.postitem import PostItem
+from bibcrawl.utils.priorityheuristic import PriorityHeuristic
+from bibcrawl.utils.ohpython import *
+from bibcrawl.utils.parsing import buildUrlFilter, parseHTML
+from bibcrawl.utils.parsing import extractLinks
+from scrapy.http import Request
+from bibcrawl.spiders.rsscrawl import RssCrawl
+from twisted.internet import reactor
+from os import listdir
+
+class EvalCrawl(RssCrawl):
+  """EvalCrawl"""
+
+  def __init__(self, startAt):
+    super(self.__class__, self).__init__(startAt)
+
+  def handleRssEntries(self, posts):
+    return imap(
+      lambda _: Request(
+        url=_.replace("{", "/"),
+        meta={ "u": _.replace("{", "/") },
+        dont_filter=True,
+        errback=self.error,
+        callback=self.crawl),
+      ifilter(
+        lambda _: self.allowed_domains[0] in _,
+        listdir("../blogforever-crawler-publication/dataset/contents/")))
+
+  def crawl(self, response):
+    self.logInfo("START:" + response.meta["u"])
+    parsedBody = parseHTML(response.body)
+    return PostItem(url=response.meta["u"], parsedBodies=(parsedBody,))
+
+  def error(self, failure):
+    self.logInfo("ERROR:" + str(failure))
+    from scrapy.contrib.spidermiddleware.httperror import HttpError
+    if isinstance(failure.value, HttpError):
+      response = failure.value.response
+      return self.crawl(response)

### 2013-12-12 success-rates/crawler/gen.sh

@@ -1,0 +1,3 @@
+#!/bin/sh
+
+for d in $(cat ../blogforever-crawler-publication/dataset/bloglist.txt); do sudo python -m bibcrawl/run $d; done

### 2013-12-12 success-rates/score.py

@@ -1,0 +1,44 @@
+import sys
+import codecs
+from Levenshtein import ratio
+from os import listdir
+
+def bigrams(string):
+  return set(map(lambda i: string[i : i + 2], xrange(len(string) - 1)))
+
+def dicesCoeffSimilarity(string1, string2):
+  bigrams1 = bigrams(string1)
+  bigrams2 = bigrams(string2)
+  intersection = bigrams1.intersection(bigrams2)
+  return (2.0 * len(intersection)) / (len(bigrams1) + len(bigrams2))
+
+def main():
+  first = sys.argv[1]
+  second = sys.argv[2]
+
+  threshold = 0.5
+  total = 0.0
+  count = 0.0
+
+  for page in listdir(first):
+    with codecs.open(first + "/" + page, "r", encoding="utf-8") as f:
+      firstpage = f.read()
+    try:
+      with codecs.open(second + "/" + page, "r", encoding="utf-8") as f:
+        secondpage = f.read()
+    except IOError:
+      secondpage = u""
+    if len(firstpage) > 20:
+      ratio = dicesCoeffSimilarity(firstpage + ".", secondpage + ".")
+      # ratio = ratio(firstpage + ".", secondpage + ".")
+      total = total + 1.0
+      if ratio > threshold:
+        count = count + 1.0
+      elif len(sys.argv) == 4:
+        print page.replace("{", "/")
+
+  print "{}: {}%".format(second, count/total * 100.0)
+
+
+if __name__ == "__main__":
+  main()

### 2013-12-12 success-rates/title/goose/gen.py

@@ -1,0 +1,20 @@
+import sys
+from goose import Goose
+from os import listdir
+import codecs
+
+def main():
+  contents = sys.argv[1]
+  goose = Goose()
+  for url in listdir(contents):
+    print url
+    with codecs.open(url, "w", encoding="utf-8") as out:
+      try:
+        extracted = goose.extract(url=url.replace("{", "/"))
+        out.write(extracted.title)
+      except (IOError, TypeError):
+        out.write("")
+        print "Error"
+
+if __name__ == "__main__":
+  main()

### 2013-12-12 success-rates/title/readability/gen.py

@@ -1,0 +1,26 @@
+import sys
+from lxml.html.clean import Cleaner
+from os import listdir
+from re import sub as resub
+from readability.readability import Document
+from urllib2 import urlopen, HTTPError
+import codecs
+
+def cleanTags(string):
+  htmlCleaned = Cleaner(allow_tags=[''], remove_unknown_tags=False, style=True
+      ).clean_html(string or u"dummy")
+  return resub(r"\s\s+" , " ", htmlCleaned)
+
+def main():
+  titles = sys.argv[1]
+  for url in listdir(titles):
+    print url
+    with codecs.open(url, "w", encoding="utf-8") as out:
+      try:
+        html = urlopen(url.replace("{", "/")).read()
+        out.write(cleanTags(Document(html).title()))
+      except HTTPError:
+        out.write("")
+
+if __name__ == "__main__":
+  main()

### 2013-12-20 tex/runningtimeFigure.tex
up

@@
 \begin{figure}[ht]
+  \capstart
+  \refstepcounter{figure}
+  \label{runningtime}
+  \vspace{-12pt}
   \hspace{-34pt}
-  \begin{gnuplot}
+  \begin{gnuplot}% nop
     set terminal epslatex color
@@
 
-    set title 'Figure 2: title'
+    set title 'Figure \arabic{figure}: Running time of articles extraction '
     set ylabel 'Cumulated running time (sec.)' offset 1.3
-    set xlabel 'Processed pages'
+    set xlabel 'Processed blog posts'
 
@@
   \end{gnuplot}
+  \vspace{-12pt}
 \end{figure}

### 2014-01-06 success-rates/crawler/bibcrawl/utils/fixbadunicode.py
Update folder structure.

@@ -1,20 +1,6 @@
+# Source; http://blog.luminoso.com/2012/08/20/fix-unicode-mistakes-with-python/
 # -*- coding: utf-8 -*-
 
-import re
-import codecs
-def main():
-  with codecs.open("apiESCAPEDDD", "r", encoding="utf-8") as f:
-    for line in f:
-      result = re.search(
-        r"^\d*,'[^']*','[^']*','([^']*)','[^']*',\d*,'([^']*)'$"
-        , line)
-      if result:
-        content = fix_bad_unicode(result.groups()[0].replace("ESCAPEDDD", "'"))
-        url = result.groups()[1].replace("/", "{")
-        with codecs.open("articles/" + url, "w", encoding="utf-8") as out:
-          out.write(content)
-
-# Source: http://blog.luminoso.com/2012/08/20/fix-unicode-mistakes-with-python/
 import unicodedata
 
 def fix_bad_unicode(text):
@@ -81,9 +67,9 @@ def fix_bad_unicode(text):
         >>> print fix_bad_unicode(u'This text was never Unicode at all\x85')
         This text was never Unicode at all…
     """
-    # if not isinstance(text, unicode):
-    #     raise TypeError("This isn't even decoded into Unicode yet. "
-    #                     "Decode it first.")
+    if not isinstance(text, unicode):
+        raise TypeError("This isn't even decoded into Unicode yet. "
+                        "Decode it first.")
     if len(text) == 0:
         return text
 
@@ -115,9 +101,11 @@ def fix_bad_unicode(text):
         else:
             return fix_bad_unicode(goodtext)
 
+
 def reinterpret_latin1_as_utf8(wrongtext):
-    newbytes = wrongtext.encode('latin-1', 'ignore')
-    return newbytes.decode('utf-8', 'ignore')
+    newbytes = wrongtext.encode('latin-1', 'replace')
+    return newbytes.decode('utf-8', 'replace')
+
 
 def reinterpret_windows1252_as_utf8(wrongtext):
     altered_bytes = []
@@ -128,12 +116,14 @@ def reinterpret_windows1252_as_utf8(wrongtext):
             altered_bytes.append(char.encode('latin-1', 'replace'))
     return ''.join(altered_bytes).decode('utf-8', 'replace')
 
+
 def reinterpret_latin1_as_windows1252(wrongtext):
     """
     Maybe this was always meant to be in a single-byte encoding, and it
     makes the most sense in Windows-1252.
     """
[…]

### 2014-01-06 success-rates/scoreAll.sh

@@ -1,6 +1,6 @@
 #!/bin/sh
 
-python score.py contents/ ../../blogforever-crawler/out
-python score.py contents/ goose/
-python score.py contents/ readability/
-python score.py contents/ boilerpipe/
+python score.py ../dataset/articles/ ../../crawler/articles
+python score.py ../dataset/articles/ articles/goose/
+python score.py ../dataset/articles/ articles/readability/
+python score.py ../dataset/articles/ articles/boilerpipe/

### 2014-01-06 success-rates/scoreTitles.sh

@@ -1,5 +1,5 @@
 #!/bin/sh
 
-python score.py titles/ ../../blogforever-crawler/titles
-python score.py titles/ TT/goose/
-python score.py titles/ TT/readability/
+python score.py ../dataset/titles/ ../../crawler/titles
+python score.py ../dataset/titles/ titles/goose/
+python score.py ../dataset/titles/ titles/readability/

### 2014-01-07 success-rates/crawler/bibcrawl/pipelines/outpropagate.py
Renaming

@@ -20,7 +20,7 @@ class OutPropagate(object):
     with codecs.open(path , "w", encoding="utf-8") as out:
       out.write(nicecontent)
 
-    path = "content/" + item.url.replace("/", "{")
+    path = "articles/" + item.url.replace("/", "{")
     spider.logInfo(path)
     nicecontent = fix_bad_unicode(cleanTags(item.content))
     with codecs.open(path , "w", encoding="utf-8") as out:

### 2014-01-09 tex/3-algorithms.tex
Minor

@@
 Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, providing the \code{Apply} function used in \autoref{extractionAlgo}.
-We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection using the absolute path in the HTML tree.
-\code{id} attributes are expected to be unique, and \code{class} attributes have showed in our experiments to have better consistency than absolute paths over pages of a blog.
+We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection using the relative path in the HTML tree.
+\code{id} attributes are expected to be unique, and \code{class} attributes have showed in our experiments to have better consistency than relative paths over pages of a blog.
 For these reasons we opt to always favor \code{class} over path, and \code{id} over \code{class}, such that the \coderef{allrulesAlgo} function returns a single rule per node.
@@
 To do so we use the following \code{ScoreFunction}:
+
 \begin{itemize}

### 2014-01-10 webarchivers/test.py
Compare webarchivers

@@ -1,0 +1,37 @@
+from selenium import webdriver
+from os.path import dirname, join
+from selenium.common.exceptions import ElementNotVisibleException
+from selenium.common.exceptions import NoSuchElementException
+from time import sleep, time
+
+def main():
+  path = join(dirname(__file__), "/home/olivier/workspace/crawler/lib/phantomjs/bin/phantomjs")
+  driver = webdriver.PhantomJS(path)
+
+  url = "http://www.chancellors.co.uk/properties/search?map=false&area=New+Barnet&longitude=0&latitude=0&radius=5&saleType=Rent"
+  buttonPath = "//a[@id='Loadmore']"
+  pricesPath = "//div[@class='list-property clearfix']//h3"
+
+  driver.get(url)
+  # sleep(2)
+  # clickWhileVisible(driver, buttonPath)
+  # sleep(2)
+  result = map(
+    lambda _: _.get_attribute("innerHTML"),
+    driver.find_elements_by_xpath(pricesPath))
+  print "\n".join(result)
+
+  driver.quit()
+
+def clickWhileVisible(driver, xPath, maxDuration=5, stepDuration=0.5):
+  try:
+    timeout = time() + maxDuration
+    while time() < timeout:
+      driver.find_element_by_xpath(xPath).click()
+      # "document.getElementsByClassName('fyre-text')[0].click()")
+      sleep(stepDuration)
+  except (ElementNotVisibleException, NoSuchElementException):
+    pass
+
+if __name__ == '__main__':
+  main()

### 2014-01-13 tex/5-evaluation.tex
up
Up

@@
 The Git repository for this paper \cite{repositoryofthispaper} contains the necessary scripts and instructions to reproduce all the evaluation experiments presented in this section.
+The crawler source code is available under the MIT license from the project's websites \cite{blogforevercrawler}.
 
@@
 
+Beside the extraction of blog post date that we have been discussing so far, it is also interesting to go one step further and preserve the design of webpages.
+One of the initial blog forever requirements is to be able to save blogs such that future generation could see them as they were originally when first crawled by the system.
+
+To achieve this property, our final solution was to embed a full web browser into our system, as presented in section *, which we use to take screen-shots of pages.
+Before choosing this tool we considered 3 other solutions: wget, wkhtmltopdf, oxpath.
+This subsection relates our evaluation of these tools for the specific purpose.
+
+The first solution we considered was the GNU/Linux tool wget.
+With the appropriate options, wget can be used to download a webpage and the associated files (css, scripts and images).
+On simple webpages, this process effectively captures all files necessary to display the page locally.
+However, it falls short* to capture webpages that download content via javascript.
+
+Another solution we considered is wkhtmltopdf, a tool to produce pdf versions of web-pages.
+It uses the "print" function of it's embedded web browser to produce it's output and therefore supports all web technologies supported by it underling web browser.
+
+The OXPath project goes one step further by offering an extension of the XPath language to specify page interactions such as clicks and forms filling.
+It also make use of a complete web browser to render pages and execute page interactions sequentially.
+OXPath makes it simple to extract comments displayed across multiple pages or that requiring clicks to be loaded.
+
+functionality |  wget  | wkhtmltopdf | oxpath | phantomjs
+---------------------------------------------------------
+js support    |        |             |        |          
+page interat  |   n    |      n      |   y    |    y     
+js support    |   n    |      y      |   y    |    y     
+running time  | 0.50s  |    7.58s    | 22.04s |  3.32s
+
 \TODO{}
+
 % intro, plan (why we pick these projects, what we want to show with this evaluation)

### 2014-01-13 tex/5-evaluation.tex
Up

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{JavaScript rendering}
+\subsection{Preservation of blog visuals}
+\TODO{visuals/design/graphic/?}
 
-Beside the extraction of blog post date that we have been discussing so far, it is also interesting to go one step further and preserve the design of webpages.
-One of the initial blog forever requirements is to be able to save blogs such that future generation could see them as they were originally when first crawled by the system.
+In addition to the extraction of blog content that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals.
+Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.
 
-To achieve this property, our final solution was to embed a full web browser into our system, as presented in section *, which we use to take screen-shots of pages.
+As presented in section \autoref{techniques}, our crawler uses a full web browser to render pages.
+
+To achieve this property, our final solution was to embed a full web browser into our system, , which we use to take screen-shots of pages.
 Before choosing this tool we considered 3 other solutions: wget, wkhtmltopdf, oxpath.
@@
 OXPath makes it simple to extract comments displayed across multiple pages or that requiring clicks to be loaded.
+
+\cmark
+\xmark
 

### 2014-01-14 tex/5-evaluation.tex
Up

@@
 Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.
+As presented in section \autoref{techniques}, our crawler embed a full web browser in the harvesting process.
+In addition (***rep) to the JavaScript rendering, the browser also take care of visu by screenschots
 
-As presented in section \autoref{techniques}, our crawler uses a full web browser to render pages.
+in order to support blogs that use JavaScript to download and display content.
 
-To achieve this property, our final solution was to embed a full web browser into our system, , which we use to take screen-shots of pages.
-Before choosing this tool we considered 3 other solutions: wget, wkhtmltopdf, oxpath.
-This subsection relates our evaluation of these tools for the specific purpose.
+*dis also takes case of screenshots*. Before opting for this we considered 3 other solutions: wget, wkhtmltopdf, oxpath. This subsection relates our evaluation of these tools for the specific purpose.
 

### 2014-01-14 tex/1-intro.tex
Improvements to the Introduction section

--- 2013-11-25 tex/1-intro.tex
@@
 
-Aims and contributions of this work. Example from my last paper to see the format:\\
+Web archiving is the process of harvesting and gathering web content in order to safely preserve it for posterity.
+As the volume and importance of the information on the World Wide Web increases, web archiving becomes more and more relevant and its importance becomes clearer.
+Web crawlers are an essential part of web archiving, allowing for automated capturing of web resources.
+An efficient and accurate web crawler is the first crucial step to successful digital preservation.
+
+By June 2008 the Technorati Internet search engine for blogs reported indexing 112.8 million blogs (reference) while in July 2005 they had estimated that the size of the blogosphere was doubling every 5.5 months (http://www.sifry.com/alerts/archives/000332.html).
+A blog is a \emph{frequently updated web site consisting of personal observations, excerpts from other sources, etc., typically run by a single person, and usually with hyperlinks to other sites; an online journal or diary.} (http://www.oed.com/view/Entry/256743\#eid11173991).
+Given the nature of blogs, they are expectedly highly volatile web resources.
+
+Blogs are a popular means of communication and expression of ideas and have been adopted by universities, institutions and scolars (reference?).
+Recenlty, blogs have also been used to disseminate ideas in times of political turmoil or even war (http://ijoc.org/index.php/ijoc/article/download/1242/597 - Social Media in the Egyptian Revolution).
+Their political, scientific and cultural significance is undisputed. (rephrase to avoid need for reference?)
+
+However, to this day there is no standard method or authority that ensures blog archiving and long-term digital preservation.
+There is no guarantee that a disappearing or disappeared blog will ever be retrievable in the future (A Tale of a Disappearing Website : http://blogs.loc.gov/digitalpreservation/2012/01/a-tale-of-a-disappearing-website/ AND Considerations for the Preservation of Blogs : http://www.digitalpreservationeurope.eu/publications/briefs/preservartion\_blogs.pdf)
+Therefore, it is crucial that the necessary foundations for blog archiving are put in place.
+
+The blogosphere is a massive web resource of unstructured data.
+Identifying, harvesting and parsing that data can be a very challenging task.
+The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of efficient extraction techniques that offer a high degree of automation necessary.
+The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents.
+Finaly, modern blogs heavily rely on dynamically created content to present information, using the latest web technologies, invalidating most traditional web crawling techniques.
+
+*** Do we need to present issues in current solutions here? Is it needed? Can we write it in "Related Work" instead? ***
+
+Our solution aims to tackle the challenges and constraints described above by employing a series of techniques and algorithms to harvest modern weblogs in a high-quality, accurate and efficient manner.
+We base our crawler on one of the most common and standard characteristics of blogs: web feeds.
+Explain:
+\begin{enumerate}
+  \item what feeds are, and what we use them for (discovery, extraction)
+  \item the use of HTML + XPATH
+  \item the use of efficient string similarity
+  \item the use of javascript rendering
+\end{enumerate}
+
+The rest of the paper is organized as follows: Related work is presented in Section 2; the algorithms we developed to extract blog post articles, authors, dates and comments are detailed in Section 3; in section 4 we give an overview of the different techniques used in our crawler; evaluation experiments are described and commented in Section 5.
+We finally conclude and present future work in Section 6.
+
+\comment{(from wikipedia) The largest web archiving organization based on a bulk crawling approach is the Internet Archive which strives to maintain an archive of the entire Web.
+National libraries, national archives and various consortia of organizations are also involved in archiving culturally important Web content.
+Commercial web archiving software and services are also available to organizations who need to archive their own web content for corporate heritage, regulatory, or legal purposes.}
+
+\comment{Aims and contributions of this work. Example from my last paper to see the format:\\
 http://purl.pt/24107/1/iPres2013\_PDF/\\
 CLEAR\%20a\%20credible\%20method\%20to\%20\\
-evaluate\%20website\%20archivability.pdf
+evaluate\%20website\%20archivability.pdf}
 
+\comment{Semi-structured nature of Web pages\\
+Labeled ordered rooted trees\\
+XML Path Language(XPath)}
+
+\TODO{should we explain here that article is the actual content (text) of a blog post?
+Or is it already clear enough?
+-> I don't know.
+I used "blog post content" as "article + title + author + date + comments" in other sentences but it might be good to say somewhere that "blog post article" refers to the "core textual content of a blog post".}
+
+\TODO{Is it ok to call this "the BlogForever cralwer", given that it will be the 3rd implementation?}
+
+Intro contents (more or less)
 \begin{enumerate}
@@
 
-Challenges consist of:
+Challenges and constraints:
 \begin{enumerate}
+  \item size of blogosphere (Dealing with large volumes of data)
+  \item heterogeneous nature of different publishing platforms
+  \item ever-changing structure
+  \item dynamically created content using modern web technologies.
+  \item complexity in parsing blogs from unstructured data to structured information.
+  \item programmatic access to blog content unavailable
+  \item unpredictable publishing rate --> scalability
   \item Providing a high degree of automation
-  \item Dealing with large volumes of data
 \end{enumerate}
-
-Semi-structured nature of Web pages
-
-Labeled ordered rooted trees
-XML Path Language(XPath)

### 2014-01-14 tex/5-evaluation.tex
Compiled

--- 2014-01-13 tex/5-evaluation.tex
@@
 
-In addition to the extraction of blog content that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals.
+Additionally to the blog content extraction that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals.
 Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.
-
-As presented in section \autoref{techniques}, our crawler uses a full web browser to render pages.
-
-To achieve this property, our final solution was to embed a full web browser into our system, , which we use to take screen-shots of pages.
-Before choosing this tool we considered 3 other solutions: wget, wkhtmltopdf, oxpath.
+Our final solution consists in taking a screenshot with our embeded web browser after the JavaScript rendering.
+Before opting for this approach, we considered 3 other solutions: GNU Wget, wkhtmltopdf and OXPath.
 This subsection relates our evaluation of these tools for the specific purpose.
@@
 
-\cmark
-\xmark
-
-functionality |  wget  | wkhtmltopdf | oxpath | phantomjs
----------------------------------------------------------
-js support    |        |             |        |
-page interat  |   n    |      n      |   y    |    y
-js support    |   n    |      y      |   y    |    y
-running time  | 0.50s  |    7.58s    | 22.04s |  3.32s
+\savevisualsTable
 

### 2014-01-14 tex/1-intro.tex
Add refs and clean up a bit

@@
 
-By June 2008 the Technorati Internet search engine for blogs reported indexing 112.8 million blogs (reference) while in July 2005 they had estimated that the size of the blogosphere was doubling every 5.5 months (http://www.sifry.com/alerts/archives/000332.html).
-A blog is a \emph{frequently updated web site consisting of personal observations, excerpts from other sources, etc., typically run by a single person, and usually with hyperlinks to other sites; an online journal or diary.} (http://www.oed.com/view/Entry/256743\#eid11173991).
+By June 2008 the Technorati Internet search engine for blogs reported indexing 112.8 million blogs \cite{technoratidata2008} while in July 2005 they had estimated that the size of the blogosphere was doubling every 5.5 months \cite{bloggrowth2005}.
+A blog is a \emph{frequently updated web site consisting of personal observations, excerpts from other sources, etc., typically run by a single person, and usually with hyperlinks to other sites; an online journal or diary.} -- Oxford English Dictionary\\
 Given the nature of blogs, they are expectedly highly volatile web resources.
@@
 Blogs are a popular means of communication and expression of ideas and have been adopted by universities, institutions and scolars (reference?).
-Recenlty, blogs have also been used to disseminate ideas in times of political turmoil or even war (http://ijoc.org/index.php/ijoc/article/download/1242/597 - Social Media in the Egyptian Revolution).
+Recenlty, blogs have also been used to disseminate ideas in times of political turmoil or even war\cite{nahedeltantawy2012}.
 Their political, scientific and cultural significance is undisputed. (rephrase to avoid need for reference?)
@@
 However, to this day there is no standard method or authority that ensures blog archiving and long-term digital preservation.
-There is no guarantee that a disappearing or disappeared blog will ever be retrievable in the future (A Tale of a Disappearing Website : http://blogs.loc.gov/digitalpreservation/2012/01/a-tale-of-a-disappearing-website/ AND Considerations for the Preservation of Blogs : http://www.digitalpreservationeurope.eu/publications/briefs/preservartion\_blogs.pdf)
+There is no guarantee that a disappearing or disappeared blog will ever be retrievable in the future \cite{anderson2012}
 Therefore, it is crucial that the necessary foundations for blog archiving are put in place.
@@
 
-\comment{(from wikipedia) The largest web archiving organization based on a bulk crawling approach is the Internet Archive which strives to maintain an archive of the entire Web.
+% \comment{(from wikipedia) The largest web archiving organization based on a bulk crawling approach is the Internet Archive which strives to maintain an archive of the entire Web.
 National libraries, national archives and various consortia of organizations are also involved in archiving culturally important Web content.
@@
 
-\comment{Aims and contributions of this work. Example from my last paper to see the format:\\
-http://purl.pt/24107/1/iPres2013\_PDF/\\
-CLEAR\%20a\%20credible\%20method\%20to\%20\\
-evaluate\%20website\%20archivability.pdf}
+% \comment{Aims and contributions of this work. Example from my last paper to see the format:\\
+% http://purl.pt/24107/1/iPres2013\_PDF/\\
+% CLEAR\%20a\%20credible\%20method\%20to\%20\\
+% evaluate\%20website\%20archivability.pdf}
 
-\comment{Semi-structured nature of Web pages\\
-Labeled ordered rooted trees\\
-XML Path Language(XPath)}
+% \comment{Semi-structured nature of Web pages\\
+% Labeled ordered rooted trees\\
+% XML Path Language(XPath)}
 
-\TODO{should we explain here that article is the actual content (text) of a blog post?
+% \TODO{should we explain here that article is the actual content (text) of a blog post?
 Or is it already clear enough?
@@
 
-\TODO{Is it ok to call this "the BlogForever cralwer", given that it will be the 3rd implementation?}
+% \TODO{Is it ok to call this "the BlogForever cralwer", given that it will be the 3rd implementation?}
 
-Intro contents (more or less)
-\begin{enumerate}
-  \item Introduce the importance for blog preservation
-  \item Explain the difficulties in harvesting blogs
-  \item Explain why open source and Invenio
-  \item Introduce the blog crawler
-\end{enumerate}
+% Intro contents (more or less)
+% \begin{enumerate}
+%   \item Introduce the importance for blog preservation
+%   \item Explain the difficulties in harvesting blogs
+%   \item Explain why open source and Invenio
+%   \item Introduce the blog crawler
+% \end{enumerate}
 
-Challenges and constraints:
-\begin{enumerate}
-  \item size of blogosphere (Dealing with large volumes of data)
-  \item heterogeneous nature of different publishing platforms
-  \item ever-changing structure
-  \item dynamically created content using modern web technologies.
-  \item complexity in parsing blogs from unstructured data to structured information.
-  \item programmatic access to blog content unavailable
-  \item unpredictable publishing rate --> scalability
-  \item Providing a high degree of automation
-\end{enumerate}
+% Challenges and constraints:
+% \begin{enumerate}
+%   \item size of blogosphere (Dealing with large volumes of data)
+%   \item heterogeneous nature of different publishing platforms
+%   \item ever-changing structure
+%   \item dynamically created content using modern web technologies.
+%   \item complexity in parsing blogs from unstructured data to structured information.
+%   \item programmatic access to blog content unavailable
+%   \item unpredictable publishing rate --> scalability
+%   \item Providing a high degree of automation
+% \end{enumerate}

### 2014-01-14 tex/runningtimeFigure.tex
Add refs and clean up a bit

@@
 
-    set yrange [0:55]
+    set yrange [0:44]
     set xrange [0:65]
@@
     plot 'data/runningtime.txt'\
-       u 0:1 smooth cumulative w lines linewidth 5 title 'Our approach',\
-    '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
-    '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
-    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
+       u 0:1 smooth cumulative w lines linewidth 3 title 'Our approach',\
+    '' u 0:4 smooth cumulative w lines linewidth 4 title 'Readability',\
+    '' u 0:2 smooth cumulative w lines linewidth 4 title 'Boilerpipe',\
+    '' u 0:3 smooth cumulative w lines linewidth 4 title 'Goose'
   \end{gnuplot}

### 2014-01-14 tex/2-related-work.tex
Improvements in the Related work section

--- 2013-11-25 tex/2-related-work.tex
@@
 \section{Related work}
-2-related-work.tex
 
-Web Object Identification for Web Automation and Meta-Search,
-\\
-http://www.dbai.tuwien.ac.at/proj/ta\\
-mcrow/download/Kordomatis2013WIMS.pdf
+Web archiving is a challenging and very interesting problem and has been the subject of many studies as well as the goal of several projects.
+\comment{Mention Internet Archive here and maybe another generic web archiving project}
 
-Self-supervised Automated Wrapper Generation for Weblog Data Extraction,
-\\
-https://github.com/OlivierBlanvillai\\
-n/blogforever-crawler-publication/raw\\
-/master/papers/bncod\_published.pdf
+A fraction of web archiving studies and projects focus on the specific problem of blog harvesting and archiving.
+They focus on the unique nature of blogs as dynamic web resources with a usually common set of attributes.
+Each entry in a blog, commonly called a post, has a title, an author, a publication date, some content and possibly some descriptive tags.
+(In this section we review some studies and projects that introduce and describe such techniques.)
 
-Web Data Extraction, Applications and Techniques: A Survey,
-\\
-http://www.emilio.ferrara.name/wp-co\\
-ntent/uploads/2011/07/survey-csur.pdf
+Blogs are strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference - needed?).
+Web feeds are structured documents (often XML-based) that advertize and provide access to a website's content.
+Given their format, web feeds constitute an excellent source for blog archiving.
+They do, however, present some problems: (a) web feeds contain only the latest posts of a blog (usually 20) and (b) web feeds may only provide a summary or a fraction of the entire content of each blog post.
+More advanced methods and techniques have to be employed in order to achieve quality blog archiving.
 
-Archiving Data Objects using Web Feeds,
-\\
-http://hal.archives-ouvertes.fr/docs\\
-/00/53/79/62/PDF/iwawienna.pdf
+Here mention projects that use web feeds for discovery and compare them to ours.
+\begin{itemize}
+  \item ( Zero-cost Labelling with Web Feeds for Weblog Data Extraction - http://www2013.org/companion/p73.pdf).
+  \item ( Self-supervised Automated Wrapper Generation for Weblog Data Extraction - https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod\_published.pdf).
+  \item ( Archiving Data Objects using Web Feeds - http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf).
+\end{itemize}
+Some of these should also be in the comparison for extraction methods.
 
-Intelligent and Adaptive Crawling of Web Applications for Web Archiving,
-\\
-http://pierre.senellart.com/publicat\\
-ions/faheem2013intelligent.pdf
+Here mention projects that use other techniques for discovery and compare them to ours.
+\begin{itemize}
+  \item ???
+\end{itemize}
 
-Zero-cost Labelling with Web Feeds for Weblog Data Extraction,
-\\
-http://www2013.org/companion/p73.pdf\\
+Here mention projects that use various techniques for extraction and compare them to ours.
+\begin{itemize}
+  \item ( Web Object Identification for Web Automation and Meta-Search - http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf).
+  \item ( OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications - http://www.vldb.org/pvldb/vol4/p1016-furche.pdf).
+  \item ( Intelligent and Adaptive Crawling of Web Applications for Web Archiving - http://pierre.senellart.com/publications/faheem2013intelligent.pdf).
+  \item ( Web Data Extraction, Applications and Techniques: A Survey - http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf).
+\end{itemize}
 
-OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications,
-\\
-http://www.vldb.org/pvldb/vol4/p1016\\
--furche.pdf
+Here mention that there is no comparison for the JavaScript rendering as there are no similar projects.
+\begin{itemize}
+  \item ???
+\end{itemize}

### 2014-01-14 tex/1-intro.tex
Add plan of the future into

@@
-\section{Intro}
+\section{Introduction}
+
+This will be reorganized like this:\\
+paragraph 1:\\
+- Blog disappear every day, Some of them are important\\
+- In contrast to newspaper and centralized services like FaceBook and Twitter there are no standards and no authorities to backup blogs\\
+- Yet, blogs are an important part of today's web (number, adoption by academics and organizations)\\
+\\
+paragraph 2:\\
+- Challenges (Now starts with "The blogosphere is a massive...")\\
+\\
+paragraph 3:\\
+- Web feed, why they are so handy (merged with "Blogs are strongly associated with web feeds...")
 
@@
 As the volume and importance of the information on the World Wide Web increases, web archiving becomes more and more relevant and its importance becomes clearer.
-Web crawlers are an essential part of web archiving, allowing for automated capturing of web resources.
-An efficient and accurate web crawler is the first crucial step to successful digital preservation.
+\comment{too early imo- Web crawlers are an essential part of web archiving, allowing for automated capturing of web resources.
+An efficient and accurate web crawler is the first crucial step to successful digital preservation.}
 
 By June 2008 the Technorati Internet search engine for blogs reported indexing 112.8 million blogs \cite{technoratidata2008} while in July 2005 they had estimated that the size of the blogosphere was doubling every 5.5 months \cite{bloggrowth2005}.
-A blog is a \emph{frequently updated web site consisting of personal observations, excerpts from other sources, etc., typically run by a single person, and usually with hyperlinks to other sites; an online journal or diary.} -- Oxford English Dictionary\\
-Given the nature of blogs, they are expectedly highly volatile web resources.
+A blog is a \emph{frequently updated web site consisting of personal observations, excerpts from other sources, etc., typically run by a single person, and usually with hyperlinks to other sites; an online journal or diary.} -- Oxford English Dictionary\\ Given the nature of blogs, they are expectedly highly volatile web resources.
 
@@
 Recenlty, blogs have also been used to disseminate ideas in times of political turmoil or even war\cite{nahedeltantawy2012}.
-Their political, scientific and cultural significance is undisputed. (rephrase to avoid need for reference?)
+Their political, scientific and cultural significance is undisputed.
+(rephrase to avoid need for reference?)
 
 However, to this day there is no standard method or authority that ensures blog archiving and long-term digital preservation.
-There is no guarantee that a disappearing or disappeared blog will ever be retrievable in the future \cite{anderson2012}
-Therefore, it is crucial that the necessary foundations for blog archiving are put in place.
+There is no guarantee that a disappearing or disappeared blog will ever be retrievable in the future \cite{anderson2012} Therefore, it is crucial that the necessary foundations for blog archiving are put in place.
 
@@
 
-*** Do we need to present issues in current solutions here? Is it needed? Can we write it in "Related Work" instead? ***
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Contributions and Overview}
+We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing, extracting content and monitoring updates of blogs.
+Our contributions are in particular:
 
-Our solution aims to tackle the challenges and constraints described above by employing a series of techniques and algorithms to harvest modern weblogs in a high-quality, accurate and efficient manner.
-We base our crawler on one of the most common and standard characteristics of blogs: web feeds.
-Explain:
-\begin{enumerate}
-  \item what feeds are, and what we use them for (discovery, extraction)
-  \item the use of HTML + XPATH
-  \item the use of efficient string similarity
-  \item the use of javascript rendering
-\end{enumerate}
+\begin{itemize}
+  \item We present a new generic algorithm to build extraction from a set of pages and target content.
+We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
+  \item We show how to use this algorithm to extract blog articles, and how it can be adapted to extract authors, publication dates and comments.
+  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
+  \item We show who use make use of a complete web browser to render JavaScript powered web pages before processing them.
+This step allows our crawler to effectively harvest blogs build with modern technology, such at the increasingly popular third-party commenting systems.
+  \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time.
+A comparison is made with three state-of-the-art article extraction algorithms.
+\end{itemize}
 
-The rest of the paper is organized as follows: Related work is presented in Section 2; the algorithms we developed to extract blog post articles, authors, dates and comments are detailed in Section 3; in section 4 we give an overview of the different techniques used in our crawler; evaluation experiments are described and commented in Section 5.
-We finally conclude and present future work in Section 6.
-
-% \comment{(from wikipedia) The largest web archiving organization based on a bulk crawling approach is the Internet Archive which strives to maintain an archive of the entire Web.
-National libraries, national archives and various consortia of organizations are also involved in archiving culturally important Web content.
-Commercial web archiving software and services are also available to organizations who need to archive their own web content for corporate heritage, regulatory, or legal purposes.}
-
-% \comment{Aims and contributions of this work. Example from my last paper to see the format:\\
-% http://purl.pt/24107/1/iPres2013\_PDF/\\
-% CLEAR\%20a\%20credible\%20method\%20to\%20\\
-% evaluate\%20website\%20archivability.pdf}
-
-% \comment{Semi-structured nature of Web pages\\
-% Labeled ordered rooted trees\\
-% XML Path Language(XPath)}
-
-% \TODO{should we explain here that article is the actual content (text) of a blog post?
-Or is it already clear enough?
--> I don't know.
-I used "blog post content" as "article + title + author + date + comments" in other sentences but it might be good to say somewhere that "blog post article" refers to the "core textual content of a blog post".}
-
-% \TODO{Is it ok to call this "the BlogForever cralwer", given that it will be the 3rd implementation?}
-
-% Intro contents (more or less)
-% \begin{enumerate}
-%   \item Introduce the importance for blog preservation
-%   \item Explain the difficulties in harvesting blogs
-%   \item Explain why open source and Invenio
-%   \item Introduce the blog crawler
-% \end{enumerate}
-
-% Challenges and constraints:
-% \begin{enumerate}
-%   \item size of blogosphere (Dealing with large volumes of data)
-%   \item heterogeneous nature of different publishing platforms
-%   \item ever-changing structure
-%   \item dynamically created content using modern web technologies.
-%   \item complexity in parsing blogs from unstructured data to structured information.
-%   \item programmatic access to blog content unavailable
-%   \item unpredictable publishing rate --> scalability
-%   \item Providing a high degree of automation
-% \end{enumerate}
+Although our crawler implementation is integrated with the BlogForever platform, the presented techniques and algorithms can be used in other applications related to Wrapper Generation and Web Data Extraction.

### 2014-01-14 tex/3-algorithms.tex
Improvements to the Introduction section
Add plan of the future into

@@
 
-This section explains in detail the algorithm we developed to extract blog posts articles as well as its variations for authors, dates and comments.
-Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of a blog \comment{Does "all posts of a blog" need a better formulation?
-Maybe "across/throughout a blog"?}.Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
+This section explains in detail the algorithm we developed to extract blog post articles as well as its variations for authors, dates and comments.
+Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of throughout a blog.
+Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
 

### 2014-01-14 tex/main.tex
Add algo1.
Pull out algos and tables, 3-algorithms close to done.
up
Time complexity.
Linear algo started.
Algorithm 2 done.
Reread it all.
Minor fixes in captions + some of variations subsection.
Variations done.
Add first gnuplot figure.
Fix compilation errors with gnuplot and commath.
Re-read all the paper, lots of rephrasing.
Remove left char that breaks the compilation.
Eval++
Minor fixes, add main.pdf under version control.
Solve some \cite TODOs.
Un-draft build.
Up
Add plan of the future into

@@
+% \documentclass[draft]{acm_proc_article-sp}
 \documentclass{acm_proc_article-sp}
 
-\usepackage[autostyle=false, style=english]{csquotes}
+\usepackage[ruled, vlined]{algorithm2e}
 \usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage{color}
+\usepackage[autostyle=false, style=english]{csquotes}
+\usepackage[usenames,dvipsnames]{color}
+\usepackage[justification=centering]{caption}
+\usepackage{amssymb}
+\usepackage{booktabs}
+\usepackage{microtype}
 \usepackage{enumitem}
-\usepackage{epsfig}
 \usepackage{graphicx}
-\usepackage{hyperref}
+\usepackage{gnuplottex}
+\usepackage{pifont}
 \usepackage{quoting}
@@
 \usepackage{sepfootnotes}
+\usepackage{setspace}
+\usepackage[pdfpagelabels=false]{hyperref}
+\usepackage{hypcap}
 
+\MakeOuterQuote{"}
 \newfootnotes{A}
-\MakeOuterQuote{"}
 \quotingsetup{vskip=0pt,font={itshape}}
-\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
-\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
+\setenumerate{noitemsep,topsep=0pt,parsep=2pt,partopsep=0pt}
+\setitemize{noitemsep,topsep=0pt,parsep=4pt,partopsep=0pt}
+\setlength\floatsep{1.25\baselineskip plus 3pt minus 2pt}
+\setlength\textfloatsep{1.25\baselineskip plus 3pt minus 2pt}
+\setlength\intextsep{1.25\baselineskip plus 3pt minus 2 pt}
+\def\algorithmautorefname{Algorithm}
+\graphicspath{{img/}}
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
 
-\newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
-\newcommand{\code}[1]{\texttt{#1}}
-\newcommand{\surl}[1]{\urlstyle{ff}\url{#1}}
+\newcommand\TODO[1]{\emph{\color{Red} TODO: #1}}
+\renewcommand\comment[1]{\emph{\color{Gray}<#1>}}
+\newcommand\edit[1]{\emph{\color{Green}<#1>}}
+\newcommand\code[1]{\texttt{#1}}
+\newcommand\coderef[1]{\texttt{\ref{#1}}}
+\newcommand\stringliteral[1]{\texttt{\char`\"#1\char`\"}}
+\newcommand\len[1]{|#1|}
+\newcommand\set[1]{\{#1\}}
+\newcommand\surl[1]{\urlstyle{ff}\url{#1}}
+\newcommand\Oof[1]{$\mathcal{O}(#1)$}
 
@@
 
-  \title{BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs}
+  \title{BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs}
 
@@
          \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
-         \affaddr{1014 Lausanne, Switzerland}\\
+         \affaddr{1015 Lausanne, Switzerland}\\
          \email{\surl{olivier.blanvillain@epfl.ch}}
@@
 
+  \hypersetup{pageanchor=false}
   \maketitle
@@
 
-  \keywords{Web archiving, Web crawling, ...}
+  \keywords{Web crawling, Web Data Extraction, Wrapper Generation, Web archiving, ...}
 
+  \input{algos.tex}
+  \input{tables.tex}
   \input{1-intro.tex}
@@
   \bibliographystyle{abbrv}
-  \bibliography{main}
+  \bibliography{main,manual}
 

### 2014-01-14 tex/5-evaluation.tex
Format preservation table and add some comments

@@
 Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.
-Our final solution consists in taking a screenshot with our embeded web browser after the JavaScript rendering.
-Before opting for this approach, we considered 3 other solutions: GNU Wget, wkhtmltopdf and OXPath.
+Our final solution consists in using the embeded web browser to take screenshots after each page rendering.
+Before opting for this approach we considered 3 other solutions: GNU wget, wkhtmltopdf and OXPath.
 This subsection relates our evaluation of these tools for the specific purpose.
+
+\TODO{Is this whole subsection legitimate?
+It this part is not really relevant we could also simply not include it...
+I guess it is not a really useful from a research point of vue, but it might still be of some use for others to know what each of them can do.
+I think it's also important to say at some point how long it takes to render a pages, because if only look at the graph it seams like this is all super fast, but when we use PhantomJS the thing seriously slows down...}
 
@@
 
-\TODO{}
-
 % intro, plan (why we pick these projects, what we want to show with this evaluation)

### 2014-01-15 tex/1-intro.tex
test
Started on the new intro

@@
 \section{Introduction}
+
+Blogs disappear every day.
+Losing data is obviously undesirable, but even more so when this data has historic, politic or scientific value.
+In contrast to books, newspapers or centralized web platforms like FaceBook and Twitter, there is no standard method or authority that ensures blog archiving and long-term digital preservation.
+\TODO{Somewere, \cite{anderson2012}}.
+
+Yet, blogs are an important part of today's web
+
+By June 2008 the Technorati Internet search engine for blogs reported indexing 112.8 million blogs \cite{technoratidata2008}
+
+Blogs are a popular means of communication and expression of ideas and have been adopted by universities, institutions and scolars (reference?).
+Recenlty, blogs have also been used to disseminate ideas in times of political turmoil or even war\cite{nahedeltantawy2012}.
+Their political, scientific and cultural significance is undisputed.
+(rephrase to avoid need for reference?)
+
+Given the nature of blogs, they are expectedly highly volatile web resources.
+
+However, to this day there is no standard method or authority that ensures blog archiving and long-term digital preservation.
+There is no guarantee that a disappearing or disappeared blog will ever be retrievable in the future \cite{anderson2012} Therefore, it is crucial that the necessary foundations for blog archiving are put in place.
+
+Recently, they have also been used to disseminate ideas in times of political turmoil or even war\cite{nahedeltantawy2012},
+
+Blogs are a popular means of communication and expression of ideas and have been adopted by universities, institutions and scolars (reference?).
+Recently, blogs have also been used to disseminate ideas in times of political turmoil or even war\cite{nahedeltantawy2012}.
+Their political, scientific and cultural significance is undisputed.
+(rephrase to avoid need for reference?)
 
@@
 paragraph 3:\\
-- Web feed, why they are so handy (merged with "Blogs are strongly associated with web feeds...")
+- Web feed, why they are so handy (merged with 
+"Blogs are strongly associated with web feeds...")
 

### 2014-01-15 tex/1-intro.tex
Intro almost done, RSS left

--- 2014-01-14 tex/1-intro.tex
@@
 
-This will be reorganized like this:\\
-paragraph 1:\\
-- Blog disappear every day, Some of them are important\\
-- In contrast to newspaper and centralized services like FaceBook and Twitter there are no standards and no authorities to backup blogs\\
-- Yet, blogs are an important part of today's web (number, adoption by academics and organizations)\\
-\\
-paragraph 2:\\
-- Challenges (Now starts with "The blogosphere is a massive...")\\
-\\
-paragraph 3:\\
-- Web feed, why they are so handy (merged with "Blogs are strongly associated with web feeds...")
+Blogs disappear every day.
+Losing data is obviously undesirable, but even more so when this data has historic, politic or scientific value.
+In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation.
+Yet, blogs are an important part of today's web: the WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}.
+Blogs also showed to be an important resources during the 2011 Egyptian revolution where they played an instrumental role in the organization and implementation of protests.
+\cite{nahedeltantawy2012}\comment{not sure where to put this one}.
+The need for preservation for this volatile communication medium is today a necessity.\comment{Do you have a better closing sentence?}
 
-Web archiving is the process of harvesting and gathering web content in order to safely preserve it for posterity.
-As the volume and importance of the information on the World Wide Web increases, web archiving becomes more and more relevant and its importance becomes clearer.
-\comment{too early imo- Web crawlers are an essential part of web archiving, allowing for automated capturing of web resources.
-An efficient and accurate web crawler is the first crucial step to successful digital preservation.}
+Among the challenges in developing a blog archiving software is providing an automatic web crawler to traverse blogs and accurately their content.
+The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary.
+The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents.
+Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, invalidating traditional web crawling techniques.
 
-By June 2008 the Technorati Internet search engine for blogs reported indexing 112.8 million blogs \cite{technoratidata2008} while in July 2005 they had estimated that the size of the blogosphere was doubling every 5.5 months \cite{bloggrowth2005}.
-A blog is a \emph{frequently updated web site consisting of personal observations, excerpts from other sources, etc., typically run by a single person, and usually with hyperlinks to other sites; an online journal or diary.} -- Oxford English Dictionary\\ Given the nature of blogs, they are expectedly highly volatile web resources.
-
-Blogs are a popular means of communication and expression of ideas and have been adopted by universities, institutions and scolars (reference?).
-Recenlty, blogs have also been used to disseminate ideas in times of political turmoil or even war\cite{nahedeltantawy2012}.
-Their political, scientific and cultural significance is undisputed.
-(rephrase to avoid need for reference?)
-
-However, to this day there is no standard method or authority that ensures blog archiving and long-term digital preservation.
-There is no guarantee that a disappearing or disappeared blog will ever be retrievable in the future \cite{anderson2012} Therefore, it is crucial that the necessary foundations for blog archiving are put in place.
-
-The blogosphere is a massive web resource of unstructured data.
-Identifying, harvesting and parsing that data can be a very challenging task.
-The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of efficient extraction techniques that offer a high degree of automation necessary.
-The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents.
-Finaly, modern blogs heavily rely on dynamically created content to present information, using the latest web technologies, invalidating most traditional web crawling techniques.
+Blogs are strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference - needed?).
+Web feeds are structured documents (often XML-based) that advertize and provide access to a website's content.
+Given their format, web feeds constitute an excellent source for blog archiving.
+They do, however, present some problems: (a) web feeds contain only the latest posts of a blog (usually 20) and (b) web feeds may only provide a summary or a fraction of the entire content of each blog post.
+More advanced methods and techniques have to be employed in order to achieve quality blog archiving.
 

### 2014-01-15 tex/3-algorithms.tex
Intro almost done, RSS left

@@
 Extracting metadata and content from HTML documents is a challenging task.
-Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}.
+Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2014}.
 For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page \cite{w3c2002}.
-More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}.
+More recently, specifications such as microdata \cite{whatwg2014} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2014}.
 In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}.

### 2014-01-15 tex/4-techniques.tex
Up
Add plan of the future into
Intro almost done, RSS left

@@
 \section{Techniques}
+\label{techniques}
 
@@
 JavaScript is a widely used language for client-side scripting.
-While some applications simply use it for aesthetics (menus, animations, \ldots), an increasing number of websites use JavaScript to download and display content.
+While some applications simply use it for aesthetics, an increasing number of websites use JavaScript to download and display content.
 In such cases, traditional HTML based crawlers do not see web pages as they are presented to a human visitor by a web browser, and might therefore be obsolete for data extraction.
@@
 In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation.
-The most frequent cases were blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services.
+The most frequent cases were blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2014} comment hosting services.
 For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
@@
 To support blogs with JavaScript-generated content, we embed a full web browser into the crawler.
-After considering multiple options, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performance and scripting capabilities.
+After considering multiple options, we opted for PhantomJS \cite{phantomjs2014}, a headless web browser with great performance and scripting capabilities.
 The JavaScript rendering is the very first step of web page processing.
@@
   \includegraphics[width=0.47\textwidth]{scrapy_architecture}
-  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2013})}
+  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2014})}
   \label{architecture}
@@
 
-Our crawler is built on top of Scrapy \cite{scrapy2013}, an open-source Python framework for web crawling.
+Our crawler is built on top of Scrapy \cite{scrapy2014}, an open-source Python framework for web crawling.
 Scrapy provides an elegant and modular architecture illustrated in \autoref{architecture}.
@@
 After being downloaded and identified as blog posts (details in \autoref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
-\begin{enumerate}[noitemsep]
+\begin{enumerate}
   \item Render JavaScript

### 2014-01-15 tex/1-intro.tex
Update 1-intro.tex

@@
 Yet, blogs are an important part of today's web: the WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}.
-Blogs also showed to be an important resources during the 2011 Egyptian revolution where they played an instrumental role in the organization and implementation of protests.
+Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests.
 \cite{nahedeltantawy2012}\comment{not sure where to put this one}.
@@
 
-Among the challenges in developing a blog archiving software is providing an automatic web crawler to traverse blogs and accurately their content.
+Among the challenges in developing a blog archiving software is* providing an automatic web crawler to \TODO{better keyword} traverse blogs and accurately extract their content.
 The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary.
 The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents.
-Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, invalidating traditional web crawling techniques.
+Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.
 
@@
   \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
-  \item We show who use make use of a complete web browser to render JavaScript powered web pages before processing them.
-This step allows our crawler to effectively harvest blogs build with modern technology, such at the increasingly popular third-party commenting systems.
+  \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them.
+This step allows our crawler to effectively harvest blogs built with modern technology, such as the increasingly popular third-party commenting systems.
   \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time.

### 2014-01-15 tex/1-intro.tex
up

--- 2014-01-15 tex/1-intro.tex
@@
 
+A key characteristic of blogs which differentiates them from regular website is their association with web feeds.
+Their primary use is to provide a uniform subscription mechanism, allowing users to keep track of the latest updates without the need periodically visit the blogs of interest.
+
+push pull model
+usefully in many ways,
+
+-> we can use web feed to build content extraction algorithm that, as we will see, outperform the more generic approaches that not rely on webfeed.
+
+an additional tool compared to regular web sites that is very usefully for monitoring updates and obtaining content.
+
+Blogs are strongly associated with web feeds, using technologies such as RSS and Atom. Web feeds are structured documents (often XML-based) that advertise and provide access to a website's content. 
+They do, however, present some problems:
+(a) web feeds contain only the latest posts of a blog (usually 20) and
+(b) web feeds may only provide a summary or a fraction of the entire content of each blog post. More advanced methods and techniques have to be employed in order to achieve quality blog archiving.
+
 Blogs are strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference - needed?).
@@
 \subsection{Contributions and Overview}
-We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing, extracting content and monitoring updates of blogs.
-Our contributions are in particular:
+We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing, extracting content and monitoring updates of blogs. Our contributions are in particular:
 
 \begin{itemize}
-  \item We present a new generic algorithm to build extraction from a set of pages and target content.
+  \item We present a new algorithm to build extraction rules from web feeds.
 We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
-  \item We show how to use this algorithm to extract blog articles, and how it can be adapted to extract authors, publication dates and comments.
+  \item We show how to use this algorithm for blog article extraction, and how it can be adapted to authors, publication dates and comments.
   \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.

### 2014-01-16 tex/1-intro.tex
Into on RSS almost done, some issues to compile w latexmk

@@
 Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests.
-\cite{nahedeltantawy2012}\comment{not sure where to put this one}.
-The need for preservation for this volatile communication medium is today a necessity.\comment{Do you have a better closing sentence?}
+\cite{nahedeltantawy2012}\comment{Not sure where to put this one...}.
+The need for preservation of this volatile communication medium is today a necessity.\comment{Do you have a better closing sentence?}
 
-Among the challenges in developing a blog archiving software is* providing an automatic web crawler to \TODO{better keyword} traverse blogs and accurately extract their content.
+Among the challenges in developing a blog archiving software is* providing a web crawler capable of efficiently traversing blogs to harvest their content.
 The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary.
@@
 A key characteristic of blogs which differentiates them from regular website is their association with web feeds.
-Their primary use is to provide a uniform subscription mechanism, allowing users to keep track of the latest updates without the need periodically visit the blogs of interest.
+Their primary use is to provide a uniform subscription mechanism, allowing users to keep track of the latest updates without the need to visit their blogs of interest.
+The two competing web feed technologies, Atom and RSS, use **the pull model**.
+Concretely, a web feed is a XML file containing links to the last posts of blog, along with abstracts or the full texts of articles and the associated metadate.
 
-push pull model
 usefully in many ways,
 
--> we can use web feed to build content extraction algorithm that, as we will see, outperform the more generic approaches that not rely on webfeed.
+-> we can use web feed to build content extraction algorithm that, as we will see, outperform the more generic approaches that not rely on web feed.
 

### 2014-01-16 tex/3-algorithms.tex
up
Into on RSS almost done, some issues to compile w latexmk

@@
 
-This section explains in detail the algorithm we developed to extract blog post articles as well as its variations for authors, dates and comments.
+This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments.
 Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of throughout a blog.
@@
 % input from observations.
-Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, its title, authors and publication date.
+Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date.
+We call these fields \emph{targets} as they constitute the data our crawler aims to extract.
 Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

### 2014-01-16 tex/1-intro.tex
Intro done

--- 2014-01-15 tex/1-intro.tex
@@
 Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests.
-\cite{nahedeltantawy2012}\comment{not sure where to put this one}.
-The need for preservation for this volatile communication medium is today a necessity.\comment{Do you have a better closing sentence?}
+\cite{nahedeltantawy2012}.
+The need for preservation of this volatile communication medium is today a necessity.
+\comment{Do you have a better closing sentence?}
 
-Among the challenges in developing a blog archiving software is* providing an automatic web crawler to \TODO{better keyword} traverse blogs and accurately extract their content.
+Among the challenges in developing a blog archiving software is the design of a web crawler capable of efficiently traversing blogs to harvest their content.
 The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary.
@@
 A key characteristic of blogs which differentiates them from regular website is their association with web feeds.
-Their primary use is to provide a uniform subscription mechanism, allowing users to keep track of the latest updates without the need periodically visit the blogs of interest.
-
-push pull model
-usefully in many ways,
-
--> we can use web feed to build content extraction algorithm that, as we will see, outperform the more generic approaches that not rely on webfeed.
-
-an additional tool compared to regular web sites that is very usefully for monitoring updates and obtaining content.
-
-Blogs are strongly associated with web feeds, using technologies such as RSS and Atom. Web feeds are structured documents (often XML-based) that advertise and provide access to a website's content. 
-They do, however, present some problems:
-(a) web feeds contain only the latest posts of a blog (usually 20) and
-(b) web feeds may only provide a summary or a fraction of the entire content of each blog post. More advanced methods and techniques have to be employed in order to achieve quality blog archiving.
-
-Blogs are strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference - needed?).
-Web feeds are structured documents (often XML-based) that advertize and provide access to a website's content.
-Given their format, web feeds constitute an excellent source for blog archiving.
-They do, however, present some problems: (a) web feeds contain only the latest posts of a blog (usually 20) and (b) web feeds may only provide a summary or a fraction of the entire content of each blog post.
-More advanced methods and techniques have to be employed in order to achieve quality blog archiving.
+Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to visit their blogs of interest.
+Concretely, a web feed is a XML file containing links to the lastest blog posts along with their articles (abstract or full text) and associated metadata.
+While web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest old content.
 

### 2014-01-16 tex/1-intro.tex
Up

@@
 The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary.
-The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents.
+The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited\TODO{"limited" repetition is odd} by the ever-changing structure of blog contents.
 Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.
 
-A key characteristic of blogs which differentiates them from regular website is their association with web feeds.
-Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to visit their blogs of interest.
-Concretely, a web feed is a XML file containing links to the lastest blog posts along with their articles (abstract or full text) and associated metadata.
-While web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest old content.
+A key characteristic of blogs which differentiates them from regular websites is their association with web feeds.
+Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to actually visit blogs.
+Concretely, a web feed is a XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata.
+Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest old content.
 
@@
 We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
-  \item We show how to use this algorithm for blog article extraction, and how it can be adapted to authors, publication dates and comments.
-  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
+  \item We show how to use this algorithm for blog article extraction and how it can be adapted to authors, publication dates and comments.
+  \item nevertheless the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
   \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them.

### 2014-01-17 tex/2-related-work.tex
Related work started

--- 2013-11-25 tex/2-related-work.tex
@@
 \section{Related work}
-2-related-work.tex
 
-Web Object Identification for Web Automation and Meta-Search,
-\\
-http://www.dbai.tuwien.ac.at/proj/ta\\
-mcrow/download/Kordomatis2013WIMS.pdf
+- Web crawlers
 
-Self-supervised Automated Wrapper Generation for Weblog Data Extraction,
-\\
-https://github.com/OlivierBlanvillai\\
-n/blogforever-crawler-publication/raw\\
-/master/papers/bncod\_published.pdf
+we merged the crawling phase with the contente extraction which removed the need to store all web pages material and leads to a lighter process as we directly send things to the db
 
-Web Data Extraction, Applications and Techniques: A Survey,
-\\
-http://www.emilio.ferrara.name/wp-co\\
-ntent/uploads/2011/07/survey-csur.pdf
+- Blog crawlers
+focused on blog detection and content analysis such as political mouvement or popular personalities.
 
-Archiving Data Objects using Web Feeds,
-\\
-http://hal.archives-ouvertes.fr/docs\\
-/00/53/79/62/PDF/iwawienna.pdf
+- Wrapper generation
+these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.
 
-Intelligent and Adaptive Crawling of Web Applications for Web Archiving,
-\\
-http://pierre.senellart.com/publicat\\
-ions/faheem2013intelligent.pdf
+% Web archiving is a challenging and very interesting problem and has been the subject of many studies as well as the goal of several projects.
+% \comment{Mention Internet Archive here and maybe another generic web archiving project}
 
-Zero-cost Labelling with Web Feeds for Weblog Data Extraction,
-\\
-http://www2013.org/companion/p73.pdf\\
+% A fraction of web archiving studies and projects focus on the specific problem of blog harvesting and archiving.
+% They focus on the unique nature of blogs as dynamic web resources with a usually common set of attributes.
+% Each entry in a blog, commonly called a post, has a title, an author, a publication date, some content and possibly some descriptive tags.
+% (In this section we review some studies and projects that introduce and describe such techniques.)
 
-OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications,
-\\
-http://www.vldb.org/pvldb/vol4/p1016\\
--furche.pdf
+% Blogs are strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference - needed?).
+% Web feeds are structured documents (often XML-based) that advertize and provide access to a website's content.
+% Given their format, web feeds constitute an excellent source for blog archiving.
+% They do, however, present some problems: (a) web feeds contain only the latest posts of a blog (usually 20) and (b) web feeds may only provide a summary or a fraction of the entire content of each blog post.
+% More advanced methods and techniques have to be employed in order to achieve quality blog archiving.
+
+% Here mention projects that use web feeds for discovery and compare them to ours.
+% \begin{itemize}
+%   \item ( Zero-cost Labelling with Web Feeds for Weblog Data Extraction - http://www2013.org/companion/p73.pdf).
+%   \item ( Self-supervised Automated Wrapper Generation for Weblog Data Extraction - https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod\_published.pdf).
+%   \item ( Archiving Data Objects using Web Feeds - http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf).
+% \end{itemize}
+% Some of these should also be in the comparison for extraction methods.
+
+% Here mention projects that use other techniques for discovery and compare them to ours.
+% \begin{itemize}
+%   \item ???
+% \end{itemize}
+
+% Here mention projects that use various techniques for extraction and compare them to ours.
+% \begin{itemize}
+%   \item ( Web Object Identification for Web Automation and Meta-Search - http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf).
+%   \item ( OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications - http://www.vldb.org/pvldb/vol4/p1016-furche.pdf).
+%   \item ( Intelligent and Adaptive Crawling of Web Applications for Web Archiving - http://pierre.senellart.com/publications/faheem2013intelligent.pdf).
+%   \item ( Web Data Extraction, Applications and Techniques: A Survey - http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf).
+% \end{itemize}
+
+% Here mention that there is no comparison for the JavaScript rendering as there are no similar projects.
+% \begin{itemize}
+%   \item ???
+% \end{itemize}

### 2014-01-17 tex/4-techniques.tex
Into on RSS almost done, some issues to compile w latexmk
Related work started

@@
 In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation.
-The most frequent cases were blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2014} comment hosting services.
+The most frequent cases were blogs using the Disqus \cite{disqus2014} and LiveFyre \cite{livefyre2014} comment hosting services.
 For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
@@
 This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.
+
+\TODO{Write this properly...}
+One of the main advantages of having full control over the crawling process is that contrarily to the general purpose crawlers, we do not to store all the web pages material.
+Instead, the content of interest is computed "on the fly", and directly saved into the back-end system.
+This propriety ...
 

### 2014-01-17 tex/1-intro.tex

@@
 Blogs disappear every day.
-Losing data is obviously undesirable, but even more so when this data has historic, politic or scientific value.
+Losing data is obviously undesirable, but even more so when this data has historic, political or scientific value.
 In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation.
@@
 The need for preservation of this volatile communication medium is today a necessity.
-\comment{Do you have a better closing sentence?}
+\comment{Do you have a better closing sentence?} \comment{NK: I like it.
+But if needed: "The need to preserve this volatile communication medium is nowadays very clear."}
 
@@
 The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary.
-The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited\TODO{"limited" repetition is odd} by the ever-changing structure of blog contents.
+The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited\TODO{"limited" repetition is odd.
+NK: constrained, restrained, narrowed?} by the ever-changing structure of blog contents.
 Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.
@@
 Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to actually visit blogs.
-Concretely, a web feed is a XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata.
-Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest old content.
+Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata.
+Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest old content.\TODO{"old" sounds a bit weird.
+Maybe "previous" (...to *also* harvest previous content).
+Apart from that, we also need to download the blog web page to download the entire article in case the feed only contains an abstract.
+Should we also mention that here?
+(...to accuratelly harvest the latest as well older content.)}
 
@@
 \subsection{Contributions and Overview}
-We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing, extracting content and monitoring updates of blogs. Our contributions are in particular:
+We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing blogs, extracting their content and monitoring their updates.
+Our contributions are in particular:\TODO{NK: Instead: "In this paper:"}
 
@@
   \item We present a new algorithm to build extraction rules from web feeds.
-We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
+We then derive an optimized reformulation tied to a particular string similarity algorithm\TODO{or "method"} and show that this reformulated algorithm has a linear time complexity.
   \item We show how to use this algorithm for blog article extraction and how it can be adapted to authors, publication dates and comments.
-  \item nevertheless the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
+  \item \TODO{NK: This sentence starts a bit weird.
+Better start with a verb (We do...) like the others.} nevertheless the overall crawler architecture and the specific components we implemented to efficiently traverse blogs.
+We explain how our design allows for both modularity and scalability.
   \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them.

### 2014-01-17 tex/1-intro.tex
Merged comments

@@
 \cite{nahedeltantawy2012}.
-The need for preservation of this volatile communication medium is today a necessity.
-\comment{Do you have a better closing sentence?} \comment{NK: I like it.
-But if needed: "The need to preserve this volatile communication medium is nowadays very clear."}
+The need to preserve this volatile communication medium is nowadays very clear.
 
@@
 The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary.
-The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited\TODO{"limited" repetition is odd.
-NK: constrained, restrained, narrowed?} by the ever-changing structure of blog contents.
+The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further narrowed by the ever-changing structure of blog contents.
 Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.
@@
 Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata.
-Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest old content.\TODO{"old" sounds a bit weird.
-Maybe "previous" (...to *also* harvest previous content).
-Apart from that, we also need to download the blog web page to download the entire article in case the feed only contains an abstract.
-Should we also mention that here?
-(...to accuratelly harvest the latest as well older content.)}
+Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order harvest previous content.
 
@@
   \item We present a new algorithm to build extraction rules from web feeds.
-We then derive an optimized reformulation tied to a particular string similarity algorithm\TODO{or "method"} and show that this reformulated algorithm has a linear time complexity.
+We then derive an optimized reformulation tied to a particular string similarity metric and show that this reformulated algorithm has a linear time complexity.
   \item We show how to use this algorithm for blog article extraction and how it can be adapted to authors, publication dates and comments.
-  \item \TODO{NK: This sentence starts a bit weird.
-Better start with a verb (We do...) like the others.} nevertheless the overall crawler architecture and the specific components we implemented to efficiently traverse blogs.
-We explain how our design allows for both modularity and scalability.
+  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
   \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them.

### 2014-01-17 tex/1-intro.tex
Added related work on large scale distributed crawlers$

@@
 In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation.
-Yet, blogs are an important part of today's web: the WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}.
+Yet, blogs are an important part of today's web: WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}.
 Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests.
@@
 Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata.
-Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order harvest previous content.
+Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest previous content.
 
@@
 We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing blogs, extracting their content and monitoring their updates.
-Our contributions are in particular:\TODO{NK: Instead: "In this paper:"}
+Our contributions are in particular:
 

### 2014-01-17 tex/2-related-work.tex
Added related work on large scale distributed crawlers$

@@
 
-- Web crawlers
+\Anotecontent{wrapper}{In the literature, procedures to extract structured data from unstructured document are commonly referred as \emph{wrappers}.
+In this paper we decided to rather employ the less generic term of \emph{extraction rules} which is closer to our implementation.}
 
-we merged the crawling phase with the contente extraction which removed the need to store all web pages material and leads to a lighter process as we directly send things to the db
+The BlogForever Crawler combines ideas from previous work on general web crawlers and extraction rule\Anote{wrapper} generation algorithms.
 
-- Blog crawlers
-focused on blog detection and content analysis such as political mouvement or popular personalities.
+Research on large scale distributed crawler such as Mercator \cite{najork2001}, used by AltaVista, the spider discussed in \cite{shkapenyuk2002} or UbiCrawler \cite{boldi2003} are enlightening regarding the difficulties arising when scale out a crawler.
+One of the core issues seems to be in sharing the list URLs which have already been visited and need to be visited.
+While \cite{najork2001} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
+Both of these approaches require complex mechanisms to achieve fault tolerance.
+The BlogForever crawler circumvent this problem by delegating all state the back-end system.
+This shared nothing architecture between crawler instance is made possible by the fact that our unit of computations, crawling a entire blog, is much large than fetching a single URL and does not generate further crawling tasks.
+In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
+This removes one layer of complexity when compared to general crawler which need use a distributed file system or implement an aggregation mechanism in order to further use the collected data.
 
-- Wrapper generation
+\cite{shkapenyuk2002} used NFS, \cite{berger2011} uses HDFS
+
+- Wrapper generation\\
 these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.

### 2014-01-18 tex/5-evaluation.tex
Remove 5.3, move related work before the conclusion

--- 2014-01-14 tex/5-evaluation.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Preservation of blog visuals}
-\TODO{visuals/design/graphic/?}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection{Preservation of blog visuals}
+% \TODO{visuals/design/graphic/?}
 
-Additionally to the blog content extraction that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals.
+% Additionally to the blog content extraction that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals.
 Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.
-Our final solution consists in taking a screenshot with our embeded web browser after the JavaScript rendering.
-Before opting for this approach, we considered 3 other solutions: GNU Wget, wkhtmltopdf and OXPath.
+Our final solution consists in using the embeded web browser to take screenshots after each page rendering.
+Before opting for this approach we considered 3 other solutions: GNU wget, wkhtmltopdf and OXPath.
 This subsection relates our evaluation of these tools for the specific purpose.
 
-The first solution we considered was the GNU/Linux tool wget.
+% \TODO{Is this whole subsection legitimate?
+It this part is not really relevant we could also simply not include it...
+I guess it is not a really useful from a research point of vue, but it might still be of some use for others to know what each of them can do.
+I think it's also important to say at some point how long it takes to render a pages, because if only look at the graph it seams like this is all super fast, but when we use PhantomJS the thing seriously slows down...}
+
+% The first solution we considered was the GNU/Linux tool wget.
 With the appropriate options, wget can be used to download a webpage and the associated files (css, scripts and images).
@@
 
-Another solution we considered is wkhtmltopdf, a tool to produce pdf versions of web-pages.
+% Another solution we considered is wkhtmltopdf, a tool to produce pdf versions of web-pages.
 It uses the "print" function of it's embedded web browser to produce it's output and therefore supports all web technologies supported by it underling web browser.
 
-The OXPath project goes one step further by offering an extension of the XPath language to specify page interactions such as clicks and forms filling.
+% The OXPath project goes one step further by offering an extension of the XPath language to specify page interactions such as clicks and forms filling.
 It also make use of a complete web browser to render pages and execute page interactions sequentially.
@@
 
-\savevisualsTable
-
-\TODO{}
+% \savevisualsTable
 

### 2014-01-18 tex/main.tex
Intro almost done, RSS left
Into on RSS almost done, some issues to compile w latexmk
Added related work on large scale distributed crawlers$
Remove 5.3, move related work before the conclusion

@@
 \newcommand\TODO[1]{\emph{\color{Red} TODO: #1}}
-\renewcommand\comment[1]{\emph{\color{Gray}<#1>}}
-\newcommand\edit[1]{\emph{\color{Green}<#1>}}
+\renewcommand\comment[1]{\emph{\color{Gray}#1}}
 \newcommand\code[1]{\texttt{#1}}
@@
 
-  % % A category with the (minimum) three required fields
-  % \category{H.4}{Information Systems Applications}{Miscellaneous}
-  % %A category including the fourth, optional field follows...
-  % \category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+  ~\\\TODO{I'm for including the first two categories:}
 
-  \terms{Algorithms, Software Engineering}
+  \category{H.3.3}{Information Storage and Retrieval}{Information Search and Retrieval}[Information filtering, Selection process]
+  \category{\\D.2.8}{Software Engineering}{Metrics}[Complexity measures, Performance measures]
+  \category{\\H.3.7}{Information Storage and Retrieval}{Digital Libraries}[Collection]
+  \category{\\H.3.4}{Information Storage and Retrieval}{Systems and Software}[Performance evaluation]
 
-  \keywords{Web crawling, Web Data Extraction, Wrapper Generation, Web archiving, ...}
+  % In order of most significant, first letter of each word capitalized.
+  \terms{Design, Algorithms, Performance, Experimentation}
+
+  % In alphabetical order, first letter of the first word capitalized.
+  \keywords{Blog crawler, wrapper generation, web data extraction}
 
@@
   \input{tables.tex}
+  ~\\
   \input{1-intro.tex}
-  \input{2-related-work.tex}
   \clearpage
@@
   \clearpage
+  \input{2-related-work.tex}
+  \clearpage
   \input{6-conclusion-and-future-work.tex}

### 2014-01-18 tex/1-intro.tex
Merge Vangelis comments

@@
 
-Blogs disappear every day.
+Blogs disappear every day \cite{johnson2008blogs}.
 Losing data is obviously undesirable, but even more so when this data has historic, political or scientific value.
@@
 
-A key characteristic of blogs which differentiates them from regular websites is their association with web feeds.
+A key characteristic of blogs which differentiates them from regular websites is their association with web feeds \cite{lindahl2003weblogs}.
 Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to actually visit blogs.
-Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata.
+Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata \cite{board2007rss}.
 Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest previous content.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Contributions and Overview}
-We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing blogs, extracting their content and monitoring their updates.
-Our contributions are in particular:
+\TODO{
+  After writing the first sentece, you should write what are our aims in this work. (keep it in the same paragraph).\\
+  \\
+  Our main objective in this work are to create better algorithms and techniques for blog content extraction. (maybe you want to write something extra here+++, then, continue with the contributions:\\
+  \\
+  Our contributions can be summarised as follows:
+}
+
+We present the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
+Our contributions can be summarized as follows:
 
@@
 This step allows our crawler to effectively harvest blogs built with modern technology, such as the increasingly popular third-party commenting systems.
-  \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time.
-A comparison is made with three state-of-the-art article extraction algorithms.
+  \item We evaluate the content extraction and execution time of our algorithm against three state-of-the-art web article extraction algorithms.
 \end{itemize}
 
+\TODO{This part should be removed and the information contained here should go before the bullets (where you say what are our aims)}
+
 Although our crawler implementation is integrated with the BlogForever platform, the presented techniques and algorithms can be used in other applications related to Wrapper Generation and Web Data Extraction.
+
+The rest of the paper is organized as follows.
+In Section 2, we present related work on web crawlers and web data extraction.
+In Section 3, we define our algorithms and in Section 4 we explain the techniques we used for implementation.
+We evaluate our algorithms and present results in Section 5.
+Finally, in Section 6 we present our conclusions and future work.

### 2014-01-18 tex/3-algorithms.tex
Merge Vangelis comments

@@
 This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments.
-Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of throughout a blog.
-Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.
+Our approach uses blog specific characteristics to build extraction rules which are applicable to all blog posts.
+Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.
 
@@
 \begin{enumerate}[label={(\arabic*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
-  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
+  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure,
+  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
 \end{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Content extraction}
+\subsection{Content extraction overview}
 \label{contentextraction}
@@
 defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
-In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing.
+In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programming.
 Finally, \autoref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

### 2014-01-18 tex/4-techniques.tex
Merge Vangelis comments

@@
 
-This section gives an overview of the different techniques used in our crawler.
-We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
-The overall software architecture is then discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
-Finally we talk about the design choices we made in view of a large scale deployment.
+This section provides an overview of the crawler system architecture and the different techniques we used.
+The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
+Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
+Finally, we talk about the design choices we made in view of a large scale deployment.
 
@@
 % blog post identification
-Given an URL entry point to a website, the default Scrapy behavior traverses all the pages of the same domain in a \emph{last-in-first-out} manner.
+Given an URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner.
 The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not.
@@
 
-% Distance-Weighted k-Nearest-Neighbor
+% Distance-Weighted k-Nearest-Neighbour
 The idea is to give high priority to URLs which are believed to point to pages with links to blog posts.
-These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}.
+These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier \cite{dudani1976}.
 Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$.
@@
 %
-where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator.
+where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the power set operator.
 By delegating all mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.

### 2014-01-18 tex/5-evaluation.tex
Merge Vangelis comments

@@
 These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
-\autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.
+\autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts from 230 blogs obtained from the Spinn3r dataset \cite{burton2011}.
 
@@
 On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules.
-Therefore, results showen in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an evidence that our approach is more suitable when working with blogs.
+Therefore, results showed in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an evidence that our approach is more suitable when working with blogs.
 
@@
 \input{runningtimeFigure.tex}
+
+\TODO{\\
+  > what is the initial computation time? It would be good to know and have some numbers.\\\\
+  The initial computations is the time we spend to go from 0 to 1 processed blog posts on the graph, which includes processing the web feed and the 15 pages it contains.
+I have the exact numbers in the repo but it's basically the tiny white space we see on the graph, ~1/8 second.
+}
 

### 2014-01-18 tex/6-conclusion-and-future-work.tex
up
minor
Merge Vangelis comments

@@
 Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates.
+
+\TODO{\\
+  > You didn't say anything about this in the evaluation, did you?
+  Either present some numbers about it or remove this thing from the conclusions.
+  \\\\
+  I think I will simply rephrase it with less precisions, but the idea is that there is some overlap between the 7\% of posts we fail to extract and the 88.1\% of posts extracted by readability, likely in the order of 7\% * 88.1\% as the conditions of failure are completely independent.
+}
+
 Even if the overall performance of our approach is better than those of comparable projects (as shown in the evaluation), there are still a few cases where other techniques managed to extract data and we did not.
@@
 Crawler greatly benefits from the use of multiple Internet access points which makes them natural candidates for distributed computing.
-We intend to explore this opportunities in our future work.
-
-% Conclude the conclude
-To open up further possibilities\comment{rephrase?}, the crawler presented in this paper is available under the MIT license from the project's website \cite{blogforevercrawler}.
+We intend to explore these opportunitie in our future work.

### 2014-01-18 tex/2-algorithms.tex
Remove comments, do a pass UK of spell checker

--- 2014-01-18 tex/3-algorithms.tex
@@
 
-% html extraction is not trival
 Extracting metadata and content from HTML documents is a challenging task.
@@
 
-% observations when working with blogs
 Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
@@
 
-% textual pseudocode
 \autoref{extractionAlgo} shows the generic procedure we use to build extraction rules.
@@
 
-% embarrassingly parallel
 One might notice that each \emph{best rule} computation is independent and operates on a different input pair.
@@
 
-% abs, plan
 Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section.
@@
 
-% xpath selectors (id, else class, else path)
 In our implementation, rules are queries in the XML Path Language (XPath).
@@
 \code{id} attributes are expected to be unique, and \code{class} attributes have showed in our experiments to have better consistency than relative paths over pages of a blog.
-For these reasons we opt to always favor \code{class} over path, and \code{id} over \code{class}, such that the \coderef{allrulesAlgo} function returns a single rule per node.
+For these reasons we opt to always favour \code{class} over path, and \code{id} over \code{class}, such that the \coderef{allrulesAlgo} function returns a single rule per node.
 
@@
 
-% score function := string similarity
 Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process.
@@
 
-% into: algo 1 defined
-The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is complet.
+The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is complete.
 We now proceed with a time complexity analysis.
 
-% algo 1 is quadratic
 First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure, indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
@@
 
-% linear reformulation
 We now present \autoref{linearAlgo}, a linear time reformulation of \autoref{extractionAlgo} for article extraction using dynamic programming.
@@
 
-% proof
 With bigrams computed in this dynamic programming manner, the overall time to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear.
@@
 
-% intro
 Using string similarity as the only score measurement leads to poor performance on author and date extraction, and is not suitable for comment extraction.
@@
 
-% authors
 The case of authors is problematic because authors' names often appear in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score.
@@
 
-% dates
 Dates are affected by the same duplication issue, as well as the inconsistency of format between web feeds and web pages.
@@
 
-% comments
 Comments are usually available in separate web feeds, one per blog post.
@@
 
-% rush some time complexity analysis
 Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity.

### 2014-01-18 tex/3-techniques.tex
Remove comments, do a pass UK of spell checker

@@
 \section{Techniques}
+\label{techniques}
 
-This section gives a high level overview of the techniques used in our crawler.
-We will first give an overview of the overall software architecture, precisely locating the different modules that are addressed in this paper.
-Secondly the JavaScript rendering process will be
+This section provides an overview of the crawler system architecture and the different techniques we used.
+The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
+Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
+Finally, we talk about the design choices we made in view of a large scale deployment.
 
-# Architecture
-- top down
-- stateless, global scalability
-- scrapy, dl policies and post identification
-- item pipeline, modularity
-- js rendering done upfront, everything else general
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{JavaScript rendering}
 
-# JavaScript rendering
-- challenges
-Ajax
-Google Blogspot Dynamic Views: \surl{http://buzz.blogger.com/2012/02/dynamic-views-update-3-gadgets.html}, \surl{https://support.google.com/blogger/answer/1229061?hl=en}
-- present phjs, also here screenshot
-- ez of use vs power
-- our click show more use case
-- parallelization
+JavaScript is a widely used language for client-side scripting.
+While some applications simply use it for aesthetics, an increasing number of websites use JavaScript to download and display content.
+In such cases, traditional HTML based crawlers do not see web pages as they are presented to a human visitor by a web browser, and might therefore be obsolete for data extraction.
 
-# Content Extraction
-- two phase process:
-- wrapper generation, next section
-- use per blog
-- a word about maintainability, given because by recompute them each tim
+In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation.
+The most frequent cases were blogs using the Disqus \cite{disqus2014} and LiveFyre \cite{livefyre2014} comment hosting services.
+For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
+Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments.
+Less commonly, some blogs are fully rendered using JavaScript.
+When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content.
+The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.
+
+To support blogs with JavaScript-generated content, we embed a full web browser into the crawler.
+After considering multiple options, we opted for PhantomJS \cite{phantomjs2014}, a headless web browser with great performance and scripting capabilities.
+The JavaScript rendering is the very first step of web page processing.
+Therefore, extracting blog post articles, comments or multimedia files works equally well on blogs with JavaScript-generated content and on traditional HTML-only blogs.
+
+When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} button.
+As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded.
+Paths to Disqus and LiveFyre \emph{Show More} buttons are manually obtained.
+They constitute the only non-generic elements of our extraction stack which require human intervention to maintain and extend to other commenting platforms.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Architecture}
+
+\begin{figure}
+  \capstart
+  \centering
+  \includegraphics[width=0.47\textwidth]{scrapy_architecture}
+  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2014})}
+  \label{architecture}
+\end{figure}
+
+Our crawler is built on top of Scrapy \cite{scrapy2014}, an open-source Python framework for web crawling.
+Scrapy provides an elegant and modular architecture illustrated in \autoref{architecture}.
+Several components can be plugged into the Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing us to implement a different type of functionality.
+
+Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog.
+After being downloaded and identified as blog posts (details in \autoref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
+\begin{enumerate}
+  \item Render JavaScript
+  \item Extract content
+  \item Extract comments
+  \item Download multimedia files
+  \item Propagate resulting records to the back end
+\end{enumerate}
+This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.
+
+\TODO{Write this properly...}
+One of the main advantages of having full control over the crawling process is that contrarily to the general purpose crawlers, we do not to store all the web pages material.
+Instead, the content of interest is computed "on the fly", and directly saved into the back-end system.
+This propriety ...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Enriching Scrapy}\label{enrichingscrapy}
+
+In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process down to the subsets of pages which are blog posts: \emph{blog post identification} and \emph{download priority heuristic}.
+
+Given an URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner.
+The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not.
+Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed.
+This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur).
+In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.
+
+In order to efficiently deal with blogs that have a large number of pages which are not posts, the \emph{blog post identification} mechanism is not sufficient.
+Indeed, after all pages identified as blog posts are processed, the crawler needs to download all other pages to search for additional blog posts.
+To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities for new URLs are determined by a machine learning system.
+This mechanism has shown to be mandatory for blogs hosted on a single domain alongside large number of other types of web pages, such as those in forums or wikis.
+
+The idea is to give high priority to URLs which are believed to point to pages with links to blog posts.
+These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier \cite{dudani1976}.
+Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$.
+Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data.
+When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$.
+$L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Scalability}
+When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}.
+The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.
+
+Heading in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
+From a high-level point of view, these two components are \emph{purely functional}:
+%
+\newcommand\URL{\mathbb{U}\text{RL}}
+\newcommand\DATE{\mathbb{D}\text{ATE}}
+\newcommand\RECORD{\mathbb{R}\text{ECORD}}
+\begin{equation*}
+  \begin{split}
+    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
+    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
+  \end{split}
+\end{equation*}
+%
+where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the power set operator.
+By delegating all mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.

### 2014-01-18 tex/5-related-work.tex
Remove comments, do a pass UK of spell checker

--- 2014-01-17 tex/2-related-work.tex
@@
 these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.
+
+\comment{One very common approach for web crawling is to follow different crawling techniques for different types of web applications and different platforms.
+Application-aware crawling is based on a knowledge base of web applications and their corresponding special web crawling instructions.
+The drawback of this type of approach is that it does not scale and it cannot cope with the increasing number and diversity of web applications.
+\cite{faheem2012intelligent}}
 

### 2014-01-18 tex/6-conclusion-and-future-work.tex
Remove comments, do a pass UK of spell checker

@@
 \section{Conclusion and Future Work}
-% What we presented, what we solved
+
 In this paper, we presented the internals of the BlogForever web crawler.
@@
 In order to support rapidly evolving web technologies such as JavaScript-generated content, the crawler uses a web browser to render pages before processing them.
-We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.\TODO{Finally, ...
-evaluation}
+We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.
+Finally, we evaluated our content extraction algorithm against three state-of-the-art web article extraction algorithms.
 
-% Future work, hybrid algos
 Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates.
@@
 
-% Deployment on a distributed architecture
 Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system.
@@
 Crawler greatly benefits from the use of multiple Internet access points which makes them natural candidates for distributed computing.
-We intend to explore these opportunitie in our future work.
+We intend to explore these opportunities in our future work.

### 2014-01-18 tex/1-intro.tex
Important reformulations

@@
 
-\TODO{
-  After writing the first sentece, you should write what are our aims in this work. (keep it in the same paragraph).\\
-  \\
-  Our main objective in this work are to create better algorithms and techniques for blog content extraction. (maybe you want to write something extra here+++, then, continue with the contributions:\\
-  \\
-  Our contributions can be summarised as follows:
-}
-
 We present the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
+Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments.
 Our contributions can be summarized as follows:
@@
 The rest of the paper is organized as follows.
-In Section 2, we present related work on web crawlers and web data extraction.
-In Section 3, we define our algorithms and in Section 4 we explain the techniques we used for implementation.
-We evaluate our algorithms and present results in Section 5.
-Finally, in Section 6 we present our conclusions and future work.
+In \hyperref[algorithms]{Section~\ref*{algorithms}}  , we define our algorithms and in \hyperref[techniques]{Section~\ref*{architecture}}   we explain the techniques we used for implementation.
+We evaluate our algorithms and present results in \hyperref[evaluation]{Section~\ref*{evaluation}} .
+In \hyperref[relatedwork]{Section~\ref*{relatedwork}}  , we present related work on web crawlers and web data extraction.
+Finally, in \hyperref[conclusionandfuturework]{Section~\ref*{conclusionandfuturework}}  we present our conclusions and future work.

### 2014-01-18 tex/3-architecture.tex
Important reformulations

--- 2013-10-29 tex/3-architecture.tex
@@
 \section{Architecture}
+\label{architecture}
 
-\subsection{Scrapy and Invenio}
-Introduce both projects with their respective strengths, tool/technology justification.
+This section provides an overview of the crawler system architecture and the different techniques we used.
+The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
+Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content.
+Finally, we talk about the design choices we made in view of a large scale deployment.
 
-\subsection{JavaScript Rendering}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Overview}
+
+Our crawler is built on top of Scrapy \cite{scrapy2014}, an open-source Python framework for web crawling.
+Scrapy provides an elegant and modular architecture illustrated in \autoref{architecture}.
+Several components can be plugged into the Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing us to implement a different type of functionality.
+
+Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog.
+After being downloaded and identified as blog posts (details in \autoref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
 \begin{enumerate}
-  \item PhantomJS
-  \item "Show more comments" click
-  \item Done upfront, every thing else is independent
+  \item Render JavaScript
+  \item Extract content
+  \item Extract comments
+  \item Download multimedia files
+  \item Propagate resulting records to the back end
 \end{enumerate}
+This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.
 
-\subsection{Extraction Process}
-High level overview: XPath build from RSS feeds
+\TODO{Write this properly...}
+One of the main advantages of having full control over the crawling process is that contrarily to the general purpose crawlers, we do not to store all the web pages material.
+Instead, the content of interest is computed "on the fly", and directly saved into the back-end system.
+This propriety ...
+
+\begin{figure}
+  \capstart
+  \centering
+  \includegraphics[width=0.47\textwidth]{scrapy_architecture}
+  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2014})}
+  \label{architecture}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Enriching Scrapy}\label{enrichingscrapy}
+
+In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process down to the subsets of pages which are blog posts: \emph{blog post identification} and \emph{download priority heuristic}.
+
+Given an URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner.
+The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not.
+Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed.
+This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur).
+In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.
+
+In order to efficiently deal with blogs that have a large number of pages which are not posts, the \emph{blog post identification} mechanism is not sufficient.
+Indeed, after all pages identified as blog posts are processed, the crawler needs to download all other pages to search for additional blog posts.
+To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities for new URLs are determined by a machine learning system.
+This mechanism has shown to be mandatory for blogs hosted on a single domain alongside large number of other types of web pages, such as those in forums or wikis.
+
+The idea is to give high priority to URLs which are believed to point to pages with links to blog posts.
+These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier \cite{dudani1976}.
+Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$.
+Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data.
+When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$.
+$L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{JavaScript rendering}
+
+JavaScript is a widely used language for client-side scripting.
+While some applications simply use it for aesthetics, an increasing number of websites use JavaScript to download and display content.
+In such cases, traditional HTML based crawlers do not see web pages as they are presented to a human visitor by a web browser, and might therefore be obsolete for data extraction.
+
+In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation.
+The most frequent cases were blogs using the Disqus \cite{disqus2014} and LiveFyre \cite{livefyre2014} comment hosting services.
+For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
+Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments.
+Less commonly, some blogs are fully rendered using JavaScript.
+When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content.
+The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.
+
+To support blogs with JavaScript-generated content, we embed a full web browser into the crawler.
+After considering multiple options, we opted for PhantomJS \cite{phantomjs2014}, a headless web browser with great performance and scripting capabilities.
+The JavaScript rendering is the very first step of web page processing.
+Therefore, extracting blog post articles, comments or multimedia files works equally well on blogs with JavaScript-generated content and on traditional HTML-only blogs.
+
+When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} button.
+As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded.
+Paths to Disqus and LiveFyre \emph{Show More} buttons are manually obtained.
+They constitute the only non-generic elements of our extraction stack which require human intervention to maintain and extend to other commenting platforms.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Scalability}
+When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}.
+The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.
+
+Heading in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components.
+From a high-level point of view, these two components are \emph{purely functional}:
+%
+\newcommand\URL{\mathbb{U}\text{RL}}
+\newcommand\DATE{\mathbb{D}\text{ATE}}
+\newcommand\RECORD{\mathbb{R}\text{ECORD}}
+\begin{equation*}
+  \begin{split}
+    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
+    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
+  \end{split}
+\end{equation*}
+%
+where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the power set operator.
+By delegating all mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.

### 2014-01-18 tex/4-evaluation.tex
Remove comments, do a pass UK of spell checker
Important reformulations

--- 2014-01-18 tex/5-evaluation.tex
@@
-\section{Evaluation}\label{evaluation}
+\section{Evaluation}
+\label{evaluation}
 
@@
 
-% An extraction was considered successful when the returned string is a least 0.5 similar to the reference string, with respect to the Sørensen–Dice coefficient similarity.
-
 \precisionTable
@@
 
-% running time eval, scalability with size of blogs
 In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure.
@@
 
-% the graph
 \autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed.
@@
 
-% standard deviations
 Data presented in this graph was obtained by taking the arithmetic mean over 10 measurements.
@@
 
-\TODO{\\
-  > what is the initial computation time? It would be good to know and have some numbers.\\\\
-  The initial computations is the time we spend to go from 0 to 1 processed blog posts on the graph, which includes processing the web feed and the 15 pages it contains.
-I have the exact numbers in the repo but it's basically the tiny white space we see on the graph, ~1/8 second.
-}
-
-Past the initial computations, the cost of processing a blog post with our approach is almost zero.
-This is a consequence of having a blog-aware, rule-based algorithm.
-As already mentioned, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog.
-The initial increase in the curve of our approach corresponds to the computation of the extraction rules, which consists of processing the web feed and all the blog posts it references.
-Subsequent computations only involve parsing blog posts and applying extraction rules, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}.
+As illustrated in \autoref{runningtime}, our approach spends the majority of it's total running time between the initialisation the processing of the first blog post.
+This initial increase of about 0.4 seconds corresponds to cost of executing \autoref{linearAlgo} to compute extraction rule for articles.
+As already mentioned, this consists in computing the \emph{best extraction rule} of each pages references by the web feed and picking the one functioning best on these pages.
+Once we have this extraction rule, processing subsequent blog posts only requires parsing and applying the rule, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}.
 The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.
 
-The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post as the test blog's web feed contains 15 blog posts.
-That being said, comparing raw performance of different algorithms implemented in different programming languages is not very informative given the high variations of running times observed across languages for identical algorithms \cite{hundt2011}.
-
-% python x23 just-in-time compilation speed up http://dl.acm.org/citation.cfm?id=2069181
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Preservation of blog visuals}
-% \TODO{visuals/design/graphic/?}
-
-% Additionally to the blog content extraction that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals.
-Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.
-Our final solution consists in using the embeded web browser to take screenshots after each page rendering.
-Before opting for this approach we considered 3 other solutions: GNU wget, wkhtmltopdf and OXPath.
-This subsection relates our evaluation of these tools for the specific purpose.
-
-% \TODO{Is this whole subsection legitimate?
-It this part is not really relevant we could also simply not include it...
-I guess it is not a really useful from a research point of vue, but it might still be of some use for others to know what each of them can do.
-I think it's also important to say at some point how long it takes to render a pages, because if only look at the graph it seams like this is all super fast, but when we use PhantomJS the thing seriously slows down...}
-
-% The first solution we considered was the GNU/Linux tool wget.
-With the appropriate options, wget can be used to download a webpage and the associated files (css, scripts and images).
-On simple webpages, this process effectively captures all files necessary to display the page locally.
-However, it falls short* to capture webpages that download content via javascript.
-
-% Another solution we considered is wkhtmltopdf, a tool to produce pdf versions of web-pages.
-It uses the "print" function of it's embedded web browser to produce it's output and therefore supports all web technologies supported by it underling web browser.
-
-% The OXPath project goes one step further by offering an extension of the XPath language to specify page interactions such as clicks and forms filling.
-It also make use of a complete web browser to render pages and execute page interactions sequentially.
-OXPath makes it simple to extract comments displayed across multiple pages or that requiring clicks to be loaded.
-
-% \savevisualsTable
-
-% intro, plan (why we pick these projects, what we want to show with this evaluation)
-
-% \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/
-% \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/ http://blogforever.eu/blog/2011/05/17/rendering-and-storing-web-pages-using-wkhtmltopdf/
-% \item OXPath
-% \item Selenium + full browser
-
-% table to recap
-
-% discussion (ez of use vs power, fine because it's automated)
+The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post.
+Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach include the cost of entirely processing these 15 entries.
+That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variations of running times observed across programming languages \cite{hundt2011}.

### 2014-01-18 tex/6-conclusion-and-future-work.tex
Important reformulations

@@
 \section{Conclusion and Future Work}
+\label{conclusionandfuturework}
 
@@
 
+\Anotecontent{notimefordat}{\TODO{This might be necessary}: An in-depth analysis of causes of failure was not included in this paper given the high amount of manual work required to identify these causes on problematic pages.}
+
 Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates.
-
-\TODO{\\
-  > You didn't say anything about this in the evaluation, did you?
-  Either present some numbers about it or remove this thing from the conclusions.
-  \\\\
-  I think I will simply rephrase it with less precisions, but the idea is that there is some overlap between the 7\% of posts we fail to extract and the 88.1\% of posts extracted by readability, likely in the order of 7\% * 88.1\% as the conditions of failure are completely independent.
-}
-
-Even if the overall performance of our approach is better than those of comparable projects (as shown in the evaluation), there are still a few cases where other techniques managed to extract data and we did not.
-This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performance.
+Indeed, we have observed\Anote{notimefordat} that the primary causes of failure of our approach were the insufficient quality of web feeds or the high structural variations of blog pages.
+This suggests that combining our approach with others techniques such as word density or spacial reasoning could lead to better performance given that these techniques are insensible to the above issues.
 

### 2014-01-18 tex/1-intro.tex
Up

@@
 
-We present the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
+This paper presents the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
 Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments.

### 2014-01-18 tex/3-architecture.tex
Up

@@
 
-This section provides an overview of the crawler system architecture and the different techniques we used.
+This section provides an overview \TODO{issue with subsection name} of the crawler system architecture and the different techniques we used.
 The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
@@
 \end{enumerate}
-This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.
+This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.
 
@@
 When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}.
-The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.
+The BlogForever Crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.
 

### 2014-01-18 tex/5-related-work.tex
Important reformulations
Up

@@
 \section{Related work}
+\label{relatedwork}
 
-\Anotecontent{wrapper}{In the literature, procedures to extract structured data from unstructured document are commonly referred as \emph{wrappers}.
-In this paper we decided to rather employ the less generic term of \emph{extraction rules} which is closer to our implementation.}
+Web crawling has been a well-studied topic over the last decade.
+One direction of study which we believe to be of crucial importance is the one of large scale distributed crawlers.
+Our design is influenced by the work Heydon and Najork work on Mercator \cite{heydon99mercator}, Boldi et al.
+work's on UbiCrawler \cite{boldi2003} and Shkapenyuk and Suel work's on their spider discussed in \cite{shkapenyuk2002}.
+One of the core issues when scaling out a crawler seems to be in sharing the list URLs that have already been visited and need to be visited next.
+While \cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
+Both of these approaches require complex mechanisms to achieve fault tolerance.
 
-The BlogForever Crawler combines ideas from previous work on general web crawlers and extraction rule\Anote{wrapper} generation algorithms.
-
-Research on large scale distributed crawler such as Mercator \cite{najork2001}, used by AltaVista, the spider discussed in \cite{shkapenyuk2002} or UbiCrawler \cite{boldi2003} are enlightening regarding the difficulties arising when scale out a crawler.
-One of the core issues seems to be in sharing the list URLs which have already been visited and need to be visited.
-While \cite{najork2001} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
-Both of these approaches require complex mechanisms to achieve fault tolerance.
-The BlogForever crawler circumvent this problem by delegating all state the back-end system.
+The BlogForever Crawler -circumvent- delegates this problem by delegating all state the back-end system.
 This shared nothing architecture between crawler instance is made possible by the fact that our unit of computations, crawling a entire blog, is much large than fetching a single URL and does not generate further crawling tasks.
@@
 \cite{faheem2012intelligent}}
+
+\Anotecontent{wrapper}{In the literature, procedures to extract structured data from unstructured document are commonly referred as \emph{wrappers}.
+In this paper we decided to rather employ the less generic term of \emph{extraction rules} which is closer to our implementation.}
+
+The BlogForever Crawler combines ideas from previous work on general web crawlers and extraction rule\Anote{wrapper} generation algorithms.
+
+Several experiments have been conducted in
+
+There have been several successful research working design distributed crawlers
 

### 2014-01-19 tex/2-algorithms.tex
Reformulated the beginning of related work

@@
 This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments.
-Our approach uses blog specific characteristics to build extraction rules which are applicable to all blog posts.
+Our approach uses blog specific characteristics to build \emph{extraction rules} which are applicable to all blog posts.
 Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.
@@
 % per blog procedure, related work
-To extract content from blog posts, we proceed by building extraction rules from the data given in the blog's web feed.
+To extract content from blog posts, we proceed by building \emph{extraction rules} from the data given in the blog's web feed.
 The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.
@@
 % input from observations.
-Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date.
+Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date.
 We call these fields \emph{targets} as they constitute the data our crawler aims to extract.

### 2014-01-19 tex/5-related-work.tex
Reformulated the beginning of related work

--- 2014-01-17 tex/2-related-work.tex
@@
 \section{Related work}
+\label{relatedwork}
 
-\Anotecontent{wrapper}{In the literature, procedures to extract structured data from unstructured document are commonly referred as \emph{wrappers}.
-In this paper we decided to rather employ the less generic term of \emph{extraction rules} which is closer to our implementation.}
+Our crawler combines ideas from previous work on general web crawlers and \emph{wrapper} generation algorithms.
+The word \emph{wrapper} is commonly used to designate procedures to extract structured data from unstructured document.
+We did not employ this word in the present paper in favour of the term of \emph{extraction rule}, which better reflects our implementation and is decoupled from the XPath engine that concretely preforms the extraction.
 
-The BlogForever Crawler combines ideas from previous work on general web crawlers and extraction rule\Anote{wrapper} generation algorithms.
+Web crawling has been a well-studied topic over the last decade.
+One direction which we believe to be of crucial importance is the one of large scale distributed crawlers.
+Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of successful distributed crawler contain useful information regarding the challenges encountered when working on a distributed architecture.
+One of the core issues when scaling out seems to be in sharing the list URLs that have already been visited and need to be visited next.
+While \cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
+Both of these approaches require the crawlers to implement complex mechanisms to achieve fault tolerance.
+%
+The BlogForever Crawler circumvent this problem by delegating all state the back-end system.
+This shared nothing architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.
+%
+In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
+This removes one layer of complexity when compared to general crawler which need use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
+Our design is inspired by the ideas of distributed active object presented in \cite{activeobject1996}.
 
-Research on large scale distributed crawler such as Mercator \cite{najork2001}, used by AltaVista, the spider discussed in \cite{shkapenyuk2002} or UbiCrawler \cite{boldi2003} are enlightening regarding the difficulties arising when scale out a crawler.
-One of the core issues seems to be in sharing the list URLs which have already been visited and need to be visited.
-While \cite{najork2001} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
-Both of these approaches require complex mechanisms to achieve fault tolerance.
-The BlogForever crawler circumvent this problem by delegating all state the back-end system.
-This shared nothing architecture between crawler instance is made possible by the fact that our unit of computations, crawling a entire blog, is much large than fetching a single URL and does not generate further crawling tasks.
-In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
-This removes one layer of complexity when compared to general crawler which need use a distributed file system or implement an aggregation mechanism in order to further use the collected data.
+A common approach in web content extraction is to manually build wrappers for the targeted websites.
+This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorising web sites according to the technology they use and use this information to obtain an appropriate wrapper from a knowledge base.
+The limiting factor of this type of approach is the high human resources needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of web.
 
-\cite{shkapenyuk2002} used NFS, \cite{berger2011} uses HDFS
-
-- Wrapper generation\\
 these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.
-
-% Web archiving is a challenging and very interesting problem and has been the subject of many studies as well as the goal of several projects.
-% \comment{Mention Internet Archive here and maybe another generic web archiving project}
-
-% A fraction of web archiving studies and projects focus on the specific problem of blog harvesting and archiving.
-% They focus on the unique nature of blogs as dynamic web resources with a usually common set of attributes.
-% Each entry in a blog, commonly called a post, has a title, an author, a publication date, some content and possibly some descriptive tags.
-% (In this section we review some studies and projects that introduce and describe such techniques.)
-
-% Blogs are strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference - needed?).
-% Web feeds are structured documents (often XML-based) that advertize and provide access to a website's content.
-% Given their format, web feeds constitute an excellent source for blog archiving.
-% They do, however, present some problems: (a) web feeds contain only the latest posts of a blog (usually 20) and (b) web feeds may only provide a summary or a fraction of the entire content of each blog post.
-% More advanced methods and techniques have to be employed in order to achieve quality blog archiving.
-
-% Here mention projects that use web feeds for discovery and compare them to ours.
-% \begin{itemize}
-%   \item ( Zero-cost Labelling with Web Feeds for Weblog Data Extraction - http://www2013.org/companion/p73.pdf).
-%   \item ( Self-supervised Automated Wrapper Generation for Weblog Data Extraction - https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod\_published.pdf).
-%   \item ( Archiving Data Objects using Web Feeds - http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf).
-% \end{itemize}
-% Some of these should also be in the comparison for extraction methods.
-
-% Here mention projects that use other techniques for discovery and compare them to ours.
-% \begin{itemize}
-%   \item ???
-% \end{itemize}
-
-% Here mention projects that use various techniques for extraction and compare them to ours.
-% \begin{itemize}
-%   \item ( Web Object Identification for Web Automation and Meta-Search - http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf).
-%   \item ( OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications - http://www.vldb.org/pvldb/vol4/p1016-furche.pdf).
-%   \item ( Intelligent and Adaptive Crawling of Web Applications for Web Archiving - http://pierre.senellart.com/publications/faheem2013intelligent.pdf).
-%   \item ( Web Data Extraction, Applications and Techniques: A Survey - http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf).
-% \end{itemize}
-
-% Here mention that there is no comparison for the JavaScript rendering as there are no similar projects.
-% \begin{itemize}
-%   \item ???
-% \end{itemize}

### 2014-01-19 tex/1-intro.tex
Fixing typos and adding some comments
* All comments start with "NK:"

--- 2014-01-18 tex/1-intro.tex
@@
 
-We present the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
+\comment{NK: the article cited for the BlogForever platform already presents the proprietary web crawler used in the BlogForever project.
+To avoid confusion maybe we should slightly rephrase this sentence to: "This paper presents the open-source version of the BlogForever Crawler..." or similar?}
+This paper presents the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
 Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments.
@@
   \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them.
-This step allows our crawler to effectively harvest blogs built with modern technology, such as the increasingly popular third-party commenting systems.
+This step allows our crawler to effectively harvest blogs built with modern technologies, such as the increasingly popular third-party commenting systems.
   \item We evaluate the content extraction and execution time of our algorithm against three state-of-the-art web article extraction algorithms.

### 2014-01-19 tex/5-related-work.tex
Fixing typos and adding some comments
* All comments start with "NK:"

@@
 Our crawler combines ideas from previous work on general web crawlers and \emph{wrapper} generation algorithms.
-The word \emph{wrapper} is commonly used to designate procedures to extract structured data from unstructured document.
-We did not employ this word in the present paper in favour of the term of \emph{extraction rule}, which better reflects our implementation and is decoupled from the XPath engine that concretely preforms the extraction.
+The word \emph{wrapper} is commonly used to designate procedures to extract structured data from unstructured documents.
+We did not employ\comment{emply VS.
+use?} this word in the present paper in favour of the term \emph{extraction rule}, which better reflects our implementation and is decoupled from the XPath engine that concretely performs the extraction.
 
-Web crawling has been a well-studied topic over the last decade.
+Web crawling has been a well-studied topic over the past decade.
 One direction which we believe to be of crucial importance is the one of large scale distributed crawlers.
-Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of successful distributed crawler contain useful information regarding the challenges encountered when working on a distributed architecture.
-One of the core issues when scaling out seems to be in sharing the list URLs that have already been visited and need to be visited next.
+Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of successful distributed crawlers and the papers describing them provide useful information regarding the challenges encountered when working on a distributed architecture.
+One of the core issues when scaling out seems to be in sharing the list of URLs that have already been visited and the ones that need to be visited next.
 While \cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
@@
 %
-The BlogForever Crawler circumvent this problem by delegating all state the back-end system.
-This shared nothing architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.
+The BlogForever Crawler circumvents this problem by delegating the state of all the blogs to the back-end system.
+This shared nothing architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.\comment{NK: This is last sentence is a bit hard to understand.
+Maybe rephrase to something like: "This architectural choice where nothing is shared among the crawler instances is made possible by the fact that our (basic/primary) unit of computation is the entrire blog, instead of single URLs to blog pages, avoiding the generation of further crawling tasks."?}
 %
-In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
-This removes one layer of complexity when compared to general crawler which need use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
+In addition, since we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
+This removes one layer of complexity when compared to general crawlers which need to use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
 Our design is inspired by the ideas of distributed active object presented in \cite{activeobject1996}.
@@
 A common approach in web content extraction is to manually build wrappers for the targeted websites.
-This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorising web sites according to the technology they use and use this information to obtain an appropriate wrapper from a knowledge base.
-The limiting factor of this type of approach is the high human resources needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of web.
+This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorises web sites according to the technology they use and uses this information to obtain an appropriate wrapper from a knowledge base.
+The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web.
 

### 2014-01-19 tex/6-conclusion-and-future-work.tex
Up
Fixing typos and adding some comments
* All comments start with "NK:"

@@
 
-Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system.
+Another possible research direction would be the deployment of the BlogForever Crawler on a large scale distributed system.
 This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck.
-Crawler greatly benefits from the use of multiple Internet access points which makes them natural candidates for distributed computing.
+Crawlers greatly benefit from the use of multiple Internet access points which makes them natural candidates for distributed computing.
 We intend to explore these opportunities in our future work.

### 2014-01-19 tex/main.tex
Merge Vangelis comments
Remove comments, do a pass UK of spell checker
Important reformulations
Fixing typos and adding some comments
* All comments start with "NK:"

@@
 \usepackage{quoting}
-\usepackage{url}
+\usepackage[hyphens]{url}
 \usepackage{sepfootnotes}
@@
   ~\\\TODO{I'm for including the first two categories:}
+  ~\\\comment{NK: What about also "Query formulation" from H.3.3 related to the XPath expressions?}
+  ~\\\comment{NK: I guess we can skip H.3.7 Digital Libraries - Collection}
+  ~\\\comment{NK: I guess H.3.4 Systems and Software - Performance evaluation is convered by D.2.8 Metrics - * measures}
 
@@
   \clearpage
-  \input{3-algorithms.tex}
+  \input{2-algorithms.tex}
   \clearpage
-  \input{4-techniques.tex}
+  \input{3-architecture.tex}
   \clearpage
-  \input{5-evaluation.tex}
+  \input{4-evaluation.tex}
   \clearpage
-  \input{2-related-work.tex}
+  \input{5-related-work.tex}
   \clearpage

### 2014-01-19 tex/1-intro.tex
Done with Related Work

--- 2014-01-18 tex/1-intro.tex
@@
 
-\TODO{This part should be removed and the information contained here should go before the bullets (where you say what are our aims)}
-
 Although our crawler implementation is integrated with the BlogForever platform, the presented techniques and algorithms can be used in other applications related to Wrapper Generation and Web Data Extraction.
-
-The rest of the paper is organized as follows.
-In \hyperref[algorithms]{Section~\ref*{algorithms}}  , we define our algorithms and in \hyperref[techniques]{Section~\ref*{architecture}}   we explain the techniques we used for implementation.
-We evaluate our algorithms and present results in \hyperref[evaluation]{Section~\ref*{evaluation}} .
-In \hyperref[relatedwork]{Section~\ref*{relatedwork}}  , we present related work on web crawlers and web data extraction.
-Finally, in \hyperref[conclusionandfuturework]{Section~\ref*{conclusionandfuturework}}  we present our conclusions and future work.

### 2014-01-19 tex/5-related-work.tex
forgot to tag a comment as "NK:"
Done with Related Work

--- 2014-01-19 tex/5-related-work.tex
@@
 Both of these approaches require the crawlers to implement complex mechanisms to achieve fault tolerance.
-%
 The BlogForever Crawler circumvent this problem by delegating all state the back-end system.
 This shared nothing architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.
-%
 In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
@@
 The limiting factor of this type of approach is the high human resources needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of web.
+Several works try to simplify this process and provide various degree of automation.
+This is the case of the Stalker algorithm \cite{stalker} which generate wrappers based on user-labelled training examples.
+Some commercial solution such as the Lixto project \cite{lixto} simplify the task of building wrappers by offering a full integrated development environment where the training data set is obtained via a graphical user interface.
 
-these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.
+Fully automatic solutions have used other techniques to identify and extract the content of interest directly from the structure and content of web page.
+The Boilerpipe project \cite{kohlschuetter2010} mentioned on our evaluation uses text density analysis to extract the main article of a web page.
+The approach presented in \cite{treeedit} is based on tree structure analysis between pages with similar templates such a news sites or blogs.
+Automatic solutions have also been designed specifically for blogs.
+Similarly to your approach, Oita and Senellart \cite{oita2010} describe a procedure to automatically build wrappers by matching article of web feeds with HTML pages.
+This work was further extended by Gkotsis, Stepanyan, Cristea and Joy \cite{gkotsis2013} with a focus on extracting content anterior to the one indexed web feeds.
+\cite{gkotsis2013} also reports to have successfully extracted blog post titles, publication dates and authors, but their approach is less generic than for the extraction of articles.
+Finally, neither \cite{oita2010} nor \cite{gkotsis2013} provide complexity analysis which we believe to be essential before putting an algorithm in production.

### 2014-01-19 tex/6-conclusion-and-future-work.tex
Done with Related Work

--- 2014-01-18 tex/6-conclusion-and-future-work.tex
@@
 
-\Anotecontent{notimefordat}{\TODO{This might be necessary}: An in-depth analysis of causes of failure was not included in this paper given the high amount of manual work required to identify these causes on problematic pages.}
+\Anotecontent{notimefordat}{An in-depth analysis of causes of failure was not included in this paper given the high amount of manual work required to identify causes of failure on problematic pages.}
 
@@
 
-Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system.
+Another possible research direction would be the deployment of the BlogForever Crawler on a large scale distributed system.
 This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck.

### 2014-01-19 tex/main.tex
Done with Related Work

--- 2014-01-18 tex/main.tex
@@
 \usepackage{quoting}
-\usepackage{url}
+\usepackage{lmodern}
+\usepackage[hyphens]{url}
 \usepackage{sepfootnotes}
@@
 
-  ~\\\TODO{I'm for including the first two categories:}
-
   \category{H.3.3}{Information Storage and Retrieval}{Information Search and Retrieval}[Information filtering, Selection process]
   \category{\\D.2.8}{Software Engineering}{Metrics}[Complexity measures, Performance measures]
-  \category{\\H.3.7}{Information Storage and Retrieval}{Digital Libraries}[Collection]
-  \category{\\H.3.4}{Information Storage and Retrieval}{Systems and Software}[Performance evaluation]
 
@@
   % In alphabetical order, first letter of the first word capitalized.
-  \keywords{Blog crawler, wrapper generation, web data extraction}
+  \keywords{Blog crawler, web data extraction, wrapper generation}
 
@@
   \input{tables.tex}
-  ~\\
+  ~\\~\\~\\~\\~\\~\\~\\
   \input{1-intro.tex}
   \clearpage
-  \input{3-algorithms.tex}
+  \input{2-algorithms.tex}
   \clearpage
-  \input{4-techniques.tex}
+  \input{3-architecture.tex}
   \clearpage
-  \input{5-evaluation.tex}
+  \input{4-evaluation.tex}
   \clearpage
-  \input{2-related-work.tex}
+  \input{5-related-work.tex}
   \clearpage

### 2014-01-19 tex/5-related-work.tex

@@
 Our crawler combines ideas from previous work on general web crawlers and \emph{wrapper} generation algorithms.
-The word \emph{wrapper} is commonly used to designate procedures to extract structured data from unstructured document.
-We did not employ this word in the present paper in favour of the term of \emph{extraction rule}, which better reflects our implementation and is decoupled from the XPath engine that concretely preforms the extraction.
+The word \emph{wrapper} is commonly used to designate procedures to extract structured data from unstructured documents.
+We did not employ\comment{NK: employ VS.
+use?} this word in the present paper in favour of the term \emph{extraction rule}, which better reflects our implementation and is decoupled from the XPath engine that concretely performs the extraction.
 
-Web crawling has been a well-studied topic over the last decade.
+Web crawling has been a well-studied topic over the past decade.
 One direction which we believe to be of crucial importance is the one of large scale distributed crawlers.
-Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of successful distributed crawler contain useful information regarding the challenges encountered when working on a distributed architecture.
-One of the core issues when scaling out seems to be in sharing the list URLs that have already been visited and need to be visited next.
+Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of successful distributed crawler and the papers describing them provide useful information regarding the challenges encountered when working on a distributed architecture.
+One of the core issues when scaling out seems to be in sharing the list of URLs that have already been visited and the one that need to be visited next.
 While \cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
 Both of these approaches require the crawlers to implement complex mechanisms to achieve fault tolerance.
-The BlogForever Crawler circumvent this problem by delegating all state the back-end system.
+The BlogForever Crawler circumvents this problem by delegating all state \TODO{state of all the blogs to the} the back-end system.
 This shared nothing architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.
-In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
-This removes one layer of complexity when compared to general crawler which need use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
+\comment{NK: This is last sentence is a bit hard to understand.
+Maybe rephrase to something like: "This architectural choice where nothing is shared among the crawler instances is made possible by the fact that our (basic/primary) unit of computation is the entrire blog, instead of single URLs to blog pages, avoiding the generation of further crawling tasks."?}.
+In addition, since we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
+This removes one layer of complexity when compared to general crawlers which need to use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
 Our design is inspired by the ideas of distributed active object presented in \cite{activeobject1996}.
@@
 A common approach in web content extraction is to manually build wrappers for the targeted websites.
-This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorising web sites according to the technology they use and use this information to obtain an appropriate wrapper from a knowledge base.
-The limiting factor of this type of approach is the high human resources needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of web.
+This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorises web sites according to the technology they use and uses this information to obtain an appropriate wrapper from a knowledge base.
+The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web.
 Several works try to simplify this process and provide various degree of automation.

### 2014-01-19 tex/2-algorithms.tex
Minor

@@
 Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
-\begin{enumerate}[label={(\arabic*)}]
+\begin{enumerate}[label={(\alph*)}]
+  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
   \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure,
-  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
 \end{enumerate}
@@
 
-The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is complete.
-We now proceed with a time complexity analysis.
+The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is now complete.
+We can therefore proceed with a time complexity analysis.
 
@@
 We now present \autoref{linearAlgo}, a linear time reformulation of \autoref{extractionAlgo} for article extraction using dynamic programming.
-While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams.
+While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams (set of pairs of adjacent characters).
 For instance, when evaluating the extraction rule for the HTML root node, \autoref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function.

### 2014-01-19 tex/5-related-work.tex
Minor

@@
 The word \emph{wrapper} is commonly used to designate procedures to extract structured data from unstructured documents.
-We did not employ\comment{NK: employ VS.
-use?} this word in the present paper in favour of the term \emph{extraction rule}, which better reflects our implementation and is decoupled from the XPath engine that concretely performs the extraction.
+We did not use this word in the present paper in favour of the term \emph{extraction rule}, which better reflects our implementation and is decoupled from the XPath engine that concretely performs the extraction.
 
@@
 Both of these approaches require the crawlers to implement complex mechanisms to achieve fault tolerance.
-The BlogForever Crawler circumvents this problem by delegating all state \TODO{state of all the blogs to the} the back-end system.
-This shared nothing architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.
+The BlogForever Crawler circumvents this problem by delegating all shared mutable state to the back-end system.
+In addition, since we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
+This removes one layer of complexity when compared to general crawlers which need to use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
+Our configuraiton is similar to the distributed active object pattern presented in \cite{activeobject1996},
+which is further simplified by the fact the state of crawler instances is
+
+with the exception that simplification
+
+This way, crawler instances as
+
+Our design is inspired by the ideas of .
+
+This \emph{shared nothing} architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.
 \comment{NK: This is last sentence is a bit hard to understand.
 Maybe rephrase to something like: "This architectural choice where nothing is shared among the crawler instances is made possible by the fact that our (basic/primary) unit of computation is the entrire blog, instead of single URLs to blog pages, avoiding the generation of further crawling tasks."?}.
-In addition, since we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
-This removes one layer of complexity when compared to general crawlers which need to use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
-Our design is inspired by the ideas of distributed active object presented in \cite{activeobject1996}.
 
 A common approach in web content extraction is to manually build wrappers for the targeted websites.
-This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorises web sites according to the technology they use and uses this information to obtain an appropriate wrapper from a knowledge base.
+This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorises web sites according to the technology they use \TODO{something better than "technology they use"...}, and uses this information to obtain an appropriate wrapper from a knowledge base.
 The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web.

### 2014-01-19 tex/main.tex
Minor

@@
   Olivier Blanvillain\\
-         \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
+         \affaddr{École Polytechnique Fédérale de Lausanne (EPFL)}\\
          \affaddr{1015 Lausanne, Switzerland}\\
@@
 
-  \category{H.3.3}{Information Storage and Retrieval}{Information Search and Retrieval}[Information filtering, Selection process]
+  \category{H.3.3}{Information Storage and Retrieval}{Information Search and Retrieval}[Information filtering, Query formulation, Selection process]
   \category{\\D.2.8}{Software Engineering}{Metrics}[Complexity measures, Performance measures]

### 2014-01-19 tex/5-related-work.tex
Two comments left on the RW

@@
 This removes one layer of complexity when compared to general crawlers which need to use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
-Our configuraiton is similar to the distributed active object pattern presented in \cite{activeobject1996},
-which is further simplified by the fact the state of crawler instances is
-
-with the exception that simplification
-
-This way, crawler instances as
-
-Our design is inspired by the ideas of .
-
-This \emph{shared nothing} architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.
-\comment{NK: This is last sentence is a bit hard to understand.
-Maybe rephrase to something like: "This architectural choice where nothing is shared among the crawler instances is made possible by the fact that our (basic/primary) unit of computation is the entrire blog, instead of single URLs to blog pages, avoiding the generation of further crawling tasks."?}.
+Our design is similar to the distributed active object pattern presented in \cite{activeobject1996},
+which is further simplified by the fact the state of crawler instances is not kept between crawls.
+\TODO{I think we should conclude this by insisting on the fact that we did not actually did a deployment on these kind of architecture, maybe justified by saying that this is out of the scope of this paper}
 

### 2014-01-19 tex/1-intro.tex
Add open-source to distinguish with the cited BF paper

@@
 
-\comment{NK: the article cited for the BlogForever platform already presents the proprietary web crawler used in the BlogForever project.
-To avoid confusion maybe we should slightly rephrase this sentence to: "This paper presents the open-source version of the BlogForever Crawler..." or similar?}
-This paper presents the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
+This paper presents the open-source BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
 Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments.

### 2014-01-19 tex/2-algorithms.tex
Minors + improvements on the bibliography

@@
 More recently, specifications such as microdata \cite{whatwg2014} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2014}.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008}.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

### 2014-01-19 tex/3-architecture.tex
Minor
Minors + improvements on the bibliography

@@
 
-Our crawler is built on top of Scrapy \cite{scrapy2014}, an open-source Python framework for web crawling.
-Scrapy provides an elegant and modular architecture illustrated in \autoref{architecture}.
-Several components can be plugged into the Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing us to implement a different type of functionality.
+Our crawler is built on top of Scrapy\footnote{\label{scrapy}\url{http://scrapy.org/}}, an open-source Python framework for web crawling.
+Scrapy provides an elegant and modular architecture illustrated in \autoref{scrapyarchitecture}.
+Several components can be plugged into the Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipeline}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing us to implement a different type of functionality.
 
@@
   \item Download multimedia files
-  \item Propagate resulting records to the back end
+  \item Propagate resulting records to the back-end
 \end{enumerate}
@@
   \includegraphics[width=0.47\textwidth]{scrapy_architecture}
-  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2014})}
-  \label{architecture}
+  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, Scrapy$^1$)} % Could not found a way...
+  \label{scrapyarchitecture}
 \end{figure}
@@
 Given an URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner.
-The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not.
+The \emph{blog post identification} function is able to identify whether an URL points to a blog post or not.
 Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed.
 This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur).
-In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.
+In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice among web developers.
 
@@
 In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation.
-The most frequent cases were blogs using the Disqus \cite{disqus2014} and LiveFyre \cite{livefyre2014} comment hosting services.
+The most frequent cases were blogs using the Disqus\footnote{\url{http://disqus.com/websites}} and LiveFyre \footnote{\url{http://web.livefyre.com}} comment hosting services.
 For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
@@
 To support blogs with JavaScript-generated content, we embed a full web browser into the crawler.
-After considering multiple options, we opted for PhantomJS \cite{phantomjs2014}, a headless web browser with great performance and scripting capabilities.
+After considering multiple options, we opted for PhantomJS\footnote{\url{http://phantomjs.org}}, a headless web browser with great performance and scripting capabilities.
 The JavaScript rendering is the very first step of web page processing.
@@
 %
-\newcommand\URL{\mathbb{U}\text{RL}}
-\newcommand\DATE{\mathbb{D}\text{ATE}}
-\newcommand\RECORD{\mathbb{R}\text{ECORD}}
+\newcommand\URL{\text{URL}}
+\newcommand\DATE{\text{DATE}}
+\newcommand\RECORD{\text{RECORD}}
 \begin{equation*}
@@
 where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the power set operator.
-By delegating all mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.
+By delegating all shared mutable state to the back-end system, web crawler instances can be added, removed and used interchangeably.

### 2014-01-19 tex/4-evaluation.tex
Minors + improvements on the bibliography

@@
 Timing measurements were made on a single dedicated core with garbage collection disabled.
-The Git repository for this paper \cite{repositoryofthispaper} contains the necessary scripts and instructions to reproduce all the evaluation experiments presented in this section.
-The crawler source code is available under the MIT license from the project's websites \cite{blogforevercrawler}.
+The Git repository for this paper\footnote{\url{https://github.com/OlivierBlanvillain/bfc-paper}} contains the necessary scripts and instructions to reproduce all the evaluation experiments presented in this section.
+The crawler source code is available under the MIT license from the project's websites\footnote{\url{https://github.com/BlogForever/crawler}}.
 
@@
 \subsection{Extraction success rates}
-To evaluate article and title extraction from blog posts we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively.
+To evaluate article and title extraction from blog posts we compare our approach to three open source projects: Readability \footnote{\url{https://github.com/gfxmonk/python-readability}}, Boilerpipe \cite{kohlschuetter2010} and Goose\footnote{\url{https://github.com/GravityLabs/goose}}, implemented in JavaScript, Java and Scala respectively.
 These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
@@
 \autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed.
-We used the Quantum Diaries \cite{quantumdiaries} blog for this experiment.
+We used the Quantum Diaries\footnote{\url{http://www.quantumdiaries.org}} blog for this experiment.
 

### 2014-01-19 tex/1-intro.tex
Apply Michael's corrections

@@
 
-Among the challenges in developing a blog archiving software is the design of a web crawler capable of efficiently traversing blogs to harvest their content.
+Among the challenges in developing a blog archiving software application is the design of a web crawler capable of efficiently traversing blogs to harvest their content.
 The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary.

### 2014-01-19 tex/2-algorithms.tex
Apply Michael's corrections

@@
 
-This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments.
-Our approach uses blog specific characteristics to build \emph{extraction rules} which are applicable to all blog posts.
+This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for extracting authors, dates and comments.
+Our approach uses blog specific characteristics to build \emph{extraction rules} which are applicable throughout a blog.
 Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.
@@
 Web feeds usually contain about 20 blog posts \cite{oita2010}, often less than the total number of posts in blogs.
-Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in web feed.
+Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in the web feed.
 
@@
 \begin{itemize}
-  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
+  \item Rules returning fewer HTML nodes than the number of comments on the feed are filtered out with a zero score,
   \item The scores of the remaining rules are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.

### 2014-01-19 tex/3-architecture.tex
Apply Michael's corrections

@@
 
-This section provides an overview \TODO{issue with subsection name} of the crawler system architecture and the different techniques we used.
+This section provides an overview of the crawler system architecture and the different techniques we used.
 The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage.
@@
 
-Given an URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner.
+Given a URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner.
 The \emph{blog post identification} function is able to identify whether an URL points to a blog post or not.
@@
 Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data.
-When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$.
+When the crawler encounters a new URL $v$, it will ask the machine learning system for an estimation of $L(v)$, and use this value as the download priority of $v$.
 $L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.

### 2014-01-19 tex/4-evaluation.tex
Apply Michael's corrections

@@
 Our evaluation is articulated in two parts.
-First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting article and title from web pages.
+First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting articles and titles from web pages.
 The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time.
@@
 
-On our test dataset \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction.
+On our test dataset, \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction.
 It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page.
 On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules.
-Therefore, results showed in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an evidence that our approach is more suitable when working with blogs.
+Therefore, results shown in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as evidence that our approach is more suitable when working with blogs.
 

### 2014-01-19 tex/5-related-work.tex
Fix technology they use

@@
 A common approach in web content extraction is to manually build wrappers for the targeted websites.
-This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorises web sites according to the technology they use \TODO{something better than "technology they use"...}, and uses this information to obtain an appropriate wrapper from a knowledge base.
+This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically assigns web sites to predefined categories and gets the appropriate wrapper from a static knowledge base.
 The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web.

### 2014-01-19 tex/5-related-work.tex
Fixes in related work

@@
 One direction which we believe to be of crucial importance is the one of large scale distributed crawlers.
-Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of successful distributed crawler and the papers describing them provide useful information regarding the challenges encountered when working on a distributed architecture.
-One of the core issues when scaling out seems to be in sharing the list of URLs that have already been visited and the one that need to be visited next.
+Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of a successful distributed crawler and the papers describing them provide useful information regarding the challenges encountered when working on a distributed architecture.
+One of the core issues when scaling out seems to be in sharing the list of URLs that have already been visited and those that need to be visited next.
 While \cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
@@
 Our design is similar to the distributed active object pattern presented in \cite{activeobject1996},
-which is further simplified by the fact the state of crawler instances is not kept between crawls.
-\TODO{I think we should conclude this by insisting on the fact that we did not actually did a deployment on these kind of architecture, maybe justified by saying that this is out of the scope of this paper}
+which is further simplified by the fact the state of the crawler instances is not kept between crawls.
+\TODO{I think we should conclude this by insisting on the fact that we did not actually did a deployment on these kind of architecture, maybe justified by saying that this is out of the scope of this paper}\comment{NK: I'm not sure a further justification is even needed here.
+It's pretty clear that we avoided that layer of complexity by not needing to store the state.
+Hence, there was no comparison or evaluation.
+It's almost self-explanatory that it's outside the scope of the paper.
+It would only make sense to say that we are not evaluating the performance of our algorithms based on the fact that they are stateless, compared to stateful algorithms from these other projects.}
 
 A common approach in web content extraction is to manually build wrappers for the targeted websites.
-This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically assigns web sites to predefined categories and gets the appropriate wrapper from a static knowledge base.
+This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically assigns web sites to predefined categories\comment{NK: from your previous TODO I had suggested something like: "...according to the {[}publishing | content management{]}) {[}platform | system{]} they {[}are based on | feature{]}" but it seems unnecessary now as the current phrasing is really nice.
+Remove comment as you want.} and gets the appropriate wrapper from a static knowledge base.
 The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web.
-Several works try to simplify this process and provide various degree of automation.
-This is the case of the Stalker algorithm \cite{stalker} which generate wrappers based on user-labelled training examples.
-Some commercial solution such as the Lixto project \cite{lixto} simplify the task of building wrappers by offering a full integrated development environment where the training data set is obtained via a graphical user interface.
+Several projects try to simplify this process and provide various degrees of automation.
+This is the case of the Stalker algorithm \cite{stalker} which generates wrappers based on user-labelled training examples.
+Some commercial solutions such as the Lixto project \cite{lixto} simplify the task of building wrappers by offering a full\comment{NK: either "fully" or "complete"} integrated development environment where the training data set is obtained via a graphical user interface.
 
-Fully automatic solutions have used other techniques to identify and extract the content of interest directly from the structure and content of web page.
+Fully automatic\comment{NK: maybe automated sounds better} solutions use other techniques to identify and extract the content of interest directly from the structure and content of the web page.
 The Boilerpipe project \cite{kohlschuetter2010} mentioned on our evaluation uses text density analysis to extract the main article of a web page.
-The approach presented in \cite{treeedit} is based on tree structure analysis between pages with similar templates such a news sites or blogs.
+The approach presented in \cite{treeedit} is based on a tree structure analysis between pages with similar templates such news sites or blogs.
 Automatic solutions have also been designed specifically for blogs.
-Similarly to your approach, Oita and Senellart \cite{oita2010} describe a procedure to automatically build wrappers by matching article of web feeds with HTML pages.
-This work was further extended by Gkotsis, Stepanyan, Cristea and Joy \cite{gkotsis2013} with a focus on extracting content anterior to the one indexed web feeds.
-\cite{gkotsis2013} also reports to have successfully extracted blog post titles, publication dates and authors, but their approach is less generic than for the extraction of articles.
+Similarly to your approach, Oita and Senellart \cite{oita2010} describe a procedure to automatically build wrappers by matching web feed articles with HTML pages.
+This work was further extended by Gkotsis, Stepanyan, Cristea and Joy \cite{gkotsis2013} with a focus on extracting content anterior to the one indexed in web feeds.
+\cite{gkotsis2013} also reports to have successfully extracted blog post titles, publication dates and authors, but their approach is less generic than the one for the extraction of articles.
 Finally, neither \cite{oita2010} nor \cite{gkotsis2013} provide complexity analysis which we believe to be essential before putting an algorithm in production.

### 2014-01-19 tex/5-related-work.tex
Merge comments

@@
 which is further simplified by the fact the state of the crawler instances is not kept between crawls.
-\TODO{I think we should conclude this by insisting on the fact that we did not actually did a deployment on these kind of architecture, maybe justified by saying that this is out of the scope of this paper}\comment{NK: I'm not sure a further justification is even needed here.
-It's pretty clear that we avoided that layer of complexity by not needing to store the state.
-Hence, there was no comparison or evaluation.
-It's almost self-explanatory that it's outside the scope of the paper.
-It would only make sense to say that we are not evaluating the performance of our algorithms based on the fact that they are stateless, compared to stateful algorithms from these other projects.}
 
 A common approach in web content extraction is to manually build wrappers for the targeted websites.
-This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically assigns web sites to predefined categories\comment{NK: from your previous TODO I had suggested something like: "...according to the {[}publishing | content management{]}) {[}platform | system{]} they {[}are based on | feature{]}" but it seems unnecessary now as the current phrasing is really nice.
-Remove comment as you want.} and gets the appropriate wrapper from a static knowledge base.
+This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically assigns web sites to predefined categories and gets the appropriate wrapper from a static knowledge base.
 The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web.
@@
 This is the case of the Stalker algorithm \cite{stalker} which generates wrappers based on user-labelled training examples.
-Some commercial solutions such as the Lixto project \cite{lixto} simplify the task of building wrappers by offering a full\comment{NK: either "fully" or "complete"} integrated development environment where the training data set is obtained via a graphical user interface.
+Some commercial solutions such as the Lixto project \cite{lixto} simplify the task of building wrappers by offering a complete integrated development environment where the training data set is obtained via a graphical user interface.
 
-Fully automatic\comment{NK: maybe automated sounds better} solutions use other techniques to identify and extract the content of interest directly from the structure and content of the web page.
-The Boilerpipe project \cite{kohlschuetter2010} mentioned on our evaluation uses text density analysis to extract the main article of a web page.
-The approach presented in \cite{treeedit} is based on a tree structure analysis between pages with similar templates such news sites or blogs.
+Automated solutions use other techniques to identify and extract information directly from the structure and content of the web page.
+The Boilerpipe project \cite{kohlschuetter2010} (mentioned in our evaluation) uses text density analysis to extract the main article of a web page.
+The approach presented in \cite{treeedit} is based on a tree structure analysis of pages with similar templates, such as news web sites or blogs.
 Automatic solutions have also been designed specifically for blogs.
-Similarly to your approach, Oita and Senellart \cite{oita2010} describe a procedure to automatically build wrappers by matching web feed articles with HTML pages.
+Similarly to our approach, Oita and Senellart \cite{oita2010} describe a procedure to automatically build wrappers by matching web feed articles with HTML pages.
 This work was further extended by Gkotsis, Stepanyan, Cristea and Joy \cite{gkotsis2013} with a focus on extracting content anterior to the one indexed in web feeds.

### 2014-01-19 tex/5-related-work.tex
Typo in the related work section

@@
 Our design is similar to the distributed active object pattern presented in \cite{activeobject1996},
-which is further simplified by the fact the state of the crawler instances is not kept between crawls.
+which is further simplified by the fact that the state of the crawler instances is not kept between crawls.
 

### 2014-01-19 tex/3-architecture.tex
Merge comments
Locking the text

@@
 This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.
-
-\TODO{Write this properly...}
-One of the main advantages of having full control over the crawling process is that contrarily to the general purpose crawlers, we do not to store all the web pages material.
-Instead, the content of interest is computed "on the fly", and directly saved into the back-end system.
-This propriety ...
 

### 2014-01-19 tex/1-intro.tex
Overflow proof in draft mode

@@
 
-Blogs disappear every day \cite{johnson2008blogs}.
+Blogs disappear every day~\cite{johnson2008blogs}.
 Losing data is obviously undesirable, but even more so when this data has historic, political or scientific value.
-In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation.
-Yet, blogs are an important part of today's web: WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}.
-Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests.
-\cite{nahedeltantawy2012}.
+In contrast to books, newspapers or centralized web platforms, there is no standard method or authority to ensure blog archiving and long-term digital preservation.
+Yet, blogs are an important part of today's web: WordPress reports more than 1 million new posts and 1.5 million new comments each day~\cite{wordpress2014}.
+Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests~\cite{nahedeltantawy2012}.
 The need to preserve this volatile communication medium is nowadays very clear.
@@
 
-A key characteristic of blogs which differentiates them from regular websites is their association with web feeds \cite{lindahl2003weblogs}.
+A key characteristic of blogs which differentiates them from regular websites is their association with web feeds~\cite{lindahl2003weblogs}.
 Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to actually visit blogs.
-Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata \cite{board2007rss}.
-Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest previous content.
+Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata~\cite{board2007rss}.
+While web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog pages in order to harvest previous content.
 
-This paper presents the open-source BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
+This paper presents the open-source BlogForever Crawler, a key component of the BlogForever platform~\cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates.
 Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments.

### 2014-01-19 tex/2-algorithms.tex
Overflow proof in draft mode

@@
 Extracting metadata and content from HTML documents is a challenging task.
-Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2014}.
-For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page \cite{w3c2002}.
-More recently, specifications such as microdata \cite{whatwg2014} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2014}.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008}.
+Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised~\cite{w3c2014}.
+For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page~\cite{w3c2002}.
+More recently, specifications such as microdata~\cite{whatwg2014} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites~\cite{andrewrogers2014}.
+In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages, and more than 95\% of pages do not pass HTML validation~\cite{brianwilson2008}.
 Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
@@
 \end{enumerate}
-Web feeds usually contain about 20 blog posts \cite{oita2010}, often less than the total number of posts in blogs.
+Web feeds usually contain about 20 blog posts~\cite{oita2010}, often less than the total number of posts in blogs.
 Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in the web feed.
@@
 % input from observations.
-Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date.
+Observation~\ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date.
 We call these fields \emph{targets} as they constitute the data our crawler aims to extract.
-Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.
+Observation~\ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.
 
@@
 When targeting articles, extraction rule scores are computed with a string similarity function comparing the extracted strings with the target strings.
-We chose the Sørensen–Dice coefficient similarity \cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:
+We chose the Sørensen–Dice coefficient similarity~\cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:
 
@@
 Properties \ref{wordorderProp} and \ref{lengthProp} are essential when dealing with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
-\autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.
+\autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein~\cite{levenshtein1966} similarity.
 
@@
 
-The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is now complete.
+With the functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is now complete.
 We can therefore proceed with a time complexity analysis.
@@
 We now present \autoref{linearAlgo}, a linear time reformulation of \autoref{extractionAlgo} for article extraction using dynamic programming.
+
+\linearAlgo
+
 While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams (set of pairs of adjacent characters).
@@
 This way, we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.
-
-\linearAlgo
 
@@
 Using string similarity as the only score measurement leads to poor performance on author and date extraction, and is not suitable for comment extraction.
-This subsection presents variations of the previously presented \code{ScoreFunction} which addresses issues of these other types of content.
+This subsection presents variations of the \code{ScoreFunction} which addresses issues of these other types of content.
 
@@
 
-Dates are affected by the same duplication issue, as well as the inconsistency of format between web feeds and web pages.
+Dates are affected by the same duplication issue, as well as the issue of inconsistencies of format between web feeds and web pages.
 Our solution for date extraction extends the \code{ScoreFunction} for authors by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original date obtained from the web feed.
-For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
+For instance, if the feed indicates that a post was published at \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
 So far we do not support dates in multiple languages, but adding new target formats based on languages detection would be a simple extension of our date extraction algorithm.
@@
 Comments are usually available in separate web feeds, one per blog post.
-Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page.
-To do so we use the following \code{ScoreFunction}:
+Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from web pages.
+To do so, we use the following \code{ScoreFunction}:
 
 \begin{itemize}
-  \item Rules returning fewer HTML nodes than the number of comments on the feed are filtered out with a zero score,
+  \item Rules returning fewer HTML nodes than the number of comments on the feed are filtered out with a zero~score,
   \item The scores of the remaining rules are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.

### 2014-01-19 tex/3-architecture.tex
Overflow proof in draft mode

@@
 
-Our crawler is built on top of Scrapy\footnote{\label{scrapy}\url{http://scrapy.org/}}, an open-source Python framework for web crawling.
+Our crawler is built on top of Scrapy\footnote{\label{scrapy}\url{http://scrapy.org/}}, an open-source framework for web crawling.
 Scrapy provides an elegant and modular architecture illustrated in \autoref{scrapyarchitecture}.
@@
 The idea is to give high priority to URLs which are believed to point to pages with links to blog posts.
-These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier \cite{dudani1976}.
+These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier~\cite{dudani1976}.
 Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$.
@@
 When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content.
-The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.
+The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism~\cite{antinharasymiv2011}.
 
@@
 \subsection{Scalability}
-When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}.
+When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind~\cite{thereactivemanifesto2013}.
 The BlogForever Crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.

### 2014-01-19 tex/4-evaluation.tex
Overflow proof in draft mode

@@
 \subsection{Extraction success rates}
-To evaluate article and title extraction from blog posts we compare our approach to three open source projects: Readability \footnote{\url{https://github.com/gfxmonk/python-readability}}, Boilerpipe \cite{kohlschuetter2010} and Goose\footnote{\url{https://github.com/GravityLabs/goose}}, implemented in JavaScript, Java and Scala respectively.
+To evaluate article and title extraction from blog posts we compare our approach to three open source projects: Readability\footnote{\url{https://github.com/gfxmonk/python-readability}}, Boilerpipe~\cite{kohlschuetter2010} and Goose\footnote{\url{https://github.com/GravityLabs/goose}}, which are implemented in JavaScript, Java and Scala respectively.
 These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
-\autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts from 230 blogs obtained from the Spinn3r dataset \cite{burton2011}.
+\autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts from 230 blogs obtained from the Spinn3r dataset~\cite{burton2011}.
 
@@
 Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach include the cost of entirely processing these 15 entries.
-That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variations of running times observed across programming languages \cite{hundt2011}.
+That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variations of running times observed across programming languages~\cite{hundt2011}.

### 2014-01-19 tex/5-related-work.tex
Overflow proof in draft mode

--- 2014-01-19 tex/5-related-work.tex
@@
 One direction which we believe to be of crucial importance is the one of large scale distributed crawlers.
-Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of a successful distributed crawler and the papers describing them provide useful information regarding the challenges encountered when working on a distributed architecture.
+Mercator~\cite{heydon99mercator}, UbiCrawler~\cite{boldi2003} and the crawler discussed in~\cite{shkapenyuk2002} are examples of a successful distributed crawler and the papers describing them provide useful information regarding the challenges encountered when working on a distributed architecture.
 One of the core issues when scaling out seems to be in sharing the list of URLs that have already been visited and those that need to be visited next.
-While \cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
+While~\cite{heydon99mercator} and~\cite{shkapenyuk2002} rely on a central node to hold this information,~\cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
 Both of these approaches require the crawlers to implement complex mechanisms to achieve fault tolerance.
@@
 In addition, since we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side.
-This removes one layer of complexity when compared to general crawlers which need to use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
-Our design is similar to the distributed active object pattern presented in \cite{activeobject1996},
-which is further simplified by the fact the state of the crawler instances is not kept between crawls.
+This removes one layer of complexity when compared to general crawlers which need to use a distributed file system (\cite{shkapenyuk2002} uses NFS,~\cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data.
+Our design is similar to the distributed active object pattern presented in~\cite{activeobject1996},
+which is further simplified by the fact that the state of the crawler instances is not kept between crawls.
 
 A common approach in web content extraction is to manually build wrappers for the targeted websites.
-This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically assigns web sites to predefined categories and gets the appropriate wrapper from a static knowledge base.
+This approach has been proposed in the crawler discussed in~\cite{faheem2012intelligent} which automatically assigns web sites to predefined categories and gets the appropriate wrapper from a static knowledge base.
 The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web.
 Several projects try to simplify this process and provide various degrees of automation.
-This is the case of the Stalker algorithm \cite{stalker} which generates wrappers based on user-labelled training examples.
-Some commercial solutions such as the Lixto project \cite{lixto} simplify the task of building wrappers by offering a complete integrated development environment where the training data set is obtained via a graphical user interface.
+This is the case of the Stalker algorithm~\cite{stalker} which generates wrappers based on user-labelled training examples.
+Some commercial solutions such as the Lixto project~\cite{lixto} simplify the task of building wrappers by offering a complete integrated development environment where the training data set is obtained via a graphical user interface.
 
 Automated solutions use other techniques to identify and extract information directly from the structure and content of the web page.
-The Boilerpipe project \cite{kohlschuetter2010} (mentioned in our evaluation) uses text density analysis to extract the main article of a web page.
-The approach presented in \cite{treeedit} is based on a tree structure analysis of pages with similar templates, such as news web sites or blogs.
+The Boilerpipe project~\cite{kohlschuetter2010} (mentioned in our evaluation) uses text density analysis to extract the main article of a web page.
+The approach presented in~\cite{treeedit} is based on a tree structure analysis of pages with similar templates, such as news web sites or blogs.
 Automatic solutions have also been designed specifically for blogs.
-Similarly to our approach, Oita and Senellart \cite{oita2010} describe a procedure to automatically build wrappers by matching web feed articles with HTML pages.
-This work was further extended by Gkotsis, Stepanyan, Cristea and Joy \cite{gkotsis2013} with a focus on extracting content anterior to the one indexed in web feeds.
-\cite{gkotsis2013} also reports to have successfully extracted blog post titles, publication dates and authors, but their approach is less generic than the one for the extraction of articles.
-Finally, neither \cite{oita2010} nor \cite{gkotsis2013} provide complexity analysis which we believe to be essential before putting an algorithm in production.
+Similarly to our approach, Oita and Senellart~\cite{oita2010} describe a procedure to automatically build wrappers by matching web feed articles with HTML pages.
+This work was further extended by Gkotsis, Stepanyan, Cristea and Joy~\cite{gkotsis2013} with a focus on extracting content anterior to the one indexed in web feeds.~\cite{gkotsis2013} also reports to have successfully extracted blog post titles, publication dates and authors, but their approach is less generic than the one for the extraction of articles.
+Finally, neither~\cite{oita2010} nor~\cite{gkotsis2013} provide complexity analysis which we believe to be essential before putting an algorithm in production.

### 2014-01-19 tex/5-related-work.tex
Add acknowledgments and additional author

@@
 One of the core issues when scaling out seems to be in sharing the list of URLs that have already been visited and those that need to be visited next.
-While~\cite{heydon99mercator} and~\cite{shkapenyuk2002} rely on a central node to hold this information,~\cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
+While~\cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing.
 Both of these approaches require the crawlers to implement complex mechanisms to achieve fault tolerance.
@@
 Similarly to our approach, Oita and Senellart~\cite{oita2010} describe a procedure to automatically build wrappers by matching web feed articles with HTML pages.
-This work was further extended by Gkotsis, Stepanyan, Cristea and Joy~\cite{gkotsis2013} with a focus on extracting content anterior to the one indexed in web feeds.~\cite{gkotsis2013} also reports to have successfully extracted blog post titles, publication dates and authors, but their approach is less generic than the one for the extraction of articles.
+This work was further extended by Gkotsis, Stepanyan, Cristea and Joy~\cite{gkotsis2013} with a focus on extracting content anterior to the one indexed in web feeds.
+\cite{gkotsis2013} also reports to have successfully extracted blog post titles, publication dates and authors, but their approach is less generic than the one for the extraction of articles.
 Finally, neither~\cite{oita2010} nor~\cite{gkotsis2013} provide complexity analysis which we believe to be essential before putting an algorithm in production.

### 2014-01-19 tex/main.tex
Minors + improvements on the bibliography
Locking the text
Overflow proof in draft mode
Add acknowledgments and additional author

@@
-% \documentclass[draft]{acm_proc_article-sp}
-\documentclass{acm_proc_article-sp}
+\documentclass[draft]{acm_proc_article-sp}
+% \documentclass{acm_proc_article-sp}
 
@@
 \usepackage[justification=centering]{caption}
+\usepackage[nodayofweek]{datetime}
 \usepackage{amssymb}
 \usepackage{booktabs}
-\usepackage{microtype}
+% \usepackage{microtype}
 \usepackage{enumitem}
@@
 \usepackage{quoting}
-\usepackage{lmodern}
 \usepackage[hyphens]{url}
@@
 \usepackage{hypcap}
+
+\newdateformat{lv}{\THEDAY{ }\shortmonthname[\THEMONTH] \THEYEAR}
+\newcommand{\lastvisited}{Last visited \lv\today}
 
@@
 
-  \numberofauthors{3}
+  \numberofauthors{7}
 
@@
          \affaddr{1015 Lausanne, Switzerland}\\
-         \email{\surl{olivier.blanvillain@epfl.ch}}
+         \email{\href{mailto:olivier.blanvillain@epfl.ch}{olivier.blanvillain@epfl.ch}}
   % 2nd. author
@@
          \affaddr{1211 Geneva 23, Switzerland}\\
-         \email{\surl{nikos.kasioumis@cern.ch}}
+         \email{\href{mailto:nikos.kasioumis@cern.ch}{nikos.kasioumis@cern.ch}}
   % 3rd. author
@@
          \affaddr{Aristotle University of Thessaloniki, Greece}\\
-         \email{\surl{vbanos@gmail.com}}
+         \email{\href{vmailto:vbanos@gmail.com}{banos@gmail.com}}
   }
+
+  \additionalauthors{Yannis Manolopoulos (Department of Informatics, Aristotle University of Thessaloniki, Greece, {\texttt{manolopo@csd.auth.gr}})}
 
@@
   \input{1-intro.tex}
-  \clearpage
   \input{2-algorithms.tex}
-  \clearpage
   \input{3-architecture.tex}
-  \clearpage
   \input{4-evaluation.tex}
-  \clearpage
   \input{5-related-work.tex}
-  \clearpage
   \input{6-conclusion-and-future-work.tex}
+  \input{7-acknowledgments.tex}
 

### 2014-01-20 tex/6-conclusion-and-future-work.tex
Minor

@@
 
-In this paper, we presented the internals of the BlogForever web crawler.
+In this paper, we presented the internals of the BlogForever Crawler.
 Its central article extraction procedure based on extraction rules generation was introduced along with theoretical and empirical evidence validating the approach.
@@
 This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck.
-Crawler greatly benefits from the use of multiple Internet access points which makes them natural candidates for distributed computing.
+Crawlers greatly benefit from the use of multiple Internet access points which makes them natural candidates for distributed computing.
 We intend to explore these opportunities in our future work.

### 2014-01-20 tex/2-algorithms.tex
Done.

@@
 \begin{enumerate}[label={(\alph*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
-  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure,
+  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
+  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
 \end{enumerate}
@@
 To extract content from blog posts, we proceed by building \emph{extraction rules} from the data given in the blog's web feed.
-The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.
+The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, to build an extraction rule capable of locating the target content on each HTML page.
 
 % input from observations.
-Observation~\ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date.
+Observation~\ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as the blog post article (either abstract or full text), its title, authors and publication date.
 We call these fields \emph{targets} as they constitute the data our crawler aims to extract.

### 2014-01-20 tex/3-architecture.tex
Seems pretty final to me
Add sucessfully printed Acrobat Distiller export
Minor
Done.

@@
   \centering
-  \includegraphics[width=0.47\textwidth]{scrapy_architecture}
-  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, Scrapy$^1$)} % Could not found a way...
+  \includegraphics[width=0.47\textwidth]{./img/scrapy_architecture.eps}
+  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, Scrapy)}
   \label{scrapyarchitecture}
@@
 The most frequent cases were blogs using the Disqus\footnote{\url{http://disqus.com/websites}} and LiveFyre \footnote{\url{http://web.livefyre.com}} comment hosting services.
-For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
+For webmasters, these tools are very handy because the entire commenting infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page.
 Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments.

### 2014-01-20 tex/4-evaluation.tex
Seems pretty final to me
Done.

@@
 
-As illustrated in \autoref{runningtime}, our approach spends the majority of it's total running time between the initialisation the processing of the first blog post.
+As illustrated in \autoref{runningtime}, our approach spends the majority of its total running time between the initialisation and the processing of the first blog post.
 This initial increase of about 0.4 seconds corresponds to cost of executing \autoref{linearAlgo} to compute extraction rule for articles.
-As already mentioned, this consists in computing the \emph{best extraction rule} of each pages references by the web feed and picking the one functioning best on these pages.
+As already mentioned, this consists of computing the \emph{best extraction rule} of each page referenced by the web feed and picking the most appropriate one.
 Once we have this extraction rule, processing subsequent blog posts only requires parsing and applying the rule, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}.
@@
 The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post.
-Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach include the cost of entirely processing these 15 entries.
-That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variations of running times observed across programming languages~\cite{hundt2011}.
+Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach includes the cost of entirely processing these 15 entries.
+That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variation of running times observed across programming languages~\cite{hundt2011}.

### 2014-01-24 slides/mk.sh
Add compilation to revealjs and a few slides

@@ -1,0 +1,6 @@
+# watchmedo shell-command --wait --patterns="*.s*.md;*.template" --command "sh mk.sh"
+
+cat *.md |pandoc \
+  -t revealjs --template revealjs.template \
+  --slide-level 1 -s -o index.html
+xdotool search --name Chrome key --window %@ ctrl+2 F5

### 2014-01-24 webarchivers/test.py

@@ -1,37 +1,0 @@
-from selenium import webdriver
-from os.path import dirname, join
-from selenium.common.exceptions import ElementNotVisibleException
-from selenium.common.exceptions import NoSuchElementException
-from time import sleep, time
-
-def main():
-  path = join(dirname(__file__), "/home/olivier/workspace/crawler/lib/phantomjs/bin/phantomjs")
-  driver = webdriver.PhantomJS(path)
-
-  url = "http://www.chancellors.co.uk/properties/search?map=false&area=New+Barnet&longitude=0&latitude=0&radius=5&saleType=Rent"
-  buttonPath = "//a[@id='Loadmore']"
-  pricesPath = "//div[@class='list-property clearfix']//h3"
-
-  driver.get(url)
-  # sleep(2)
-  # clickWhileVisible(driver, buttonPath)
-  # sleep(2)
-  result = map(
-    lambda _: _.get_attribute("innerHTML"),
-    driver.find_elements_by_xpath(pricesPath))
-  print "\n".join(result)
-
-  driver.quit()
-
-def clickWhileVisible(driver, xPath, maxDuration=5, stepDuration=0.5):
-  try:
-    timeout = time() + maxDuration
-    while time() < timeout:
-      driver.find_element_by_xpath(xPath).click()
-      # "document.getElementsByClassName('fyre-text')[0].click()")
-      sleep(stepDuration)
-  except (ElementNotVisibleException, NoSuchElementException):
-    pass
-
-if __name__ == '__main__':
-  main()

### 2014-03-29 tex/main.tex
Seems pretty final to me
Minor
Done.
Having fun with latexmk and markdown
Add Copyright

@@
-\documentclass[draft]{acm_proc_article-sp}
-% \documentclass{acm_proc_article-sp}
+% \documentclass[draft]{acm_proc_article-sp}
+\documentclass{acm_proc_article-sp}
+
+% Toggle comment this line, the url and the hyperref package
+% to generate a PDF/X-1a compliant output.
+% \usepackage[x-1a]{pdfx}
 
@@
 \usepackage{booktabs}
-% \usepackage{microtype}
+\usepackage{balance}
 \usepackage{enumitem}
@@
 \usepackage{quoting}
-\usepackage[hyphens]{url}
 \usepackage{sepfootnotes}
 \usepackage{setspace}
+\usepackage[hyphens]{url}
 \usepackage[pdfpagelabels=false]{hyperref}
@@
 
-  \numberofauthors{7}
+  \numberofauthors{3}
 
@@
          \affaddr{Aristotle University of Thessaloniki, Greece}\\
-         \email{\href{vmailto:vbanos@gmail.com}{banos@gmail.com}}
+         \email{\href{mailto:vbanos@gmail.com}{vbanos@gmail.com}}
   }
 
-  \additionalauthors{Yannis Manolopoulos (Department of Informatics, Aristotle University of Thessaloniki, Greece, {\texttt{manolopo@csd.auth.gr}})}
+  \permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that that copies bear this notice and the full citation on the first page.
+To copy otherwise, to republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.}
+  \conferenceinfo{WIMS'14,}{June 2-4, 2014 Thessaloniki, Greece}
+  \CopyrightYear{2014}
+  \crdata{978-1-4503-2538-7/14/06}
+  \global\copyrightetc{Copyright \the\copyrtyr\ ACM \the\acmcopyr\ ...\$15.00.}
 
@@
   \begin{abstract}
-    \input{0-abstract.tex}
+    \input{0-abstract.mdtex}
   \end{abstract}
@@
   ~\\~\\~\\~\\~\\~\\~\\
-  \input{1-intro.tex}
-  \input{2-algorithms.tex}
-  \input{3-architecture.tex}
-  \input{4-evaluation.tex}
-  \input{5-related-work.tex}
-  \input{6-conclusion-and-future-work.tex}
-  \input{7-acknowledgments.tex}
+
+  \section{Introduction}
+  \label{introduction}
+  \input{1-introduction.mdtex}
+
+  \section{Algorithms}
+  \label{algorithms}
+  \input{2-algorithms.mdtex}
+
+  \section{Architecture}
+  \label{architecture}
+  \input{3-architecture.mdtex}
+
+  \section{Evaluation}
+  \label{evaluation}
+  \input{4-evaluation.mdtex}
+
+  \section{Related Work}
+  \label{relatedwork}
+  \input{5-related-work.mdtex}
+
+  \section{Conclusion and Future Work}
+  \label{conclusionandfuturework}
+  \input{6-conclusion-and-future-work.mdtex}
+
+  \section{Acknowledgments}
+  \label{acknowledgments}
+  \input{7-acknowledgments.mdtex}
+
+  \balance
 

### 2014-04-01 tex/main.tex
Add reviewers comments
Adjust the text according to reviwers comments
Integrate N&V comments
Reformated with sig-alternate

@@
-% \documentclass[draft]{acm_proc_article-sp}
-\documentclass{acm_proc_article-sp}
+% \documentclass[draft]{sig-alternate}
+\documentclass{sig-alternate}
 
@@
 
+\parindent 0pt
 \usepackage[ruled, vlined]{algorithm2e}
+\parindent 10pt
 \usepackage[T1]{fontenc}
@@
 \usepackage{gnuplottex}
-\usepackage{pifont}
 \usepackage{quoting}
@@
 
+\MakeOuterQuote{"}
+\setenumerate{noitemsep, topsep=10pt, parsep=6pt,partopsep=0pt}
+\setitemize{noitemsep,topsep=10pt, parsep=6pt, partopsep=0pt}
+\def\algorithmautorefname{Algorithm}
+\graphicspath{{img/}}
+
 \newdateformat{lv}{\THEDAY{ }\shortmonthname[\THEMONTH] \THEYEAR}
 \newcommand{\lastvisited}{Last visited \lv\today}
-
-\MakeOuterQuote{"}
-\newfootnotes{A}
-\quotingsetup{vskip=0pt,font={itshape}}
-\setenumerate{noitemsep,topsep=0pt,parsep=2pt,partopsep=0pt}
-\setitemize{noitemsep,topsep=0pt,parsep=4pt,partopsep=0pt}
-\setlength\floatsep{1.25\baselineskip plus 3pt minus 2pt}
-\setlength\textfloatsep{1.25\baselineskip plus 3pt minus 2pt}
-\setlength\intextsep{1.25\baselineskip plus 3pt minus 2 pt}
-\def\algorithmautorefname{Algorithm}
-\graphicspath{{img/}}
-\newcommand{\cmark}{\ding{51}}
-\newcommand{\xmark}{\ding{55}}
-
 \newcommand\TODO[1]{\emph{\color{Red} TODO: #1}}
-\renewcommand\comment[1]{\emph{\color{Gray}#1}}
+\newcommand\noop[1]{\emph{\emph{#1}}}
+\newcommand\edit[1]{\emph{\color{Green}#1}}
 \newcommand\code[1]{\texttt{#1}}
@@
   \author{
-  % 1st. author
   \alignauthor
@@
          \email{\href{mailto:olivier.blanvillain@epfl.ch}{olivier.blanvillain@epfl.ch}}
-  % 2nd. author
   \alignauthor
@@
          \email{\href{mailto:nikos.kasioumis@cern.ch}{nikos.kasioumis@cern.ch}}
-  % 3rd. author
   \alignauthor
@@
 
-  \permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that that copies bear this notice and the full citation on the first page.
-To copy otherwise, to republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.}
   \conferenceinfo{WIMS'14,}{June 2-4, 2014 Thessaloniki, Greece}
@@
   \crdata{978-1-4503-2538-7/14/06}
-  \global\copyrightetc{Copyright \the\copyrtyr\ ACM \the\acmcopyr\ ...\$15.00.}
 
-  \hypersetup{pageanchor=false}
   \maketitle
@@
   \category{\\D.2.8}{Software Engineering}{Metrics}[Complexity measures, Performance measures]
-
-  % In order of most significant, first letter of each word capitalized.
   \terms{Design, Algorithms, Performance, Experimentation}
-
-  % In alphabetical order, first letter of the first word capitalized.
   \keywords{Blog crawler, web data extraction, wrapper generation}
@@
   \input{tables.tex}
-  ~\\~\\~\\~\\~\\~\\~\\
 
@@
   \bibliographystyle{abbrv}
-  \bibliography{main,manual}
+  \bibliography{short}
 

### 2014-04-01 tex/runningtimeFigure.tex
Reformated with sig-alternate

@@
-\begin{figure}[ht]
+\begin{figure}[t]
   \capstart
@@
 
-    set title 'Figure \arabic{figure}: Running time of articles extraction '
+    set title 'Figure \arabic{figure}: Running time of articles extraction.'
     set ylabel 'Cumulated running time (sec.)' offset 1.3

### 2014-04-04 tex/answers-to-reviewers-comments.txt
Add answers-to-reviewers-comments

> ----------------------- REVIEW 1 ---------------------
> page 2, footnote 1:
> The term "insufficient amount of text" needs a couple of lines more
> explanation. Why does this lead to a failure?
We added two sentences to clarify this, but I would also like to give a
concrete example. On this blog post [1], the textual content of the post is "A
floral embroidered coat seems to be all the rage on chic girls this Winter".
Now suppose that the layout adds some noise, for instance by also containing
in deepest div containing with the article the text "facebook twitter email 27
comments Posted in Women Tags: Coats, If You're Thinking About....". Then the
div containing the title of the post, "If You’re Thinking About... Floral
Embroidered Coats", or even the div of one of the comment, might be the more
similar to the text provided than the actual article div.

[1]: <http://www.thesartorialist.com/photos/if-youre-thinking-about-floral-embroidered-coats/>

> section 2.4, 2nd paragraph:
> A definition of n is missing (although it can be guessed).
We added it.

> section 2.5, 7th paragraph:
> This paragraph is hard to follow! What is "an overflow on its comment feed"?
> Do you mean comments content arriving by means of AJAX calls? Please
> explain. The second sentence of the paragraph is also not clear ("..narrow
> down ...fixint a target..."). Please rewrite this paragraph.
Indeed this paragraph was not very clear. The information it contained was
also really not important so we decided to remove it all together. The first
sentence was a repetition of the "Similarly to blog feeds..." sentence in the
paragraph before the bullet points: if the comment feed is not full there is
no need to extract comments from the page. Regarding the "comment content is
extracted first", this is a small optimization I did to first get the exact
number of comments by matching the comment content (which is usually more
unique and accurate that doing a matching on author/date), and use this number
to then accurately get the other fields.

> section 3.1, 3rd paragraph: Is the modularity mentioned available in the
> current system implementation? For example, can you "sense" somehow the
> presence of JavaScript content so as to exclude the "Render JavaScript" step
> in the pipeline?
Not this modularity is only "at source code level", but the pipeline is not
dynamically modified at runtime. We added some clarifications on this.

> section 3.2, 2nd paragraph:
> who is building the regular expressions out of the blog post URLs? Is it
> done manually or automatically? Please clarify. Additionally, what if the
> blog does not use friendly URLs (which they do support well the idea of
> constructing regular expressions out of the URLs)? Consider for example a
> WordPress based blog with URLs of the form http://<domain>/?p=234. How such
> a non informative URL affects your approach?
We included precisions on this (automatic) process. For a blog with URLs on
the format of "http://example.com/?p=234", the generated regular expression
will be something like ^http://example.com/?[a-zA-Z0-9]+=[0-9]+$.

> section 3.2, 4th paragraph:
> The priority queue used, prioritizes the URLs based on a machine learning
> algorithm trained on the basis of the URL and the number of links it
> contains.
> a) Is there any assumption here that the links of the page lead to plog
>    posts? Why do URLs with more links are preferred?
> b) What is the aim here? To prioritize or to prune? The former makes no
>    sense (at the end you will have to deal with all the pages). The latter,
>    if it holds, is not clear - I was expecting to read about some threshold
>    value under which pages are dropped out of the queue.
> Please clarify both the above.
a) The "blog post identification function" described before serves this
   purpose.
b) The aim is to prune uninteresting pages, we wrote an additional paragraph
   to make this clear. It explains that this mechanism allows to add
   "termination conditions" in order to save some resources. Studying this
   kind or engineering coefficient/heuristic requires to experiment with a
   large amount of blogs, which was out of the scope of this paper.

> ----------------------- REVIEW 2 ---------------------
> The only comment is that the authors could have used some of the non-used
> space (8 out of 12 pages) to further discuss some of the pointed directions
> for future work.
We extensively discussed this point at the beginning of our work on the
crawler, and we decided to split the work into two parts. We originally aimed
for the "short paper" format, and planned our work to have it ready for the
first deadline (09/12/13), but we did not evaluated the length properly and
finally switched to the "full paper" format.

### 2014-04-05 tex/runningtimeFigure.tex
Invert legend order on the grnuplot figure
Formatting revisions

@@
 
-    set title 'Figure \arabic{figure}: Running time of articles extraction.'
+    set title '\textbf{Figure \arabic{figure}: Running time of article extraction}'
     set ylabel 'Cumulated running time (sec.)' offset 1.3
@@
     set xrange [0:65]
+    set key invert
 

### 2014-04-14 tex/runningtimeFigure.tex
Place caption below figure 2

@@
 \begin{figure}[t]
-  \capstart
   \refstepcounter{figure}
@@
     set terminal epslatex color
-    set size 0.76
+    set size 0.75
     set size ratio 0.618
 
-    set title '\textbf{Figure \arabic{figure}: Running time of article extraction}'
     set ylabel 'Cumulated running time (sec.)' offset 1.3
@@
   \end{gnuplot}
-  \vspace{-12pt}
+  \vspace{-18pt}
+  \caption{Running time of article extraction.}
 \end{figure}

### 2014-04-25 tex/main.tex
Minor typos and reformulations
Invert legend order on the grnuplot figure
Fix two typos
Formatting revisions
Hardcode the bibliography to adjust margins
Update license

@@
 \documentclass{sig-alternate}
-
-% Toggle comment this line, the url and the hyperref package
-% to generate a PDF/X-1a compliant output.
-% \usepackage[x-1a]{pdfx}
 
@@
 \usepackage[usenames,dvipsnames]{color}
-\usepackage[justification=centering]{caption}
 \usepackage[nodayofweek]{datetime}
@@
 \usepackage{booktabs}
+\usepackage[tableposition=top, font=bf]{caption}
 \usepackage{balance}
@@
 \usepackage{gnuplottex}
+\usepackage{ifthen}
 \usepackage{quoting}
@@
 \usepackage{setspace}
+\usepackage{xcolor}
 \usepackage[hyphens]{url}
-\usepackage[pdfpagelabels=false]{hyperref}
+\usepackage[pdfpagelabels=false,draft=true]{hyperref}
 \usepackage{hypcap}
@@
 \MakeOuterQuote{"}
-\setenumerate{noitemsep, topsep=10pt, parsep=6pt,partopsep=0pt}
-\setitemize{noitemsep,topsep=10pt, parsep=6pt, partopsep=0pt}
 \def\algorithmautorefname{Algorithm}
-\graphicspath{{img/}}
 
-\newdateformat{lv}{\THEDAY{ }\shortmonthname[\THEMONTH] \THEYEAR}
+\newdateformat{lv}{\THEDAY{ }\monthname[\THEMONTH] \THEYEAR}
 \newcommand{\lastvisited}{Last visited \lv\today}
@@
 \newcommand\Oof[1]{$\mathcal{O}(#1)$}
+\newboolean{fref}
 
@@
 
-  \conferenceinfo{WIMS'14,}{June 2-4, 2014 Thessaloniki, Greece}
-  \CopyrightYear{2014}
+  \permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+Copyrights for components of this work owned by others than the author(s) must be honored.
+Abstracting with credit is permitted.
+To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.
+Request permissions from Permissions@acm.org.}
+
+  \conferenceinfo{WIMS'14,}{June 02-04, 2014 Thessaloniki, Greece}
   \crdata{978-1-4503-2538-7/14/06}
+  \newcommand{\doi}{http://dx.doi.org/10.1145/2611040.2611067}
+
+  \global\copyrightetc{Copyright is held by the owner/authors. Publication rights licensed to ACM. ACM \the\acmcopyr\$15.00.\\\doi}
 
@@
 
+  \vspace{3pt}
+
   \balance
 
+  \def\changemargin{\list{}{\leftmargin3pt}\item[]}
+  \let\endchangemargin=\endlist
+  \let\oldbibitem\bibitem
+
+  \setboolean{fref}{true}
+  \renewcommand\bibitem[1]{
+    \ifthenelse{\boolean{fref}}{
+      \setboolean{fref}{false}
+      \vspace{4pt}
+      \oldbibitem{#1}
+      \begin{changemargin}
+    }{
+      \end{changemargin}
+      \oldbibitem{#1}
+      \begin{changemargin}
+    }
+  }
+
   \bibliographystyle{abbrv}
-  \bibliography{short}
+  \input{hardcoded.bbl}
+  % \bibliography{short}
 

### 2014-12-16 0-abstract.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

Blogs are one of the most prominent means of communication on the web. 
Their content, interconnections and influence constitute a unique 
socio-technical artefact of our times which needs to be preserved. 
The BlogForever project has established best practices and developed an 
innovative system to harvest, preserve, manage and reuse blog content. 
This paper presents the latest developments of the blog crawler which 
is a key component of the BlogForever platform. More precisely, our 
work concentrates on techniques to automatically extract content such 
as articles, authors, dates and comments from blog posts. To achieve 
this goal, we introduce a simple yet robust and scalable algorithm to 
generate extraction rules based on string matching using the blog's 
web feed in conjunction with blog hypertext. Furthermore, we present a 
system architecture which is characterised by efficiency, modularity, 
scalability and interoperability with third-party systems. Finally, 
we conduct thorough evaluations of the performance and accuracy of
our system.

### 2014-12-16 1-intro.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

\section{Introduction}

The blogosphere is an established channel of online communication which 
bears great significance~\cite{oevre2012}. Wordpress, a single blog 
publishing company, reports more than 1 million new posts and 1.5 million 
new comments each day~\cite{wordpress2014}. These overwhelming numbers 
illustrate the importance of blogs in most aspects of private and 
business life~\cite{chung2007uses}. Blogs contain data with historic, 
political, social and scientific value which need to be accessible 
for current and future generations. For instance, blogs proved to 
be an important resource during the 2011 Egyptian revolution by 
playing an instrumental role in the organization and implementation of 
protests~\cite{nahedeltantawy2012}. The problem is that blogs disappear 
every day~\cite{johnson2008blogs} because there is no standard method or 
authority to ensure blog archiving and long-term digital preservation.

Among the challenges in developing a blog archiving software
is the design of a web crawler capable of efficiently traversing blogs 
to harvest their content. The sheer size of the blogosphere combined with 
an unpredictable publishing rate of new information call for a highly 
scalable system, while the lack of programmatic access to the complete 
blog content makes the use of automatic extraction techniques necessary. 
The variety of available blog publishing platforms offers a limited 
common set of properties that a crawler can exploit, further narrowed by 
the ever-changing structure of blog contents. Finally, an increasing 
number of blogs heavily rely on dynamically created content to present 
information, using the latest web technologies, hence invalidating 
traditional web crawling techniques.

A key characteristic of blogs which differentiates them from regular 
websites is their association with web feeds~\cite{lindahl2003weblogs}. 
Their primary use is to provide a uniform subscription mechanism, thereby 
allowing users to keep track of the latest updates without the need to 
actually visit blogs. Concretely, a web feed is an XML file containing 
links to the latest blog posts along with their articles (abstract or 
full text) and associated metadata~\cite{board2007rss}. While web feeds 
essentially solve the question of update monitoring, their limited size 
makes it necessary to download blog pages to harvest previous content.

This paper presents the latest developments of the open-source 
BlogForever Crawler, a key component of the BlogForever 
platform~\cite{kasioumis2013towards} responsible for traversing blogs, 
extracting their content and monitoring their updates. Our main 
objectives in this work are to introduce a new approach to blog data 
extraction and to present the architecture and implementation of a blog 
crawler capable of extracting articles, authors, publication dates, 
comments and potentially any other element which appear in weblog
web feeds. Our contributions can be summarized as follows:

\begin{itemize}
\item 
A new algorithm to build extraction rules from web feeds and an optimised 
reformulation based on a particular string similarity algorithm featuring
linear time complexity.
\item 
A methodology to use the algorithm for blog article extraction and how 
it can be augmented to be used with other blog elements such as authors, 
publication dates and comments.
\item 
The overall BlogForever crawler architecture and implementation with a 
focus on design decisions, modularity, scalability and interoperability.
\item 
An approach to use a complete web browser to render JavaScript powered 
web pages before processing them. This step allows our crawler to 
effectively harvest blogs built with modern technologies, such as 
the increasingly popular third-party commenting systems.
\item 
A mapping of the extracted blog content to Archival Information Packages 
(AIPs) using METS and MARCXML standards for interoperability purposes.
\item 
An evaluation of the content extraction and execution time of our 
algorithm against three state-of-the-art web article extraction algorithms.\\
\end{itemize}

The concepts emerging from our research are viewed in the context of the 
BlogForever platform but the presented algorithms, techniques and system 
architectures can be used in other applications related to Wrapper 
Generation and Web Data Extraction.

The rest of this work is structured as follows: Section 2 presents 
related work. Section 3 introduces the new algorithms to extract data 
from blogs. Section 4 presents the blog crawler system architecture and 
implementation. Section 5 presents the evaluation and results. Finally, 
our conclusions and some discussion on our work are presented in section 6.

### 2014-12-16 2-related-work.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

\section{Related work}
\label{relatedwork}

Web crawlers are complex software systems which often combine techniques 
from various disciplines in computer science. Our work on the BlogForever 
crawler is related to the fields of web data extraction, distributed 
computing and natural language processing. In the literature on web 
data extraction, the word \emph{wrapper} is commonly used to designate 
procedures to extract structured data from unstructured documents. 
We did not use this word in the present paper in favour of the term 
\emph{extraction rule}, which better reflects our implementation and 
is decoupled from software that concretely performs the extraction.

A common approach in web data extraction is to manually build wrappers 
for the targeted websites. This approach has been proposed for the 
crawler discussed in \cite{faheem2012intelligent} which automatically 
assigns web sites to predefined categories and gets the appropriate 
wrapper from a static knowledge base. The limiting factor in this type 
of approach is the substantial amount of manual work needed to write and 
maintain the wrappers, which is not compatible with the increasing size 
and diversity of the web. Several projects try to simplify this process 
and provide various degrees of automation. This is the case of the 
Stalker algorithm \cite{stalker} which generates wrappers based on 
user-labelled training examples. Some commercial solutions such as 
the Lixto project \cite{lixto} simplify the task of building wrappers 
by offering a complete integrated development environment where the 
training data set is obtained via a graphical user interface.

As an alternative to dedicated software for the creation and maintenance 
of wrappers, some query languages have been designed specifically for 
wrappers. These languages rely on their users to manually identify 
the structure of the data to be extracted. This structure can then 
be formalised as a small declarative program, which can then be turned
into an concrete wrapper by an execution engine. The OXPath language 
\cite{oxpath2013} is an interesting extension to XPath designed to 
incorporate interaction in the extraction process. It supports simulated
user actions such as filling forms or clicking buttons to obtain 
information that would not be accessible otherwise. Another extension of 
XPath, called Spatial XPath \cite{sxpath2010}, allows to write spacial 
rules in the extraction queries. The execution engine embeds a complete 
web browser which computes the visual representation of the page.

Fully automated solutions use different techniques to identify and 
extract information directly from the structure and content of the web 
page, without the need of any manual intervention. The Boilerpipe project 
\cite{kohlschuetter2010} (which is also used in our evaluation) uses text 
density analysis to extract the main article of a web page. The approach 
presented in \cite{treeedit} is based on a tree structure analysis of 
pages with similar templates, such as news web sites or blogs. Automatic 
solutions have also been designed specifically for blogs. Similarly to 
our approach, Oita and Senellart \cite{oita2010} describe a procedure 
to automatically build wrappers by matching web feed articles to
HTML pages. This work was further extended by Gkotsis et al. with 
a focus on extracting content anterior to the one indexed in web 
feeds~\cite{gkotsis2013}. They also report to have successfully extracted 
blog post titles, publication dates and authors, but their approach 
is less generic than the one for the extraction of articles. Finally, 
neither \cite{oita2010} nor \cite{gkotsis2013} provide complexity 
analysis which we believe to be essential before using an algorithm 
in production.

One interesting research direction is the one of large scale distributed 
crawlers. Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} 
and the crawler discussed in \cite{shkapenyuk2002} are examples of 
successful distributed crawlers. The associated articles provide useful 
information regarding the challenges encountered when working on a 
distributed architecture. One of the core issues when scaling out seems 
to be in sharing the list of URLs that have already been visited and 
those that need to be visited next. While \cite{heydon99mercator} and 
\cite{shkapenyuk2002} rely on a central node to hold this information, 
\cite{boldi2003} uses a fully distributed architecture where URLs are 
divided among nodes using consistent hashing. Both of these approaches 
require the crawlers to implement complex mechanisms to achieve 
fault tolerance. The BlogForever Crawler circumvents this problem by 
delegating all shared mutable state to the back-end system. In addition, 
since we process web pages on the fly and directly emit the extracted 
content to the back-end, there is no need for persistent storage on 
the crawler's side. This removes one layer of complexity when compared 
to general crawlers which need to use a distributed file system 
(\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or 
implement an aggregation mechanism to further exploit the collected data. 
Our design is similar to the distributed active object pattern presented 
in \cite{activeobject1996}, which is further simplified by the fact that 
the state of the crawler instances is not kept between crawls.

### 2014-12-16 3-algorithms.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

--- 2014-01-19 tex/2-algorithms.tex
@@
 \label{algorithms}
-
-This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for extracting authors, dates and comments.
-Our approach uses blog specific characteristics to build \emph{extraction rules} which are applicable throughout a blog.
-Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.
+We propose a new set of algorithms to extract blog post articles as well 
+as variations for extracting authors, dates and comments. We start with 
+our motivation to use blog specific characteristics, followed by our 
+approach to build \emph{extraction rules} which are applicable throughout 
+a blog. Our focus is on minimising the algorithmic complexity while 
+keeping our approach simple and generic.
 
@@
 
-Extracting metadata and content from HTML documents is a challenging task.
-Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised~\cite{w3c2014}.
-For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page~\cite{w3c2002}.
-More recently, specifications such as microdata~\cite{whatwg2014} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites~\cite{andrewrogers2014}.
-In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages, and more than 95\% of pages do not pass HTML validation~\cite{brianwilson2008}.
-Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.
+Extracting metadata and content from HTML documents is a challenging task 
+because standards and format recommendations suffer from very low usage. 
+W3C has been publishing web standards and format recommendations for 
+quite some time~\cite{w3c2014}. For instance, according to the W3C 
+HTML guidelines, the \code{<h1></h1>} tags have to contain the 
+highest-level heading of the page and must not appear more than 
+once per page~\cite{w3c2002}. More recently, specifications such 
+as microdata~\cite{whatwg2014} define ways to embed semantic information 
+and metadata inside HTML documents, but these still suffer from 
+very low usage: estimated to be used in less than 0.5\% of 
+websites~\cite{andrewrogers2014}. In fact, the majority of websites rely 
+on the generic \code{<span></span>} and \code{<div></div>} container 
+elements with custom \code{id} or \code{class} attributes to organise 
+the structure of pages, and more than 95\% of pages do not pass HTML 
+validation~\cite{brianwilson2008}. Under such circumstances, relying 
+on HTML structure to extract content from web pages is not viable and 
+other techniques need to be employed.
 
-\Anotecontent{observations}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these observations, or to an insufficient amount of text in posts.}
+Having blogs as our target websites, we made the following observations 
+which play a central role in the extraction process:
 
-Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
-\begin{enumerate}[label={(\alph*)}]
-  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
-  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure,
+\begin{enumerate}
+\item\label{havefeedAssum} 
+Blogs provide web feeds: structured and standardized views of the latest 
+posts of a blog.
+\item\label{similarhtmlAssum} 
+Posts of the same blog share a similar HTML structure.
 \end{enumerate}
-Web feeds usually contain about 20 blog posts~\cite{oita2010}, often less than the total number of posts in blogs.
-Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in the web feed.
+
+Web feeds usually contain about 20 blog posts~\cite{oita2010}, 
+often less than the total number of posts in blogs. Consequently, to 
+effectively archive the entire content of a blog, it is necessary to 
+download and process pages beyond the ones referenced in the web feed.
 
@@
 % per blog procedure, related work
-To extract content from blog posts, we proceed by building \emph{extraction rules} from the data given in the blog's web feed.
-The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.
+To extract content from blog posts, we proceed by building 
+\emph{extraction rules} from the data given in the blog's web feed. 
+The idea is to use a set of \emph{training data}, pairs of HTML pages 
+and target content, which are used to build an extraction rule capable 
+of locating the target content on each HTML page.
 
 % input from observations.
-Observation~\ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date.
-We call these fields \emph{targets} as they constitute the data our crawler aims to extract.
-Observation~\ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.
+Observation (\ref{havefeedAssum}) allows the crawler to obtain input for 
+the extraction rule generation algorithm: each web feed entry contains a 
+link to the corresponding web page as well as blog post article (either 
+abstract or full text), its title, authors and publication date. We call 
+these fields \emph{targets} as they constitute the data our crawler aims 
+to extract. Observation (\ref{similarhtmlAssum}) guarantees the existence 
+of an appropriate extraction rule, as well as its applicability to all 
+posts of the blog.
 
-\autoref{extractionAlgo} shows the generic procedure we use to build extraction rules.
-The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute, out of all possible extraction rules, the best one with respect to a certain \code{ScoreFunction}.
-The rule which is most frequently the \emph{best rule} is then returned.
+\autoref{extractionAlgo} shows the generic procedure we use to build 
+extraction rules. The idea is quite simple: for each \code{(}\emph{page, 
+target}\code{)} input, compute, out of all possible extraction rules, 
+the best one with respect to a certain \code{ScoreFunction}. The rule 
+which is most frequently the \emph{best rule} is then returned.
 
@@
 
-One might notice that each \emph{best rule} computation is independent and operates on a different input pair.
-This implies that \autoref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.
+One might notice that each \emph{best rule} computation is 
+independent and operates on a different input pair. This implies that 
+\autoref{extractionAlgo} is \emph{embarrassingly parallel}: iterations 
+of the outer loop can trivially be executed on multiple threads.
 
-Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section.
+Functions in \autoref{extractionAlgo} are voluntarily abstract at this 
+point and will be explained in detail in the remaining of this section.
 \hyperref[extractionrulesandstringsimilarity]{Subsection~\ref*{extractionrulesandstringsimilarity}} % Waiting for \Autoref{}...
-defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction.
-In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programming.
-Finally, \autoref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
+defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use 
+for article extraction. In \autoref{timecomplexityandlinearreformulation} 
+we analyse the time complexity of \autoref{extractionAlgo} and give a 
+linear time reformulation using dynamic programming. Finally, 
+\autoref{variationsforauthorsdatesandcomments} shows how the 
+\code{ScoreFunction} can be adapted to extract authors, dates and 
+comments.
 
@@
 
-In our implementation, rules are queries in the XML Path Language (XPath).
-Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, providing the \code{Apply} function used in \autoref{extractionAlgo}.
-We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection using the relative path in the HTML tree.
-\code{id} attributes are expected to be unique, and \code{class} attributes have showed in our experiments to have better consistency than relative paths over pages of a blog.
-For these reasons we opt to always favour \code{class} over path, and \code{id} over \code{class}, such that the \coderef{allrulesAlgo} function returns a single rule per node.
+In our implementation, rules are queries in the XML Path Language 
+(XPath). Consequently, standard libraries can be used to parse HTML pages 
+and apply extraction rules, providing the \code{Apply} function used in 
+\autoref{extractionAlgo}. We experimented with 3 types of XPath queries: 
+selection over the HTML \code{id} attribute, selection over the HTML 
+\code{class} attribute and selection using the relative path in the HTML 
+tree. \code{id} attributes are expected to be unique, and \code{class} 
+attributes have showed in our experiments to have better consistency than 
+relative paths over pages of a blog. For these reasons we opt to always 
+favour \code{class} over path, and \code{id} over \code{class}, such 
+that the \coderef{allrulesAlgo} function returns a single rule per node.
 
@@
 
-Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process.
-When targeting articles, extraction rule scores are computed with a string similarity function comparing the extracted strings with the target strings.
-We chose the Sørensen–Dice coefficient similarity~\cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:
+Unsurprisingly, the choice of \code{ScoreFunction} greatly influences 
+the running time and precision of the extraction process. When targeting 
+articles, extraction rule scores are computed with a string similarity 
+function comparing the extracted strings with the target strings. 
+We chose the Sorensen–Dice coefficient similarity~\cite{dice1945}, 
+which is, to the best of our knowledge, the only string similarity 
+algorithm fulfilling the following criteria:
 
-\begin{enumerate}
+\begin{itemize}
 \item\label{wordorderProp} Has low sensitivity to word ordering,
@@
 \item\label{linearProp} Runs in linear time.
-\end{enumerate}
+\end{itemize}
 
-Properties \ref{wordorderProp} and \ref{lengthProp} are essential when dealing with cases where the blog's web feed only contains an abstract or a subset of the entire post article.
-\autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein~\cite{levenshtein1966} similarity.
+Properties \ref{wordorderProp} and \ref{lengthProp} are essential when 
+dealing with cases where the blog's web feed only contains an abstract 
+or a subset of the entire post article. \autoref{similarityTable} 
+gives examples to illustrate how these two properties hold for the 
+Sorensen–Dice coefficient similarity but do not for \emph{edit distance} 
+based similarities such as the Levenshtein~\cite{levenshtein1966} 
+similarity.
 
-\similarityTable
+\begin{table}
+\tbl{Examples of string similarities.}
+{\begin{tabular}{@{}llcc@{}} \toprule
+        \textbf{string1} & \textbf{string2} & \textbf{Sorensen-Dice} & \textbf{Levenshtein} \\
+    \midrule
+    \stringliteral{Scheme Scala} & \stringliteral{Scala Scheme}
+    & 90\% & 50\% \\
+    \stringliteral{Rachid} & \stringliteral{Richard}
+    & 18\% & 61\% \\
+    \stringliteral{Rachid} & \stringliteral{Amy, Rachid and all their friends}
+    & 29\% & 31\% \\ \hline
+\end{tabular}}
+\label{similarityTable}
+\end{table}
 
-The Sørensen–Dice coefficient similarity algorithm operates by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:
+The Sorensen–Dice coefficient similarity algorithm operates by 
+first building sets of pairs of adjacent characters, also known as 
+\emph{bigrams}, and then applying the \emph{quotient of similarity} formula:
 
@@
 
-With the functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is now complete.
-We can therefore proceed with a time complexity analysis.
+With the functions \coderef{allrulesAlgo}, \code{Apply} and 
+\coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the 
+definition of \autoref{extractionAlgo} for article extraction is now 
+complete. We can therefore proceed with a time complexity analysis.
 
-First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure, indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}.
-As stated before, the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument.
-Therefore, the body of the inner loop will be executed \Oof{n} times.
-Because each extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.
+First, let's assume that we have at our disposal a linear time HTML 
+parser that constructs an appropriate data structure, indexing HTML 
+nodes on their \code{id} and \code{class} attributes, effectively making 
+\code{Apply}~$\in$~\Oof{1}. As stated before, the outer loop splits 
+the input into independent computations and each call to 
+\coderef{allrulesAlgo} returns (in linear time) at most as many rules as 
+the number of nodes in its \emph{page} argument. Therefore, the body of 
+the inner loop will be executed \Oof{n} times. Because each extraction 
+rule can return any subtree of the queried page, each call to 
+\coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic 
+running time.
 
-We now present \autoref{linearAlgo}, a linear time reformulation of \autoref{extractionAlgo} for article extraction using dynamic programming.
+We now present \autoref{linearAlgo}, a linear time reformulation of 
+\autoref{extractionAlgo} for article extraction using dynamic programming.
 
@@
 
-While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams (set of pairs of adjacent characters).
-For instance, when evaluating the extraction rule for the HTML root node, \autoref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function.
-At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string.
-To overcome this limitation and implement \emph{memoization} over the bigrams computations, \autoref{linearAlgo} uses a post-order traversal of the HTML tree and computes node bigrams from their children bigrams.
-This way, we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.
+While very intuitive, the original idea of first generating extraction 
+rules and then picking these best rules prevents us from effectively 
+reusing previously computed $N$-grams (sets of adjacent characters). 
+For instance, when evaluating the extraction rule for the HTML root node, 
+\autoref{extractionAlgo} will obtain the complete string of the page 
+and pass it to the \coderef{similarityAlgo} function. At this point, 
+the information on where the string could be split into substrings with 
+already computed $N$-grams is not accessible, and the $N$-grams of 
+the page have to be computed by linearly traversing the entire string. 
+To overcome this limitation and implement \emph{memoization} over the 
+$N$-gram computations, \autoref{linearAlgo} uses a post-order traversal 
+of the HTML tree and computes node $N$-grams from their children 
+$N$-grams. This way, we avoid serializing HTML subtrees for each 
+$N$-gram computation and have the guarantee that each character of the 
+HTML page will be read at most once during the $N$-gram computation.
 
-With bigrams computed in this dynamic programming manner, the overall time to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear.
-To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time.
-As the number of edges in a tree is one less than the number of nodes, the \emph{amortized} number of bigrams unions per inner loop iteration tends to one.
-Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations.
-Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.
+An interesting question is what is the optimal $N$ for $N$-gram 
+computation. To answer this question, we conduct some simple experiments. 
+Using sample blog post excerpts and full texts, we calculate the string 
+similarity between each excerpt and full text. For instance, using a blog 
+post full text and associated text excerpt from the popular blog TechCrunch
+as presented in Table \ref{table:techcrunch}, the text similarity results
+(Table \ref{table:similarity-n-values}) using different $N$ values support
+the selection of bigrams ($N$=2).
+
+\begin{table}
+\tbl{TechCrunch blog post example.}
+{\begin{tabular}{@{}p{12cm}@{}} \toprule
+\emph{Blog post text} \\ \hline
+Apple has a new version of iOS 8 out, just a short time after the 
+initial launch of the software. The update, 8.0.1, includes a number of 
+fixes, but most notably (and listed first), it addressed the bug that 
+prevented HealthKit apps from being available at launch. It also zaps 
+some bugs with third-party keyboards, which should make them remain the 
+default option until a user switches to another, which has been a sore 
+spot for fans of the new external software keyboard options.
+
+Unfortunately, installing the iOS 8.0.1 update revealed that despite 
+Apple’s promised fixes, it actually completely disables cellular service 
+and Touch ID on many devices, though some iPhone 5s and older model 
+owners report no issues. The bottom line is that you should definitely 
+NOT install this update, at least until an updated version appears, 
+at which time we’ll let you know it’s safe to go ahead.
+
+As you can see in the image below, Apple is also addressing an issue that 
+blocked some photos from appearing in Photo Library, fixing reliability 
+concerns around Reachability on iPhone 6 and 6 Plus (which brings the top 
+of the screen down when you double touch the Home button), zapping bugs 
+that cause unexpected data use when communicating via SMS or MMS, and 
+improving the “Ask to Buy” feature for Family Sharing, specifically 
+around in-app purchases, in addition to other minor bugs.\\ \hline
+
+\emph{Weblog post text abstract from RSS} \\ \hline
+Apple has a new version of iOS 8 out, just a short time after the 
+initial launch of the software. The update, 8.0.1, includes a number of 
+fixes, but most notably (and listed first), it addressed the bug that 
+prevented HealthKit apps from being available at launch. It also zaps... \\ \hline
+\end{tabular}}
+\label{table:techcrunch}
+\end{table}
+
+\begin{table}
+\tbl{Blog post excerpt and full text similarity using different $N$ values.}
+{\begin{tabular}{@{}lccc@{}} \toprule
+        \emph{$N$} & \emph{2} & \emph{3} & \emph{4} \\ \hline
+Similarity & 0.7817 & 0.6680 & 0.6212 \\ \hline
+\end{tabular}}
+\label{table:similarity-n-values}
+\end{table}
+
+With bigrams computed in this dynamic programming manner, the overall 
+time to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} 
+is linear. To conclude the proof that \autoref{linearAlgo} runs in linear 
+time we show that all other computations of the inner loop can be done 
+in constant \emph{amortized} time. As the number of edges in a tree is 
+one less than the number of nodes, the \emph{amortized} number of bigrams 
+unions per inner loop iteration tends to one. Each \emph{quotient of 
+similarity} computation requires one bigrams intersection and three 
+bigrams length computations. Over a finite alphabet (we used printable 
+ASCII), bigrams sizes have bounded size and each of these operations 
+takes constant time.
 
@@
 
-Using string similarity as the only score measurement leads to poor performance on author and date extraction, and is not suitable for comment extraction.
-This subsection presents variations of the \code{ScoreFunction} which addresses issues of these other types of content.
+Using string similarity as the only score measurement leads to poor 
+performance on author and date extraction, and is not suitable for 
+comment extraction. This subsection presents variations of the 
+\code{ScoreFunction} which addresses issues of these other types of content.
 
-The case of authors is problematic because authors' names often appear in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score.
-The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for author extraction rules: the \emph{tree distance} between the evaluated node and the post content node.
-This new component takes advantage of the positioning of a post's authors node which often is a direct child or shares its parent with the post content node.
+The case of authors is problematic because authors' names often appear in 
+multiple places of a page, which results in several rules with maximum 
+\coderef{similarityAlgo} score. The heuristic we use to get around this 
+issue consists of adding a new component in the \code{ScoreFunction} for 
+author extraction rules: the \emph{tree distance} between the evaluated 
+node and the post content node. This new component takes advantage of 
+the positioning of a post's authors node which often is a direct child 
+or shares its parent with the post content node.
 
-Dates are affected by the same duplication issue, as well as the issue of inconsistencies of format between web feeds and web pages.
-Our solution for date extraction extends the \code{ScoreFunction} for authors by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original date obtained from the web feed.
-For instance, if the feed indicates that a post was published at \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on.
-So far we do not support dates in multiple languages, but adding new target formats based on languages detection would be a simple extension of our date extraction algorithm.
+Dates are affected by the same duplication issue, as well as the issue of 
+inconsistencies of format between web feeds and web pages. Our solution 
+for date extraction extends the \code{ScoreFunction} for authors by 
+comparing the \emph{extracted} string to multiple \emph{targets}, each 
+being a different string representation of the original date obtained 
+from the web feed. For instance, if the feed indicates that a post was 
+published at \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm 
+will search for a rule that returns one of \stringliteral{Thursday 
+January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years 
+ago} and so on. So far we do not support dates in multiple languages, 
+but adding new target formats based on languages detection would be a 
+simple extension of our date extraction algorithm.
 
 Comments are usually available in separate web feeds, one per blog post. 
-Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from web pages.
-To do so, we use the following \code{ScoreFunction}:
+Similarly to blog feeds, comment feeds have a limited number of entries, 
+and when the number of comments on a blog post exceeds this limit, 
+comments have to be extracted from web pages. To do so, we use the 
+following \code{ScoreFunction}:
 
 \begin{itemize}
-  \item Rules returning fewer HTML nodes than the number of comments on the feed are filtered out with a zero~score,
-  \item The scores of the remaining rules are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
+\item 
+Rules returning fewer HTML nodes than the number of comments on the feed 
+are filtered out with a zero~score,
+\item 
+The scores of the remaining rules are computed with the value of the 
+\emph{maximum weighted matching} in the \emph{complete bipartite graph} 
+$G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, 
+$V$ is the set of target comment fields from the web feed (such as 
+comment authors) and $E(u, v)$ has weight equal to 
+\coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
 \end{itemize}
-Our crawler executes this algorithm on each post with an overflow on its comment feed, thus supporting blogs with multiple commenting engines.
-The comment content is extracted first, allowing us to narrow down the initial filtering by fixing a target number of comments.
 
-Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity.
-Computing scores of comment extraction rules requires a more expensive algorithm.
-However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice.
-Analogous reformulations to the one done with \autoref{linearAlgo} can be straightforwardly applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.
+Regarding time complexity, computing the \emph{tree distance} of each 
+node of a graph to a single reference node can be done in linear time, 
+and multiplying the number of targets by a constant factor does not 
+affect the asymptotic computational complexity. Computing scores of 
+comment extraction rules requires a more expensive algorithm. However, 
+this is compensated by the fact that the proportion of candidates left, 
+after filtering out rules not returning enough results, is very low in 
+practice. Analogous reformulations to the one done with 
+\autoref{linearAlgo} can be straightforwardly applied on each 
+\code{ScoreFunction} to minimize the time spent in 
+\coderef{similarityAlgo}.

### 2014-12-16 4-architecture.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

\section{Architecture}
\label{architecture}

We present the BlogForever crawler system architecture which implements 
the proposed algorithms for weblog data extraction via the generation 
of extraction rules. We describe the system architecture and discuss 
the software tools and techniques we used, such as the enrichment of the 
Scrapy framework for our specific usage and the integration of a headless 
web browser into the harvesting process to achieve content extraction 
from webpages which use JavaScript to display content. Following, 
we focus on the scalability design and distributed architecture of our 
system. Finally, we present our provisions for interoperability using 
established open standards which increases the value and reusability 
of the proposed system in many contexts.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{System and workflow}

The BlogForever crawler is a Python\footnote{\label{python}\url{http://www.python.org/}} 
application which is based on  Scrapy, an open-source framework for web crawling. 
Scrapy provides an elegant and modular architecture illustrated 
in Fig. \ref{scrapyarchitecture}. Several components can be plugged into 
the Scrapy core infrastructure. Following, we present each part of the 
architecture and our own contributions:

\begin{itemize}
\item 
\emph{Spiders} define how a target website is scraped, including how to 
perform the crawl (i.e. follow links). The BlogForever crawer implementation
includes two new types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl},
which implement the logic to respectively crawl a new blog and get updates
from a previously crawled blog.
\item 
\emph{Item Pipeline} defines the processing of extracted data from 
the spiders through several components that are executed sequentially. 
The BlogForever crawler implementation includes a new item pipeline 
which orchestrates all aspects of crawling. More specifically the 
BlogForever pipeline is defined as follows:
  \begin{enumerate}
  \item JavaScript rendering,
  \item Extract content,
  \item Extract comments,
  \item Download multimedia files,
  \item Prepare Archival Information Packages (APIs) to propagate 
the results to potential back-ends.
  \end{enumerate}
\item 
\emph{Downloader Middlewares} is a framework of hooks into Scrapy’s 
request/response processing and altering Scrapy’s requests and responses. 
\item 
\emph{Spider Middlewares} is a framework of hooks into Scrapy’s spider 
processing mechanism.
\end{itemize}

\begin{figure}[t]
\capstart
\centering
\includegraphics[width=\textwidth]{./img/scrapy_architecture.eps}
\caption{Overview of the crawler architecture. (Credit: Pablo Hoffman, Daniel Graña, Scrapy)}
\label{scrapyarchitecture}
\end{figure}

The system architecture providers great modularity. This is illustrated 
clearly in our work with the following
example:

\begin{itemize}
\item 
If it is necessary to disable JavaScript rendering or plugging in an 
alternative back-end can be done by editing a single line of code. 
\item The features to extract comments and download multimedia files 
were implemented after creating the initial logic to extract content 
and were added as extra steps in the pipeline.
\item The requirement to implement interoperability provisions later 
presented in section \ref{interop} was easily covered with the implementation 
of an extra middleware plugin which was invoked from the main crawler 
architecture. No further modifications were necessary in the code.
\end{itemize}

In the remaining parts of this section, we elaborate our work on each 
specific part of the crawler system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}

JavaScript is a widely used language for client-side scripting. 
While some applications simply use it for aesthetics, an increasing 
number of websites use JavaScript to download and display content. 
In such cases, traditional HTML based crawlers do not see web pages 
as they are presented to a human visitor by a web browser, and might 
therefore be obsolete for data extraction.

In our experiments whilst crawling the blogosphere, we encountered 
several blogs where crawled data was incomplete because of the lack 
of JavaScript interpretation. The most frequent cases were blogs using 
the Disqus\footnote{\url{http://disqus.com/websites}} and 
LiveFyre\footnote{\url{http://web.livefyre.com}} comment hosting services. 
For webmasters, these tools are very handy because the entire comments 
infrastructure is externalized and their setup essentially comes down 
to including a JavaScript snippet in each target page. Both of these 
services heavily rely on JavaScript to download and display the comments, 
even providing functionalities such as real-time updates for edits and 
newly written comments. Less commonly, some blogs are fully rendered 
using JavaScript. When loading such websites, the web browser will not 
receive the page content as an HTML document, but will instead have 
to execute JavaScript code to download and display the page content. 
The Blogger platform provides the \emph{Dynamic Views} as a default 
template, which uses this mechanism~\cite{antinharasymiv2011}.

To support blogs with JavaScript-generated content, we embed a full web 
browser into the crawler. After considering multiple options, we opted 
for PhantomJS\footnote{\url{http://phantomjs.org}}, a headless web 
browser with great performance and scripting capabilities. The JavaScript 
rendering is the very first step of web page processing. Therefore, 
extracting blog post articles, comments or multimedia files works equally 
well on blogs with JavaScript-generated content and on traditional 
HTML-only blogs.

When the number of comments on a page exceeds a certain threshold, both 
Disqus and LiveFyre will only load the most recent ones and the stream 
of comments will end with a \emph{Show More Comments} button. As part of 
the page loading process, we instruct PhantomJS to repeatedly click on 
these buttons until all comments are loaded. Paths to Disqus and LiveFyre 
\emph{Show More} buttons are manually obtained. They constitute the 
only non-generic elements of our extraction stack which require human 
intervention to maintain and extend to other commenting platforms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}\label{enrichingscrapy}

In order to identify web pages as blog posts, our implementation enriches 
Scrapy with two components to narrow the extraction process down to the 
subsets of pages which are blog posts: \emph{blog post identification} 
and \emph{download priority heuristic}.

Given a URL entry point to a website, the default Scrapy behaviour 
traverses all the pages of the same domain in a \emph{last-in-first-out} 
manner. The \emph{blog post identification} function is able to identify 
whether an URL points to a blog post or not. Internally, for each blog, 
this function uses a regular expression constructed from the blog post 
URLs found in the web feed. This simple approach requires that blogs use 
the same URL pattern for all their posts (or false negatives will occur) 
which has to be distinct for pages that are not posts (or false positives 
will occur). In practice, this assumption holds for all blog platforms 
we encountered and seems to be a common practice among web developers.

In order to efficiently deal with blogs that have a large number of 
pages which are not posts, the \emph{blog post identification} mechanism 
is not sufficient. Indeed, after all pages identified as blog posts 
are processed, the crawler needs to download all other pages to search 
for additional blog posts. To replace the naive \emph{random walk}, 
\emph{depth first search} or \emph{breadth first search} web site 
traversals, we use a priority queue where priorities for new URLs are 
determined by a machine learning system. This mechanism has shown 
to be mandatory for blogs hosted on a single domain alongside large 
number of other types of web pages, such as those in forums or wikis.

The idea is to give high priority to URLs which are believed to 
point to pages with links to blog posts. These predictions are 
done using an active \emph{Distance-Weighted $k$-Nearest-Neighbour} 
classifier~\cite{dudani1976}. Let $L(u)$ be the number of links to blog 
posts contained in a page with URL $u$. Whenever a page is downloaded, 
its URL $u$ and $L(u)$ are given to the machine learning system as 
training data. When the crawler encounters a new URL $v$, it will ask the 
machine learning system for an estimation of $L(v)$, and use this value 
as the download priority of $v$. $L(v)$ is estimated by calculating a 
weighted average of the values of the $k$ URLs most similar to $v$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The BlogForever metadata schema for interoperability}
\label{interop}

One of the key BlogForever project goals is interoperability with third 
party platforms. The original BlogForever crawler was intended to
insert blog data directly to the BlogForever repository component but
later the architecture was reworked to make it possible to use
other storage and archiving systems as well. 
To achieve this goal, we implement a special interoperability middleware 
for the spider to produce Archival Information Packages (AIPs) from 
harvested blog content. The AIPs can be used by any software platform 
which complies with the OAIS reference model~\cite{lavoie2000meeting}. 
It must be noted also that this is the first time weblog content is 
encoded in this way.

The AIPs consist of XML files structured using the 
METS~\cite{cantara2005mets} standard for encoding metadata and 
content. METS is widely adopted and supported by all popular digital 
library systems. In addition, the blog content attributes which 
are included in the METS XML packages are encoded using the MARCXML
Schema\cite{marc2003official}. The reason for the selection of MARCXML 
is the wide adoption of the standard, its flexibility and extensibility, 
as well as previous experience with the Invenio digital library
system\footnote{\url{http://invenio-software.org/}} which is also based
on MARCXML.

There are three kinds of entities which can be included in an AIP: 
Blog, Entry and Comment. The content extracted from weblogs is mapped 
to the relevant entities using the following rule: If an attribute is 
already defined in MARC for other content types use the same MARC code 
for blogs. If an attribute is totally new, an unused MARC 9xx tag is 
chosen to represent it, composing therefore the BlogForever metadata 
schema~\cite{llopis2012d4}. Following, we present the BlogForever 
metadata schema for Blog, Post, Page and Comment entities in Tables 
\ref{table:blog-record-attributes}, 
\ref{table:post-page-shared-attributes} and 
\ref{table:comment-attributes}.

\begin{table}
\tbl{Blog record attributes - MARC 21 representations mapping.}
{\begin{tabular}{@{}ll@{}} \toprule
\textbf{Blog attribute} & \textbf{MARC 21 representation} \\ \hline
title & 245 \$a \\
subtitle & 245 \$b \\
URI & 520 \$u\\
aliases & 100 \$g \\
status\_code & 952 \$a\\
language & 041 \$a\\
encoding & 532\\
sitemap\_uri & 520\\
platform & 781 \$a\\
platform\_version & 781 \$b\\
webmaster & 955 \$a\\
hosting\_ip & 956 \$a\\
location\_city & 270 \$d\\
location\_country & 270 \$b\\
last\_activity\_date & 954 \$a\\
post\_frequency & 954 \$b\\
update\_frequency & 954 \$c\\
copyright & 542\\
ownership\_rights & 542\\
distribution\_rights & 542\\
access\_rights & 542\\
license & 542 \$f\\ \hline
\end{tabular}}
\label{table:blog-record-attributes}
\end{table}

\begin{table}
\tbl{Blog record attributes - MARC 21 representations mapping.}
{\begin{tabular}{@{}ll@{}} \toprule
\textbf{Post and page attribute} & \textbf{MARC 21 representation} \\ \hline
title & 245 \$a \\
subtitle & 245 \$b \\
full\_content & 520 \$a \\
full\_content\_format & 520 \$b \\
author & 100 \$a \\
URI & 520 \$u \\
aliases & 100 \$g \\
alt\_identifier (UR) & 0247 \$a \\
date\_created & 269 \$c\\
date\_modified & 260 \$m \\
version & 950 \$a \\
status\_code & 952 \$a \\
response\_code & 952 \$b \\
geo\_longitude & 342 \$g \\
geo\_latitude & 342 \$h \\
access\_restriction & 506 \\
has\_reply & 788 \$a \\
last\_reply\_date & 788 \$c \\
num\_of\_replies & 788 \$b \\
child\_of & 760 \$o \$4 \$w\\
\hline
\end{tabular}}
\label{table:post-page-shared-attributes}
\end{table}

\begin{table}
\tbl{Comment record attributes - MARC tags mapping.}
{\begin{tabular}{@{}ll@{}} \toprule
\textbf{Comment attribute} & \textbf{MARC 21 representation} \\ \hline
subject & 245 \$a\\
author & 100 \$a \\
full\_content & 520 \$a \\
full\_content\_format & 520 \$b \\
URI & 520 \$u\\
status & 952 \$a\\
date\_added & 269 \$c\\
date\_modified & 269 \$m\\
addressed\_to\_URI & 789 \$u\\
%& \textit{timezone} & \\
%& \textit{format} & \\
%& comment\_type (UR) & \\
%& source\_URI (UR) & \\
%& source\_name (UR) & \\
geo\_longitude & 342 \$g \\
geo\_latitude & 342 \$h \\
has\_reply & 788 \$a \\
num\_replies & 788 \$b\\
is\_child\_of\_post & 773 \$o \$4 \$w\\
is\_child\_of\_comment & 773 \$o \$4 \$w\\ \hline
\end{tabular}}
\label{table:comment-attributes}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Distributed architecture and scalability}
\label{scalability}

One of the problems of web crawling is the large amount 
of input which need to be processed. To address this issue, 
it is crucial to build every layer of the system with scalability in 
mind~\cite{thereactivemanifesto2013}.

The BlogForever Crawler, and in particular the two core procedures 
\emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as 
part of an event-driven, scalable and fault-resilient distributed system. 
Heading in this direction, we made the key design choice to have 
both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. 
From a high-level point of view, these two components are \emph{purely functional}:
%
\begin{eqnarray*}
NewCrawl:    &~ URL \rightarrow \mathcal{P}(RECORD) \\
UpdateCrawl: &~ URL \times DATE \rightarrow \mathcal{P}(RECORD)
\end{eqnarray*}
%
where $URL$, $DATE$ and $RECORD$ are respectively the set of all URLs, 
dates and records, and $\mathcal{P}$ designates the power set operator. 
By delegating all shared mutable state to the back-end system, 
web crawler instances can be added, removed and used interchangeably.

To implement a distributed crawler architecture, we choose to use 
Scrapyd\footnote{\url{http://scrapyd.readthedocs.org/en/latest/}}, 
an application for deploying and running Scrapy spiders. 
The process is quite straightforward:

\begin{enumerate}
\item 
Deploy the BlogForever crawler in any number of servers according 
to requirements. Using the Scrapyd component which is run as a system 
daemon, each crawler is listening for requests to run crawling tasks 
and spawn a process for each new command.
\item 
Implement a small control program that reads the list of target weblogs 
which need to be crawled and issue commands in a round-robin fashion 
using the Scrapyd JSON 
API\footnote{\url{http://scrapyd.readthedocs.org/en/latest/api.html}}. 
\item 
All crawlers share a common storage service where they save the crawling 
results. 
\end{enumerate}

### 2014-12-16 5-evaluation.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

--- 2014-01-19 tex/4-evaluation.tex
@@
 
-Our evaluation is articulated in two parts.
-First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting articles and titles from web pages.
-The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time.
-Second, a discussion is held regarding the different solutions available to archive data beyond what is available in the HTML source code.
-Extraction of authors, dates and comments is not part of this evaluation because of the lack of publicly available competing projects and reference data sets.
+Our evaluation is articulated in two parts. First, we compare the 
+article extraction procedure presented in \autoref{algorithms} with 
+three open-source projects capable of extracting articles and titles 
+from web pages. The comparison will show that our weblog-targeted solution 
+has better performance both in terms of success rate and running time. 
+Second, a discussion is held regarding the different solutions available 
+to archive data beyond what is available in the HTML source code. 
+Extraction of authors, dates and comments is not part of this evaluation 
+because of the lack of publicly available competing projects and 
+reference data sets.
 
-In our experiments we used \emph{Debian GNU/Linux 7.2}, \emph{Python 2.7} and an \emph{Intel Core i7-3770 3.4 GHz} processor.
-Timing measurements were made on a single dedicated core with garbage collection disabled.
-The Git repository for this paper\footnote{\url{https://github.com/OlivierBlanvillain/bfc-paper}} contains the necessary scripts and instructions to reproduce all the evaluation experiments presented in this section.
-The crawler source code is available under the MIT license from the project's websites\footnote{\url{https://github.com/BlogForever/crawler}}.
+In our experiments we used \emph{Debian GNU/Linux 7.2}, \emph{Python 2.7} 
+and an \emph{Intel Core i7-3770 3.4 GHz} processor. Timing measurements 
+were made on a single dedicated core with garbage collection disabled. 
+The Git repository for this 
+paper\footnote{\url{https://github.com/OlivierBlanvillain/bfc-paper}} 
+contains the necessary scripts and instructions to reproduce all the 
+evaluation experiments presented in this section. The crawler source 
+code is available under the MIT license from the project's 
+websites\footnote{\url{https://github.com/BlogForever/crawler}}.
 
@@
 \subsection{Extraction success rates}
-To evaluate article and title extraction from blog posts we compare our approach to three open source projects: Readability\footnote{\url{https://github.com/gfxmonk/python-readability}}, Boilerpipe~\cite{kohlschuetter2010} and Goose\footnote{\url{https://github.com/GravityLabs/goose}}, which are implemented in JavaScript, Java and Scala respectively.
-These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).
-\autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts from 230 blogs obtained from the Spinn3r dataset~\cite{burton2011}.
 
-\precisionTable
+To evaluate article and title extraction from weblog posts 
+we compare our approach to three open source projects: 
+Readability\footnote{\url{https://github.com/gfxmonk/python-readability}}, 
+Boilerpipe~\cite{kohlschuetter2010} and Goose\footnote{\url{https://github.com/GravityLabs/goose}}, 
+which are implemented in JavaScript, Java and Scala respectively. 
+These projects are more generic than our blog-specific approach in the 
+sense that they are able to identify and extract data directly from HTML 
+source code, and do not make use of web feeds or structural similarities 
+between pages of the same weblog (observations (\ref{havefeedAssum}) and 
+(\ref{similarhtmlAssum})). Table \ref{table:evaluation-performance} shows the extraction 
+success rates for article and title on a test sample of 2300 posts 
+from 230 weblogs obtained from the Spinn3r dataset~\cite{burton2011}.
 
-On our test dataset, \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction.
-It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page.
-On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules.
-Therefore, results shown in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as evidence that our approach is more suitable when working with blogs.
+\begin{table}
+\tbl{Extraction success rates for different algorithms.}
+{\begin{tabular}{@{}lcccc@{}} \toprule
+		\textbf{Target} & \textbf{Our~approach} & \textbf{Readability} & \textbf{Boilerpipe} & \textbf{Goose} \\ \hline
+    Article & 93.0\% & 88.1\% & 79.3\% & 79.2\% \\
+    Title   & 95.0\% & 74.0\% & N/A    & 84.9\% \\ \hline
+\end{tabular}}
+\label{table:evaluation-performance}
+\end{table}
+
+On our test dataset, \autoref{extractionAlgo} outperformed the 
+competition by 4.9\% on article extraction and 10.1\% on title 
+extraction. It is important to stress that Readability, Boilerpipe 
+and Goose rely on generic techniques such as word density, paragraph 
+clustering and heuristics on HTML tagging conventions, which are designed 
+to work for any type of web page. On the contrary, our algorithm is 
+only suitable for pages with associated web feeds, as these provide the 
+reference data used to build extraction rules. Therefore, results shown 
+in Table \ref{table:evaluation-performance} should not be interpreted as a general 
+quality evaluation of the different projects, but simply as evidence 
+that our approach is more suitable when working with weblogs.
 
@@
 
-In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure.
-The main point of interest is the ability of the extraction procedure to scale as the number of posts in the processed blog increases.
-This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all published content on a blog.
+In addition to the quality of the extracted data we also evaluated the 
+running time of the extraction procedure. The main point of interest is 
+the ability of the extraction procedure to scale as the number of posts 
+in the processed weblog increases. This corresponds to the evaluation of 
+a \emph{NewCrawl} task, which is in charge of harvesting all published 
+content on a weblog.
 
-\autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed.
-We used the Quantum Diaries\footnote{\url{http://www.quantumdiaries.org}} blog for this experiment.
+Figure \ref{runningtime} shows the cumulated time spent for each article 
+extraction procedure (this excludes common tasks such as downloading 
+pages and storing results) as a function of the number of weblog posts 
+processed. We used the Quantum Diaries\footnote{\url{http://www.quantumdiaries.org}} 
+blog for this experiment. Data presented in this graph was obtained
+by taking the arithmetic mean over 10 measurements. These results are
+believed to be significant given that standard deviations are of
+the order of 2 milliseconds.
 
-Data presented in this graph was obtained by taking the arithmetic mean over 10 measurements.
-These results are believed to be significant given that standard deviations are of the order of 2 milliseconds.
+\begin{figure*}[!hbt]
+\centering
+\label{runningtime}
+\input{main-gnuplottex-fig1.tex}
+\end{figure*}
 
-\input{runningtimeFigure.tex}
+As illustrated in \autoref{runningtime}, our approach spends the majority 
+of its total running time between the initialisation the processing 
+of the first weblog post. This initial increase of about 0.4 seconds 
+corresponds to cost of executing \autoref{linearAlgo} to compute 
+extraction rule for articles. As already mentioned, this consists 
+in computing the \emph{best extraction rule} of each pages references 
+by the web feed and picking the one functioning best on these pages. 
+Once we have this extraction rule, processing subsequent weblog posts only 
+requires parsing and applying the rule, which takes about 3 milliseconds 
+and are barely visible on the scale of \autoref{runningtime}. The other 
+evaluated solutions do not function this way: each weblog post is processed 
+as new and independent input, leading to approximately linear running 
+times.
 
-As illustrated in \autoref{runningtime}, our approach spends the majority of it's total running time between the initialisation the processing of the first blog post.
-This initial increase of about 0.4 seconds corresponds to cost of executing \autoref{linearAlgo} to compute extraction rule for articles.
-As already mentioned, this consists in computing the \emph{best extraction rule} of each pages references by the web feed and picking the one functioning best on these pages.
-Once we have this extraction rule, processing subsequent blog posts only requires parsing and applying the rule, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}.
-The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.
-
-The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post.
-Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach include the cost of entirely processing these 15 entries.
-That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variations of running times observed across programming languages~\cite{hundt2011}.
+The vertical dashed line at 15 processed weblog posts represents a suitable 
+point of comparison of processing time per post. Indeed, as the 
+web feed of our test weblog contains 15 posts, the extraction rule 
+computation performed by our approach include the cost of entirely 
+processing these 15 entries. That being said, comparing raw performance 
+of algorithms implemented in different programming languages is not very 
+informative given the high variations of running times observed across 
+programming languages~\cite{hundt2011}.

### 2014-12-16 6-conclusion-and-future-work.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

\section{Discussion and Conclusions}
\label{conclusionandfuturework}
In this article, we presented our extended work on a scalable approach to 
harvest modern weblogs. Our approach is based on a new algorithm to build 
extraction rules from web feeds. The key observations which led us to 
the inception and implementation of this algorithm are the facts that: 
(1) weblogs provide web feeds which include structured and standardized 
views of the latest blog posts, and (2) post of the same weblog share 
a similar HTML structure. Following, we presented a simple adaptation 
of this procedure that allows extracting different types of content, 
including authors, dates, comments and potentially any other element. 
The elaboration of this process enables the wider use of this method 
as it is feasible to devise variations of the proposed method to extract 
any kind of weblog content.

A critical part of this work was the presentation of the BlogForever 
crawler architecture and discussion of the software tools and the novel 
techniques we used. In order to support rapidly evolving web technologies 
such as JavaScript-generated content, the crawler uses a headless web 
browser to render pages before processing them. Another important aspect 
of the crawler architecture was the interoperability provisions. 
In our design, we introduced a new metadata schema for interoperability, 
encoding weblog crawling results in Archival Information Packages (AIPs) 
using established open standards. This feature enables the use of our 
system in many contexts and with multiple different back-ends, increasing 
its relevance and reusability. We also highlighted the design choices 
made to achieve both modularity and scalability. This is particularly 
relevant in the domain of web crawling given that intensive network 
operations can be a serious bottleneck. Crawlers greatly benefit from 
the use of multiple Internet access points which makes them natural 
candidates for distributed computing.

Our method had great success with content extraction accuracy and 
performance against state-of-the-art open source web article extraction 
systems as presented in the evaluation section. We have to note thought 
that our experiments on a considerably large weblogs dataset showed that 
there were some failing tests which stem from either the violation of one 
of our two key observations, or from an insufficient amount of text in 
posts. Therefore, it is suggested to potential users to ensure that these 
observations are valid on the target weblogs before proceeding with using 
the BlogForever crawler. Future work could attempt to alleviate this problem
using \emph{hybrid} extraction algorithms. Combining our approach with
others techniques such as word density or special reasoning could lead
to better performance given that these techniques are insensible to the
above issues.

### 2014-12-16 dataset/bloglist.py

@@ -1,6 +1,0 @@
-from os import listdir
-from itertools import imap
-
-print "\n".join(set(imap(
-  lambda _: _.split("{")[2],
-  listdir("contents/"))))

### 2014-12-16 running-times/crawler/bibcrawl/pipelines/timeextrator.py

@@ -1,92 +1,0 @@
-# """TimeExtrator"""
-
-# from bibcrawl.utils.ohpython import *
-# from bibcrawl.utils.parsing import parseHTML
-# from bibcrawl.utils.stringsimilarity import cleanTags
-# from boilerpipe.extract import Extractor
-# from goose import Goose
-# from readability.readability import Document
-# from scrapy import log
-# from time import time
-# import gc
-# import sys
-
-# class TimeExtrator(object):
-#   def process_item(self, item, spider):
-#     gcenabled = gc.isenabled()
-#     gc.disable()
-#     try:
-#       contentExtractor = lambda _: spider.contentExtractor(parseHTML(_))
-#       boilerpipeExtractor = lambda _: Extractor(html=_).getText()
-#       gooseExtractor = lambda _: Goose().extract(raw_html=_).cleaned_text
-#       readabilityExtractor = lambda _: cleanTags(Document(_).summary())
-
-#       # CE, BP, GO, RE
-#       log.msg("{} {} {} {}".format(
-#         timeMeThis(partial(contentExtractor,     item.rawHtml)),
-#         timeMeThis(partial(boilerpipeExtractor,  item.rawHtml)),
-#         timeMeThis(partial(gooseExtractor,       item.rawHtml)),
-#         timeMeThis(partial(readabilityExtractor, item.rawHtml)),
-#       ))
-#     finally:
-#       if gcenabled:
-#         gc.enable()
-
-# def timeMeThis(e):
-#   t0 = time()
-#   e()
-#   return time() - t0
-
-"""TimeExtrator"""
-
-from bibcrawl.utils.ohpython import *
-from bibcrawl.utils.parsing import parseHTML
-from bibcrawl.utils.stringsimilarity import cleanTags
-from boilerpipe.extract import Extractor
-from goose import Goose
-from readability.readability import Document
-from scrapy import log
-from time import time
-import gc
-import sys
-from numpy import median, mean, std
-
-class TimeExtrator(object):
-  def process_item(self, item, spider):
-    gcenabled = gc.isenabled()
-    gc.disable()
-    try:
-      contentExtractor = lambda _: spider.contentExtractor(parseHTML(_))
-      boilerpipeExtractor = lambda _: Extractor(html=_).getText()
-      gooseExtractor = lambda _: Goose().extract(raw_html=_).cleaned_text
[…]

### 2014-12-16 running-times/crawler/bibcrawl/run.py

@@ -1,71 +1,0 @@
-"""main"""
-
-from bibcrawl.spiders.newcrawl import NewCrawl
-from bibcrawl.spiders.updatecrawl import UpdateCrawl
-from bibcrawl.spiders.evalcrawl import EvalCrawl
-from scrapy import signals
-from scrapy.crawler import Crawler
-from scrapy.settings import Settings
-from twisted.internet import reactor
-from datetime import date, timedelta, datetime
-from scrapy import log
-import sys
-
-def stop_reactor():
-  """Stops the twistedreactor."""
-  reactor.stop()
-
-def startSpider(spider):
-  pass
-
-def main():
-  """Crawler entry point."""
-  settings = Settings({
-      "ITEM_PIPELINES": [
-          # 'bibcrawl.pipelines.renderjavascript.RenderJavascript',
-          'bibcrawl.pipelines.processhtml.ProcessHtml',
-          'bibcrawl.pipelines.timeextrator.TimeExtrator',
-          # 'bibcrawl.pipelines.downloadimages.DownloadImages',
-          # 'bibcrawl.pipelines.downloadfeeds.DownloadFeeds',
-          # 'bibcrawl.pipelines.extractcomments.ExtractComments',
-          # 'bibcrawl.pipelines.backendpropagate.BackendPropagate',
-          # 'bibcrawl.pipelines.outpropagate.OutPropagate',
-      ],
-      "HTTPCACHE_POLICY": "scrapy.contrib.httpcache.DummyPolicy",
-      "HTTPCACHE_STORAGE": "scrapy.contrib.httpcache.FilesystemCacheStorage",
-      "HTTPCACHE_ENABLED": True,
-      "FILES_STORE": "img",
-
-      # "CONCURRENT_ITEMS": 1,
-      "STATS_DUMP": False,
-      "LOG_LEVEL": "DEBUG",
-      # "CONCURRENT_REQUESTS": 1,
-      # "CONCURRENT_REQUESTS_PER_DOMAIN": 1,
-      # "CONCURRENT_REQUESTS_PER_IP": 1
-  })
-
-  # Need test cases for this one: letitcrash.com
-  # techcrunch.com
-  # keikolynn.com
-
-  # spider = NewCrawl(domain="korben.info", maxDownloads=500)
-  # spider = UpdateCrawl(
-  #   startAt="http://korben.info/feed",
-  #   domain="korben.info",
-  #   since=datetime.now() - timedelta(days=1))
-
[…]

### 2014-12-16 slides/mk.sh

@@ -1,7 +1,0 @@
-# watchmedo shell-command --wait --patterns="*.s*.md;*.template" --command "sh mk.sh"
-
-cat *.md | pandoc \
-  -t revealjs --template revealjs.template \
-  --slide-level 1 -s -o index.html
-   
-xdotool search --name Chrome key --window %@ F5

### 2014-12-16 success-rates/articles/boilerpipe/gen.py

@@ -1,20 +1,0 @@
-import sys
-from boilerpipe.extract import Extractor
-from os import listdir
-from urllib2 import urlopen, HTTPError
-import codecs
-
-def main():
-  contents = sys.argv[1]
-  for url in listdir(contents):
-    print url
-    with codecs.open(url, "w", encoding="utf-8") as out:
-      try:
-        html = urlopen(url.replace("{", "/")).read()
-        extracted = Extractor(html=html)
-        out.write(extracted.getText())
-      except HTTPError:
-        out.write("")
-
-if __name__ == "__main__":
-  main()

### 2014-12-16 success-rates/articles/goose/gen.py

@@ -1,19 +1,0 @@
-import sys
-from goose import Goose
-from os import listdir
-import codecs
-
-def main():
-  contents = sys.argv[1]
-  goose = Goose()
-  for url in listdir(contents):
-    print url
-    with codecs.open(url, "w", encoding="utf-8") as out:
-      try:
-        extracted = goose.extract(url=url.replace("{", "/"))
-        out.write(extracted.cleaned_text)
-      except IOError:
-        out.write("")
-
-if __name__ == "__main__":
-  main()

### 2014-12-16 success-rates/articles/readability/gen.py

@@ -1,21 +1,0 @@
-import sys
-from lxml.html.clean import Cleaner
-from os import listdir
-from re import sub as resub
-from readability.readability import Document
-from urllib2 import urlopen, HTTPError
-import codecs
-
-def main():
-  contents = sys.argv[1]
-  for url in listdir(contents):
-    print url
-    with codecs.open(url, "w", encoding="utf-8") as out:
-      try:
-        html = urlopen(url.replace("{", "/")).read()
-        out.write((Document(html).summary()))
-      except HTTPError:
-        out.write("")
-
-if __name__ == "__main__":
-  main()

### 2014-12-16 success-rates/crawler/bibcrawl/pipelines/outpropagate.py

@@ -1,29 +1,0 @@
-"""OutPropagate"""
-from bibcrawl.utils.fixbadunicode import fix_bad_unicode
-from bibcrawl.utils.stringsimilarity import cleanTags
-
-class OutPropagate(object):
-  """
-  @type  item: bibcrawl.model.postitem.PostItem
-  @param item: the item to process
-  @type  spider: scrapy.spider.BaseSpider
-  @param spider: the spider that emitted this item
-  @rtype: bibcrawl.model.postitem.PostItem
-  @return: the processed item
-  """
-  def process_item(self, item, spider):
-    import codecs
-
-    path = "titles/" + item.url.replace("/", "{")
-    spider.logInfo(path)
-    nicecontent = fix_bad_unicode(cleanTags(item.title))
-    with codecs.open(path , "w", encoding="utf-8") as out:
-      out.write(nicecontent)
-
-    path = "articles/" + item.url.replace("/", "{")
-    spider.logInfo(path)
-    nicecontent = fix_bad_unicode(cleanTags(item.content))
-    with codecs.open(path , "w", encoding="utf-8") as out:
-      out.write(nicecontent)
-
-    spider.logInfo("DONE:" + item.url)

### 2014-12-16 success-rates/crawler/bibcrawl/run.py

@@ -1,71 +1,0 @@
-"""main"""
-
-from bibcrawl.spiders.newcrawl import NewCrawl
-from bibcrawl.spiders.updatecrawl import UpdateCrawl
-from bibcrawl.spiders.evalcrawl import EvalCrawl
-from scrapy import signals
-from scrapy.crawler import Crawler
-from scrapy.settings import Settings
-from twisted.internet import reactor
-from datetime import date, timedelta, datetime
-from scrapy import log
-import sys
-
-def stop_reactor():
-  """Stops the twistedreactor."""
-  reactor.stop()
-
-def startSpider(spider):
-  pass
-
-def main():
-  """Crawler entry point."""
-  settings = Settings({
-      "ITEM_PIPELINES": [
-          # 'bibcrawl.pipelines.renderjavascript.RenderJavascript',
-          'bibcrawl.pipelines.processhtml.ProcessHtml',
-          # 'bibcrawl.pipelines.timeextrator.TimeExtrator',
-          # 'bibcrawl.pipelines.downloadimages.DownloadImages',
-          # 'bibcrawl.pipelines.downloadfeeds.DownloadFeeds',
-          # 'bibcrawl.pipelines.extractcomments.ExtractComments',
-          # 'bibcrawl.pipelines.backendpropagate.BackendPropagate',
-          'bibcrawl.pipelines.outpropagate.OutPropagate',
-      ],
-      "HTTPCACHE_POLICY": "scrapy.contrib.httpcache.DummyPolicy",
-      "HTTPCACHE_STORAGE": "scrapy.contrib.httpcache.FilesystemCacheStorage",
-      "HTTPCACHE_ENABLED": True,
-      "FILES_STORE": "img",
-
-      # "CONCURRENT_ITEMS": 1,
-      "STATS_DUMP": False,
-      "LOG_LEVEL": "DEBUG",
-      # "CONCURRENT_REQUESTS": 1,
-      # "CONCURRENT_REQUESTS_PER_DOMAIN": 1,
-      # "CONCURRENT_REQUESTS_PER_IP": 1
-  })
-
-  # Need test cases for this one: letitcrash.com
-  # techcrunch.com
-  # keikolynn.com
-
-  # spider = NewCrawl(domain="korben.info", maxDownloads=500)
-  # spider = UpdateCrawl(
-  #   startAt="http://korben.info/feed",
-  #   domain="korben.info",
-  #   since=datetime.now() - timedelta(days=1))
-
[…]

### 2014-12-16 success-rates/crawler/gen.sh

@@ -1,3 +1,0 @@
-#!/bin/sh
-
-for d in $(cat ../blogforever-crawler-publication/dataset/bloglist.txt); do sudo python -m bibcrawl/run $d; done

### 2014-12-16 success-rates/score.py

@@ -1,44 +1,0 @@
-import sys
-import codecs
-from Levenshtein import ratio
-from os import listdir
-
-def bigrams(string):
-  return set(map(lambda i: string[i : i + 2], xrange(len(string) - 1)))
-
-def dicesCoeffSimilarity(string1, string2):
-  bigrams1 = bigrams(string1)
-  bigrams2 = bigrams(string2)
-  intersection = bigrams1.intersection(bigrams2)
-  return (2.0 * len(intersection)) / (len(bigrams1) + len(bigrams2))
-
-def main():
-  first = sys.argv[1]
-  second = sys.argv[2]
-
-  threshold = 0.5
-  total = 0.0
-  count = 0.0
-
-  for page in listdir(first):
-    with codecs.open(first + "/" + page, "r", encoding="utf-8") as f:
-      firstpage = f.read()
-    try:
-      with codecs.open(second + "/" + page, "r", encoding="utf-8") as f:
-        secondpage = f.read()
-    except IOError:
-      secondpage = u""
-    if len(firstpage) > 20:
-      ratio = dicesCoeffSimilarity(firstpage + ".", secondpage + ".")
-      # ratio = ratio(firstpage + ".", secondpage + ".")
-      total = total + 1.0
-      if ratio > threshold:
-        count = count + 1.0
-      elif len(sys.argv) == 4:
-        print page.replace("{", "/")
-
-  print "{}: {}%".format(second, count/total * 100.0)
-
-
-if __name__ == "__main__":
-  main()

### 2014-12-16 success-rates/scoreArticles.sh

@@ -1,6 +1,0 @@
-#!/bin/sh
-
-python score.py ../dataset/articles/ ../../crawler/articles
-python score.py ../dataset/articles/ articles/goose/
-python score.py ../dataset/articles/ articles/readability/
-python score.py ../dataset/articles/ articles/boilerpipe/

### 2014-12-16 success-rates/scoreTitles.sh

@@ -1,5 +1,0 @@
-#!/bin/sh
-
-python score.py ../dataset/titles/ ../../crawler/titles
-python score.py ../dataset/titles/ titles/goose/
-python score.py ../dataset/titles/ titles/readability/

### 2014-12-16 success-rates/titles/goose/gen.py

@@ -1,20 +1,0 @@
-import sys
-from goose import Goose
-from os import listdir
-import codecs
-
-def main():
-  contents = sys.argv[1]
-  goose = Goose()
-  for url in listdir(contents):
-    print url
-    with codecs.open(url, "w", encoding="utf-8") as out:
-      try:
-        extracted = goose.extract(url=url.replace("{", "/"))
-        out.write(extracted.title)
-      except (IOError, TypeError):
-        out.write("")
-        print "Error"
-
-if __name__ == "__main__":
-  main()

### 2014-12-16 success-rates/titles/readability/gen.py

@@ -1,26 +1,0 @@
-import sys
-from lxml.html.clean import Cleaner
-from os import listdir
-from re import sub as resub
-from readability.readability import Document
-from urllib2 import urlopen, HTTPError
-import codecs
-
-def cleanTags(string):
-  htmlCleaned = Cleaner(allow_tags=[''], remove_unknown_tags=False, style=True
-      ).clean_html(string or u"dummy")
-  return resub(r"\s\s+" , " ", htmlCleaned)
-
-def main():
-  titles = sys.argv[1]
-  for url in listdir(titles):
-    print url
-    with codecs.open(url, "w", encoding="utf-8") as out:
-      try:
-        html = urlopen(url.replace("{", "/")).read()
-        out.write(cleanTags(Document(html).title()))
-      except HTTPError:
-        out.write("")
-
-if __name__ == "__main__":
-  main()

### 2014-12-16 3-algorithms.tex
Merge detailed answers to reviewers comments

@@
 of an appropriate extraction rule, as well as its applicability to all 
-posts of the blog.
+posts of the blog. Each page is uniquely identified by its URL. If a page is already processed, it is not processed again in the future.
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 \item\label{wordorderProp} Has low sensitivity to word ordering,
@@
 \item\label{linearProp} Runs in linear time.
-\end{itemize}
+\end{enumerate}
 
@@
 time to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} 
-is linear. To conclude the proof that \autoref{linearAlgo} runs in linear 
+is linear. To conclude the argument that \autoref{linearAlgo} runs in linear 
 time we show that all other computations of the inner loop can be done 
@@
 
-Regarding time complexity, computing the \emph{tree distance} of each 
-node of a graph to a single reference node can be done in linear time, 
-and multiplying the number of targets by a constant factor does not 
-affect the asymptotic computational complexity. Computing scores of 
-comment extraction rules requires a more expensive algorithm. However, 
-this is compensated by the fact that the proportion of candidates left, 
-after filtering out rules not returning enough results, is very low in 
-practice. Analogous reformulations to the one done with 
-\autoref{linearAlgo} can be straightforwardly applied on each 
-\code{ScoreFunction} to minimize the time spent in 
-\coderef{similarityAlgo}.
+Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node and multiplying the number of targets by a constant factor can be done in linear time.
+However, computing scores of comment extraction rules requires a more expensive algorithm.
+This is compensated by the fact that the proportion of candidate HTML nodes left, after filtering out rules not returning enough results, is very low in practice.
+Analogous reformulations to the one done with \autoref{linearAlgo} can be straightforwardly applied on each ScoreFunction to minimize the time spent in \coderef{similarityAlgo} calculations.
+
+It must be noted that there is no limitation due to comment nesting as long as comments follow the same format.

### 2014-12-16 5-evaluation.tex
Merge detailed answers to reviewers comments

@@
 programming languages~\cite{hundt2011}.
+
+When compared to the other parts of crawling, the content extraction is sufficiently quick not to be a bottleneck.
+Indeed, extracting the content of 100 pages takes about half a second, downloading 100 pages takes at least 1 second, and, if enabled, rendering and taking screenshots takes about half a second per page.
